### 2024-11-11 autovi_paper.qmd
tidy up

---
title: "Software for Automated Residual Plot Assessment: autovi and autovi.web"
subtitle: ANZJS Quarto Template
format:
  quarto-anzjs-pdf:
    keep-tex: true  
    shorttitle: "Software for Automated Residual Plot Assessment"
    double-space: true
    line-numbers: true
    # You can specify extra preamble in the file below.
    include-in-header:
      - template-header.tex
date: today
date-format: "YYYY" # used to define volumeyear
author:
  - name: Weihao Li
    email: weihao.li@monash.edu
    corresponding: true
    affiliations:
      - name: Monash University
        department: Department of Econometrics and Business Statistics
        address: Wellington Road, VIC 3800, Australia
    orcid: 0000-0003-4959-106X
  - name: Dianne Cook
    email: dicook@monash.edu 
    affiliations:
      - name: Monash University
        department: Department of Econometrics and Business Statistics
        address: Wellington Road, VIC 3800, Australia
    orcid: 0000-0002-3813-7155
  - name: Emi Tanaka
    email: emi.tanaka@anu.edu.au
    affiliations: 
      - name: The Australian National University
        department: Biological Data Science Institute
        address: 46 Sullivan's Creek Road, ACT 2600, Australia
    orcid: 0000-0002-1455-259X
  - name: Susan VanderPlas
    email: emi.tanaka@anu.edu.au
    affiliations:
      - name: University of Nebraska
        department: Department of Statistics
        address: Hardin Hall, 3310 Holdrege St Suite 340, Lincoln, NE 68583, United States
    orcid: 0000-0002-3803-0972
  - name: Klaus Ackermann
    email: Klaus.Ackermann@monash.edu 
    affiliations:
      - name: Monash University
        department: Department of Econometrics and Business Statistics
        address: Wellington Road, VIC 3800, Australia
    orcid: 0000-0001-7693-8538
# Note that the Journal requires that a paper must begin with a
# "Summary" not an "Abstract".  This is automatically taken care
# of by the anzsauth document style.  So even though the following
# says "abstract" the heading "Summary" will appear in
# the processed version.
abstract: |
  Regression software is widely available today, but tools for effective diagnostics are still lagging. Perhaps, one of the reasons is that it is hard. Conventional tests, that would make the task easy, are often too sensitive, which would result in adequate models being abandoned if the analyst strictly adhered to the test decision. The recommended advice is to have the analyst assess the strength of patterns in residual plots. This requires human effort and also suffers from the potential for inconsistent decisions from different analysts. Using a lineup protocol can help to alleviate inconsistency, but requires even more human effort. This is the type of task where a robot might be employed to do the disagreeable work that currently requires a human. Here we describe a new R package that includes a computer vision model for automated assessment of residual plots, and an accompanying Shiny app for ease of use. For a user-provided sample of residuals, it predicts a measure of visual signal strength (VSS) and provides a suite of supporting information to assist the analyst diagnose their model fit. 
# Below shows how acknowledgements should appear in the Journal.
# Note that if you are acknowledging financial support, grant
# numbers should *not* usually be specified.
acknowledgement: >
  The author acknowledges that this template is based on the latex template for Australian and New Zealand Journal of Statistics and intersperses some text from the original prototype document. \newline\vspace{1ex}\newline
  Opinions and attitudes expressed in this document,
  which are not explicitly designated as Journal policy, are those of
  the author and are _not_ necessarily endorsed by the Journal,
  its editorial board, its publisher Wiley or by the Australian
  Statistical Publishing Association Inc.
# Note that "keywords" should not include words and phrases
# that form part of the title of the paper.
# Also keywords (with the exception of proper names and
# certain abbreviations that conventionally appear all in
# capital letters) should *not* be capitalised.
keywords: [statistical software, statistical graphics, data visualization, visual inference, computer vision, machine learning, hypothesis testing, reression analysis]
bibliography: bibliography.bib  
#nocite: |
# @PussyRiot2014, @Nixon1984, @Turner2017, @Brillinger2007
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  echo = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "100%", 
  fig.align = "center")
```

# Introduction {#sec-autovi-introduction}

Regression analysis is a fundamental statistical technique widely used for modeling data from many fields. To diagnose the fit of a model it is recommended that the residuals are plotted. If the fit is good, any variation remaining should be noise, consistent with sampling from a distribution specified by the error model. Deviations that might be observed from a residual plot are non-normality, heteroscedasticity, and other associations with the fitted values. In @li2024plot, we demonstrated that visual methods for assessing residuals are advantageous over conventional tests due to their reduced sensitivity to minor departures. Building on this, @li2024automated introduced a computer vision model aimed at alleviating the human effort required for visual assessment of residual plots. The next step is to deliver the use of the computer vision model to potential users, so that it can be widely used to the benefit of the analytics community.

Software for regression analysis tools is widely available. The Comprehensive R Archive Network (CRAN) [@hornik2012comprehensive] hosts a vast array of packages, many of which provide tools to diagnose models using residual plots. These packages can be broadly categorized into three groups: general-purpose, enhanced visual diagnostics, and visual diagnostics with statistical testing.

General-purpose regression analysis tools are the most widely used group of packages. While not specifically designed for graphical diagnostics of residuals in linear regression, they include this functionality as part of a broader suite of statistical tools. For example, the `stats` package [@stats] offers standard diagnostic plots such as residuals vs. fitted values, quantile-quantile (Q-Q) plots, and residuals vs. leverage plots. Additional packages like `jtools` [@jtools], `olsrr` [@olsrr], `rockchalk` [@rockchalk], and `ggResidpanel` [@ggresidpanel] provide similar graphical diagnostics, often with alternative aesthetics or interactive features. All of these tools deliver the types of diagnostic plots outlined in the classical text by @cook1982residuals. However, as discussed in @li2024plot, relying solely on subjective assessments of these plots can lead to issues, such as over-interpreting random patterns as model violations.

The second group consists of enhanced visual diagnostics tools, which provide advanced aids for interpreting diagnostic plots. For instance, `ecostats` [@warton_global_2023] incorporates simulation envelopes into residual plots, while `DHARMa` [@dharma] compares empirical quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical counterparts. `DHARMa` is particularly focused on detecting model violations such as heteroscedasticity, incorrect functional forms, and issues specific to generalized linear and mixed-effect models, like over/under-dispersion. It also includes annotations from conventional tests, displayed as labels or text within the plot, to help avoid misinterpretation.

The third group, visual diagnostics with statistical testing, offers tools for formally testing patterns observed in diagnostic plots [@buja2009statistical]. A common method for visual testing of residual plots is the lineup protocol, where the true residual plot is embedded within a set of null plots generated by simulating residuals under the null hypothesis $H_0$ that the regression model is correctly specified. Observers are asked to identify the plot that appears most different from the others. If a significant proportion of observers correctly identify the true residual plot, it provides evidence against $H_0$, as the true residual plot should be indistinguishable from the null plots if all residuals are generated by the same process, according to @buja2009statistical. Packages in this group, such as `nullabor` [@nullabor], `HLMdiag` [@loy2014hlmdiag], and `regressinator` [@regressinator], enable users to compare observed residual plots with samples from null distributions, helping to quantify the significance of any detected patterns.

However, as discussed in @li2024automated, the lineup protocol has significant limitations in large-scale applications due dependence on human labor. Thus a computer vision model was developed with an associated statistical testing procedure to automate the assessment of residual plots. This model takes a residual plot and a vector of auxiliary variables (such as the number of observations) as inputs and outputs the predicted visual signal strength (VSS). This strength estimates the distance between the residual distribution of the fitted regression model and the reference distribution assumed under correct model specification.

To make the statistical testing procedure and trained computer vision model widely accessible, we developed the R package `autovi`, and a web interface, `autovi.web` to make it easy for users to automatically read their residual plots with the trained computer vision model.

The remainder of this paper is structured as follows: @sec-autovi provides a detailed documentation of the `autovi` package, including its usage and infrastructure. @sec-autovi-web focuses on the `autovi.web` interface, describing its design and usage, along with illustrative examples. Finally, @sec-autovi-conclusion presents the main conclusions of this work.

# R package: autovi {#sec-autovi}

The main purpose of `autovi` is to provide rejection decisions and $p$-values for testing whether a regression model is correctly specified. The package introduces a novel approach to automating statistical analysis, particularly in the interpretation of residual plots. The name `autovi` stands for automated visual inference. While initially designed for linear regression residual diagnostics, it has the potential to be extended to broader visual inference applications, as we discuss in section @sec-autovi-infrastructure.

## Implementation {#sec-autovi-implementation}

The `autovi` package is built on the `bandicoot` object-oriented programming (OOP) system [@bandicoot], marking a departure from R’s traditional S3 generic system. This OOP architecture enhances flexibility and modularity, allowing users to redefine key functions through method overriding. While similar functionality could be achieved using R’s S3 system with generic functions, the OOP framework offers a more structured and extensible foundation for the package.

The `autovi` infrastructure effectively integrates multiple programming languages and libraries into a comprehensive analytical tool. It relies on five core libraries from Python and R, each playing a critical role in the analysis pipeline. In Python, `pillow` [@clark2015pillow] handles image processing tasks such as reading and resizing PNG files of residual plots, then converting them into input tensors for further analysis. The `TensorFlow` [@abadi2016tensorflow] library, a key component of modern machine learning, is used to predict the VSS of these plots through a pre-trained convolutional neural network.

In the R environment, `autovi` utilizes several libraries. `ggplot2` [@ggplot2] generates the initial residual plots, saved as PNG files for visual input. The `cassowaryr` [@mason2022cassowaryr] library computes scagnostics (scatter plot diagnostics), providing numerical features that capture statistical properties of the plots. These scagnostics complement the visual analysis by offering quantitative metrics as secondary input to the computer vision model. The `reticulate` [@reticulate] package bridges R and Python, enabling seamless communication between the two languages and supporting the integrated infrastructure.

## Installation

The `autovi` package is available on CRAN. It is actively developed and maintained, with the latest updates accessible on GitHub at [https://github.com/TengMCing/autovi](https://github.com/TengMCing/autovi). The code discussed in this paper is based on `autovi` version 0.4.1.

The package includes internal functions to check the current Python environment used by the `reticulate` package. If the necessary Python packages are not installed in the Python interpreter, an error will be raised. If you want to select a specific Python environment, you can do so by calling the `reticulate::use_python()` function before using the `autovi` package.

## Usage {#sec-autovi-usage}

To get started quickly, only three function calls are needed to obtain a summary of the automated residual assessment:

```{r}
set.seed(10086)
```

```r
library(autovi) 
checker <- residual_checker(lm(dist ~ speed, data = cars))
checker$check() 
```

```{r}
library(autovi)
checker <- auto_vi(fitted_model = lm(dist ~ speed, data = cars))
```

```{r message=TRUE}
if (!file.exists("cached_data/autovi_check_demo.rds")) {
  checker$keras_model <- get_keras_model("vss_phn_32") 
  checker$check()
  saveRDS(checker$check_result, "cached_data/autovi_check_demo.rds")
} else {
  checker$check_result <- readRDS("cached_data/autovi_check_demo.rds")
}

checker
```

The three functions are explained as follows:

1. Load the `autovi` package using the `library()` function.
2. Create a checker object with a linear regression model.
3. Call the `check()` method of the checker, which, by default, predicts the VSS for the true residual plot, 100 null plots, and 100 bootstrapped plots, storing the predictions internally. A concise report of the check results is then printed.

The summary reports key findings such as the VSS of the true residual plot and the $p$-value of the automated visual test. The $p$-value is the ratio of null plots that have VSS greater than or equal to that of the true residual plot. We typically reject the null hypothesis when the $p$-value is smaller than or equal to a desired significance level, such as 5%. The report also provides sample quantiles of VSS for null and bootstrapped plots, helping to explain the severity and likelihood of model violations.

Although the $p$-value is sufficient for automated decision-making, users can visually inspect the original residual plot alongside a sample null plot. This visual comparison can clarify why $H_0$ is either rejected or not, and help identify potential remedies. The `plot_pair()` and `plot_lineup()` methods facilitate this comparison.

```{r fig-plot-pair, echo = TRUE, fig.height=3, fig.width=4, fig.cap="True plot alongside one null plot, for quick comparison."}
checker$plot_pair()
```

The `plot_pair()` method (@fig-plot-pair) displays the true residual plot on the left and a single null plot on the right. If a full lineup was shown, the true residual plot would be embedded in a page of null plots. Users should look for any distinct visual patterns in the true residual plot that are absent in the null plot. Running these functions multiple times can help any visual suspicions, as each execution generates new random null plots for comparison.

The package offers a straightforward visualization of the assessment result through the `summary_plot()` function.

```{r fig-summary-plot, echo = TRUE, fig.height=3, fig.width=6, fig.cap="Summary plot comparing the densities of VSS for bootstrapped residual samples (red) relative to VSS for null plots (blue)."}
checker$summary_plot()
```

In the result, shown in @fig-summary-plot, the blue area represents the density of VSS for null residual plots, while the red area shows the density for bootstrapped residual plots. The dashed line indicates the VSS of the true residual plot, and the solid line marks the critical value at a 95% significance level. The $p$-value and the likelihood ratio are displayed in the subtitle. The likelihood ratio represents the ratio of the likelihood of observing the VSS of the true residual plot from the bootstrapped distribution compared to the null distribution.

Interpreting the plot involves several key aspects. If the dashed line falls to the right of the solid line, it suggests rejecting the null hypothesis. The degree of overlap between the red and blue areas indicates similarity between the true residual plot and null plots; greater overlap suggests more similarity. Lastly, the portion of the red area to the right of the solid line represents the percentage of bootstrapped models considered to have model violations.

This visual summary provides an intuitive way to assess the model's fit and potential violations, allowing users to quickly grasp the results of the automated analysis.

## Modularized Infrastructure {#sec-autovi-infrastructure}

```{r out.width = "100%"}
#| label: fig-autovi-diag
#| fig-cap: "Diagram illustrating the infrastructure of the R package autovi. The modules in green are primary inputs provided by users. Modules in blue are overridable methods that can be modified to accommodate users' specific needs. The module in yellow is a pre-defined non-overridable method. The modules in red are primary outputs of the package."
magick::image_read_pdf("figures/autovi.pdf")
```

The initial motivation for developing `autovi` was to create a convenient interface for sharing the models described and trained in @li2024automated. However, recognizing that the classical normal linear regression model represents a restricted class of models, we sought to avoid limiting the potential for future extensions, whether by the original developers or other users. As a result, the package was designed to function seamlessly with linear regression models with minimal modification and few required arguments, while also accommodating other classes of models through partial infrastructure substitution. This modular and customizable design allows `autovi` to handle a wide range of residual diagnostics tasks.

The infrastructure of `autovi` consists of ten core modules: data extraction, bootstrapping and model refitting, fitted values and residuals extraction, auxiliary computation, null residual simulation, plotting, plot saving, image reading and resizing, VSS prediction, and $p$-value computation. Each module is designed with minimal dependency on the preceding modules, allowing users to customize parts of the infrastructure without affecting its overall integrity. An overview of this infrastructure is illustrated in @fig-autovi-diag.

The modules for VSS prediction and $p$-value computation are predefined and cannot be overridden, although users can interact with them directly through function arguments. Similarly, the image reading and resizing module is fixed but will adapt to different Keras models by checking their input shapes. The remaining seven modules are designed to be overridable, enabling users to tailor the infrastructure to their specific needs. These modules are discussed in detail in the following sections.

### Initialization

An `autovi` checker can be initialized by supplying two primary inputs, including a regression model object, such as an `lm` object representing the result of a linear regression model, and a trained computer vision model compatible with the `Keras` [@chollet2015keras] Application Programming Interface (API), to the `AUTO_VI` class constructor `auto_vi()`. The `residual_checker()` introduced in @sec-autovi-usage is a thin wrapper around `auto_vi()`, which will call `get_keras_model()` during initialization. `get_keras_model()` is a function to download a trained computer vision model (described in @li2024automated) from GitHub. “vss_phn_32” specifies a model that predicts VSS and is trained on residuals with polynomial, heteroskedasticity, and non-normality patterns (phn). More details about the hosted models will be provided in @sec-trained-model-hosting.

The input of the constructor will be stored as attributes of the checker and can be accessed by the user through the `$` operator.

```r
library(autovi)
checker <- auto_vi(fitted_model = lm(dist ~ speed, data = cars), 
                   keras_model = get_keras_model("vss_phn_32"))
```

Optionally, the user may specify the node index of the output layer of the trained computer vision model to be monitored by the checker via the `node_index` argument if there are multiple output nodes. This is particularly useful for multiclass classifiers when the user wants to use one of the nodes as a VSS indicator.

After initializing the object, you can print the checker to view its status.

```r
── <AUTO_VI object>
Status:
 - Fitted model: lm
 - Keras model: (None, 32, 32, 3) + (None, 5) -> (None, 1)
    - Output node index: 1
 - Result: UNKNOWN 
```

The status includes the list of regression model classes (as provided by the built-in `class()` function), the input and output shapes of the Keras model in the standard `Numpy` format [@harris2020array], the output node index being monitored, and the assessment result. If no check has been run yet, the assessment result will display as "UNKNOWN".

### Fitted Values and Residuals Extraction

To be able to predict VSS for a residual plot, both fitted values and residuals are needed to be extracted from the regression model object supplied by the user. In R, statistical models like `lm` (linear model) and `glm` (generalized linear model) typically support the use of generic functions such as `fitted()` and `resid()` to retrieve these values. The `get_fitted_and_resid()` method, called by the checker, relies on these generic functions by default. However, generic functions only work with classes that have appropriate method implementations. Some regression modeling packages may not fully adhere to the `stats` package guidelines for implementing these functions. In such cases, overriding the method becomes necessary.

By design, the `get_fitted_and_resid()` method accepts a regression model object as input and returns a `tibble` (a modern presentation of the `data.frame`) with two columns: `.fitted` and `.resid`, representing the fitted values and residuals, respectively. If no input is supplied, the method uses the regression model object stored in the checker. Although modules in the `autovi` infrastructure make minimal assumptions about other modules, they do require strictly defined input and output formats to ensure data validation and prevent fatal bugs. Therefore, any overridden method should follow to these conventions.

```{r echo=TRUE}
checker$get_fitted_and_resid()
```

### Data Extraction

For linear regression model in R, the model frame contains all the data required by a formula for evaluation. This is essential for bootstrapping and refitting the model when constructing a bootstrapped distribution of VSS. Typically, the model frame can be extracted from the regression model object using the `model.frame()` generic function, which is the default method used by `get_data()`. However, some regression models do not use a formula or are evaluated differently, potentially lacking a model frame. In such cases, users can either provide the data used to fit the regression model through the `data` argument when constructing the checker, or customize the method to better suit their needs. It's worth noting that this module is only necessary if bootstrapping is required, as the model frame is not used in other modules of the infrastructure.

The `get_data()` method accepts a regression model object as input and returns a `data.frame` representing the model frame of the fitted regression model. If no input is supplied, the regression model stored in the checker will be used.

```{r echo=TRUE}
checker$get_data() |> 
  head()
```

### Bootstrapping and Model Refitting

Bootstrapping a regression model typically involves sampling the observations with replacement and refitting the model with the bootstrapped data. The `boot_method()` method follows this bootstrapping scheme by default. It accepts a fitted regression model and a `data.frame` as inputs, and returns a `tibble` of bootstrapped residuals. If no inputs are provided, the method uses the regression model stored in the checker and the result of the `get_data()` method.

Note that instead of calling `get_data()` implicitly within the method, it is used as part of the default argument definition. This approach allows users to bypass the `get_data()` method entirely and directly supply a `data.frame` to initiate the bootstrap process. Many other methods in `autovi` adopt this principle when possible, where dependencies are explicitly listed in the formal arguments. This design choice enhances the reusability and isolation of modules, offers better control for testing, and simplifies the overall process.

```{r echo=TRUE}
checker$boot_method(data = checker$get_data())
```

### Auxiliary Computation

As described in @li2024automated, in some cases, a residual plot alone may not provide enough information to accurately determine VSS. For instance, when the points in the residual plot have significant overlap, the trend and shape of the residual pattern can be difficult to discern. Including auxiliary variables, such as the number of observations, as additional inputs to the computer vision model can be beneficial. To address this, `autovi` includes internal functions within the checker that automatically detect the number of inputs required by the provided Keras model. If multiple inputs are necessary, the checker invokes the `auxiliary()` method to compute these additional inputs.

The `auxiliary()` method takes a `data.frame` containing fitted values and residuals as input and returns a `data.frame` with five numeric columns. These columns represent four scagnostics — "Monotonic", "Sparse", "Striped", and "Splines" — calculated using the `cassowaryr` package, as well as the number of observations. This approach is consistent with the training process of the computer vision models described in @li2024automated. If no `data.frame` is provided, the method will default to retrieving fitted values and residuals by calling `get_fitted_and_resid()`.

Technically, any Keras-implemented computer vision model can be adapted to accept an image as the primary input and additional variables as secondary inputs by adding a data pre-processing layer before the actual input layer. If users wish to override `auxiliary()`, the output should be a `data.frame` with a single row and the number of columns such that its concatenation matches the number of parameters for the corresponding layer in the supplied Keras model.

```{r echo=TRUE}
checker$auxiliary()
```

### Null Residual Simulation {#sec-autovi-null-method}

A fundamental element of the automated residual assessment described in @li2024automated is comparing the VSS of null plots with that of the true residual plot. However, due to the variety of regression models, there is no universal method for simulating null residuals that are consistent with model assumptions. Fortunately, for classical normal linear regression models, null residuals can be effectively simulated using the residual rotation method, as outlined in @buja2009statistical. This process involves generating random draws from a standard normal distribution, regressing these draws on the original predictors, and then rescaling the resulting residuals by the ratio of the residual sum of squares to the that of the original linear regression model. Other regression models, such as `glm` (generalized linear model) and `gam` (generalized additive model), generally cannot use this method to efficiently simulate null residuals. Therefore, it is recommended that users override the `null_method()` to suit their specific model. The `null_method()` takes a fitted regression model as input, defaulting to the regression model stored in the checker, and returns a `tibble`.

```{r echo=TRUE}
checker$null_method()
```

### Plotting

Plotting is a crucial aspect of residual plot diagnostics because aesthetic elements like marker size, marker color, and auxiliary lines impact the presentation of information. There are computer vision models trained to handle images captured in various scenarios. For example, the VGG16 model [@simonyan2014very] can classify objects in images taken under different lighting conditions and is robust to image rotation. However, data plots are a special type of image as the plotting style can always be consistent if controlled properly. Therefore, we assume computer vision models built for reading residual plots will be trained with residual plots of a specific aesthetic style. In this case, it is best to predict plots using the same style for optimal performance. The plotting method `plot_resid()` handles this aspect.

`plot_resid()` accepts a `data.frame` containing fitted values and residuals, along with several customization options: a `ggplot` theme, an `alpha` value to control the transparency of data points, a `size` value to set the size of data points, and a `stroke` value to define the thickness of data point edges. Additionally, it includes four Boolean arguments to toggle the display of axes, legends, grid lines, and a horizontal red line. By default, it replicates the style we used to generate the training samples for the computer vision models described in @li2024automated. In brief, the residual plot omits axis text and ticks, titles, and background grid lines, featuring only a red line at $y = 0$. It retains only the necessary components of a residual plot. If the computer vision model is trained with a different but consistent aesthetic style, `plot_resid()` should be overridden.

The method returns a `ggplot` object (@fig-autovi-plot-resid), which can be saved as a PNG file in the following module. If no data is provided, the method will use `get_fitted_and_resid()` to retrieve the fitted values and residuals from the regression model stored in the checker.

```{r fig-autovi-plot-resid, echo=TRUE, fig.height=3, fig.width=4, fig.cap = "Residual plot of the regression model stored in the checker."}
checker$plot_resid()
```

To manually generate true residual plots, null plots, or bootstrapped residual plots, you can pass the corresponding `data.frame` produced by the `get_fitted_and_resid()`, `null_method()`, and `boot_method()` methods to the `plot_resid()` method, respectively.

### Plot Saving

Another key aspect of a standardized residual plot is its resolution. In @li2024automated, we used an image format of 420 pixels in height and 525 pixels in width. This resolution was chosen because the original set, consisting of 20 residual plots arranged in a four by five grid, was represented by an image of 2100 by 2100 pixels. The `save_plot()` method accepts a `ggplot` object as input and saves it as a PNG file to the location specified by the `path` argument. If no path is provided, the PNG file is saved to a temporary file.

```{r echo=TRUE}
checker$plot_resid() |> 
  checker$save_plot()
```

### Image Reading and Resizing

When training computer vision models, it is common to test various input sizes for the same architecture to identify the optimal setup. This involves preparing the original training image at a higher resolution than required and then resizing it to match the input size during training. The `autovi` package includes a class, `KERAS_WRAPPER`, to simplify this process. This Keras wrapper class features a method called `image_to_array()`, which reads an image as a `PIL` image using the `pillow` Python package, resizes it to the target input size required by the Keras model, and converts it to a `Numpy` array.

To construct a `KERAS_WRAPPER` object, you need to provide the Keras model as the main argument. However, users generally do not need to interact with this class directly, as the `autovi` checker automatically invokes its methods when performing VSS predictions. The `image_to_array()` method takes the path to the image file, the target height, and the target width as inputs and returns a `Numpy` array. If not specified, the target height and target width will be retrieved from the input layer of the Keras model by the `get_input_height()` and `get_input_width()` method of `KERAS_WRAPPER`.

The following code example demonstrate the way to manually generate the true residual plot, save it as PNG file, and load it back as `Numpy` array.

```r
wrapper <- keras_wrapper(keras_model = checker$keras_model)  
input_array <- checker$plot_resid() |> 
  checker$save_plot() |>
  wrapper$image_to_array()
input_array$shape
```

```{r}
# If the Keras model can not be loaded
if (!file.exists("cached_data/autovi_check_demo.rds")) {
  wrapper <- keras_wrapper(keras_model = checker$keras_model)  
  input_array <- checker$plot_resid() |> 
    checker$save_plot() |>
    wrapper$image_to_array()
  input_array$shape
} else {
  cat("(1, 32, 32, 3)")
}
```

### Visual Signal Strength (VSS) Prediction

VSS, as discussed in @li2024automated, estimates the distance between the input residual plot and a theoretically good  residual plot. It can be defined in various ways, much like different methods for measuring the distance between two points. This will not impact the `autovi` infrastructure as long as the provided Keras model can predict the intended measure.

There are several ways to obtain VSS from the checker, with the most direct being the `vss()` method. By default, this method predicts the VSS for the true residual plot. If a `ggplot` or a `data.frame`, such as null residuals generated by the `null_method()`, is explicitly provided, the method will use that input to predict VSS accordingly. Note that if a `ggplot` is provided, auxiliary inputs must be supplied manually via the `auxiliary` argument, as we assume that auxiliary variables can not be computed directly from a `ggplot`.

Another way to obtain VSS is by calling the `check()` method. This comprehensive method perform extensive diagnostics on the true residual plot and store the VSS in the `check_result` field of the checker. Additionally, for obtaining VSS for null residual plots and bootstrapped residual plots, there are two specialized methods, `null_vss()` and `boot_vss()`, designed for this purpose respectively.

Calling the `vss()` method without arguments will predict the VSS for the true residual plot and return the result as a single-element `tibble`.

```r
checker$vss()
```

```{r}
if (!file.exists("cached_data/autovi_check_demo_2.rds")) {
  checker$keras_model <- get_keras_model("vss_phn_32") 
  saveRDS(checker$vss(), "cached_data/autovi_check_demo_2.rds")
  checker$vss()
} else {
  readRDS("cached_data/autovi_check_demo_2.rds")
}
```

Providing a `data.frame` of null residuals or a null residual plot yields the same VSS.

```r
null_resid <- checker$null_method()
checker$vss(null_resid)
```

```{r}
null_resid <- checker$null_method()

if (!file.exists("cached_data/autovi_check_demo_3.rds")) {
  checker$keras_model <- get_keras_model("vss_phn_32") 
  saveRDS(checker$vss(null_resid), "cached_data/autovi_check_demo_3.rds")
  checker$vss(null_resid)
} else {
  readRDS("cached_data/autovi_check_demo_3.rds")
}
```

```r
null_resid |>
  checker$plot_resid() |>
  checker$vss()
```

```{r}
readRDS("cached_data/autovi_check_demo_3.rds")
```

The `null_vss()` helper method primarily takes the number of null plots as input. If the user wants to use a ad hoc null simulation scheme, it can be provided via the `null_method` argument. Intermediate results, including null residuals and null plots, can be returned by enabling `keep_null_data` and `keep_null_plot`. The VSS, along with null residuals and null plots, will be stored in a `tibble` with three columns. The following code example demonstrates how to predict the VSS for five null residual plots while keeping the intermediate results.

```r
checker$null_vss(5L, 
                 keep_null_data = TRUE, 
                 keep_null_plot = TRUE)
```

```{r}
if (!file.exists("cached_data/autovi_check_demo_4.rds")) {
  checker$keras_model <- get_keras_model("vss_phn_32") 
  result <- checker$null_vss(5L, 
                             keep_null_data = TRUE, 
                             keep_null_plot = TRUE)
  saveRDS(result, "cached_data/autovi_check_demo_4.rds")
  result
} else {
  readRDS("cached_data/autovi_check_demo_4.rds")
}
```

The `boot_vss()` helper method is similar to `null_vss()`, with some differences in argument names. The following code example demonstrates how to predict the VSS for five bootstrapped residual plots while keeping the intermediate results.

```r
checker$boot_vss(5L,
                 keep_boot_data = TRUE,
                 keep_boot_plot = TRUE)
```

```{r}
if (!file.exists("cached_data/autovi_check_demo_5.rds")) {
  checker$keras_model <- get_keras_model("vss_phn_32") 
  result <- checker$boot_vss(5L, 
                             keep_boot_data = TRUE, 
                             keep_boot_plot = TRUE)
  saveRDS(result, "cached_data/autovi_check_demo_5.rds")
  result
} else {
  readRDS("cached_data/autovi_check_demo_5.rds")
}
```

### $p$-value Computation

Once we have obtained the VSS from both the true residual plot and the null plots, we can compute the $p$-value. This $p$-value represents the ratio of plots with VSS greater than or equal to that of the true residual plot. We can perform this calculation using the `check()` method. The main inputs for this method are the number of null plots and the number of bootstrapped plots to generate. If you need to access intermediate residuals and plots, you can enable the `keep_data` and `keep_plot` options. The method stores the final result in the `check_result` field of the object. To obtain the p-value using the `check()` method, you can use the following code.

```r
checker$check(boot_draws = 100L, null_draws = 100L)
checker$check_result$p_value
```

```{r}
if (!file.exists("cached_data/autovi_check_demo_6.rds")) {
  checker$keras_model <- get_keras_model("vss_phn_32") 
  checker$check(boot_draws = 100L, null_draws = 100L)
  saveRDS(checker$check_result, "cached_data/autovi_check_demo_6.rds")
} else {
  checker$check_result <- readRDS("cached_data/autovi_check_demo_6.rds")
}

checker$check_result$p_value
```

## Summary Plots

After executing the `check()` method, `autovi` offers two visualization options for the assessment result through the `summary_plot()` method, including the density plot and the rank plot. We have already discussed and interpreted the density plot in @sec-autovi-usage. Here, we would like to highlight the flexibility in choosing which elements to display in the density plot as shown in @fig-autovi-summary-plot-option. For instance, you can omit the bootstrapped distribution by setting `boot_dist` to `NULL`. Similarly, you can hide the null distribution (`null_dist`), the $p$-value (`p_value`), or the likelihood ratio (`likelihood_ratio`) as needed. The following example demonstrates how to create a summary plot without the results from bootstrapped plots.

```{r fig-autovi-summary-plot-option, echo=TRUE, fig.cap = "Density plot of the VSS for null plots."}
checker$summary_plot(boot_dist = NULL,
                     likelihood_ratio = NULL)
```

This customization allows you to focus on specific aspects of the assessment, tailoring the visualization to your analytical needs.

The rank plot (@fig-autovi-rank-plot), creating by setting `type` to "rank", is a bar plot where the $x$-axis represents the rank and the $y$-axis shows the VSS. The bar that is coloured in red corresponding to the VSS of the true residual plot. By examining the rank plot, you can intuitively understand how the observed VSS compares to the null VSSs and identify any outliers in the null distribution.

```{r fig-autovi-rank-plot, echo=TRUE, fig.cap = "Rank plot of the VSS for null plots."}
checker$summary_plot(type = "rank")
```

## Feature Extraction

In addition to predicting VSS and computing $p$-values, `autovi` offers methods to extract features from any layer of the Keras model. To see which layers are available in the current Keras model, you can use the `list_layer_name()` method from the `KERAS_WRAPPER` class.

The following code example lists the layer names of the currently used Keras model:

```r
wrapper <- keras_wrapper(checker$keras_model)
wrapper$list_layer_name()
```

```{r}
if (!file.exists("cached_data/autovi_check_demo_8.rds")) {
  wrapper <- keras_wrapper(get_keras_model("vss_phn_32"))
  result <- wrapper$list_layer_name()
  saveRDS(result, "cached_data/autovi_check_demo_8.rds")
} else {
  readRDS("cached_data/autovi_check_demo_8.rds")
}
```

Among these layers, the "global_max_pooling2d" layer is a 2D global max pooling layer that outputs the results from the last convolutional blocks. As @simonyan2014very noted, all preceding convolutional blocks can be viewed as a large feature extractor. Consequently, the output from this layer provides features that can be utilized for various purposes, such as performing transfer learning.

To obtain the features, provide the layer name using the `extract_feature_from_layer` argument in the `predict()` method. This will return a `tibble` with the VSS and all features extracted from that layer. Each row corresponds to one plot. The features will be flattened into 2D and named with the prefix "f_" followed by a number from one to the total number of features.

```r
checker$plot_resid() |>
  checker$save_plot() |>
  wrapper$image_to_array() |>
  wrapper$predict(auxiliary = checker$auxiliary(),
                  extract_feature_from_layer = "global_max_pooling2d")
```

```{r}
if (!file.exists("cached_data/autovi_check_demo_7.rds")) {
  checker$keras_model <- get_keras_model("vss_phn_32") 
  result <- checker$plot_resid() |>
    checker$save_plot() |>
    wrapper$image_to_array() |>
    wrapper$predict(auxiliary = checker$auxiliary(),
                    extract_feature_from_layer = "global_max_pooling2d")
  saveRDS(result, "cached_data/autovi_check_demo_7.rds")
} else {
  readRDS("cached_data/autovi_check_demo_7.rds")
}
```

Alternatively, the `AUTO_VI` class provides a way to extract features using the `vss()` method. This method is essentially a high-level wrapper around the `predict()` method of `KERAS_WRAPPER`, but it offers a more straightforward interface and better default arguments.

The results from the previous code example can be replicated with a single line of code as shown below.

```r
checker$vss(extract_feature_from_layer = "global_max_pooling2d")
```

```{r}
readRDS("cached_data/autovi_check_demo_7.rds")
```

The argument `extract_feature_from_layer` is also available in other functions that build on the `vss()` method, including `null_vss()`, `boot_vss()`, and `check()`.

## Trained Model Hosting {#sec-trained-model-hosting}

The trained computer vision models described in @li2024automated are hosted on a GitHub repository at [https://github.com/TengMCing/autovi_data](https://github.com/TengMCing/autovi_data). Currently, there are six models available. You can view them by calling `list_keras_model()`, which will return a `tibble` showing the input shape and a description of each model.

```{r echo = TRUE}
list_keras_model() |>
  str()
```

The `get_keras_model()` function can be used to download a model to a temporary directory and load it into memory using `TensorFlow`. It requires only the model name, which is the value in the first column of the `tibble` returned by `list_keras_model()`.

# Web interface: autovi.web {#sec-autovi-web}

The `autovi.web` package extends the functionality of `autovi` by offering a user-friendly web interface for automated residual plot assessment. This eliminates the common challenges associated with software installation, so users can avoid managing Python environments or handling version requirements for R libraries. The platform is cross-platform and accessible on various devices and operating systems, making it suitable even for users without R programming experience. Additionally, updates are managed centrally, ensuring that users always have access to the latest features.

The `autovi.web` interface is available at [autoviweb.netlify.app](autoviweb.netlify.app). This section discusses the implementation based on `autovi.web` version 0.1.0.

## Implementation

The package `autovi.web` is built using the `shiny` [@shiny] and `shinydashboard` [@shinydashboard] R packages. Hosted on the [shinyapps.io](https://www.shinyapps.io) domain, the application is accessible through any modern web browser. The R packages `htmltools` [@htmltools] and `shinycssloaders` [@shinycssloaders] are used to render markdown documentation in shiny application, and for loading animations for shiny widgets, respectively.

Determining the best way to implement the interface was difficult. In our initial planning for `autovi.web`, we considered implementing the entire web application using the `webr` framework [@webr], which would have allowed the entire application to run directly in the user's browser. However, this approach was not feasible at the time of writing this paper. The reason is that one of the R packages `autovi` depends on the R package `splancs` [@splancs], which uses compiled Fortran code. A working Emscripten [@zakai2011emscripten] version of this package, which would be required for `webr`, was not available.

We also explored the possibility of implementing the web interface using frameworks built on other languages, such as Python. However, server hosting domains that natively support Python servers typically do not have the latest version of R installed. Additionally, calling R from Python is typically done using the `rpy2` Python library [@rpy2], but this approach can be awkward when dealing with language syntax related to non-standard evaluation. Another option we considered was renting a server where we could have full control, such as those provided by cloud platforms like Google Cloud Platform (GCP) or Amazon Web Services (AWS). However, correctly setting up the server and ensuring a secure deployment requires significant expertise. Ultimately, the most practical solution was to use the `shiny` and `shinydashboard` frameworks, which are well-established in the R community and offer a solid foundation for web application development.

The server-side configuration of `autovi.web` is carefully designed to support its functionality. Most required Python libraries, including `pillow` and `NumPy`, are pre-installed on the server. These libraries are integrated into the Shiny application using the `reticulate` package, which provides an interface between R and Python.

Due to the resource allocation policy of shinyapps.io, the server enters a sleep mode during periods of inactivity, resulting in the clearing of the local Python virtual environment. Consequently, when the application "wakes up" for a new user session, these libraries need to be reinstalled. While this ensures a clean environment for each session, it may lead to slightly longer loading times for the first user after a period of inactivity.

In contrast to `autovi`, `autovi.web` does not use the native Python version of `TensorFlow`. Instead, it leverages `TensorFlow.js`, a JavaScript library that allows the execution of machine learning models directly in the browser. This choice enables native browser execution, enhancing compatibility across different user environments, and shifts the computational load from the server to the client-side. `TensorFlow.js` also offers better scalability and performance, especially when dealing with resource-intensive computer vision models on shinyapps.io.

While `autovi` requires downloading the pre-trained computer vision models from GitHub, these models in ".keras" file format are incompatible with `TensorFlow.js`. Therefore, we extract and store the model weights in JSON files and include them as extra resources in the Shiny application. When the application initializes, `TensorFlow.js` rebuilds the computer vision model using these pre-stored weights.

To allow communication between `TensorFlow.js` and other components of the Shiny application, the `shinyjs` R package is used. This package allows calling custom JavaScript code within the Shiny framework. The specialized JavaScript code for initializing `TensorFlow.js` and calling `TensorFlow.js` for VSS prediction is deployed alongside the Shiny application as additional resources.

## Design {#sec-autovi-web-design}

```{r fig-autovi-web, out.width = "100%", fig.cap = "Overview of the `autovi.web` graphical user interface (GUI). This default view may change based on user interactions. Region 1 is the sidebar menu, containing the residual assessment tab and the information tab. Region 2 is the data upload panel, where users can provide a CSV file and specify the type of data it contains. Region 3 includes dropdown menus for selecting the columns to be analyzed, a slider to control the number of bootstrapping samples, and a numeric input box for setting the simulation seed. Region 4 displays the initialization status and offers a button to start the analysis. Region 5 is empty in the default view but will be populated with results once the analysis is started. "}
knitr::include_graphics("figures/autovi_web.png")
```

While the R package `autovi` aims to provide tools that can be extended to broader visual inference applications, `autovi.web` is only focus on providing  a straightforward and clean user interface. An overview of the graphical user interface of `autovi.web` is provided in @fig-autovi-web. This is the default view of the web application, and there are five regions that user can mainly interact with. Region 1 of @fig-autovi-web is a sidebar menu which can switch between the analysis page and the information page. The analysis page is the focus of this section.

Region 2 of @fig-autovi-web is a panel for data uploading and CSV type selection. Clicking the "upload CSV" button opens a window where the user can select a file from their local system. The data status displayed above the button provides information about the number of rows and columns in the current dataset. Additionally, there are two example datasets available beneath the "upload CSV" button: one is a lineup example using a CSV file with three columns, and the other is a single plot example using a CSV file with two columns. More details about these example datasets are be discussed in @sec-autovi-web-workflow.

While the `autovi` package typically expects a fitted regression model object provided by the user, this approach is impractical for a web interface. Saving the R model object to the filesystem involves extra steps and requires users to have specific knowledge, which does not align with the goal of the web application. Moreover, the regression model object may contain sensitive, non-shareable data, making it unsuitable for uploading. Additionally, model objects are often unnecessarily large, containing extra information not needed for residual diagnostics. In contrast, a CSV file is easier to generate using various software programs, not just R. CSV files are widely accepted and can be easily viewed and modified using common desktop applications like Excel. They are generally less sensitive than raw data, as they exclude most information about the predictors.

The web application is designed to assess either a single residual plot or a lineup of residual plots. Therefore, it accepts only two types of CSV files: one with at least two columns representing the fitted values and residuals of a single residual plot, and another with at least three columns, where the additional column serves as the label or identifier for a lineup of multiple residual plots. For a single residual plot, 19 null plots are generated by simulating normal random draws from a distribution with the same variance as the original residual plot, and comparisons are made with the original residual plot. For a lineup, comparisons are made among the plots within the lineup. After uploading the CSV file, the user must select the correct format to ensure the web interface interprets the data correctly.

```{r fig-autovi-web-type, out.width = "100%", fig.cap = "The panels for selecting target columns and simulation settings are updated when a different CSV type is selected in the left panel. Compared to @fig-autovi-web, where the CSV type is a single residual plot, choosing a CSV type that includes a lineup of multiple residual plots adds a dropdown menu for specifying a column for the residual plot identifier. Additionally, an optional dropdown menu for specifying the true residual plot identifier will appear under the simulation settings."}
knitr::include_graphics("figures/autovi_web_type.png")
```

Region 3 of @fig-autovi-web is a panel for column selection and simulation settings. As shown in @fig-autovi-web, if the CSV type is set to a single residual plot, there will be two dropdown menus for specifying the columns for fitted values and residuals, respectively. The default variable names for these columns are `.fitted` and `.resid`. After uploading the CSV file, the content of these dropdown menus will be updated to reflect the existing columns in the dataset. As displayed in @fig-autovi-web-type, for the CSV type that is a lineup of multiple residual plots, an additional dropdown menu will appear for specifying the column of residual plot labels. The default variable name for this column is `.sample`. If this variable name does not exist in the dataset, the dropdown menu will remain empty, allowing the user to specify the correct column. The number of levels for each option in this dropdown menu will be displayed to help avoid the selection of a variable with too many levels, which could significantly slow down the application due to extensive computation.

Under the simulation settings, there is a slider for specifying the number of bootstrapped samples needed for the assessment. A higher value on this slider will result in a more accurate bootstrap distribution estimation, though it will require more computation time. The simulation seed can be set in a numeric input box below the slider to control the reproducibility of the assessment. By default, a random seed is set each time the web page is refreshed. When the CSV type is a lineup of multiple residual plots, an optional dropdown menu will appear next to the simulation seed input box, allowing the user to specify an identifier for the true residual plot. If no label is provided for the true residual plot, the assessment will only estimate the VSS for each residual plot in the lineup, without providing a $p$-value, as it cannot be computed. Consequently, some result panels may be missing due to insufficient information. This option is useful when the lineup consists solely of null plots or if the user simply wants to obtain the VSS for multiple residual plots.

Region 4 of @fig-autovi-web is the panel for triggering the assessment. It contains a large play button to start the assessment. Above the play button, a text message displays the status of `TensorFlow.js`, allowing users to monitor whether the JavaScript library and Keras model have been loaded correctly. The play button will remain disabled until both the data status in Region 1 and the `TensorFlow.js` status in Region 4 indicate that everything is ready, with both showing a green status.

Once the play button is clicked, region 5 of @fig-autovi-web will be populated with panels displaying the assessment results. Generally, there will be four result panels, as shown in @fig-autovi-web-result and @fig-autovi-web-result2.

```{r fig-autovi-web-result, out.width = "100%", fig.cap = "The first two panels of results from the automated residual assessment are shown. The application provides four results panels in total, and these screenshots display the first two. In region 1, there is an interactive table detailing the VSS, with a summary of the analysis provided in the paragraph below. Region 2 displays a lineup of residual plots."}
knitr::include_graphics("figures/autovi_web_result.png")
```

```{r fig-autovi-web-result2, out.width = "100%", fig.cap = "The last two panels of results from the automated residual assessment are shown. The application provides four results panels in total, and these screenshots display the final two. Region 1 presents a density plot comparing the bootstrapped VSS with the null VSS. Region 2 includes an attention map of the true residual plot."}
knitr::include_graphics("figures/autovi_web_result2.png")
```

```{r fig-autovi-web-gradient-hide, out.width = "50%", fig.cap = "The attention map is hidden if the assessment indicates a $p$-value greater than 0.05. A button is available to toggle the display of the attention map."}
knitr::include_graphics("figures/autovi_web_gradient_hide.png")
```

Region 6 of @fig-autovi-web-result contains an interactive table created with the R package `DT` [@dt], which provides the VSS. This table includes four columns: `.sample`, `vss`, `rank`, and `null`. The `.sample` column shows the residual plot labels. For a CSV type that is a lineup, these labels are taken from an identifier column in the dataset specified by the user. In the case of the CSV type is a single residual plot, labels are automatically generated from 1 to 20, with the true residual plot receiving a randomly assigned label. The `vss` column displays the VSS for each residual plot, rounded to three decimal places. The `rank` column indicates the ranking of each residual plot based on VSS. The `null` column reveals whether the plot is a null plot. For the CSV type that is a single residual plot, only the true residual plot will have "false" in this column, while all other plots will be marked "true." For the CSV type that is a lineup, if the true residual plot identifier has not been provided, this column will show "NA" to represent missing values. If the identifier is provided by user, the column behaves as if the CSV type is a single residual plot.

The `DT` table provides several interactive features. Users can download the table in four formats, including text, CSV, Excel, and PDF, using the buttons located above the table. Additionally, the table is searchable via the text input field also positioned above it. Below the table, a text message displays the $p$-value of the assessment for the true residual plot and summarizes the number of null plots with VSS greater than that of the true residual plot. This helps the user determine whether the true residual plot shows visual patterns that suggest model violations.

Region 7 of @fig-autovi-web-result provides a lineup of plots corresponding to each `.sample` value from the table in Region 6. Due to space limitations, a maximum of 20 residual plots will be displayed, ensuring that the true residual plot, if known, will be included in the lineup. The plots are generated using `ggplot2`, the same as in `autovi`. Users can perform a visual test with this lineup to check if the true residual plot is distinguishable from the other plots, helping to determine the significance of model violations.

Region 8 of @fig-autovi-web-result2 displays the density plot for bootstrapped VSS and null VSS. The densities are shown in distinct colors that are friendly for colorblind users. A solid vertical line marks the VSS of the true residual plot, while rug lines at the bottom of the plot provide a clearer view of individual cases. Below the plot, a text message indicates the number and percentage of bootstrapped residual plots that would be rejected by the visual test when compared to the null plots. Note that the bootstrapped residual plots in this application are generated differently from `autovi`. Since we do not have the R model object, we can not refit the regression model with bootstrapped data. Instead, we bootstrap the residuals of the true residual plot directly to obtain bootstrapped residual plots. As as result, this panel will disappear when the true residual plot is unknown.

Region 9 of @fig-autovi-web-result2 displays an attention map for the true residual plot, generated by computing the gradient of the Keras model's output with respect to the greyscale input of the plot. The attention map helps to understand how the Keras model predicts VSS and which areas it is focusing on. We use a greyscale input because it is easier to generate a clear attention map in this format, and it usually conveys all the essential information, as most of the important details of the plot are drawn in black. If the $p$-value of the true residual plot is greater than 0.05, checking the attention map is not necessary. However, to provide users with the option to review it if they wish, a button will be available, as shown in @fig-autovi-web-gradient-hide. This button allows users to toggle the display of the attention map.

## Workflow {#sec-autovi-web-workflow}

The workflow of `autovi.web` is designed to be straightforward, with numbered steps displayed in each panel shown in @fig-autovi-web. There are two example datasets provided by the web application, as mentioned in @sec-autovi-web-design. The single residual plot example uses the `dino` dataset from the R package `datasauRus` [@datasaurus]. The lineup example uses residuals from a simulated regression model that has a non-linearity issue. We will walk through the lineup example to further demonstrate the workflow of the web application.

As shown in @fig-autovi-web-workflow-example1, to use the lineup example data, click the "Use Lineup Example" button. The data status will then update to show the number of rows and columns in the dataset, and the CSV type will automatically be selected to the correct option. Since the example dataset follows the variable naming conventions assumed by the web application, the columns for fitted values, residuals, and labels of residual plots are set automatically (@fig-autovi-web-workflow-example2). If the user is working with a custom dataset, these options must be set accordingly. Regardless of the dataset, the user must manually select the label for the true residual plot, as the web application allows assessments without this label. The next step is to click the play button to start the assessment.

Results are provided in multiple panels as displayed in @fig-autovi-web-workflow-example3, @fig-autovi-web-workflow-example4, @fig-autovi-web-workflow-example5 and @fig-autovi-web-workflow-example6. In @fig-autovi-web-workflow-example3, the first row of the table is the most crucial to check, as it provides the VSS and the rank of the true residual plot among the other plots. The summary text beneath the table provides the $p$-value, which can be used for quick decision-making. In @fig-autovi-web-workflow-example4, the lineup is for manual inspection, and the user should see if the true residual plot is visually distinguishable from the other plots, to confirm if the model violation is serious. The density plot in @fig-autovi-web-workflow-example5 offers a more robust result, allowing the user to compare the distribution of bootstrapped VSS with the distribution of null VSS. Finally, the grayscale attention map shown in @fig-autovi-web-workflow-example6 can be used to check if the target visual features, like the non-linearity present in the lineup example, are captured by the computer vision model, ensuring the quality of the assessment.

```{r fig-autovi-web-workflow-example1, out.width = "80%", fig.cap = 'To begin the workflow for `autovi` using the lineup example dataset, the user clicks the "Use Lineup Example" button to load the example dataset, during which the data status and CSV type will be automatically updated.'}
magick::image_read_pdf("figures/autovi_web_workflow_1.pdf")
```

```{r fig-autovi-web-workflow-example2, out.width = "80%", fig.cap = 'After clicking the button in @fig-autovi-web-workflow-example1, the target columns are selected automatically, though the user must manually select the label for the true residual plot, as the web application permits assessment without this label.'}
magick::image_read_pdf("figures/autovi_web_workflow_2.pdf")
```

```{r fig-autovi-web-workflow-example3, out.width = "55%", fig.cap = 'After finishing the required steps in @fig-autovi-web-workflow-example1 and @fig-autovi-web-workflow-example2, the user initiates the assessment of the lineup example data by clicking the run button.'}
magick::image_read_pdf("figures/autovi_web_workflow_3.pdf")
```

```{r fig-autovi-web-workflow-example4, out.width = "100%", fig.cap = 'The VSS of the true residual plot is displayed in the first row of the table, with a summary text beneath the table providing the $p$-value to aid in decision-making.'}
magick::image_read_pdf("figures/autovi_web_workflow_4.pdf")
```

```{r fig-autovi-web-workflow-example5, out.width = "100%", fig.cap = 'A lineup of residual plots allows for manual inspection.'}
magick::image_read_pdf("figures/autovi_web_workflow_5.pdf")
```

```{r fig-autovi-web-workflow-example6, out.width = "100%", fig.cap = 'The density plot helps verify if the bootstrapped distribution differs from the null distribution.'}
magick::image_read_pdf("figures/autovi_web_workflow_6.pdf")
```

```{r fig-autovi-web-workflow-example7, out.width = "100%", fig.cap = 'The attention map offers insights into whether the computer vision model has captured the intended visual features of the true residual plot.'}
magick::image_read_pdf("figures/autovi_web_workflow_7.pdf")
```

# Conclusions {#sec-autovi-conclusion}

This paper presents new regression diagnostics software, the R package `autovi` and its accompanying web interface package, `autovi.web`. It addresses a critical gap in the current landscape of statistical software. While regression tools are widely available, effective and efficient diagnostic methods have lagged behind, particularly in the field of residual plot interpretation.

The `autovi` R package, introduced in this paper, automates the assessment of residual plots by incorporating a computer vision model, eliminating the need for time-consuming and potentially inconsistent human interpretation. This automation improves the efficiency of the diagnostic process and promotes consistency in model evaluation across different users and studies.

The development of the accompanying Shiny app, `autovi.web`, expands access to these advanced diagnostic tools, by providing a user-friendly interface. It makes automated residual plot assessment accessible to a broader audience, including those who may not have extensive programming experience. This web-based solution effectively addresses the potential barriers to adoption, such as complex dependencies and installation requirements, that are often associated with advanced statistical software.

The combination of `autovi` and `autovi.web` offers a comprehensive solution to the challenges of residual plot interpretation in regression analysis. These tools have the potential to significantly improve the quality and consistency of model diagnostics across various fields, from academic research to industry applications. By automating a critical aspect of model evaluation, they allow researchers and analysts to focus more on interpreting results and refining models, rather than grappling with the intricacies of plot assessment.

The framework established by `autovi` and `autovi.web` opens up exciting possibilities for further research and development. Future work could explore the extension of these automated assessment techniques to other types of diagnostic plots and statistical models, potentially revolutionizing how we approach statistical inference using visual displays more broadly.

# Availability

The web interface is housed at [autoviweb.netlify.app](autoviweb.netlify.app).

The the current version of `autovi` can be installed from CRAN, and source code for both packages are available at [https://github.com/TengMCing/](https://github.com/TengMCing/).

### 2024-11-11 autovi_paper.tex
tidy up

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
doublespace,
  times]{anzsauth}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

% The following \newcommands are intended for use in the *current*
% document ("protoType"). It is unlikely that authors of papers submitted
% to the Journal will need them.  (Of course if it turns out that you
% do indeed need them, then by all means feel free to make use of them.)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{lipsum}

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\newcommand\MiKTeX{{\rmfamily M\kern-.05em \textsc{i\kern-.025em K}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\newcommand\PracTeX{{\rmfamily P\kern-.05em \textsc{r\kern-.025em a\kern-.025em
c}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{pmboxdraw}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{anzsj}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Software for Automated Residual Plot Assessment: autovi and autovi.web},
  pdfauthor={Weihao Li; Dianne Cook; Emi Tanaka; Susan VanderPlas; Klaus Ackermann},
  pdfkeywords={statistical software, statistical graphics, data
visualization, visual inference, computer vision, machine
learning, hypothesis testing, reression analysis},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\usepackage{moreverb}
\usepackage{url}
\usepackage{grffile}
\usepackage[UKenglish]{isodate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The year in the following may need to be updated!
\def\volumeyear{2024}

% The following command ("obviously") effects line numbering
% of the document.

\usepackage{lineno}
\linenumbers

\def\firstletters{\bgroup \catcode`-=10 \catcode`(=10 \filA}
\def\filA#1{\filB#1 {\end} }
\def\filB#1#2 {\ifx\end#1\egroup \else#1 \expandafter\filB\fi}

\runningheads{
Software for Automated Residual Plot Assessment
}{
\firstletters{WEIHAO}LI, \firstletters{DIANNE}COOK, \firstletters{EMI}TANAKA, \firstletters{SUSAN}VANDERPLAS, AND  \firstletters{KLAUS}ACKERMANN
}

\title{Software for Automated Residual Plot Assessment: autovi and
autovi.web}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{ANZJS Quarto Template}

\author{
Weihao Li\addressnum{1},
Dianne Cook\addressnum{1},
Emi Tanaka\addressnum{2},
Susan VanderPlas\addressnum{3} and
Klaus Ackermann
\addressnum{1}
}
\affiliation{
Monash University,
The Australian National University and
University of Nebraska
}

\address{
\addressnum{1} Department of Econometrics and Business
Statistics, Monash University, Wellington Road, VIC 3800, Australia\\
\addressnum{2} Biological Data Science Institute, The Australian
National University, 46 Sullivan's Creek Road, ACT 2600, Australia\\
\addressnum{3} Department of Statistics, University of Nebraska, Hardin
Hall, 3310 Holdrege St Suite 340, Lincoln, NE 68583, United States\\
\hspace*{1ex} Email: \texttt{weihao.li@monash.edu}    
}

\date{2024}
\begin{document}

\begin{abstract}
Regression software is widely available today, but tools for effective
diagnostics are still lagging. Perhaps, one of the reasons is that it is
hard. Conventional tests, that would make the task easy, are often too
sensitive, which would result in adequate models being abandoned if the
analyst strictly adhered to the test decision. The recommended advice is
to have the analyst assess the strength of patterns in residual plots.
This requires human effort and also suffers from the potential for
inconsistent decisions from different analysts. Using a lineup protocol
can help to alleviate inconsistency, but requires even more human
effort. This is the type of task where a robot might be employed to do
the disagreeable work that currently requires a human. Here we describe
a new R package that includes a computer vision model for automated
assessment of residual plots, and an accompanying Shiny app for ease of
use. For a user-provided sample of residuals, it predicts a measure of
visual signal strength (VSS) and provides a suite of supporting
information to assist the analyst diagnose their model fit.
\end{abstract}

\keywords{statistical software; statistical graphics; data
visualization; visual inference; computer vision; machine
learning; hypothesis testing; reression analysis}

\ack{The author acknowledges that this template is based on the latex
template for Australian and New Zealand Journal of Statistics and
intersperses some text from the original prototype document.
\newline\vspace{1ex}\newline Opinions and attitudes expressed in this
document, which are not explicitly designated as Journal policy, are
those of the author and are \emph{not} necessarily endorsed by the
Journal, its editorial board, its publisher Wiley or by the Australian
Statistical Publishing Association Inc.}

\maketitle

\section{Introduction}\label{sec-autovi-introduction}

Regression analysis is a fundamental statistical technique widely used
for modeling data from many fields. To diagnose the fit of a model it is
recommended that the residuals are plotted. If the fit is good, any
variation remaining should be noise, consistent with sampling from a
distribution specified by the error model. Deviations that might be
observed from a residual plot are non-normality, heteroscedasticity, and
other associations with the fitted values. In \citet{li2024plot}, we
demonstrated that visual methods for assessing residuals are
advantageous over conventional tests due to their reduced sensitivity to
minor departures. Building on this, \citet{li2024automated} introduced a
computer vision model aimed at alleviating the human effort required for
visual assessment of residual plots. The next step is to deliver the use
of the computer vision model to potential users, so that it can be
widely used to the benefit of the analytics community.

Software for regression analysis tools is widely available. The
Comprehensive R Archive Network (CRAN) \citep{hornik2012comprehensive}
hosts a vast array of packages, many of which provide tools to diagnose
models using residual plots. These packages can be broadly categorized
into three groups: general-purpose, enhanced visual diagnostics, and
visual diagnostics with statistical testing.

General-purpose regression analysis tools are the most widely used group
of packages. While not specifically designed for graphical diagnostics
of residuals in linear regression, they include this functionality as
part of a broader suite of statistical tools. For example, the
\texttt{stats} package \citep{stats} offers standard diagnostic plots
such as residuals vs.~fitted values, quantile-quantile (Q-Q) plots, and
residuals vs.~leverage plots. Additional packages like \texttt{jtools}
\citep{jtools}, \texttt{olsrr} \citep{olsrr}, \texttt{rockchalk}
\citep{rockchalk}, and \texttt{ggResidpanel} \citep{ggresidpanel}
provide similar graphical diagnostics, often with alternative aesthetics
or interactive features. All of these tools deliver the types of
diagnostic plots outlined in the classical text by
\citet{cook1982residuals}. However, as discussed in \citet{li2024plot},
relying solely on subjective assessments of these plots can lead to
issues, such as over-interpreting random patterns as model violations.

The second group consists of enhanced visual diagnostics tools, which
provide advanced aids for interpreting diagnostic plots. For instance,
\texttt{ecostats} \citep{warton_global_2023} incorporates simulation
envelopes into residual plots, while \texttt{DHARMa} \citep{dharma}
compares empirical quantiles (0.25, 0.5, and 0.75) of scaled residuals
to their theoretical counterparts. \texttt{DHARMa} is particularly
focused on detecting model violations such as heteroscedasticity,
incorrect functional forms, and issues specific to generalized linear
and mixed-effect models, like over/under-dispersion. It also includes
annotations from conventional tests, displayed as labels or text within
the plot, to help avoid misinterpretation.

The third group, visual diagnostics with statistical testing, offers
tools for formally testing patterns observed in diagnostic plots
\citep{buja2009statistical}. A common method for visual testing of
residual plots is the lineup protocol, where the true residual plot is
embedded within a set of null plots generated by simulating residuals
under the null hypothesis \(H_0\) that the regression model is correctly
specified. Observers are asked to identify the plot that appears most
different from the others. If a significant proportion of observers
correctly identify the true residual plot, it provides evidence against
\(H_0\), as the true residual plot should be indistinguishable from the
null plots if all residuals are generated by the same process, according
to \citet{buja2009statistical}. Packages in this group, such as
\texttt{nullabor} \citep{nullabor}, \texttt{HLMdiag}
\citep{loy2014hlmdiag}, and \texttt{regressinator}
\citep{regressinator}, enable users to compare observed residual plots
with samples from null distributions, helping to quantify the
significance of any detected patterns.

However, as discussed in \citet{li2024automated}, the lineup protocol
has significant limitations in large-scale applications due dependence
on human labor. Thus a computer vision model was developed with an
associated statistical testing procedure to automate the assessment of
residual plots. This model takes a residual plot and a vector of
auxiliary variables (such as the number of observations) as inputs and
outputs the predicted visual signal strength (VSS). This strength
estimates the distance between the residual distribution of the fitted
regression model and the reference distribution assumed under correct
model specification.

To make the statistical testing procedure and trained computer vision
model widely accessible, we developed the R package \texttt{autovi}, and
a web interface, \texttt{autovi.web} to make it easy for users to
automatically read their residual plots with the trained computer vision
model.

The remainder of this paper is structured as follows:
Section~\ref{sec-autovi} provides a detailed documentation of the
\texttt{autovi} package, including its usage and infrastructure.
Section~\ref{sec-autovi-web} focuses on the \texttt{autovi.web}
interface, describing its design and usage, along with illustrative
examples. Finally, Section~\ref{sec-autovi-conclusion} presents the main
conclusions of this work.

\section{R package: autovi}\label{sec-autovi}

The main purpose of \texttt{autovi} is to provide rejection decisions
and \(p\)-values for testing whether a regression model is correctly
specified. The package introduces a novel approach to automating
statistical analysis, particularly in the interpretation of residual
plots. The name \texttt{autovi} stands for automated visual inference.
While initially designed for linear regression residual diagnostics, it
has the potential to be extended to broader visual inference
applications, as we discuss in section
Section~\ref{sec-autovi-infrastructure}.

\subsection{Implementation}\label{sec-autovi-implementation}

The \texttt{autovi} package is built on the \texttt{bandicoot}
object-oriented programming (OOP) system \citep{bandicoot}, marking a
departure from R's traditional S3 generic system. This OOP architecture
enhances flexibility and modularity, allowing users to redefine key
functions through method overriding. While similar functionality could
be achieved using R's S3 system with generic functions, the OOP
framework offers a more structured and extensible foundation for the
package.

The \texttt{autovi} infrastructure effectively integrates multiple
programming languages and libraries into a comprehensive analytical
tool. It relies on five core libraries from Python and R, each playing a
critical role in the analysis pipeline. In Python, \texttt{pillow}
\citep{clark2015pillow} handles image processing tasks such as reading
and resizing PNG files of residual plots, then converting them into
input tensors for further analysis. The \texttt{TensorFlow}
\citep{abadi2016tensorflow} library, a key component of modern machine
learning, is used to predict the VSS of these plots through a
pre-trained convolutional neural network.

In the R environment, \texttt{autovi} utilizes several libraries.
\texttt{ggplot2} \citep{ggplot2} generates the initial residual plots,
saved as PNG files for visual input. The \texttt{cassowaryr}
\citep{mason2022cassowaryr} library computes scagnostics (scatter plot
diagnostics), providing numerical features that capture statistical
properties of the plots. These scagnostics complement the visual
analysis by offering quantitative metrics as secondary input to the
computer vision model. The \texttt{reticulate} \citep{reticulate}
package bridges R and Python, enabling seamless communication between
the two languages and supporting the integrated infrastructure.

\subsection{Installation}\label{installation}

The \texttt{autovi} package is available on CRAN. It is actively
developed and maintained, with the latest updates accessible on GitHub
at \url{https://github.com/TengMCing/autovi}. The code discussed in this
paper is based on \texttt{autovi} version 0.4.1.

The package includes internal functions to check the current Python
environment used by the \texttt{reticulate} package. If the necessary
Python packages are not installed in the Python interpreter, an error
will be raised. If you want to select a specific Python environment, you
can do so by calling the \texttt{reticulate::use\_python()} function
before using the \texttt{autovi} package.

\subsection{Usage}\label{sec-autovi-usage}

To get started quickly, only three function calls are needed to obtain a
summary of the automated residual assessment:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(autovi) }
\NormalTok{checker }\OtherTok{\textless{}{-}} \FunctionTok{residual\_checker}\NormalTok{(}\FunctionTok{lm}\NormalTok{(dist }\SpecialCharTok{\textasciitilde{}}\NormalTok{ speed, }\AttributeTok{data =}\NormalTok{ cars))}
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{check}\NormalTok{() }
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
\end{verbatim}

\begin{verbatim}
-- <AUTO_VI object>
Status:
 - Fitted model: lm
 - Keras model: UNKNOWN
    - Output node index: 1
 - Result:
    - Observed visual signal strength: 3.162 (p-value = 0.0396)
    - Null visual signal strength: [100 draws]
       - Mean: 1.274
       - Quantiles: 
          ╔═════════════════════════════════════════════════╗
          ║   25%    50%    75%    80%    90%    95%    99% ║
          ║0.8021 1.1109 1.5751 1.6656 1.9199 2.6564 3.3491 ║
          ╚═════════════════════════════════════════════════╝
    - Bootstrapped visual signal strength: [100 draws]
       - Mean: 2.786 (p-value = 0.05941)
       - Quantiles: 
          ╔══════════════════════════════════════════╗
          ║  25%   50%   75%   80%   90%   95%   99% ║
          ║2.452 2.925 3.173 3.285 3.463 3.505 3.652 ║
          ╚══════════════════════════════════════════╝
    - Likelihood ratio: 0.7275 (boot) / 0.06298 (null) = 11.55 
\end{verbatim}

The three functions are explained as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Load the \texttt{autovi} package using the \texttt{library()}
  function.
\item
  Create a checker object with a linear regression model.
\item
  Call the \texttt{check()} method of the checker, which, by default,
  predicts the VSS for the true residual plot, 100 null plots, and 100
  bootstrapped plots, storing the predictions internally. A concise
  report of the check results is then printed.
\end{enumerate}

The summary reports key findings such as the VSS of the true residual
plot and the \(p\)-value of the automated visual test. The \(p\)-value
is the ratio of null plots that have VSS greater than or equal to that
of the true residual plot. We typically reject the null hypothesis when
the \(p\)-value is smaller than or equal to a desired significance
level, such as 5\%. The report also provides sample quantiles of VSS for
null and bootstrapped plots, helping to explain the severity and
likelihood of model violations.

Although the \(p\)-value is sufficient for automated decision-making,
users can visually inspect the original residual plot alongside a sample
null plot. This visual comparison can clarify why \(H_0\) is either
rejected or not, and help identify potential remedies. The
\texttt{plot\_pair()} and \texttt{plot\_lineup()} methods facilitate
this comparison.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{plot\_pair}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-plot-pair-1.pdf}

}

\caption{\label{fig-plot-pair}True plot alongside one null plot, for
quick comparison.}

\end{figure}%

The \texttt{plot\_pair()} method (Figure~\ref{fig-plot-pair}) displays
the true residual plot on the left and a single null plot on the right.
If a full lineup was shown, the true residual plot would be embedded in
a page of null plots. Users should look for any distinct visual patterns
in the true residual plot that are absent in the null plot. Running
these functions multiple times can help any visual suspicions, as each
execution generates new random null plots for comparison.

The package offers a straightforward visualization of the assessment
result through the \texttt{summary\_plot()} function.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{summary\_plot}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-summary-plot-1.pdf}

}

\caption{\label{fig-summary-plot}Summary plot comparing the densities of
VSS for bootstrapped residual samples (red) relative to VSS for null
plots (blue).}

\end{figure}%

In the result, shown in Figure~\ref{fig-summary-plot}, the blue area
represents the density of VSS for null residual plots, while the red
area shows the density for bootstrapped residual plots. The dashed line
indicates the VSS of the true residual plot, and the solid line marks
the critical value at a 95\% significance level. The \(p\)-value and the
likelihood ratio are displayed in the subtitle. The likelihood ratio
represents the ratio of the likelihood of observing the VSS of the true
residual plot from the bootstrapped distribution compared to the null
distribution.

Interpreting the plot involves several key aspects. If the dashed line
falls to the right of the solid line, it suggests rejecting the null
hypothesis. The degree of overlap between the red and blue areas
indicates similarity between the true residual plot and null plots;
greater overlap suggests more similarity. Lastly, the portion of the red
area to the right of the solid line represents the percentage of
bootstrapped models considered to have model violations.

This visual summary provides an intuitive way to assess the model's fit
and potential violations, allowing users to quickly grasp the results of
the automated analysis.

\subsection{Modularized Infrastructure}\label{sec-autovi-infrastructure}

\begin{figure}

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-diag-1.png}

}

\caption{\label{fig-autovi-diag}Diagram illustrating the infrastructure
of the R package autovi. The modules in green are primary inputs
provided by users. Modules in blue are overridable methods that can be
modified to accommodate users' specific needs. The module in yellow is a
pre-defined non-overridable method. The modules in red are primary
outputs of the package.}

\end{figure}%

The initial motivation for developing \texttt{autovi} was to create a
convenient interface for sharing the models described and trained in
\citet{li2024automated}. However, recognizing that the classical normal
linear regression model represents a restricted class of models, we
sought to avoid limiting the potential for future extensions, whether by
the original developers or other users. As a result, the package was
designed to function seamlessly with linear regression models with
minimal modification and few required arguments, while also
accommodating other classes of models through partial infrastructure
substitution. This modular and customizable design allows
\texttt{autovi} to handle a wide range of residual diagnostics tasks.

The infrastructure of \texttt{autovi} consists of ten core modules: data
extraction, bootstrapping and model refitting, fitted values and
residuals extraction, auxiliary computation, null residual simulation,
plotting, plot saving, image reading and resizing, VSS prediction, and
\(p\)-value computation. Each module is designed with minimal dependency
on the preceding modules, allowing users to customize parts of the
infrastructure without affecting its overall integrity. An overview of
this infrastructure is illustrated in Figure~\ref{fig-autovi-diag}.

The modules for VSS prediction and \(p\)-value computation are
predefined and cannot be overridden, although users can interact with
them directly through function arguments. Similarly, the image reading
and resizing module is fixed but will adapt to different Keras models by
checking their input shapes. The remaining seven modules are designed to
be overridable, enabling users to tailor the infrastructure to their
specific needs. These modules are discussed in detail in the following
sections.

\subsubsection{Initialization}\label{initialization}

An \texttt{autovi} checker can be initialized by supplying two primary
inputs, including a regression model object, such as an \texttt{lm}
object representing the result of a linear regression model, and a
trained computer vision model compatible with the \texttt{Keras}
\citep{chollet2015keras} Application Programming Interface (API), to the
\texttt{AUTO\_VI} class constructor \texttt{auto\_vi()}. The
\texttt{residual\_checker()} introduced in
Section~\ref{sec-autovi-usage} is a thin wrapper around
\texttt{auto\_vi()}, which will call \texttt{get\_keras\_model()} during
initialization. \texttt{get\_keras\_model()} is a function to download a
trained computer vision model (described in \citet{li2024automated})
from GitHub. ``vss\_phn\_32'' specifies a model that predicts VSS and is
trained on residuals with polynomial, heteroskedasticity, and
non-normality patterns (phn). More details about the hosted models will
be provided in Section~\ref{sec-trained-model-hosting}.

The input of the constructor will be stored as attributes of the checker
and can be accessed by the user through the \texttt{\$} operator.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(autovi)}
\NormalTok{checker }\OtherTok{\textless{}{-}} \FunctionTok{auto\_vi}\NormalTok{(}\AttributeTok{fitted\_model =} \FunctionTok{lm}\NormalTok{(dist }\SpecialCharTok{\textasciitilde{}}\NormalTok{ speed, }\AttributeTok{data =}\NormalTok{ cars), }
                   \AttributeTok{keras\_model =} \FunctionTok{get\_keras\_model}\NormalTok{(}\StringTok{"vss\_phn\_32"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

Optionally, the user may specify the node index of the output layer of
the trained computer vision model to be monitored by the checker via the
\texttt{node\_index} argument if there are multiple output nodes. This
is particularly useful for multiclass classifiers when the user wants to
use one of the nodes as a VSS indicator.

After initializing the object, you can print the checker to view its
status.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{── }\SpecialCharTok{\textless{}}\NormalTok{AUTO\_VI object}\SpecialCharTok{\textgreater{}}
\NormalTok{Status}\SpecialCharTok{:}
 \SpecialCharTok{{-}}\NormalTok{ Fitted model}\SpecialCharTok{:}\NormalTok{ lm}
 \SpecialCharTok{{-}}\NormalTok{ Keras model}\SpecialCharTok{:}\NormalTok{ (None, }\DecValTok{32}\NormalTok{, }\DecValTok{32}\NormalTok{, }\DecValTok{3}\NormalTok{) }\SpecialCharTok{+}\NormalTok{ (None, }\DecValTok{5}\NormalTok{) }\OtherTok{{-}\textgreater{}}\NormalTok{ (None, }\DecValTok{1}\NormalTok{)}
    \SpecialCharTok{{-}}\NormalTok{ Output node index}\SpecialCharTok{:} \DecValTok{1}
 \SpecialCharTok{{-}}\NormalTok{ Result}\SpecialCharTok{:}\NormalTok{ UNKNOWN }
\end{Highlighting}
\end{Shaded}

The status includes the list of regression model classes (as provided by
the built-in \texttt{class()} function), the input and output shapes of
the Keras model in the standard \texttt{Numpy} format
\citep{harris2020array}, the output node index being monitored, and the
assessment result. If no check has been run yet, the assessment result
will display as ``UNKNOWN''.

\subsubsection{Fitted Values and Residuals
Extraction}\label{fitted-values-and-residuals-extraction}

To be able to predict VSS for a residual plot, both fitted values and
residuals are needed to be extracted from the regression model object
supplied by the user. In R, statistical models like \texttt{lm} (linear
model) and \texttt{glm} (generalized linear model) typically support the
use of generic functions such as \texttt{fitted()} and \texttt{resid()}
to retrieve these values. The \texttt{get\_fitted\_and\_resid()} method,
called by the checker, relies on these generic functions by default.
However, generic functions only work with classes that have appropriate
method implementations. Some regression modeling packages may not fully
adhere to the \texttt{stats} package guidelines for implementing these
functions. In such cases, overriding the method becomes necessary.

By design, the \texttt{get\_fitted\_and\_resid()} method accepts a
regression model object as input and returns a \texttt{tibble} (a modern
presentation of the \texttt{data.frame}) with two columns:
\texttt{.fitted} and \texttt{.resid}, representing the fitted values and
residuals, respectively. If no input is supplied, the method uses the
regression model object stored in the checker. Although modules in the
\texttt{autovi} infrastructure make minimal assumptions about other
modules, they do require strictly defined input and output formats to
ensure data validation and prevent fatal bugs. Therefore, any overridden
method should follow to these conventions.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{get\_fitted\_and\_resid}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# A tibble: 50 x 2
   .fitted .resid
     <dbl>  <dbl>
 1   -1.85   3.85
 2   -1.85  11.8 
 3    9.95  -5.95
 4    9.95  12.1 
 5   13.9    2.12
 6   17.8   -7.81
 7   21.7   -3.74
 8   21.7    4.26
 9   21.7   12.3 
10   25.7   -8.68
# i 40 more rows
\end{verbatim}

\subsubsection{Data Extraction}\label{data-extraction}

For linear regression model in R, the model frame contains all the data
required by a formula for evaluation. This is essential for
bootstrapping and refitting the model when constructing a bootstrapped
distribution of VSS. Typically, the model frame can be extracted from
the regression model object using the \texttt{model.frame()} generic
function, which is the default method used by \texttt{get\_data()}.
However, some regression models do not use a formula or are evaluated
differently, potentially lacking a model frame. In such cases, users can
either provide the data used to fit the regression model through the
\texttt{data} argument when constructing the checker, or customize the
method to better suit their needs. It's worth noting that this module is
only necessary if bootstrapping is required, as the model frame is not
used in other modules of the infrastructure.

The \texttt{get\_data()} method accepts a regression model object as
input and returns a \texttt{data.frame} representing the model frame of
the fitted regression model. If no input is supplied, the regression
model stored in the checker will be used.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{get\_data}\NormalTok{() }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{head}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
  dist speed
1    2     4
2   10     4
3    4     7
4   22     7
5   16     8
6   10     9
\end{verbatim}

\subsubsection{Bootstrapping and Model
Refitting}\label{bootstrapping-and-model-refitting}

Bootstrapping a regression model typically involves sampling the
observations with replacement and refitting the model with the
bootstrapped data. The \texttt{boot\_method()} method follows this
bootstrapping scheme by default. It accepts a fitted regression model
and a \texttt{data.frame} as inputs, and returns a \texttt{tibble} of
bootstrapped residuals. If no inputs are provided, the method uses the
regression model stored in the checker and the result of the
\texttt{get\_data()} method.

Note that instead of calling \texttt{get\_data()} implicitly within the
method, it is used as part of the default argument definition. This
approach allows users to bypass the \texttt{get\_data()} method entirely
and directly supply a \texttt{data.frame} to initiate the bootstrap
process. Many other methods in \texttt{autovi} adopt this principle when
possible, where dependencies are explicitly listed in the formal
arguments. This design choice enhances the reusability and isolation of
modules, offers better control for testing, and simplifies the overall
process.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{boot\_method}\NormalTok{(}\AttributeTok{data =}\NormalTok{ checker}\SpecialCharTok{$}\FunctionTok{get\_data}\NormalTok{())}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# A tibble: 50 x 2
   .fitted .resid
     <dbl>  <dbl>
 1   27.0   -2.96
 2   38.8  -12.8 
 3   34.8   -8.82
 4   27.0  -13.0 
 5   11.2    4.76
 6   42.7   -2.68
 7   42.7   -2.68
 8   38.8  -18.8 
 9   38.8   15.2 
10   -4.47   6.47
# i 40 more rows
\end{verbatim}

\subsubsection{Auxiliary Computation}\label{auxiliary-computation}

As described in \citet{li2024automated}, in some cases, a residual plot
alone may not provide enough information to accurately determine VSS.
For instance, when the points in the residual plot have significant
overlap, the trend and shape of the residual pattern can be difficult to
discern. Including auxiliary variables, such as the number of
observations, as additional inputs to the computer vision model can be
beneficial. To address this, \texttt{autovi} includes internal functions
within the checker that automatically detect the number of inputs
required by the provided Keras model. If multiple inputs are necessary,
the checker invokes the \texttt{auxiliary()} method to compute these
additional inputs.

The \texttt{auxiliary()} method takes a \texttt{data.frame} containing
fitted values and residuals as input and returns a \texttt{data.frame}
with five numeric columns. These columns represent four scagnostics ---
``Monotonic'', ``Sparse'', ``Striped'', and ``Splines'' --- calculated
using the \texttt{cassowaryr} package, as well as the number of
observations. This approach is consistent with the training process of
the computer vision models described in \citet{li2024automated}. If no
\texttt{data.frame} is provided, the method will default to retrieving
fitted values and residuals by calling
\texttt{get\_fitted\_and\_resid()}.

Technically, any Keras-implemented computer vision model can be adapted
to accept an image as the primary input and additional variables as
secondary inputs by adding a data pre-processing layer before the actual
input layer. If users wish to override \texttt{auxiliary()}, the output
should be a \texttt{data.frame} with a single row and the number of
columns such that its concatenation matches the number of parameters for
the corresponding layer in the supplied Keras model.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{auxiliary}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# A tibble: 1 x 5
  measure_monotonic measure_sparse measure_splines measure_striped     n
              <dbl>          <dbl>           <dbl>           <dbl> <int>
1            0.0621          0.470          0.0901            0.62    50
\end{verbatim}

\subsubsection{Null Residual Simulation}\label{sec-autovi-null-method}

A fundamental element of the automated residual assessment described in
\citet{li2024automated} is comparing the VSS of null plots with that of
the true residual plot. However, due to the variety of regression
models, there is no universal method for simulating null residuals that
are consistent with model assumptions. Fortunately, for classical normal
linear regression models, null residuals can be effectively simulated
using the residual rotation method, as outlined in
\citet{buja2009statistical}. This process involves generating random
draws from a standard normal distribution, regressing these draws on the
original predictors, and then rescaling the resulting residuals by the
ratio of the residual sum of squares to the that of the original linear
regression model. Other regression models, such as \texttt{glm}
(generalized linear model) and \texttt{gam} (generalized additive
model), generally cannot use this method to efficiently simulate null
residuals. Therefore, it is recommended that users override the
\texttt{null\_method()} to suit their specific model. The
\texttt{null\_method()} takes a fitted regression model as input,
defaulting to the regression model stored in the checker, and returns a
\texttt{tibble}.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{null\_method}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# A tibble: 50 x 2
   .fitted  .resid
     <dbl>   <dbl>
 1   -1.85  18.2  
 2   -1.85  -0.765
 3    9.95 -12.8  
 4    9.95  18.6  
 5   13.9    2.57 
 6   17.8    7.03 
 7   21.7  -11.1  
 8   21.7  -13.2  
 9   21.7  -12.6  
10   25.7    3.57 
# i 40 more rows
\end{verbatim}

\subsubsection{Plotting}\label{plotting}

Plotting is a crucial aspect of residual plot diagnostics because
aesthetic elements like marker size, marker color, and auxiliary lines
impact the presentation of information. There are computer vision models
trained to handle images captured in various scenarios. For example, the
VGG16 model \citep{simonyan2014very} can classify objects in images
taken under different lighting conditions and is robust to image
rotation. However, data plots are a special type of image as the
plotting style can always be consistent if controlled properly.
Therefore, we assume computer vision models built for reading residual
plots will be trained with residual plots of a specific aesthetic style.
In this case, it is best to predict plots using the same style for
optimal performance. The plotting method \texttt{plot\_resid()} handles
this aspect.

\texttt{plot\_resid()} accepts a \texttt{data.frame} containing fitted
values and residuals, along with several customization options: a
\texttt{ggplot} theme, an \texttt{alpha} value to control the
transparency of data points, a \texttt{size} value to set the size of
data points, and a \texttt{stroke} value to define the thickness of data
point edges. Additionally, it includes four Boolean arguments to toggle
the display of axes, legends, grid lines, and a horizontal red line. By
default, it replicates the style we used to generate the training
samples for the computer vision models described in
\citet{li2024automated}. In brief, the residual plot omits axis text and
ticks, titles, and background grid lines, featuring only a red line at
\(y = 0\). It retains only the necessary components of a residual plot.
If the computer vision model is trained with a different but consistent
aesthetic style, \texttt{plot\_resid()} should be overridden.

The method returns a \texttt{ggplot} object
(Figure~\ref{fig-autovi-plot-resid}), which can be saved as a PNG file
in the following module. If no data is provided, the method will use
\texttt{get\_fitted\_and\_resid()} to retrieve the fitted values and
residuals from the regression model stored in the checker.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{plot\_resid}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-plot-resid-1.pdf}

}

\caption{\label{fig-autovi-plot-resid}Residual plot of the regression
model stored in the checker.}

\end{figure}%

To manually generate true residual plots, null plots, or bootstrapped
residual plots, you can pass the corresponding \texttt{data.frame}
produced by the \texttt{get\_fitted\_and\_resid()},
\texttt{null\_method()}, and \texttt{boot\_method()} methods to the
\texttt{plot\_resid()} method, respectively.

\subsubsection{Plot Saving}\label{plot-saving}

Another key aspect of a standardized residual plot is its resolution. In
\citet{li2024automated}, we used an image format of 420 pixels in height
and 525 pixels in width. This resolution was chosen because the original
set, consisting of 20 residual plots arranged in a four by five grid,
was represented by an image of 2100 by 2100 pixels. The
\texttt{save\_plot()} method accepts a \texttt{ggplot} object as input
and saves it as a PNG file to the location specified by the
\texttt{path} argument. If no path is provided, the PNG file is saved to
a temporary file.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{plot\_resid}\NormalTok{() }\SpecialCharTok{|\textgreater{}} 
\NormalTok{  checker}\SpecialCharTok{$}\FunctionTok{save\_plot}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
[1] "/var/folders/61/bv7_1qzs20x6fjb2rsv7513r0000gn/T//RtmpfYtMdO/file37817b7b5b6.png"
\end{verbatim}

\subsubsection{Image Reading and
Resizing}\label{image-reading-and-resizing}

When training computer vision models, it is common to test various input
sizes for the same architecture to identify the optimal setup. This
involves preparing the original training image at a higher resolution
than required and then resizing it to match the input size during
training. The \texttt{autovi} package includes a class,
\texttt{KERAS\_WRAPPER}, to simplify this process. This Keras wrapper
class features a method called \texttt{image\_to\_array()}, which reads
an image as a \texttt{PIL} image using the \texttt{pillow} Python
package, resizes it to the target input size required by the Keras
model, and converts it to a \texttt{Numpy} array.

To construct a \texttt{KERAS\_WRAPPER} object, you need to provide the
Keras model as the main argument. However, users generally do not need
to interact with this class directly, as the \texttt{autovi} checker
automatically invokes its methods when performing VSS predictions. The
\texttt{image\_to\_array()} method takes the path to the image file, the
target height, and the target width as inputs and returns a
\texttt{Numpy} array. If not specified, the target height and target
width will be retrieved from the input layer of the Keras model by the
\texttt{get\_input\_height()} and \texttt{get\_input\_width()} method of
\texttt{KERAS\_WRAPPER}.

The following code example demonstrate the way to manually generate the
true residual plot, save it as PNG file, and load it back as
\texttt{Numpy} array.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{wrapper }\OtherTok{\textless{}{-}} \FunctionTok{keras\_wrapper}\NormalTok{(}\AttributeTok{keras\_model =}\NormalTok{ checker}\SpecialCharTok{$}\NormalTok{keras\_model)  }
\NormalTok{input\_array }\OtherTok{\textless{}{-}}\NormalTok{ checker}\SpecialCharTok{$}\FunctionTok{plot\_resid}\NormalTok{() }\SpecialCharTok{|\textgreater{}} 
\NormalTok{  checker}\SpecialCharTok{$}\FunctionTok{save\_plot}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
\NormalTok{  wrapper}\SpecialCharTok{$}\FunctionTok{image\_to\_array}\NormalTok{()}
\NormalTok{input\_array}\SpecialCharTok{$}\NormalTok{shape}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
(1, 32, 32, 3)
\end{verbatim}

\subsubsection{Visual Signal Strength (VSS)
Prediction}\label{visual-signal-strength-vss-prediction}

VSS, as discussed in \citet{li2024automated}, estimates the distance
between the input residual plot and a theoretically good residual plot.
It can be defined in various ways, much like different methods for
measuring the distance between two points. This will not impact the
\texttt{autovi} infrastructure as long as the provided Keras model can
predict the intended measure.

There are several ways to obtain VSS from the checker, with the most
direct being the \texttt{vss()} method. By default, this method predicts
the VSS for the true residual plot. If a \texttt{ggplot} or a
\texttt{data.frame}, such as null residuals generated by the
\texttt{null\_method()}, is explicitly provided, the method will use
that input to predict VSS accordingly. Note that if a \texttt{ggplot} is
provided, auxiliary inputs must be supplied manually via the
\texttt{auxiliary} argument, as we assume that auxiliary variables can
not be computed directly from a \texttt{ggplot}.

Another way to obtain VSS is by calling the \texttt{check()} method.
This comprehensive method perform extensive diagnostics on the true
residual plot and store the VSS in the \texttt{check\_result} field of
the checker. Additionally, for obtaining VSS for null residual plots and
bootstrapped residual plots, there are two specialized methods,
\texttt{null\_vss()} and \texttt{boot\_vss()}, designed for this purpose
respectively.

Calling the \texttt{vss()} method without arguments will predict the VSS
for the true residual plot and return the result as a single-element
\texttt{tibble}.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{vss}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# A tibble: 1 x 1
    vss
  <dbl>
1  3.16
\end{verbatim}

Providing a \texttt{data.frame} of null residuals or a null residual
plot yields the same VSS.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{null\_resid }\OtherTok{\textless{}{-}}\NormalTok{ checker}\SpecialCharTok{$}\FunctionTok{null\_method}\NormalTok{()}
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{vss}\NormalTok{(null\_resid)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# A tibble: 1 x 1
    vss
  <dbl>
1  1.23
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{null\_resid }\SpecialCharTok{|\textgreater{}}
\NormalTok{  checker}\SpecialCharTok{$}\FunctionTok{plot\_resid}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
\NormalTok{  checker}\SpecialCharTok{$}\FunctionTok{vss}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# A tibble: 1 x 1
    vss
  <dbl>
1  1.23
\end{verbatim}

The \texttt{null\_vss()} helper method primarily takes the number of
null plots as input. If the user wants to use a ad hoc null simulation
scheme, it can be provided via the \texttt{null\_method} argument.
Intermediate results, including null residuals and null plots, can be
returned by enabling \texttt{keep\_null\_data} and
\texttt{keep\_null\_plot}. The VSS, along with null residuals and null
plots, will be stored in a \texttt{tibble} with three columns. The
following code example demonstrates how to predict the VSS for five null
residual plots while keeping the intermediate results.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{null\_vss}\NormalTok{(}\DecValTok{5}\NormalTok{L, }
                 \AttributeTok{keep\_null\_data =} \ConstantTok{TRUE}\NormalTok{, }
                 \AttributeTok{keep\_null\_plot =} \ConstantTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# A tibble: 5 x 3
    vss data              plot  
  <dbl> <list>            <list>
1 0.982 <tibble [50 x 2]> <gg>  
2 1.58  <tibble [50 x 2]> <gg>  
3 2.09  <tibble [50 x 2]> <gg>  
4 0.742 <tibble [50 x 2]> <gg>  
5 2.21  <tibble [50 x 2]> <gg>  
\end{verbatim}

The \texttt{boot\_vss()} helper method is similar to
\texttt{null\_vss()}, with some differences in argument names. The
following code example demonstrates how to predict the VSS for five
bootstrapped residual plots while keeping the intermediate results.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{boot\_vss}\NormalTok{(}\DecValTok{5}\NormalTok{L,}
                 \AttributeTok{keep\_boot\_data =} \ConstantTok{TRUE}\NormalTok{,}
                 \AttributeTok{keep\_boot\_plot =} \ConstantTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# A tibble: 5 x 3
    vss data              plot  
  <dbl> <list>            <list>
1  3.12 <tibble [50 x 2]> <gg>  
2  2.37 <tibble [50 x 2]> <gg>  
3  2.87 <tibble [50 x 2]> <gg>  
4  1.85 <tibble [50 x 2]> <gg>  
5  3.66 <tibble [50 x 2]> <gg>  
\end{verbatim}

\subsubsection{\texorpdfstring{\(p\)-value
Computation}{p-value Computation}}\label{p-value-computation}

Once we have obtained the VSS from both the true residual plot and the
null plots, we can compute the \(p\)-value. This \(p\)-value represents
the ratio of plots with VSS greater than or equal to that of the true
residual plot. We can perform this calculation using the
\texttt{check()} method. The main inputs for this method are the number
of null plots and the number of bootstrapped plots to generate. If you
need to access intermediate residuals and plots, you can enable the
\texttt{keep\_data} and \texttt{keep\_plot} options. The method stores
the final result in the \texttt{check\_result} field of the object. To
obtain the p-value using the \texttt{check()} method, you can use the
following code.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{check}\NormalTok{(}\AttributeTok{boot\_draws =} \DecValTok{100}\NormalTok{L, }\AttributeTok{null\_draws =} \DecValTok{100}\NormalTok{L)}
\NormalTok{checker}\SpecialCharTok{$}\NormalTok{check\_result}\SpecialCharTok{$}\NormalTok{p\_value}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
[1] 0.02970297
\end{verbatim}

\subsection{Summary Plots}\label{summary-plots}

After executing the \texttt{check()} method, \texttt{autovi} offers two
visualization options for the assessment result through the
\texttt{summary\_plot()} method, including the density plot and the rank
plot. We have already discussed and interpreted the density plot in
Section~\ref{sec-autovi-usage}. Here, we would like to highlight the
flexibility in choosing which elements to display in the density plot as
shown in Figure~\ref{fig-autovi-summary-plot-option}. For instance, you
can omit the bootstrapped distribution by setting \texttt{boot\_dist} to
\texttt{NULL}. Similarly, you can hide the null distribution
(\texttt{null\_dist}), the \(p\)-value (\texttt{p\_value}), or the
likelihood ratio (\texttt{likelihood\_ratio}) as needed. The following
example demonstrates how to create a summary plot without the results
from bootstrapped plots.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{summary\_plot}\NormalTok{(}\AttributeTok{boot\_dist =} \ConstantTok{NULL}\NormalTok{,}
                     \AttributeTok{likelihood\_ratio =} \ConstantTok{NULL}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-summary-plot-option-1.pdf}

}

\caption{\label{fig-autovi-summary-plot-option}Density plot of the VSS
for null plots.}

\end{figure}%

This customization allows you to focus on specific aspects of the
assessment, tailoring the visualization to your analytical needs.

The rank plot (Figure~\ref{fig-autovi-rank-plot}), creating by setting
\texttt{type} to ``rank'', is a bar plot where the \(x\)-axis represents
the rank and the \(y\)-axis shows the VSS. The bar that is coloured in
red corresponding to the VSS of the true residual plot. By examining the
rank plot, you can intuitively understand how the observed VSS compares
to the null VSSs and identify any outliers in the null distribution.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{summary\_plot}\NormalTok{(}\AttributeTok{type =} \StringTok{"rank"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-rank-plot-1.pdf}

}

\caption{\label{fig-autovi-rank-plot}Rank plot of the VSS for null
plots.}

\end{figure}%

\subsection{Feature Extraction}\label{feature-extraction}

In addition to predicting VSS and computing \(p\)-values,
\texttt{autovi} offers methods to extract features from any layer of the
Keras model. To see which layers are available in the current Keras
model, you can use the \texttt{list\_layer\_name()} method from the
\texttt{KERAS\_WRAPPER} class.

The following code example lists the layer names of the currently used
Keras model:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{wrapper }\OtherTok{\textless{}{-}} \FunctionTok{keras\_wrapper}\NormalTok{(checker}\SpecialCharTok{$}\NormalTok{keras\_model)}
\NormalTok{wrapper}\SpecialCharTok{$}\FunctionTok{list\_layer\_name}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
 [1] "input_1"                  "tf.__operators__.getitem"
 [3] "tf.nn.bias_add"           "grey_scale"              
 [5] "block1_conv1"             "batch_normalization"     
 [7] "activation"               "block1_conv2"            
 [9] "batch_normalization_1"    "activation_1"            
[11] "block1_pool"              "dropout"                 
[13] "block2_conv1"             "batch_normalization_2"   
[15] "activation_2"             "block2_conv2"            
[17] "batch_normalization_3"    "activation_3"            
[19] "block2_pool"              "dropout_1"               
[21] "block3_conv1"             "batch_normalization_4"   
[23] "activation_4"             "block3_conv2"            
[25] "batch_normalization_5"    "activation_5"            
[27] "block3_conv3"             "batch_normalization_6"   
[29] "activation_6"             "block3_pool"             
[31] "dropout_2"                "block4_conv1"            
[33] "batch_normalization_7"    "activation_7"            
[35] "block4_conv2"             "batch_normalization_8"   
[37] "activation_8"             "block4_conv3"            
[39] "batch_normalization_9"    "activation_9"            
[41] "block4_pool"              "dropout_3"               
[43] "block5_conv1"             "batch_normalization_10"  
[45] "activation_10"            "block5_conv2"            
[47] "batch_normalization_11"   "activation_11"           
[49] "block5_conv3"             "batch_normalization_12"  
[51] "activation_12"            "block5_pool"             
[53] "dropout_4"                "global_max_pooling2d"    
[55] "additional_input"         "concatenate"             
[57] "dense"                    "dropout_5"               
[59] "activation_13"            "dense_1"                 
\end{verbatim}

Among these layers, the ``global\_max\_pooling2d'' layer is a 2D global
max pooling layer that outputs the results from the last convolutional
blocks. As \citet{simonyan2014very} noted, all preceding convolutional
blocks can be viewed as a large feature extractor. Consequently, the
output from this layer provides features that can be utilized for
various purposes, such as performing transfer learning.

To obtain the features, provide the layer name using the
\texttt{extract\_feature\_from\_layer} argument in the
\texttt{predict()} method. This will return a \texttt{tibble} with the
VSS and all features extracted from that layer. Each row corresponds to
one plot. The features will be flattened into 2D and named with the
prefix ``f\_'' followed by a number from one to the total number of
features.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{plot\_resid}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
\NormalTok{  checker}\SpecialCharTok{$}\FunctionTok{save\_plot}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
\NormalTok{  wrapper}\SpecialCharTok{$}\FunctionTok{image\_to\_array}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
\NormalTok{  wrapper}\SpecialCharTok{$}\FunctionTok{predict}\NormalTok{(}\AttributeTok{auxiliary =}\NormalTok{ checker}\SpecialCharTok{$}\FunctionTok{auxiliary}\NormalTok{(),}
                  \AttributeTok{extract\_feature\_from\_layer =} \StringTok{"global\_max\_pooling2d"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# A tibble: 1 x 257
    vss   f_1   f_2   f_3   f_4   f_5    f_6   f_7    f_8   f_9   f_10  f_11
  <dbl> <dbl> <dbl> <dbl> <dbl> <dbl>  <dbl> <dbl>  <dbl> <dbl>  <dbl> <dbl>
1  3.16 0.151     0     0     0     0 0.0203 0.109 0.0203     0 0.0834     0
# i 245 more variables: f_12 <dbl>, f_13 <dbl>, f_14 <dbl>, f_15 <dbl>,
#   f_16 <dbl>, f_17 <dbl>, f_18 <dbl>, f_19 <dbl>, f_20 <dbl>, f_21 <dbl>,
#   f_22 <dbl>, f_23 <dbl>, f_24 <dbl>, f_25 <dbl>, f_26 <dbl>, f_27 <dbl>,
#   f_28 <dbl>, f_29 <dbl>, f_30 <dbl>, f_31 <dbl>, f_32 <dbl>, f_33 <dbl>,
#   f_34 <dbl>, f_35 <dbl>, f_36 <dbl>, f_37 <dbl>, f_38 <dbl>, f_39 <dbl>,
#   f_40 <dbl>, f_41 <dbl>, f_42 <dbl>, f_43 <dbl>, f_44 <dbl>, f_45 <dbl>,
#   f_46 <dbl>, f_47 <dbl>, f_48 <dbl>, f_49 <dbl>, f_50 <dbl>, f_51 <dbl>, ...
\end{verbatim}

Alternatively, the \texttt{AUTO\_VI} class provides a way to extract
features using the \texttt{vss()} method. This method is essentially a
high-level wrapper around the \texttt{predict()} method of
\texttt{KERAS\_WRAPPER}, but it offers a more straightforward interface
and better default arguments.

The results from the previous code example can be replicated with a
single line of code as shown below.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{vss}\NormalTok{(}\AttributeTok{extract\_feature\_from\_layer =} \StringTok{"global\_max\_pooling2d"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# A tibble: 1 x 257
    vss   f_1   f_2   f_3   f_4   f_5    f_6   f_7    f_8   f_9   f_10  f_11
  <dbl> <dbl> <dbl> <dbl> <dbl> <dbl>  <dbl> <dbl>  <dbl> <dbl>  <dbl> <dbl>
1  3.16 0.151     0     0     0     0 0.0203 0.109 0.0203     0 0.0834     0
# i 245 more variables: f_12 <dbl>, f_13 <dbl>, f_14 <dbl>, f_15 <dbl>,
#   f_16 <dbl>, f_17 <dbl>, f_18 <dbl>, f_19 <dbl>, f_20 <dbl>, f_21 <dbl>,
#   f_22 <dbl>, f_23 <dbl>, f_24 <dbl>, f_25 <dbl>, f_26 <dbl>, f_27 <dbl>,
#   f_28 <dbl>, f_29 <dbl>, f_30 <dbl>, f_31 <dbl>, f_32 <dbl>, f_33 <dbl>,
#   f_34 <dbl>, f_35 <dbl>, f_36 <dbl>, f_37 <dbl>, f_38 <dbl>, f_39 <dbl>,
#   f_40 <dbl>, f_41 <dbl>, f_42 <dbl>, f_43 <dbl>, f_44 <dbl>, f_45 <dbl>,
#   f_46 <dbl>, f_47 <dbl>, f_48 <dbl>, f_49 <dbl>, f_50 <dbl>, f_51 <dbl>, ...
\end{verbatim}

The argument \texttt{extract\_feature\_from\_layer} is also available in
other functions that build on the \texttt{vss()} method, including
\texttt{null\_vss()}, \texttt{boot\_vss()}, and \texttt{check()}.

\subsection{Trained Model Hosting}\label{sec-trained-model-hosting}

The trained computer vision models described in \citet{li2024automated}
are hosted on a GitHub repository at
\url{https://github.com/TengMCing/autovi_data}. Currently, there are six
models available. You can view them by calling
\texttt{list\_keras\_model()}, which will return a \texttt{tibble}
showing the input shape and a description of each model.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{list\_keras\_model}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{str}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
tibble [6 x 11] (S3: tbl_df/tbl/data.frame)
 $ model_name          : chr [1:6] "vss_32" "vss_64" "vss_128" "vss_phn_32" ...
 $ path                : chr [1:6] "keras_model/vss_32.keras.zip" "keras_model/vss_64.keras.zip" "keras_model/vss_128.keras.zip" "keras_model/vss_phn_32.keras.zip" ...
 $ volume_path         : chr [1:6] "keras_model_volumes/vss_32.zip.001" "keras_model_volumes/vss_64.zip.001" "keras_model_volumes/vss_128.zip.001" "keras_model_volumes/vss_phn_32.zip.001" ...
 $ volume_size         : int [1:6] 4 1 8 2 8 8
 $ npz_path            : chr [1:6] "keras_model_npz/vss_32.npz" "keras_model_npz/vss_64.npz" "keras_model_npz/vss_128.npz" "keras_model_npz/vss_phn_32.npz" ...
 $ npz_py              : chr [1:6] "keras_model_npz/vss_32_rebuild.py" "keras_model_npz/vss_64_rebuild.py" "keras_model_npz/vss_128_rebuild.py" "keras_model_npz/vss_phn_32_rebuild.py" ...
 $ input_height        : int [1:6] 32 64 128 32 64 128
 $ input_width         : int [1:6] 32 64 128 32 64 128
 $ input_channels      : int [1:6] 3 3 3 3 3 3
 $ auxiliary_input_size: int [1:6] 0 0 0 5 5 5
 $ description         : chr [1:6] "A Keras model trained with residual plots containing non-linearity and heteroskedasticity patterns." "A Keras model trained with residual plots containing non-linearity and heteroskedasticity patterns." "A Keras model trained with residual plots containing non-linearity and heteroskedasticity patterns." "A Keras model trained with residual plots containing non-linearity, heteroskedasticity and non-normality patterns." ...
\end{verbatim}

The \texttt{get\_keras\_model()} function can be used to download a
model to a temporary directory and load it into memory using
\texttt{TensorFlow}. It requires only the model name, which is the value
in the first column of the \texttt{tibble} returned by
\texttt{list\_keras\_model()}.

\section{Web interface: autovi.web}\label{sec-autovi-web}

The \texttt{autovi.web} package extends the functionality of
\texttt{autovi} by offering a user-friendly web interface for automated
residual plot assessment. This eliminates the common challenges
associated with software installation, so users can avoid managing
Python environments or handling version requirements for R libraries.
The platform is cross-platform and accessible on various devices and
operating systems, making it suitable even for users without R
programming experience. Additionally, updates are managed centrally,
ensuring that users always have access to the latest features.

The \texttt{autovi.web} interface is available at
\url{autoviweb.netlify.app}. This section discusses the implementation
based on \texttt{autovi.web} version 0.1.0.

\subsection{Implementation}\label{implementation}

The package \texttt{autovi.web} is built using the \texttt{shiny}
\citep{shiny} and \texttt{shinydashboard} \citep{shinydashboard} R
packages. Hosted on the \href{https://www.shinyapps.io}{shinyapps.io}
domain, the application is accessible through any modern web browser.
The R packages \texttt{htmltools} \citep{htmltools} and
\texttt{shinycssloaders} \citep{shinycssloaders} are used to render
markdown documentation in shiny application, and for loading animations
for shiny widgets, respectively.

Determining the best way to implement the interface was difficult. In
our initial planning for \texttt{autovi.web}, we considered implementing
the entire web application using the \texttt{webr} framework
\citep{webr}, which would have allowed the entire application to run
directly in the user's browser. However, this approach was not feasible
at the time of writing this paper. The reason is that one of the R
packages \texttt{autovi} depends on the R package \texttt{splancs}
\citep{splancs}, which uses compiled Fortran code. A working Emscripten
\citep{zakai2011emscripten} version of this package, which would be
required for \texttt{webr}, was not available.

We also explored the possibility of implementing the web interface using
frameworks built on other languages, such as Python. However, server
hosting domains that natively support Python servers typically do not
have the latest version of R installed. Additionally, calling R from
Python is typically done using the \texttt{rpy2} Python library
\citep{rpy2}, but this approach can be awkward when dealing with
language syntax related to non-standard evaluation. Another option we
considered was renting a server where we could have full control, such
as those provided by cloud platforms like Google Cloud Platform (GCP) or
Amazon Web Services (AWS). However, correctly setting up the server and
ensuring a secure deployment requires significant expertise. Ultimately,
the most practical solution was to use the \texttt{shiny} and
\texttt{shinydashboard} frameworks, which are well-established in the R
community and offer a solid foundation for web application development.

The server-side configuration of \texttt{autovi.web} is carefully
designed to support its functionality. Most required Python libraries,
including \texttt{pillow} and \texttt{NumPy}, are pre-installed on the
server. These libraries are integrated into the Shiny application using
the \texttt{reticulate} package, which provides an interface between R
and Python.

Due to the resource allocation policy of shinyapps.io, the server enters
a sleep mode during periods of inactivity, resulting in the clearing of
the local Python virtual environment. Consequently, when the application
``wakes up'' for a new user session, these libraries need to be
reinstalled. While this ensures a clean environment for each session, it
may lead to slightly longer loading times for the first user after a
period of inactivity.

In contrast to \texttt{autovi}, \texttt{autovi.web} does not use the
native Python version of \texttt{TensorFlow}. Instead, it leverages
\texttt{TensorFlow.js}, a JavaScript library that allows the execution
of machine learning models directly in the browser. This choice enables
native browser execution, enhancing compatibility across different user
environments, and shifts the computational load from the server to the
client-side. \texttt{TensorFlow.js} also offers better scalability and
performance, especially when dealing with resource-intensive computer
vision models on shinyapps.io.

While \texttt{autovi} requires downloading the pre-trained computer
vision models from GitHub, these models in ``.keras'' file format are
incompatible with \texttt{TensorFlow.js}. Therefore, we extract and
store the model weights in JSON files and include them as extra
resources in the Shiny application. When the application initializes,
\texttt{TensorFlow.js} rebuilds the computer vision model using these
pre-stored weights.

To allow communication between \texttt{TensorFlow.js} and other
components of the Shiny application, the \texttt{shinyjs} R package is
used. This package allows calling custom JavaScript code within the
Shiny framework. The specialized JavaScript code for initializing
\texttt{TensorFlow.js} and calling \texttt{TensorFlow.js} for VSS
prediction is deployed alongside the Shiny application as additional
resources.

\subsection{Design}\label{sec-autovi-web-design}

\begin{figure}

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{figures/autovi_web.png}

}

\caption{\label{fig-autovi-web}Overview of the \texttt{autovi.web}
graphical user interface (GUI). This default view may change based on
user interactions. Region 1 is the sidebar menu, containing the residual
assessment tab and the information tab. Region 2 is the data upload
panel, where users can provide a CSV file and specify the type of data
it contains. Region 3 includes dropdown menus for selecting the columns
to be analyzed, a slider to control the number of bootstrapping samples,
and a numeric input box for setting the simulation seed. Region 4
displays the initialization status and offers a button to start the
analysis. Region 5 is empty in the default view but will be populated
with results once the analysis is started.}

\end{figure}%

While the R package \texttt{autovi} aims to provide tools that can be
extended to broader visual inference applications, \texttt{autovi.web}
is only focus on providing a straightforward and clean user interface.
An overview of the graphical user interface of \texttt{autovi.web} is
provided in Figure~\ref{fig-autovi-web}. This is the default view of the
web application, and there are five regions that user can mainly
interact with. Region 1 of Figure~\ref{fig-autovi-web} is a sidebar menu
which can switch between the analysis page and the information page. The
analysis page is the focus of this section.

Region 2 of Figure~\ref{fig-autovi-web} is a panel for data uploading
and CSV type selection. Clicking the ``upload CSV'' button opens a
window where the user can select a file from their local system. The
data status displayed above the button provides information about the
number of rows and columns in the current dataset. Additionally, there
are two example datasets available beneath the ``upload CSV'' button:
one is a lineup example using a CSV file with three columns, and the
other is a single plot example using a CSV file with two columns. More
details about these example datasets are be discussed in
Section~\ref{sec-autovi-web-workflow}.

While the \texttt{autovi} package typically expects a fitted regression
model object provided by the user, this approach is impractical for a
web interface. Saving the R model object to the filesystem involves
extra steps and requires users to have specific knowledge, which does
not align with the goal of the web application. Moreover, the regression
model object may contain sensitive, non-shareable data, making it
unsuitable for uploading. Additionally, model objects are often
unnecessarily large, containing extra information not needed for
residual diagnostics. In contrast, a CSV file is easier to generate
using various software programs, not just R. CSV files are widely
accepted and can be easily viewed and modified using common desktop
applications like Excel. They are generally less sensitive than raw
data, as they exclude most information about the predictors.

The web application is designed to assess either a single residual plot
or a lineup of residual plots. Therefore, it accepts only two types of
CSV files: one with at least two columns representing the fitted values
and residuals of a single residual plot, and another with at least three
columns, where the additional column serves as the label or identifier
for a lineup of multiple residual plots. For a single residual plot, 19
null plots are generated by simulating normal random draws from a
distribution with the same variance as the original residual plot, and
comparisons are made with the original residual plot. For a lineup,
comparisons are made among the plots within the lineup. After uploading
the CSV file, the user must select the correct format to ensure the web
interface interprets the data correctly.

\begin{figure}

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{figures/autovi_web_type.png}

}

\caption{\label{fig-autovi-web-type}The panels for selecting target
columns and simulation settings are updated when a different CSV type is
selected in the left panel. Compared to Figure~\ref{fig-autovi-web},
where the CSV type is a single residual plot, choosing a CSV type that
includes a lineup of multiple residual plots adds a dropdown menu for
specifying a column for the residual plot identifier. Additionally, an
optional dropdown menu for specifying the true residual plot identifier
will appear under the simulation settings.}

\end{figure}%

Region 3 of Figure~\ref{fig-autovi-web} is a panel for column selection
and simulation settings. As shown in Figure~\ref{fig-autovi-web}, if the
CSV type is set to a single residual plot, there will be two dropdown
menus for specifying the columns for fitted values and residuals,
respectively. The default variable names for these columns are
\texttt{.fitted} and \texttt{.resid}. After uploading the CSV file, the
content of these dropdown menus will be updated to reflect the existing
columns in the dataset. As displayed in
Figure~\ref{fig-autovi-web-type}, for the CSV type that is a lineup of
multiple residual plots, an additional dropdown menu will appear for
specifying the column of residual plot labels. The default variable name
for this column is \texttt{.sample}. If this variable name does not
exist in the dataset, the dropdown menu will remain empty, allowing the
user to specify the correct column. The number of levels for each option
in this dropdown menu will be displayed to help avoid the selection of a
variable with too many levels, which could significantly slow down the
application due to extensive computation.

Under the simulation settings, there is a slider for specifying the
number of bootstrapped samples needed for the assessment. A higher value
on this slider will result in a more accurate bootstrap distribution
estimation, though it will require more computation time. The simulation
seed can be set in a numeric input box below the slider to control the
reproducibility of the assessment. By default, a random seed is set each
time the web page is refreshed. When the CSV type is a lineup of
multiple residual plots, an optional dropdown menu will appear next to
the simulation seed input box, allowing the user to specify an
identifier for the true residual plot. If no label is provided for the
true residual plot, the assessment will only estimate the VSS for each
residual plot in the lineup, without providing a \(p\)-value, as it
cannot be computed. Consequently, some result panels may be missing due
to insufficient information. This option is useful when the lineup
consists solely of null plots or if the user simply wants to obtain the
VSS for multiple residual plots.

Region 4 of Figure~\ref{fig-autovi-web} is the panel for triggering the
assessment. It contains a large play button to start the assessment.
Above the play button, a text message displays the status of
\texttt{TensorFlow.js}, allowing users to monitor whether the JavaScript
library and Keras model have been loaded correctly. The play button will
remain disabled until both the data status in Region 1 and the
\texttt{TensorFlow.js} status in Region 4 indicate that everything is
ready, with both showing a green status.

Once the play button is clicked, region 5 of Figure~\ref{fig-autovi-web}
will be populated with panels displaying the assessment results.
Generally, there will be four result panels, as shown in
Figure~\ref{fig-autovi-web-result} and
Figure~\ref{fig-autovi-web-result2}.

\begin{figure}

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{figures/autovi_web_result.png}

}

\caption{\label{fig-autovi-web-result}The first two panels of results
from the automated residual assessment are shown. The application
provides four results panels in total, and these screenshots display the
first two. In region 1, there is an interactive table detailing the VSS,
with a summary of the analysis provided in the paragraph below. Region 2
displays a lineup of residual plots.}

\end{figure}%

\begin{figure}

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{figures/autovi_web_result2.png}

}

\caption{\label{fig-autovi-web-result2}The last two panels of results
from the automated residual assessment are shown. The application
provides four results panels in total, and these screenshots display the
final two. Region 1 presents a density plot comparing the bootstrapped
VSS with the null VSS. Region 2 includes an attention map of the true
residual plot.}

\end{figure}%

\begin{figure}

\centering{

\includegraphics[width=0.5\textwidth,height=\textheight]{figures/autovi_web_gradient_hide.png}

}

\caption{\label{fig-autovi-web-gradient-hide}The attention map is hidden
if the assessment indicates a \(p\)-value greater than 0.05. A button is
available to toggle the display of the attention map.}

\end{figure}%

Region 6 of Figure~\ref{fig-autovi-web-result} contains an interactive
table created with the R package \texttt{DT} \citep{dt}, which provides
the VSS. This table includes four columns: \texttt{.sample},
\texttt{vss}, \texttt{rank}, and \texttt{null}. The \texttt{.sample}
column shows the residual plot labels. For a CSV type that is a lineup,
these labels are taken from an identifier column in the dataset
specified by the user. In the case of the CSV type is a single residual
plot, labels are automatically generated from 1 to 20, with the true
residual plot receiving a randomly assigned label. The \texttt{vss}
column displays the VSS for each residual plot, rounded to three decimal
places. The \texttt{rank} column indicates the ranking of each residual
plot based on VSS. The \texttt{null} column reveals whether the plot is
a null plot. For the CSV type that is a single residual plot, only the
true residual plot will have ``false'' in this column, while all other
plots will be marked ``true.'' For the CSV type that is a lineup, if the
true residual plot identifier has not been provided, this column will
show ``NA'' to represent missing values. If the identifier is provided
by user, the column behaves as if the CSV type is a single residual
plot.

The \texttt{DT} table provides several interactive features. Users can
download the table in four formats, including text, CSV, Excel, and PDF,
using the buttons located above the table. Additionally, the table is
searchable via the text input field also positioned above it. Below the
table, a text message displays the \(p\)-value of the assessment for the
true residual plot and summarizes the number of null plots with VSS
greater than that of the true residual plot. This helps the user
determine whether the true residual plot shows visual patterns that
suggest model violations.

Region 7 of Figure~\ref{fig-autovi-web-result} provides a lineup of
plots corresponding to each \texttt{.sample} value from the table in
Region 6. Due to space limitations, a maximum of 20 residual plots will
be displayed, ensuring that the true residual plot, if known, will be
included in the lineup. The plots are generated using \texttt{ggplot2},
the same as in \texttt{autovi}. Users can perform a visual test with
this lineup to check if the true residual plot is distinguishable from
the other plots, helping to determine the significance of model
violations.

Region 8 of Figure~\ref{fig-autovi-web-result2} displays the density
plot for bootstrapped VSS and null VSS. The densities are shown in
distinct colors that are friendly for colorblind users. A solid vertical
line marks the VSS of the true residual plot, while rug lines at the
bottom of the plot provide a clearer view of individual cases. Below the
plot, a text message indicates the number and percentage of bootstrapped
residual plots that would be rejected by the visual test when compared
to the null plots. Note that the bootstrapped residual plots in this
application are generated differently from \texttt{autovi}. Since we do
not have the R model object, we can not refit the regression model with
bootstrapped data. Instead, we bootstrap the residuals of the true
residual plot directly to obtain bootstrapped residual plots. As as
result, this panel will disappear when the true residual plot is
unknown.

Region 9 of Figure~\ref{fig-autovi-web-result2} displays an attention
map for the true residual plot, generated by computing the gradient of
the Keras model's output with respect to the greyscale input of the
plot. The attention map helps to understand how the Keras model predicts
VSS and which areas it is focusing on. We use a greyscale input because
it is easier to generate a clear attention map in this format, and it
usually conveys all the essential information, as most of the important
details of the plot are drawn in black. If the \(p\)-value of the true
residual plot is greater than 0.05, checking the attention map is not
necessary. However, to provide users with the option to review it if
they wish, a button will be available, as shown in
Figure~\ref{fig-autovi-web-gradient-hide}. This button allows users to
toggle the display of the attention map.

\subsection{Workflow}\label{sec-autovi-web-workflow}

The workflow of \texttt{autovi.web} is designed to be straightforward,
with numbered steps displayed in each panel shown in
Figure~\ref{fig-autovi-web}. There are two example datasets provided by
the web application, as mentioned in
Section~\ref{sec-autovi-web-design}. The single residual plot example
uses the \texttt{dino} dataset from the R package \texttt{datasauRus}
\citep{datasaurus}. The lineup example uses residuals from a simulated
regression model that has a non-linearity issue. We will walk through
the lineup example to further demonstrate the workflow of the web
application.

As shown in Figure~\ref{fig-autovi-web-workflow-example1}, to use the
lineup example data, click the ``Use Lineup Example'' button. The data
status will then update to show the number of rows and columns in the
dataset, and the CSV type will automatically be selected to the correct
option. Since the example dataset follows the variable naming
conventions assumed by the web application, the columns for fitted
values, residuals, and labels of residual plots are set automatically
(Figure~\ref{fig-autovi-web-workflow-example2}). If the user is working
with a custom dataset, these options must be set accordingly. Regardless
of the dataset, the user must manually select the label for the true
residual plot, as the web application allows assessments without this
label. The next step is to click the play button to start the
assessment.

Results are provided in multiple panels as displayed in
Figure~\ref{fig-autovi-web-workflow-example3},
Figure~\ref{fig-autovi-web-workflow-example4},
Figure~\ref{fig-autovi-web-workflow-example5} and
Figure~\ref{fig-autovi-web-workflow-example6}. In
Figure~\ref{fig-autovi-web-workflow-example3}, the first row of the
table is the most crucial to check, as it provides the VSS and the rank
of the true residual plot among the other plots. The summary text
beneath the table provides the \(p\)-value, which can be used for quick
decision-making. In Figure~\ref{fig-autovi-web-workflow-example4}, the
lineup is for manual inspection, and the user should see if the true
residual plot is visually distinguishable from the other plots, to
confirm if the model violation is serious. The density plot in
Figure~\ref{fig-autovi-web-workflow-example5} offers a more robust
result, allowing the user to compare the distribution of bootstrapped
VSS with the distribution of null VSS. Finally, the grayscale attention
map shown in Figure~\ref{fig-autovi-web-workflow-example6} can be used
to check if the target visual features, like the non-linearity present
in the lineup example, are captured by the computer vision model,
ensuring the quality of the assessment.

\begin{figure}

\centering{

\includegraphics[width=0.8\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example1-1.png}

}

\caption{\label{fig-autovi-web-workflow-example1}To begin the workflow
for \texttt{autovi} using the lineup example dataset, the user clicks
the ``Use Lineup Example'' button to load the example dataset, during
which the data status and CSV type will be automatically updated.}

\end{figure}%

\begin{figure}

\centering{

\includegraphics[width=0.8\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example2-1.png}

}

\caption{\label{fig-autovi-web-workflow-example2}After clicking the
button in Figure~\ref{fig-autovi-web-workflow-example1}, the target
columns are selected automatically, though the user must manually select
the label for the true residual plot, as the web application permits
assessment without this label.}

\end{figure}%

\begin{figure}

\centering{

\includegraphics[width=0.55\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example3-1.png}

}

\caption{\label{fig-autovi-web-workflow-example3}After finishing the
required steps in Figure~\ref{fig-autovi-web-workflow-example1} and
Figure~\ref{fig-autovi-web-workflow-example2}, the user initiates the
assessment of the lineup example data by clicking the run button.}

\end{figure}%

\begin{figure}

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example4-1.png}

}

\caption{\label{fig-autovi-web-workflow-example4}The VSS of the true
residual plot is displayed in the first row of the table, with a summary
text beneath the table providing the \(p\)-value to aid in
decision-making.}

\end{figure}%

\begin{figure}

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example5-1.png}

}

\caption{\label{fig-autovi-web-workflow-example5}A lineup of residual
plots allows for manual inspection.}

\end{figure}%

\begin{figure}

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example6-1.png}

}

\caption{\label{fig-autovi-web-workflow-example6}The density plot helps
verify if the bootstrapped distribution differs from the null
distribution.}

\end{figure}%

\begin{figure}

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example7-1.png}

}

\caption{\label{fig-autovi-web-workflow-example7}The attention map
offers insights into whether the computer vision model has captured the
intended visual features of the true residual plot.}

\end{figure}%

\section{Conclusions}\label{sec-autovi-conclusion}

This paper presents new regression diagnostics software, the R package
\texttt{autovi} and its accompanying web interface package,
\texttt{autovi.web}. It addresses a critical gap in the current
landscape of statistical software. While regression tools are widely
available, effective and efficient diagnostic methods have lagged
behind, particularly in the field of residual plot interpretation.

The \texttt{autovi} R package, introduced in this paper, automates the
assessment of residual plots by incorporating a computer vision model,
eliminating the need for time-consuming and potentially inconsistent
human interpretation. This automation improves the efficiency of the
diagnostic process and promotes consistency in model evaluation across
different users and studies.

The development of the accompanying Shiny app, \texttt{autovi.web},
expands access to these advanced diagnostic tools, by providing a
user-friendly interface. It makes automated residual plot assessment
accessible to a broader audience, including those who may not have
extensive programming experience. This web-based solution effectively
addresses the potential barriers to adoption, such as complex
dependencies and installation requirements, that are often associated
with advanced statistical software.

The combination of \texttt{autovi} and \texttt{autovi.web} offers a
comprehensive solution to the challenges of residual plot interpretation
in regression analysis. These tools have the potential to significantly
improve the quality and consistency of model diagnostics across various
fields, from academic research to industry applications. By automating a
critical aspect of model evaluation, they allow researchers and analysts
to focus more on interpreting results and refining models, rather than
grappling with the intricacies of plot assessment.

The framework established by \texttt{autovi} and \texttt{autovi.web}
opens up exciting possibilities for further research and development.
Future work could explore the extension of these automated assessment
techniques to other types of diagnostic plots and statistical models,
potentially revolutionizing how we approach statistical inference using
visual displays more broadly.

\section{Availability}\label{availability}

The web interface is housed at \url{autoviweb.netlify.app}.

The the current version of \texttt{autovi} can be installed from CRAN,
and source code for both packages are available at
\url{https://github.com/TengMCing/}.

  \bibliography{bibliography.bib}

\end{document}

### 2024-11-11 paper.qmd
tidy up

--- 2024-11-11 autovi_paper.qmd
@@
 ---
-title: "Software for Automated Residual Plot Assessment: autovi and autovi.web"
-subtitle: ANZJS Quarto Template
-format:
-  quarto-anzjs-pdf:
-    keep-tex: true  
-    shorttitle: "Software for Automated Residual Plot Assessment"
-    double-space: true
-    line-numbers: true
-    # You can specify extra preamble in the file below.
-    include-in-header:
-      - template-header.tex
-date: today
-date-format: "YYYY" # used to define volumeyear
-author:
-  - name: Weihao Li
-    email: weihao.li@monash.edu
-    corresponding: true
-    affiliations:
-      - name: Monash University
-        department: Department of Econometrics and Business Statistics
-        address: Wellington Road, VIC 3800, Australia
-    orcid: 0000-0003-4959-106X
-  - name: Dianne Cook
-    email: dicook@monash.edu 
-    affiliations:
-      - name: Monash University
-        department: Department of Econometrics and Business Statistics
-        address: Wellington Road, VIC 3800, Australia
-    orcid: 0000-0002-3813-7155
-  - name: Emi Tanaka
-    email: emi.tanaka@anu.edu.au
-    affiliations: 
-      - name: The Australian National University
-        department: Biological Data Science Institute
-        address: 46 Sullivan's Creek Road, ACT 2600, Australia
-    orcid: 0000-0002-1455-259X
-  - name: Susan VanderPlas
-    email: emi.tanaka@anu.edu.au
-    affiliations:
-      - name: University of Nebraska
-        department: Department of Statistics
-        address: Hardin Hall, 3310 Holdrege St Suite 340, Lincoln, NE 68583, United States
-    orcid: 0000-0002-3803-0972
-  - name: Klaus Ackermann
-    email: Klaus.Ackermann@monash.edu 
-    affiliations:
-      - name: Monash University
-        department: Department of Econometrics and Business Statistics
-        address: Wellington Road, VIC 3800, Australia
-    orcid: 0000-0001-7693-8538
-# Note that the Journal requires that a paper must begin with a
-# "Summary" not an "Abstract".  This is automatically taken care
-# of by the anzsauth document style.  So even though the following
-# says "abstract" the heading "Summary" will appear in
-# the processed version.
-abstract: |
+
+---
+
+# Software for Automated Residual Plot Assessment: autovi and autovi.web {#sec-third-paper}
+
 Regression software is widely available today, but tools for effective diagnostics are still lagging.
@@
 For a user-provided sample of residuals, it predicts a measure of visual signal strength (VSS) and provides a suite of supporting information to assist the analyst diagnose their model fit.
-# Below shows how acknowledgements should appear in the Journal.
-# Note that if you are acknowledging financial support, grant
-# numbers should *not* usually be specified.
-acknowledgement: >
-  The author acknowledges that this template is based on the latex template for Australian and New Zealand Journal of Statistics and intersperses some text from the original prototype document.
-\newline\vspace{1ex}\newline
-  Opinions and attitudes expressed in this document,
-  which are not explicitly designated as Journal policy, are those of
-  the author and are _not_ necessarily endorsed by the Journal,
-  its editorial board, its publisher Wiley or by the Australian
-  Statistical Publishing Association Inc.
-# Note that "keywords" should not include words and phrases
-# that form part of the title of the paper.
-# Also keywords (with the exception of proper names and
-# certain abbreviations that conventionally appear all in
-# capital letters) should *not* be capitalised.
-keywords: [statistical software, statistical graphics, data visualization, visual inference, computer vision, machine learning, hypothesis testing, reression analysis]
-bibliography: bibliography.bib  
-#nocite: |
-# @PussyRiot2014, @Nixon1984, @Turner2017, @Brillinger2007
----
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-  message = FALSE, 
-  warning = FALSE, 
-  echo = FALSE,
-  fig.width = 8,
-  fig.height = 6,
-  out.width = "100%", 
-  fig.align = "center")
-```
-
-# Introduction {#sec-autovi-introduction}
+## Introduction {#sec-autovi-introduction}
 
@@
 Deviations that might be observed from a residual plot are non-normality, heteroscedasticity, and other associations with the fitted values.
-In @li2024plot, we demonstrated that visual methods for assessing residuals are advantageous over conventional tests due to their reduced sensitivity to minor departures.
-Building on this, @li2024automated introduced a computer vision model aimed at alleviating the human effort required for visual assessment of residual plots.
+@sec-first-paper established that visual methods for assessing residuals are superior to conventional testing in that they are not so sensitive to small departures.
+@sec-second-paper provides a computer vision model to alleviate the human labor needed to visually assessing residual plots.
 The next step is to deliver the use of the computer vision model to potential users, so that it can be widely used to the benefit of the analytics community.
@@
 The Comprehensive R Archive Network (CRAN) [@hornik2012comprehensive] hosts a vast array of packages, many of which provide tools to diagnose models using residual plots.
-These packages can be broadly categorized into three groups: general-purpose, enhanced visual diagnostics, and visual diagnostics with statistical testing.
+These packages can be broadly categorized into three groups: general purpose, enhanced diagnostics, diagnostics with statistical testing.
 
-General-purpose regression analysis tools are the most widely used group of packages.
-While not specifically designed for graphical diagnostics of residuals in linear regression, they include this functionality as part of a broader suite of statistical tools.
-For example, the `stats` package [@stats] offers standard diagnostic plots such as residuals vs.
-fitted values, quantile-quantile (Q-Q) plots, and residuals vs.
-leverage plots.
-Additional packages like `jtools` [@jtools], `olsrr` [@olsrr], `rockchalk` [@rockchalk], and `ggResidpanel` [@ggresidpanel] provide similar graphical diagnostics, often with alternative aesthetics or interactive features.
-All of these tools deliver the types of diagnostic plots outlined in the classical text by @cook1982residuals.
-However, as discussed in @li2024plot, relying solely on subjective assessments of these plots can lead to issues, such as over-interpreting random patterns as model violations.
+General-purpose regression analysis tools are the largest and most commonly used group.
+These packages are not specifically designed for graphical diagnostics of residuals in linear regression but offer this functionality as part of a broader set of statistical tools.
+These include the `stats` package [@stats], which includes common diagnostic plots like residuals vs fitted values, quantile-quantile (Q-Q) plots, and residuals vs leverage plots.
+Other packages such as `jtools` [@jtools], `olsrr` [@olsrr], `rockchalk` [@rockchalk], and `ggResidpanel` [@ggresidpanel] provide similar graphical tools with alternative aesthetic styles or interactive features.
+They all fundamentally deliver diagnostic plots as outlined in the classic text @cook1982residuals.
+<!-- However, consistently drawing accurate conclusions from these tools can be challenging due to individual differences in interpreting statistical graphics.--> As noted in @li2024plot, relying solely on subjective assessments of data plots can lead to problems, such as over-interpreting random patterns as model violations.
 
-The second group consists of enhanced visual diagnostics tools, which provide advanced aids for interpreting diagnostic plots.
-For instance, `ecostats` [@warton_global_2023] incorporates simulation envelopes into residual plots, while `DHARMa` [@dharma] compares empirical quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical counterparts.
-`DHARMa` is particularly focused on detecting model violations such as heteroscedasticity, incorrect functional forms, and issues specific to generalized linear and mixed-effect models, like over/under-dispersion.
-It also includes annotations from conventional tests, displayed as labels or text within the plot, to help avoid misinterpretation.
+Enhanced visual diagnostics forms the second group, which offer advanced visual aids for interpreting diagnostic plots.
+This includes `ecostats` [@warton_global_2023], which adds simulation envelopes to  residual plots, and `DHARMa` [@dharma], which compares the empirical 0.25, 0.5, and 0.75 quantiles in scaled residuals with their theoretical counterparts.
+`DHARMa`'s focus is detecting model violations such as heteroscedasticity and incorrect functional forms, and uncovering issues specific to generalized linear models and mixed-effect models, like over/under-dispersion.
+<!--By offering these enhanced visualizations, `DHARMa` enables users to more easily identify potential issues in their regression models that might not be immediately apparent with standard diagnostic plots.
+In summary, this group of packages enhances the interpretability of diagnostic plots by drawing attention to critical elements such as trends, clusters, and outliers.--> It also adds results from conventional tests as annotations, labels, or text within the plot, to assist in avoiding misinterpretation.
 
-The third group, visual diagnostics with statistical testing, offers tools for formally testing patterns observed in diagnostic plots [@buja2009statistical].
-A common method for visual testing of residual plots is the lineup protocol, where the true residual plot is embedded within a set of null plots generated by simulating residuals under the null hypothesis $H_0$ that the regression model is correctly specified.
-Observers are asked to identify the plot that appears most different from the others.
-If a significant proportion of observers correctly identify the true residual plot, it provides evidence against $H_0$, as the true residual plot should be indistinguishable from the null plots if all residuals are generated by the same process, according to @buja2009statistical.
-Packages in this group, such as `nullabor` [@nullabor], `HLMdiag` [@loy2014hlmdiag], and `regressinator` [@regressinator], enable users to compare observed residual plots with samples from null distributions, helping to quantify the significance of any detected patterns.
+Statistical testing for visual discoveries is the third group, which focuses on providing tools for conducting formal statistical tests for visual discoveries obtained from diagnostic plots [@buja2009statistical].
+Packages include the `nullabor` [@nullabor] `HLMdiag` [@loy2014hlmdiag] and `regressinator` [@regressinator].
+These enables users to compare the actual residual plot with samples from null distributions, and can help quantify the significance of patterns.
+<!--This approach addresses the issue of inconsistent interpretation of diagnostic plots by bridging the gap between visual inspection and formal statistical inference, thus offering a more robust framework for regression diagnostics.
 
-However, as discussed in @li2024automated, the lineup protocol has significant limitations in large-scale applications due dependence on human labor.
+Conducting a visual test for a residual plot, which is among the most common diagnostic plots in regression analysis, involves using a lineup protocol.
+In this protocol, the true residual plot is embedded within a lineup of several null plots and presented to one or more observers.
+The null plots are created by simulating residuals consistent with the null hypothesis $H_0$ that the regression model is correctly specified.
+Observers are then asked to identify the plot that appears most different from the others.
+If a significant percentage of observers correctly identify the true residual plot, it provides evidence against the $H_0$, as according to @buja2009statistical, the true residual plot would have no distinguishable difference from the null plots if all residuals are generated by the same process.-->
+
+However, as discussed in @sec-second-paper, the lineup protocol has significant limitations in large-scale applications due dependence on human labor.
 Thus a computer vision model was developed with an associated statistical testing procedure to automate the assessment of residual plots.
@@
 
+<!--By estimating the visual signal strength for all plots in a lineup, we can compute a $p$-value based on the ratio of plots with visual signal strength greater than or equal to that of the true residual plot.
+This $p$-value has a lower bound of one divided by the number of plots in the lineup.
+Additionally, we can construct a null distribution of visual signal strength using the strengths of null plots.
+
+We can also apply bootstrapping to obtain a distribution of visual signal strengths.
+This involves bootstrapping the data used to fit the linear regression model, refitting the model to obtain bootstrapped residuals, and then using the computer vision model to predict visual signal strength for these residuals.
+The resulting bootstrapped distribution can be compared against the null distribution.
+If these distributions are largely similar, it suggests that the bootstrapped residual plots are similar to the null plots.
+The proportion of bootstrapped visual signal strengths exceeding a critical value (such as the 95% sample quantile of the null distribution) indicates how often the assumed regression model would be considered incorrect if the data could be repeatedly obtained from the same data-generating process.-->
+
 To make the statistical testing procedure and trained computer vision model widely accessible, we developed the R package `autovi`, and a web interface, `autovi.web` to make it easy for users to automatically read their residual plots with the trained computer vision model.
 
-The remainder of this paper is structured as follows: @sec-autovi provides a detailed documentation of the `autovi` package, including its usage and infrastructure.
+The remainder of this chapter is structured as follows: @sec-autovi provides a detailed documentation of the `autovi` package, including its usage and infrastructure.
 @sec-autovi-web focuses on the `autovi.web` interface, describing its design and usage, along with illustrative examples.
@@
 
-# R package: autovi {#sec-autovi}
+## R package: autovi {#sec-autovi}
 
@@
 
-## Implementation {#sec-autovi-implementation}
+### Implementation {#sec-autovi-implementation}
 
-The `autovi` package is built on the `bandicoot` object-oriented programming (OOP) system [@bandicoot], marking a departure from R’s traditional S3 generic system.
-This OOP architecture enhances flexibility and modularity, allowing users to redefine key functions through method overriding.
-While similar functionality could be achieved using R’s S3 system with generic functions, the OOP framework offers a more structured and extensible foundation for the package.
+The package `autovi` is built upon the `bandicoot` object-oriented programming (OOP) system [@bandicoot], which marks a departure from R's conventional S3 generic system.
+The adoption of an OOP architecture enhances flexibility and modularity, enabling users to redefine key functions within the infrastructure through method overriding.
+While similar functionality could be replicated using R's S3 system with generic functions, the OOP system offers a more structured and extensible foundation for the package.
 
-The `autovi` infrastructure effectively integrates multiple programming languages and libraries into a comprehensive analytical tool.
-It relies on five core libraries from Python and R, each playing a critical role in the analysis pipeline.
-In Python, `pillow` [@clark2015pillow] handles image processing tasks such as reading and resizing PNG files of residual plots, then converting them into input tensors for further analysis.
-The `TensorFlow` [@abadi2016tensorflow] library, a key component of modern machine learning, is used to predict the VSS of these plots through a pre-trained convolutional neural network.
+The infrastructure of `autovi` demonstrates the effective integration of multiple programming languages and libraries to create a comprehensive analytical tool.
+It depends on five core libraries from Python and R, each contributing critically to the analysis pipeline.
+In Python, `pillow` [@clark2015pillow] handles image processing tasks, including reading PNG files of residual plots, resizing them, and converting them into input tensors for further analysis.
+The `TensorFlow` [@abadi2016tensorflow] library, a cornerstone of contemporary machine learning, is employed to predict the VSS of these residual plots, utilizing a pre-trained convolutional neural network.
 
-In the R environment, `autovi` utilizes several libraries.
-`ggplot2` [@ggplot2] generates the initial residual plots, saved as PNG files for visual input.
-The `cassowaryr` [@mason2022cassowaryr] library computes scagnostics (scatter plot diagnostics), providing numerical features that capture statistical properties of the plots.
-These scagnostics complement the visual analysis by offering quantitative metrics as secondary input to the computer vision model.
-The `reticulate` [@reticulate] package bridges R and Python, enabling seamless communication between the two languages and supporting the integrated infrastructure.
+Within the R environment, `autovi` utilizes several libraries.
+`ggplot2` [@ggplot2] is employed to generate the initial residual plots, which are then saved as PNG files, using as the primary visual input for the analysis.
+The `cassowaryr` [@mason2022cassowaryr] library calculates scagnostics (scatter plot diagnostics) of the residual plots, providing numerical features that capture various statistical properties of the plots.
+These scagnostics complement the visual analysis by supplying quantitative metrics as secondary input to the computer vision model.
+The `reticulate` [@reticulate] package is used to bridge R and Python, allowing for seamless communication between the two languages and supporting an integrated infrastructure.
 
-## Installation
+### Installation
 
@@
 It is actively developed and maintained, with the latest updates accessible on GitHub at [https://github.com/TengMCing/autovi](https://github.com/TengMCing/autovi).
-The code discussed in this paper is based on `autovi` version 0.4.1.
+The code discussed in this chapter is based on `autovi` version 0.4.1.
 
@@
 
-## Usage {#sec-autovi-usage}
+### Usage {#sec-autovi-usage}
 
-To get started quickly, only three function calls are needed to obtain a summary of the automated residual assessment:
+To get started quickly, only calls three functions are necessary to obtain a summary of the automated residual assessment:
 
@@
 library(autovi) 
-checker <- residual_checker(lm(dist ~ speed, data = cars))
+checker <- residual_checker(fitted_model = lm(dist ~ speed, data = cars))
 checker$check() 
@@
 
-The three functions are explained as follows:
-
-1. Load the `autovi` package using the `library()` function.
-2. Create a checker object with a linear regression model.
+1. Load the package using the `library()` function.
+2. Construct a checker with a linear regression model.
 3.
-Call the `check()` method of the checker, which, by default, predicts the VSS for the true residual plot, 100 null plots, and 100 bootstrapped plots, storing the predictions internally.
-A concise report of the check results is then printed.
+Call the `check()` method of the checker with default arguments.
+This predicts the VSS for the true residual plot, 100 null plots, and 100 bootstrapped plots, storing the predictions internally.
+A concise report of the check results will be printed.
 
@@
 
-## Modularized Infrastructure {#sec-autovi-infrastructure}
+### Modularized Infrastructure {#sec-autovi-infrastructure}
 
@@
 
-The initial motivation for developing `autovi` was to create a convenient interface for sharing the models described and trained in @li2024automated.
+The initial motivation for developing `autovi` was to create a convenient interface for sharing the models described and trained in @sec-second-paper.
 However, recognizing that the classical normal linear regression model represents a restricted class of models, we sought to avoid limiting the potential for future extensions, whether by the original developers or other users.
@@
 Each module is designed with minimal dependency on the preceding modules, allowing users to customize parts of the infrastructure without affecting its overall integrity.
-An overview of this infrastructure is illustrated in @fig-autovi-diag.
+An overview of this infrastructure is illustrated in Figure @fig-autovi-diag.
 
@@
 
-### Initialization
+#### Initialization
 
@@
 The `residual_checker()` introduced in @sec-autovi-usage is a thin wrapper around `auto_vi()`, which will call `get_keras_model()` during initialization.
-`get_keras_model()` is a function to download a trained computer vision model (described in @li2024automated) from GitHub.
+`get_keras_model()` is a function to download a trained computer vision model (described in @sec-second-paper) from GitHub.
 “vss_phn_32” specifies a model that predicts VSS and is trained on residuals with polynomial, heteroskedasticity, and non-normality patterns (phn).
@@
 
-The input of the constructor will be stored as attributes of the checker and can be accessed by the user through the `$` operator.
+The input of the constructor will be stored in the checker and can be accessed by the user through the `$` operator.
 
@@
 
-### Fitted Values and Residuals Extraction
+#### Fitted Values and Residuals Extraction
 
@@
 
-### Data Extraction
+#### Data Extraction
 
@@
 
-### Bootstrapping and Model Refitting
+#### Bootstrapping and Model Refitting
 
@@
 
-### Auxiliary Computation
+#### Auxiliary Computation
 
-As described in @li2024automated, in some cases, a residual plot alone may not provide enough information to accurately determine VSS.
+As described in @sec-second-paper, in some cases, a residual plot alone may not provide enough information to accurately determine VSS.
 For instance, when the points in the residual plot have significant overlap, the trend and shape of the residual pattern can be difficult to discern.
@@
 These columns represent four scagnostics — "Monotonic", "Sparse", "Striped", and "Splines" — calculated using the `cassowaryr` package, as well as the number of observations.
-This approach is consistent with the training process of the computer vision models described in @li2024automated.
+This approach is consistent with the training process of the computer vision models described in @sec-second-paper.
 If no `data.frame` is provided, the method will default to retrieving fitted values and residuals by calling `get_fitted_and_resid()`.
@@
 
-### Null Residual Simulation {#sec-autovi-null-method}
+#### Null Residual Simulation {#sec-autovi-null-method}
 
-A fundamental element of the automated residual assessment described in @li2024automated is comparing the VSS of null plots with that of the true residual plot.
+A fundamental element of the automated residual assessment described in @sec-second-paper is comparing the VSS of null plots with that of the true residual plot.
 However, due to the variety of regression models, there is no universal method for simulating null residuals that are consistent with model assumptions.
@@
 
-### Plotting
+#### Plotting
 
@@
 Additionally, it includes four Boolean arguments to toggle the display of axes, legends, grid lines, and a horizontal red line.
-By default, it replicates the style we used to generate the training samples for the computer vision models described in @li2024automated.
+By default, it replicates the style we used to generate the training samples for the computer vision models described in @sec-second-paper.
 In brief, the residual plot omits axis text and ticks, titles, and background grid lines, featuring only a red line at $y = 0$.
@@
 
-### Plot Saving
+#### Plot Saving
 
 Another key aspect of a standardized residual plot is its resolution.
-In @li2024automated, we used an image format of 420 pixels in height and 525 pixels in width.
+In @sec-second-paper, we used an image format of 420 pixels in height and 525 pixels in width.
 This resolution was chosen because the original set, consisting of 20 residual plots arranged in a four by five grid, was represented by an image of 2100 by 2100 pixels.
@@
 
-### Image Reading and Resizing
+#### Image Reading and Resizing
 
@@
 
-### Visual Signal Strength (VSS) Prediction
+#### Visual Signal Strength (VSS) Prediction
 
-VSS, as discussed in @li2024automated, estimates the distance between the input residual plot and a theoretically good  residual plot.
+VSS, as discussed in @sec-second-paper, estimates the distance between the input residual plot and a theoretically good  residual plot.
 It can be defined in various ways, much like different methods for measuring the distance between two points.
@@
 
-### $p$-value Computation
+#### $p$-value Computation
 
@@
 
-## Summary Plots
+You can also check the $p$-value by printing the checker, which includes it in the summary report.
+
+```{r echo=TRUE, message=TRUE}
+checker
+```
+
+### Summary Plots
 
@@
 
-```{r fig-autovi-rank-plot, echo=TRUE, fig.cap = "Rank plot of the VSS for null plots."}
+```{r fig-autovi-rank-plot, echo=TRUE, fig.cap = "Density plot of the VSS for null plots."}
 checker$summary_plot(type = "rank")
@@
 
-## Feature Extraction
+### Feature Extraction
 
@@
 
-## Trained Model Hosting {#sec-trained-model-hosting}
+### Trained Model Hosting {#sec-trained-model-hosting}
 
-The trained computer vision models described in @li2024automated are hosted on a GitHub repository at [https://github.com/TengMCing/autovi_data](https://github.com/TengMCing/autovi_data).
+The trained computer vision models described in @sec-second-paper are hosted on a GitHub repository at [https://github.com/TengMCing/autovi_data](https://github.com/TengMCing/autovi_data).
 Currently, there are six models available.
@@
 
-```{r echo = TRUE}
-list_keras_model() |>
-  str()
+```{r}
+list_keras_model()
 ```
@@
 
-# Web interface: autovi.web {#sec-autovi-web}
+## Web interface: autovi.web {#sec-autovi-web}
 
-The `autovi.web` package extends the functionality of `autovi` by offering a user-friendly web interface for automated residual plot assessment.
-This eliminates the common challenges associated with software installation, so users can avoid managing Python environments or handling version requirements for R libraries.
-The platform is cross-platform and accessible on various devices and operating systems, making it suitable even for users without R programming experience.
-Additionally, updates are managed centrally, ensuring that users always have access to the latest features.
+The web interface package, called `autovi.web`, builds on `autovi`, and makes it easier for users easier to do automated residual plot assessment.
+It eliminates software installation issues, so users no longer need to struggle with managing Python environments or installing and maintaining the correct versions of R libraries.
+The interface is cross-platform, accessible on different devices and operating systems, and for users without R programming knowledge.
+The additional benefit is that updates can be controlled centrally so that users will always have the latest features.
 
-The `autovi.web` interface is available at [autoviweb.netlify.app](autoviweb.netlify.app). This section discusses the implementation based on `autovi.web` version 0.1.0.
+The web interface `autovi.web` is available at [autoviweb.netlify.app](autoviweb.netlify.app). The implementation discussed in this chapter is based on `autovi.web` version 0.1.0.
 
-## Implementation
+### Implementation
 
@@
 In our initial planning for `autovi.web`, we considered implementing the entire web application using the `webr` framework [@webr], which would have allowed the entire application to run directly in the user's browser.
-However, this approach was not feasible at the time of writing this paper.
+However, this approach was not feasible at the time of writing this chapter.
 The reason is that one of the R packages `autovi` depends on the R package `splancs` [@splancs], which uses compiled Fortran code.
@@
 
-## Design {#sec-autovi-web-design}
+### Design {#sec-autovi-web-design}
 
@@
 
-## Workflow {#sec-autovi-web-workflow}
+### Workflow {#sec-autovi-web-workflow}
 
@@
 
-# Conclusions {#sec-autovi-conclusion}
+## Conclusions {#sec-autovi-conclusion}
 
-This paper presents new regression diagnostics software, the R package `autovi` and its accompanying web interface package, `autovi.web`.
+This chapter presents new regression diagnostics software, the R package `autovi` and its accompanying web interface package, `autovi.web`.
 It addresses a critical gap in the current landscape of statistical software.
@@
 
-The `autovi` R package, introduced in this paper, automates the assessment of residual plots by incorporating a computer vision model, eliminating the need for time-consuming and potentially inconsistent human interpretation.
+The `autovi` R package, introduced in this chapter, automates the assessment of residual plots by incorporating a computer vision model, eliminating the need for time-consuming and potentially inconsistent human interpretation.
 This automation improves the efficiency of the diagnostic process and promotes consistency in model evaluation across different users and studies.
@@
 
-# Availability
+## Availability
 

### 2024-11-17 autovi_paper.qmd
added new section to motivate and changed availability section to resources and supplementary

@@
 # capital letters) should *not* be capitalised.
-keywords: [statistical software, statistical graphics, data visualization, visual inference, computer vision, machine learning, hypothesis testing, reression analysis]
+keywords: [initial data analysis, statistical graphics, data visualization, visual inference, computer vision, machine learning, hypothesis testing, regression analysis]
 bibliography: bibliography.bib  
 #nocite: |
-# @PussyRiot2014, @Nixon1984, @Turner2017, @Brillinger2007
 ---
@@
 The name `autovi` stands for automated visual inference.
-While initially designed for linear regression residual diagnostics, it has the potential to be extended to broader visual inference applications, as we discuss in section @sec-autovi-infrastructure.
+<!--While initially designed for linear regression residual diagnostics, it has the potential to be extended to broader visual inference applications, as we discuss in section @sec-autovi-infrastructure.-->
+
+There are two ways to access the package, directly using R or through a web interface, `autovi.web`.
+The web interface has the advantage that it can be used without installing Python, R and the relevant packages locally.
+
+## Why use it {#sec-why}
+
+@fig-three-examples shows three sets of plots of residuals against fitted values.
+The simulated example in (a) might be interpreted as a heteroskedastic pattern, however the automated reading would predict this to have a visual signal strength (VSS) of 1.53, with a corresponding $p$-value of 0.25.
+This means it is would be interpreted as a good residual plot, that there is nothing in the data to indicate a violation of model assumptions.
+Skewness in the predictor variables is generating the apparent heteroskedasticity, where the smaller variance in residuals at larger fitted values is due to smaller sample size only.
+The Breusch-Pagan test  [@breusch1979simple] for heteroskedasticity would also not reject this as good residual plot.
+
+The data in (b) is generated by fitting a linear model predicting `mpg` based on `hp` using the `datasets::mtcars`.
+It is a small data set, and there is a hint of nonlinear structure not captured by the model.
+The automated plot reading would predict a VSS of 3.57, which has a $p$-value less than 0.05.
+That is, the nonlinear structure is most likely real, and indicates a problem with the model.
+The conventional test, a Ramsey Regression Equation Specification Error Test (RESET) [@ramsey1969tests] would also strongly detect the nonlinearity.
+
+The third example is generated using the `surreal` package [@surreal] where structured residuals are hidden in data, to be revealed if the correct model is specified.
+Here a quote based on Tukey is used as the residual structure "visual summaries focus on unexpected values".
+The automated plot reading predicts the VSS to be 5.87, with a $p$-value less than 0.05.
+This structure is blindingly obvious visually, but a RESET test for nonlinear structure would not report a problem.
+(It would be detected by a Breusch-Pagan for heteroskedasticity and also Shapiro-Wilk test [@shapiro1965analysis] for non-normality.)
+
+```{r}
+#| label: three-examples
+#| fig-cap: "Reading residual plots can be a difficult task, particular for students new to statistical modeling.
+The autovi package makes it easier.
+Here are three examples of residual plots, which may appear to have structure.
+According to autovi, the visual signal strengths (VSS) of these three examples are approximately (a) 1.53, (b) 3.57, (c) 5.87, resulting in (b), (c) being significant violations of good residuals, but (a) is consistent with a good residual plot."
+#| fig-width: 9
+#| fig-height: 3
+#| out-width: 100%
+library(readr)
+library(dplyr)
+library(ggplot2)
+library(patchwork)
+library(ggthemes)
+
+test_resid <- read_csv("residuals/test_resid.csv")
+p1 <- ggplot(test_resid, aes(x=.fitted, y=.resid)) +
+  geom_hline(yintercept=0, colour="red") + 
+  geom_point() + 
+  ggtitle("a. simulated") +
+  theme_base(base_size = 12) + 
+  theme(aspect.ratio = 1.1, 
+        axis.text = element_blank(),
+        axis.title = element_blank(),
+        axis.ticks = element_blank(),
+        plot.background = element_rect(fill = NA, 
+                                       colour = NA))
+
+mtcars_all2 <- read_csv("residuals/mtcars_all2.csv")
+p2 <- ggplot(mtcars_all2, aes(x=.fitted, y=.resid)) +
+  geom_hline(yintercept=0, colour="red") + 
+  geom_point() + 
+  ggtitle("b. mtcars") +
+  theme_base(base_size = 12) + 
+  theme(aspect.ratio = 1.1, 
+        axis.text = element_blank(),
+        axis.title = element_blank(),
+        axis.ticks = element_blank(),
+        plot.background = element_rect(fill = NA, 
+                                       colour = NA))
+
+sur_all <- read_csv("residuals/sur_all.csv")
+p3 <- ggplot(sur_all, aes(x=.fitted, y=.resid)) +
+  geom_hline(yintercept=0, colour="red") + 
+  geom_point() + 
+  ggtitle("c. surreal") +
+  theme_base(base_size = 12) + 
+  theme(aspect.ratio = 1.1, 
+        axis.text = element_blank(),
+        axis.title = element_blank(),
+        axis.ticks = element_blank(),
+        plot.background = element_rect(fill = NA, 
+                                       colour = NA))
+
+p1 + p2 + p3 + plot_layout(ncol=3)
+```
 
@@
 
-# Availability
-
-The web interface is housed at [autoviweb.netlify.app](autoviweb.netlify.app).
-
-The the current version of `autovi` can be installed from CRAN, and source code for both packages are available at [https://github.com/TengMCing/](https://github.com/TengMCing/).
+# Resources and Supplementary Material
+
+The the current version of `autovi` can be installed from CRAN, and source code for both packages are available at [https://github.com/TengMCing/autovi](https://github.com/TengMCing/autovi).
+The web interface is available from [autoviweb.netlify.app](autoviweb.netlify.app).
+
+These `R` packages were used for the work: `tidyverse` [@tidyverse], `lmtest` [@lmtest], `kableExtra` [@kableextra], `patchwork` [@patchwork], `rcartocolor` [@rcartocolor], `glue` [@glue],  `here` [@here], `magick` [@magick], `yardstick` [@yardstick] and `reticulate` [@reticulate].

### 2024-11-17 autovi_paper.qmd
adjusted abstract

@@
 abstract: |
-  Regression software is widely available today, but tools for effective diagnostics are still lagging.
-Perhaps, one of the reasons is that it is hard.
-Conventional tests, that would make the task easy, are often too sensitive, which would result in adequate models being abandoned if the analyst strictly adhered to the test decision.
-The recommended advice is to have the analyst assess the strength of patterns in residual plots.
-This requires human effort and also suffers from the potential for inconsistent decisions from different analysts.
-Using a lineup protocol can help to alleviate inconsistency, but requires even more human effort.
-This is the type of task where a robot might be employed to do the disagreeable work that currently requires a human.
+  Regression software is widely available, and there are many tools for generating diagnostics and computing conventional residual tests.
+However, the advice remains that the analyst should look at the residual plot to check the fit.
+Perhaps, one of the reasons is that conventional tests are too sensitive, strictly resulting in adequate models being abandoned.
+Visually assess the strength of patterns in residual plots requires human effort and suffers from the potential for inconsistent decisions from different analysts.
+Using a lineup protocol, where the residual plot is embedded among null plots, can help to alleviate inconsistency, but requires even more human effort.
+This is the type of task that in today's world might employ a robot to do the tedious work for a human.
 Here we describe a new R package that includes a computer vision model for automated assessment of residual plots, and an accompanying Shiny app for ease of use.
-For a user-provided sample of residuals, it predicts a measure of visual signal strength (VSS) and provides a suite of supporting information to assist the analyst diagnose their model fit.
+For a user-provided sample of residuals, it predicts a measure of visual signal strength (VSS) and provides a suite of supporting information to assist the analyst decide on the appropriateness their model fit.
 # Below shows how acknowledgements should appear in the Journal.

### 2024-11-18 autovi_paper.qmd
reduced intro

@@
 
-Regression analysis is a fundamental statistical technique widely used for modeling data from many fields.
-To diagnose the fit of a model it is recommended that the residuals are plotted.
+Regression analysis is a widely used statistical modeling technique widely for data in many fields.
+There are a vast array of software for conducting regression modeling and generating diagnostics.
+The package `lmtest` [@lmtest] provides a suite of conventional tests.
+The `stats` package [@stats] offers standard diagnostic plots such as residuals vs.
+fitted values, quantile-quantile (Q-Q) plots, and residuals vs.
+leverage plots.
+Packages like `jtools` [@jtools], `olsrr` [@olsrr], `rockchalk` [@rockchalk], and `ggResidpanel` [@ggresidpanel] provide similar graphical diagnostics, often with alternative aesthetics or interactive features.
+All of these tools deliver the types of diagnostic plots outlined in the classical text by @cook1982residuals.
+The `ecostats` package [@warton_global_2023] incorporates simulation envelopes into residual plots, while `DHARMa` [@dharma] compares empirical quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical counterparts.
+`DHARMa` is particularly focused on detecting model violations such as heteroscedasticity, incorrect functional forms, and issues specific to generalized linear and mixed-effect models, like over/under-dispersion.
+It also includes conventional test annotations to help avoid misinterpretation.
+
+<!-- However, as discussed in @li2024plot, relying solely on subjective assessments of these plots can lead to issues, such as over-interpreting random patterns as model violations. -->
+
+<!-- To diagnose the fit of a model it is recommended that the residuals are plotted.
 If the fit is good, any variation remaining should be noise, consistent with sampling from a distribution specified by the error model.
-Deviations that might be observed from a residual plot are non-normality, heteroscedasticity, and other associations with the fitted values.
-In @li2024plot, we demonstrated that visual methods for assessing residuals are advantageous over conventional tests due to their reduced sensitivity to minor departures.
-Building on this, @li2024automated introduced a computer vision model aimed at alleviating the human effort required for visual assessment of residual plots.
-The next step is to deliver the use of the computer vision model to potential users, so that it can be widely used to the benefit of the analytics community.
-
-Software for regression analysis tools is widely available.
+Deviations that might be observed from a residual plot are non-normality, heteroscedasticity, and other associations with the fitted values.-->
+
+However relying solely on subjective assessments of these plots can lead to issues, such as over-interpreting random patterns as model violations.
+@li2024plot demonstrated that visual methods using the lineup protocol [@buja2009statistical] for assessing residuals are more useful, and also perform more practically than conventional tests due to their reduced sensitivity to minor departures.
+Packages such as `nullabor` [@nullabor], `HLMdiag` [@loy2014hlmdiag], and `regressinator` [@regressinator], enable users to compare observed residual plots with samples from null distributions, helping to quantify the significance of any detected patterns.
+However, the
+
+However, as discussed in @li2024automated, the lineup protocol has significant limitations in large-scale applications due dependence on human labor.
+Thus a computer vision model was developed with an associated statistical testing procedure to automate the assessment of residual plots.
+This model takes a residual plot and a vector of auxiliary variables (such as the number of observations) as inputs and outputs the predicted visual signal strength (VSS).
+This strength estimates the distance between the residual distribution of the fitted regression model and the reference distribution assumed under correct model specification.
+
+<!--Software for regression analysis tools is widely available.
 The Comprehensive R Archive Network (CRAN) [@hornik2012comprehensive] hosts a vast array of packages, many of which provide tools to diagnose models using residual plots.
-These packages can be broadly categorized into three groups: general-purpose, enhanced visual diagnostics, and visual diagnostics with statistical testing.
-
-General-purpose regression analysis tools are the most widely used group of packages.
+These packages can be broadly categorized into three groups: general-purpose, enhanced visual diagnostics, and visual diagnostics with statistical testing.-->
+
+<!--General-purpose regression analysis tools are the most widely used group of packages.
 While not specifically designed for graphical diagnostics of residuals in linear regression, they include this functionality as part of a broader suite of statistical tools.
@@
 All of these tools deliver the types of diagnostic plots outlined in the classical text by @cook1982residuals.
-However, as discussed in @li2024plot, relying solely on subjective assessments of these plots can lead to issues, such as over-interpreting random patterns as model violations.
-
-The second group consists of enhanced visual diagnostics tools, which provide advanced aids for interpreting diagnostic plots.
+However, as discussed in @li2024plot, relying solely on subjective assessments of these plots can lead to issues, such as over-interpreting random patterns as model violations.-->
+
+<!-- The second group consists of enhanced visual diagnostics tools, which provide advanced aids for interpreting diagnostic plots.
 For instance, `ecostats` [@warton_global_2023] incorporates simulation envelopes into residual plots, while `DHARMa` [@dharma] compares empirical quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical counterparts.
 `DHARMa` is particularly focused on detecting model violations such as heteroscedasticity, incorrect functional forms, and issues specific to generalized linear and mixed-effect models, like over/under-dispersion.
-It also includes annotations from conventional tests, displayed as labels or text within the plot, to help avoid misinterpretation.
-
-The third group, visual diagnostics with statistical testing, offers tools for formally testing patterns observed in diagnostic plots [@buja2009statistical].
+It also includes annotations from conventional tests, displayed as labels or text within the plot, to help avoid misinterpretation.-->
+
+<!-- The third group, visual diagnostics with statistical testing, offers tools for formally testing patterns observed in diagnostic plots [@buja2009statistical].
 A common method for visual testing of residual plots is the lineup protocol, where the true residual plot is embedded within a set of null plots generated by simulating residuals under the null hypothesis $H_0$ that the regression model is correctly specified.
@@
 Packages in this group, such as `nullabor` [@nullabor], `HLMdiag` [@loy2014hlmdiag], and `regressinator` [@regressinator], enable users to compare observed residual plots with samples from null distributions, helping to quantify the significance of any detected patterns.
-
-However, as discussed in @li2024automated, the lineup protocol has significant limitations in large-scale applications due dependence on human labor.
+-->
+
+<!-- However, as discussed in @li2024automated, the lineup protocol has significant limitations in large-scale applications due dependence on human labor.
 Thus a computer vision model was developed with an associated statistical testing procedure to automate the assessment of residual plots.
 This model takes a residual plot and a vector of auxiliary variables (such as the number of observations) as inputs and outputs the predicted visual signal strength (VSS).
-This strength estimates the distance between the residual distribution of the fitted regression model and the reference distribution assumed under correct model specification.
+This strength estimates the distance between the residual distribution of the fitted regression model and the reference distribution assumed under correct model specification.-->
 
@@
 @fig-three-examples shows three sets of plots of residuals against fitted values.
-The simulated example in (a) might be interpreted as a heteroskedastic pattern, however the automated reading would predict this to have a visual signal strength (VSS) of 1.53, with a corresponding $p$-value of 0.25.
+The simulated example in (a) might be interpreted as a heteroscedastic pattern, however the automated reading would predict this to have a visual signal strength (VSS) of 1.53, with a corresponding $p$-value of 0.25.
 This means it is would be interpreted as a good residual plot, that there is nothing in the data to indicate a violation of model assumptions.
-Skewness in the predictor variables is generating the apparent heteroskedasticity, where the smaller variance in residuals at larger fitted values is due to smaller sample size only.
-The Breusch-Pagan test  [@breusch1979simple] for heteroskedasticity would also not reject this as good residual plot.
+Skewness in the predictor variables is generating the apparent heteroscedasticity, where the smaller variance in residuals at larger fitted values is due to smaller sample size only.
+The Breusch-Pagan test  [@breusch1979simple] for heteroscedasticity would also not reject this as good residual plot.
 
@@
 This structure is blindingly obvious visually, but a RESET test for nonlinear structure would not report a problem.
-(It would be detected by a Breusch-Pagan for heteroskedasticity and also Shapiro-Wilk test [@shapiro1965analysis] for non-normality.)
+(It would be detected by a Breusch-Pagan for heteroscedasticity and also Shapiro-Wilk test [@shapiro1965analysis] for non-normality.)
 
@@
 `get_keras_model()` is a function to download a trained computer vision model (described in @li2024automated) from GitHub.
-“vss_phn_32” specifies a model that predicts VSS and is trained on residuals with polynomial, heteroskedasticity, and non-normality patterns (phn).
+“vss_phn_32” specifies a model that predicts VSS and is trained on residuals with polynomial, heteroscedasticity, and non-normality patterns (phn).
 More details about the hosted models will be provided in @sec-trained-model-hosting.

### 2024-11-18 residuals/residuals.R
residual files

@@ -1,0 +1,45 @@
+library(ggplot2)
+library(readr)
+library(dplyr)
+library(broom)
+library(surreal)
+
+# Example 1
+set.seed(856)
+test_resid <- tibble(.fitted = rexp(855), .resid = rnorm(855))
+ggplot(test_resid, aes(x=.fitted, y=.resid)) + geom_point()
+write_csv(test_resid, file="residuals/test_resid.csv")
+
+# Example 2
+mtcars_fit2 <- lm(mpg~hp, data=mtcars)
+mtcars_all2 <- augment(mtcars_fit2, mtcars)
+ggplot(mtcars_all2, aes(x=.fitted, y=.resid)) + geom_point()
+write_csv(mtcars_all2, file="residuals/mtcars_all2.csv")
+
+# Example 3
+std <- function(x) {
+  (x-mean(x))/sd(x)
+}
+set.seed(332)
+sur_data <- surreal_text("visual summaries\n  focus on\n unexpected values", 
+                      p = 4, R_squared = 0.1, cex = 1, 
+                      n_add_points = 0) |>
+  as_tibble() |>
+  rename(x1 = X.1,
+         x2 = X.2,
+         x3 = X.3,
+         x4 = X.4) |>
+  mutate_all(std)  
+sur_model <- lm(y ~ x1 + x2 + x3 + x4, data = sur_data)
+sur_all <- augment(sur_model)
+ggplot(sur_all, aes(x=.fitted, y=.resid)) +
+  geom_point()
+write_csv(sur_all, file="residuals/sur_all.csv")
+
+library(lmtest)
+test_fit <- lm(.resid~.fitted, data=test_resid)
+bptest(test_fit)
+resettest(mtcars_fit2, type="regressor")
+resettest(sur_model, type="regressor")
+bptest(sur_model)
+shapiro.test(sur_all$.resid)

### 2024-11-18 autovi_paper.tex
compile the paper

@@
   pdfauthor={Weihao Li; Dianne Cook; Emi Tanaka; Susan VanderPlas; Klaus Ackermann},
-  pdfkeywords={statistical software, statistical graphics, data
+  pdfkeywords={initial data analysis, statistical graphics, data
 visualization, visual inference, computer vision, machine
-learning, hypothesis testing, reression analysis},
+learning, hypothesis testing, regression analysis},
   colorlinks=true,
@@
 \begin{abstract}
-Regression software is widely available today, but tools for effective
-diagnostics are still lagging. Perhaps, one of the reasons is that it is
-hard. Conventional tests, that would make the task easy, are often too
-sensitive, which would result in adequate models being abandoned if the
-analyst strictly adhered to the test decision. The recommended advice is
-to have the analyst assess the strength of patterns in residual plots.
-This requires human effort and also suffers from the potential for
-inconsistent decisions from different analysts. Using a lineup protocol
-can help to alleviate inconsistency, but requires even more human
-effort. This is the type of task where a robot might be employed to do
-the disagreeable work that currently requires a human. Here we describe
-a new R package that includes a computer vision model for automated
-assessment of residual plots, and an accompanying Shiny app for ease of
-use. For a user-provided sample of residuals, it predicts a measure of
-visual signal strength (VSS) and provides a suite of supporting
-information to assist the analyst diagnose their model fit.
+Regression software is widely available, and there are many tools for
+generating diagnostics and computing conventional residual tests.
+However, the advice remains that the analyst should look at the residual
+plot to check the fit. Perhaps, one of the reasons is that conventional
+tests are too sensitive, strictly resulting in adequate models being
+abandoned. Visually assess the strength of patterns in residual plots
+requires human effort and suffers from the potential for inconsistent
+decisions from different analysts. Using a lineup protocol, where the
+residual plot is embedded among null plots, can help to alleviate
+inconsistency, but requires even more human effort. This is the type of
+task that in today's world might employ a robot to do the tedious work
+for a human. Here we describe a new R package that includes a computer
+vision model for automated assessment of residual plots, and an
+accompanying Shiny app for ease of use. For a user-provided sample of
+residuals, it predicts a measure of visual signal strength (VSS) and
+provides a suite of supporting information to assist the analyst decide
+on the appropriateness their model fit.
 \end{abstract}
 
-\keywords{statistical software; statistical graphics; data
+\keywords{initial data analysis; statistical graphics; data
 visualization; visual inference; computer vision; machine
-learning; hypothesis testing; reression analysis}
+learning; hypothesis testing; regression analysis}
 
@@
 
-Regression analysis is a fundamental statistical technique widely used
-for modeling data from many fields. To diagnose the fit of a model it is
-recommended that the residuals are plotted. If the fit is good, any
-variation remaining should be noise, consistent with sampling from a
-distribution specified by the error model. Deviations that might be
-observed from a residual plot are non-normality, heteroscedasticity, and
-other associations with the fitted values. In \citet{li2024plot}, we
-demonstrated that visual methods for assessing residuals are
-advantageous over conventional tests due to their reduced sensitivity to
-minor departures. Building on this, \citet{li2024automated} introduced a
-computer vision model aimed at alleviating the human effort required for
-visual assessment of residual plots. The next step is to deliver the use
-of the computer vision model to potential users, so that it can be
-widely used to the benefit of the analytics community.
-
-Software for regression analysis tools is widely available. The
-Comprehensive R Archive Network (CRAN) \citep{hornik2012comprehensive}
-hosts a vast array of packages, many of which provide tools to diagnose
-models using residual plots. These packages can be broadly categorized
-into three groups: general-purpose, enhanced visual diagnostics, and
-visual diagnostics with statistical testing.
-
-General-purpose regression analysis tools are the most widely used group
-of packages. While not specifically designed for graphical diagnostics
-of residuals in linear regression, they include this functionality as
-part of a broader suite of statistical tools. For example, the
-\texttt{stats} package \citep{stats} offers standard diagnostic plots
-such as residuals vs.~fitted values, quantile-quantile (Q-Q) plots, and
-residuals vs.~leverage plots. Additional packages like \texttt{jtools}
+Regression analysis is a widely used statistical modeling technique
+widely for data in many fields. There are a vast array of software for
+conducting regression modeling and generating diagnostics. The package
+\texttt{lmtest} \citep{lmtest} provides a suite of conventional tests.
+The \texttt{stats} package \citep{stats} offers standard diagnostic
+plots such as residuals vs.~fitted values, quantile-quantile (Q-Q)
+plots, and residuals vs.~leverage plots. Packages like \texttt{jtools}
 \citep{jtools}, \texttt{olsrr} \citep{olsrr}, \texttt{rockchalk}
@@
 diagnostic plots outlined in the classical text by
-\citet{cook1982residuals}. However, as discussed in \citet{li2024plot},
-relying solely on subjective assessments of these plots can lead to
-issues, such as over-interpreting random patterns as model violations.
-
-The second group consists of enhanced visual diagnostics tools, which
-provide advanced aids for interpreting diagnostic plots. For instance,
-\texttt{ecostats} \citep{warton_global_2023} incorporates simulation
-envelopes into residual plots, while \texttt{DHARMa} \citep{dharma}
-compares empirical quantiles (0.25, 0.5, and 0.75) of scaled residuals
-to their theoretical counterparts. \texttt{DHARMa} is particularly
-focused on detecting model violations such as heteroscedasticity,
-incorrect functional forms, and issues specific to generalized linear
-and mixed-effect models, like over/under-dispersion. It also includes
-annotations from conventional tests, displayed as labels or text within
-the plot, to help avoid misinterpretation.
-
-The third group, visual diagnostics with statistical testing, offers
-tools for formally testing patterns observed in diagnostic plots
-\citep{buja2009statistical}. A common method for visual testing of
-residual plots is the lineup protocol, where the true residual plot is
-embedded within a set of null plots generated by simulating residuals
-under the null hypothesis \(H_0\) that the regression model is correctly
-specified. Observers are asked to identify the plot that appears most
-different from the others. If a significant proportion of observers
-correctly identify the true residual plot, it provides evidence against
-\(H_0\), as the true residual plot should be indistinguishable from the
-null plots if all residuals are generated by the same process, according
-to \citet{buja2009statistical}. Packages in this group, such as
-\texttt{nullabor} \citep{nullabor}, \texttt{HLMdiag}
+\citet{cook1982residuals}. The \texttt{ecostats} package
+\citep{warton_global_2023} incorporates simulation envelopes into
+residual plots, while \texttt{DHARMa} \citep{dharma} compares empirical
+quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical
+counterparts. \texttt{DHARMa} is particularly focused on detecting model
+violations such as heteroscedasticity, incorrect functional forms, and
+issues specific to generalized linear and mixed-effect models, like
+over/under-dispersion. It also includes conventional test annotations to
+help avoid misinterpretation.
+
+However relying solely on subjective assessments of these plots can lead
+to issues, such as over-interpreting random patterns as model
+violations. \citet{li2024plot} demonstrated that visual methods using
+the lineup protocol \citep{buja2009statistical} for assessing residuals
+are more useful, and also perform more practically than conventional
+tests due to their reduced sensitivity to minor departures. Packages
+such as \texttt{nullabor} \citep{nullabor}, \texttt{HLMdiag}
 \citep{loy2014hlmdiag}, and \texttt{regressinator}
@@
 with samples from null distributions, helping to quantify the
-significance of any detected patterns.
+significance of any detected patterns. However, the
 
@@
 plots. The name \texttt{autovi} stands for automated visual inference.
-While initially designed for linear regression residual diagnostics, it
-has the potential to be extended to broader visual inference
-applications, as we discuss in section
-Section~\ref{sec-autovi-infrastructure}.
+
+There are two ways to access the package, directly using R or through a
+web interface, \texttt{autovi.web}. The web interface has the advantage
+that it can be used without installing Python, R and the relevant
+packages locally.
+
+\subsection{Why use it}\label{sec-why}
+
+\textbf{?@fig-three-examples} shows three sets of plots of residuals
+against fitted values. The simulated example in (a) might be interpreted
+as a heteroscedastic pattern, however the automated reading would
+predict this to have a visual signal strength (VSS) of 1.53, with a
+corresponding \(p\)-value of 0.25. This means it is would be interpreted
+as a good residual plot, that there is nothing in the data to indicate a
+violation of model assumptions. Skewness in the predictor variables is
+generating the apparent heteroscedasticity, where the smaller variance
+in residuals at larger fitted values is due to smaller sample size only.
+The Breusch-Pagan test \citep{breusch1979simple} for heteroscedasticity
+would also not reject this as good residual plot.
+
+The data in (b) is generated by fitting a linear model predicting
+\texttt{mpg} based on \texttt{hp} using the \texttt{datasets::mtcars}.
+It is a small data set, and there is a hint of nonlinear structure not
+captured by the model. The automated plot reading would predict a VSS of
+3.57, which has a \(p\)-value less than 0.05. That is, the nonlinear
+structure is most likely real, and indicates a problem with the model.
+The conventional test, a Ramsey Regression Equation Specification Error
+Test (RESET) \citep{ramsey1969tests} would also strongly detect the
+nonlinearity.
+
+The third example is generated using the \texttt{surreal} package
+\citep{surreal} where structured residuals are hidden in data, to be
+revealed if the correct model is specified. Here a quote based on Tukey
+is used as the residual structure ``visual summaries focus on unexpected
+values''. The automated plot reading predicts the VSS to be 5.87, with a
+\(p\)-value less than 0.05. This structure is blindingly obvious
+visually, but a RESET test for nonlinear structure would not report a
+problem. (It would be detected by a Breusch-Pagan for heteroscedasticity
+and also Shapiro-Wilk test \citep{shapiro1965analysis} for
+non-normality.)
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/three-examples-1.pdf}
+
+}
+
+\caption{Reading residual plots can be a difficult task, particular for
+students new to statistical modeling. The autovi package makes it
+easier. Here are three examples of residual plots, which may appear to
+have structure. According to autovi, the visual signal strengths (VSS)
+of these three examples are approximately (a) 1.53, (b) 3.57, (c) 5.87,
+resulting in (b), (c) being significant violations of good residuals,
+but (a) is consistent with a good residual plot.}
+
+\end{figure}%
 
@@
 from GitHub. ``vss\_phn\_32'' specifies a model that predicts VSS and is
-trained on residuals with polynomial, heteroskedasticity, and
+trained on residuals with polynomial, heteroscedasticity, and
 non-normality patterns (phn). More details about the hosted models will
@@
 \begin{verbatim}
-[1] "/var/folders/61/bv7_1qzs20x6fjb2rsv7513r0000gn/T//RtmpfYtMdO/file37817b7b5b6.png"
+[1] "/var/folders/61/bv7_1qzs20x6fjb2rsv7513r0000gn/T//Rtmp6Lce76/file135f86b4a7b69.png"
 \end{verbatim}
@@
 
-\section{Availability}\label{availability}
-
-The web interface is housed at \url{autoviweb.netlify.app}.
+\section{Resources and Supplementary
+Material}\label{resources-and-supplementary-material}
 
@@
 and source code for both packages are available at
-\url{https://github.com/TengMCing/}.
+\url{https://github.com/TengMCing/autovi}. The web interface is
+available from \url{autoviweb.netlify.app}.
+
+These \texttt{R} packages were used for the work: \texttt{tidyverse}
+\citep{tidyverse}, \texttt{lmtest} \citep{lmtest}, \texttt{kableExtra}
+\citep{kableextra}, \texttt{patchwork} \citep{patchwork},
+\texttt{rcartocolor} \citep{rcartocolor}, \texttt{glue} \citep{glue},
+\texttt{here} \citep{here}, \texttt{magick} \citep{magick},
+\texttt{yardstick} \citep{yardstick} and \texttt{reticulate}
+\citep{reticulate}.
 

### 2024-11-18 autovi_paper.qmd
drastic paper trimming

@@
 ---
-title: "Software for Automated Residual Plot Assessment: autovi and autovi.web"
+title: "Automated Residual Plot Assessment with the R Package autovi and Shiny App autovi.web"
 subtitle: ANZJS Quarto Template
@@
     keep-tex: true  
-    shorttitle: "Software for Automated Residual Plot Assessment"
+    shorttitle: "Automated Residual Plot Assessment"
     double-space: true
@@
 
-The main purpose of `autovi` is to provide rejection decisions and $p$-values for testing whether a regression model is correctly specified.
-The package introduces a novel approach to automating statistical analysis, particularly in the interpretation of residual plots.
-The name `autovi` stands for automated visual inference.
+The main purpose of `autovi` is to provide rejection decisions and $p$-values for testing the null hypothesis ($H_0$) that the regression model is correctly specified.
+The package provides automated interpretation of residual plots using computer vision.
+The name `autovi` stands for **auto**mated **v**isual **i**nference.
 <!--While initially designed for linear regression residual diagnostics, it has the potential to be extended to broader visual inference applications, as we discuss in section @sec-autovi-infrastructure.-->
@@
 ```{r}
-#| label: three-examples
+#| label: fig-three-examples
 #| fig-cap: "Reading residual plots can be a difficult task, particular for students new to statistical modeling.
@@
 According to autovi, the visual signal strengths (VSS) of these three examples are approximately (a) 1.53, (b) 3.57, (c) 5.87, resulting in (b), (c) being significant violations of good residuals, but (a) is consistent with a good residual plot."
-#| fig-width: 9
-#| fig-height: 3
+#| fig-width: 12
+#| fig-height: 4
 #| out-width: 100%
@@
 
-The `autovi` package is available on CRAN.
-It is actively developed and maintained, with the latest updates accessible on GitHub at [https://github.com/TengMCing/autovi](https://github.com/TengMCing/autovi).
-The code discussed in this paper is based on `autovi` version 0.4.1.
+The `autovi` package is available on CRAN. It is actively developed and maintained, with the latest updates accessible on GitHub. The code discussed in this paper is based on `autovi` version 0.4.1.
 
@@
 
-## Usage {#sec-autovi-usage}
-
-To get started quickly, only three function calls are needed to obtain a summary of the automated residual assessment:
-
-```{r}
+We recommend using the Shiny app `autovi.web` if encountering installation problems.
+
+## Numerical Summary {#sec-autovi-usage}
+
+Three steps are needed to get an automated assessment of a set of residuals and fitted values:
+
+1. Load the `autovi` package using the `library()` function.
+2. Create a checker object with a linear regression model.
+3.
+Call the `check()` method of the checker, which, by default, predicts the VSS for the true residual plot, 100 null plots, and 100 bootstrapped plots, storing the predictions internally.
+A concise report of the check results is then printed.
+
+The code to do this is:
+
+```{r}
+#| echo: false
 set.seed(10086)
@@
 ```
+
+It produces the following summary:
 
@@
 
-The three functions are explained as follows:
-
-1. Load the `autovi` package using the `library()` function.
-2. Create a checker object with a linear regression model.
-3.
-Call the `check()` method of the checker, which, by default, predicts the VSS for the true residual plot, 100 null plots, and 100 bootstrapped plots, storing the predictions internally.
-A concise report of the check results is then printed.
-
-The summary reports key findings such as the VSS of the true residual plot and the $p$-value of the automated visual test.
-The $p$-value is the ratio of null plots that have VSS greater than or equal to that of the true residual plot.
-We typically reject the null hypothesis when the $p$-value is smaller than or equal to a desired significance level, such as 5%.
-The report also provides sample quantiles of VSS for null and bootstrapped plots, helping to explain the severity and likelihood of model violations.
-
-Although the $p$-value is sufficient for automated decision-making, users can visually inspect the original residual plot alongside a sample null plot.
+The summary includes observed VSS of the true residual plot and associated $p$-value of the automated visual test.
+The $p$-value is the proportion of null plots (out of the total 100) that have VSS greater than or equal to that of the true residual plot.
+<!--We typically reject the null hypothesis when the $p$-value is smaller than or equal to a desired significance level, such as 5%.--> The report also provides sample quantiles of VSS for null samples and bootstrapped data plots, providing more information about the sampling variability and a likelihood of model violations.
+The likelihood is computed from the proportion of values greater than the observed VSS in both the bootstrapped data values and the simulated null values.
+
+## Visual Summary {#sec-autovi-visual}
+
+Users can visually inspect the original residual plot alongside a sample null plot using `plot_pair()` or a lineup of null plot `plot_lineup()`.
 This visual comparison can clarify why $H_0$ is either rejected or not, and help identify potential remedies.
-The `plot_pair()` and `plot_lineup()` methods facilitate this comparison.
-
-```{r fig-plot-pair, echo = TRUE, fig.height=3, fig.width=4, fig.cap="True plot alongside one null plot, for quick comparison."}
+
+```{r fig-plot-pair, echo = TRUE, fig.height=2, fig.width=3, out.width="60%", fig.cap="True plot alongside one null plot, for quick comparison."}
 checker$plot_pair()
@@
 The remaining seven modules are designed to be overridable, enabling users to tailor the infrastructure to their specific needs.
-These modules are discussed in detail in the following sections.
-
+These modules are discussed in detail on the software's website.
+<!-- in the following sections.-->
+
+<!--
 ### Initialization
@@
 It requires only the model name, which is the value in the first column of the `tibble` returned by `list_keras_model()`.
+-->
 
@@
 Additionally, updates are managed centrally, ensuring that users always have access to the latest features.
-
-The `autovi.web` interface is available at [autoviweb.netlify.app](autoviweb.netlify.app). This section discusses the implementation based on `autovi.web` version 0.1.0.
+<!--The `autovi.web` interface is available at [autoviweb.netlify.app](autoviweb.netlify.app).--> This section discusses the implementation based on `autovi.web` version 0.1.0.
 

### 2024-11-18 autovi_paper.tex
drastic paper trimming

@@
 \makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\newsavebox\pandoc@box
+\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
+  \sbox\pandoc@box{#1}%
+  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
+  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
+  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
+  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
+  \else\usebox{\pandoc@box}%
+  \fi%
+}
 % Set default figure placement to htbp
-\makeatletter
 \def\fps@figure{htbp}
@@
 
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
 \usepackage[]{natbib}
@@
 \hypersetup{
-  pdftitle={Software for Automated Residual Plot Assessment: autovi and autovi.web},
+  pdftitle={Automated Residual Plot Assessment with the R Package autovi and Shiny App autovi.web},
   pdfauthor={Weihao Li; Dianne Cook; Emi Tanaka; Susan VanderPlas; Klaus Ackermann},
@@
 \runningheads{
-Software for Automated Residual Plot Assessment
+Automated Residual Plot Assessment
 }{
@@
 
-\title{Software for Automated Residual Plot Assessment: autovi and
-autovi.web}
+\title{Automated Residual Plot Assessment with the R Package autovi and
+Shiny App autovi.web}
 \usepackage{etoolbox}
@@
 The main purpose of \texttt{autovi} is to provide rejection decisions
-and \(p\)-values for testing whether a regression model is correctly
-specified. The package introduces a novel approach to automating
-statistical analysis, particularly in the interpretation of residual
-plots. The name \texttt{autovi} stands for automated visual inference.
+and \(p\)-values for testing the null hypothesis (\(H_0\)) that the
+regression model is correctly specified. The package provides automated
+interpretation of residual plots using computer vision. The name
+\texttt{autovi} stands for \textbf{auto}mated \textbf{v}isual
+\textbf{i}nference.
 
@@
 
-\textbf{?@fig-three-examples} shows three sets of plots of residuals
+Figure~\ref{fig-three-examples} shows three sets of plots of residuals
 against fitted values. The simulated example in (a) might be interpreted
@@
 
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/three-examples-1.pdf}
-
-}
-
-\caption{Reading residual plots can be a difficult task, particular for
-students new to statistical modeling. The autovi package makes it
-easier. Here are three examples of residual plots, which may appear to
-have structure. According to autovi, the visual signal strengths (VSS)
-of these three examples are approximately (a) 1.53, (b) 3.57, (c) 5.87,
-resulting in (b), (c) being significant violations of good residuals,
-but (a) is consistent with a good residual plot.}
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-three-examples-1.pdf}
+
+}
+
+\caption{\label{fig-three-examples}Reading residual plots can be a
+difficult task, particular for students new to statistical modeling. The
+autovi package makes it easier. Here are three examples of residual
+plots, which may appear to have structure. According to autovi, the
+visual signal strengths (VSS) of these three examples are approximately
+(a) 1.53, (b) 3.57, (c) 5.87, resulting in (b), (c) being significant
+violations of good residuals, but (a) is consistent with a good residual
+plot.}
 
@@
 The \texttt{autovi} package is available on CRAN. It is actively
-developed and maintained, with the latest updates accessible on GitHub
-at \url{https://github.com/TengMCing/autovi}. The code discussed in this
-paper is based on \texttt{autovi} version 0.4.1.
+developed and maintained, with the latest updates accessible on GitHub.
+The code discussed in this paper is based on \texttt{autovi} version
+0.4.1.
 
@@
 
-\subsection{Usage}\label{sec-autovi-usage}
-
-To get started quickly, only three function calls are needed to obtain a
-summary of the automated residual assessment:
+We recommend using the Shiny app \texttt{autovi.web} if encountering
+installation problems.
+
+\subsection{Numerical Summary}\label{sec-autovi-usage}
+
+Three steps are needed to get an automated assessment of a set of
+residuals and fitted values:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Load the \texttt{autovi} package using the \texttt{library()}
+  function.
+\item
+  Create a checker object with a linear regression model.
+\item
+  Call the \texttt{check()} method of the checker, which, by default,
+  predicts the VSS for the true residual plot, 100 null plots, and 100
+  bootstrapped plots, storing the predictions internally. A concise
+  report of the check results is then printed.
+\end{enumerate}
+
+The code to do this is:
 
@@
 \end{Shaded}
+
+It produces the following summary:
 
@@
 
-The three functions are explained as follows:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Load the \texttt{autovi} package using the \texttt{library()}
-  function.
-\item
-  Create a checker object with a linear regression model.
-\item
-  Call the \texttt{check()} method of the checker, which, by default,
-  predicts the VSS for the true residual plot, 100 null plots, and 100
-  bootstrapped plots, storing the predictions internally. A concise
-  report of the check results is then printed.
-\end{enumerate}
-
-The summary reports key findings such as the VSS of the true residual
-plot and the \(p\)-value of the automated visual test. The \(p\)-value
-is the ratio of null plots that have VSS greater than or equal to that
-of the true residual plot. We typically reject the null hypothesis when
-the \(p\)-value is smaller than or equal to a desired significance
-level, such as 5\%. The report also provides sample quantiles of VSS for
-null and bootstrapped plots, helping to explain the severity and
-likelihood of model violations.
-
-Although the \(p\)-value is sufficient for automated decision-making,
-users can visually inspect the original residual plot alongside a sample
-null plot. This visual comparison can clarify why \(H_0\) is either
-rejected or not, and help identify potential remedies. The
-\texttt{plot\_pair()} and \texttt{plot\_lineup()} methods facilitate
-this comparison.
+The summary includes observed VSS of the true residual plot and
+associated \(p\)-value of the automated visual test. The \(p\)-value is
+the proportion of null plots (out of the total 100) that have VSS
+greater than or equal to that of the true residual plot. The report also
+provides sample quantiles of VSS for null samples and bootstrapped data
+plots, providing more information about the sampling variability and a
+likelihood of model violations. The likelihood is computed from the
+proportion of values greater than the observed VSS in both the
+bootstrapped data values and the simulated null values.
+
+\subsection{Visual Summary}\label{sec-autovi-visual}
+
+Users can visually inspect the original residual plot alongside a sample
+null plot using \texttt{plot\_pair()} or a lineup of null plot
+\texttt{plot\_lineup()}. This visual comparison can clarify why \(H_0\)
+is either rejected or not, and help identify potential remedies.
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-plot-pair-1.pdf}
+\includegraphics[width=0.6\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-plot-pair-1.pdf}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-summary-plot-1.pdf}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-summary-plot-1.pdf}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-diag-1.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-diag-1.png}
 
@@
 be overridable, enabling users to tailor the infrastructure to their
-specific needs. These modules are discussed in detail in the following
-sections.
-
-\subsubsection{Initialization}\label{initialization}
-
-An \texttt{autovi} checker can be initialized by supplying two primary
-inputs, including a regression model object, such as an \texttt{lm}
-object representing the result of a linear regression model, and a
-trained computer vision model compatible with the \texttt{Keras}
-\citep{chollet2015keras} Application Programming Interface (API), to the
-\texttt{AUTO\_VI} class constructor \texttt{auto\_vi()}. The
-\texttt{residual\_checker()} introduced in
-Section~\ref{sec-autovi-usage} is a thin wrapper around
-\texttt{auto\_vi()}, which will call \texttt{get\_keras\_model()} during
-initialization. \texttt{get\_keras\_model()} is a function to download a
-trained computer vision model (described in \citet{li2024automated})
-from GitHub. ``vss\_phn\_32'' specifies a model that predicts VSS and is
-trained on residuals with polynomial, heteroscedasticity, and
-non-normality patterns (phn). More details about the hosted models will
-be provided in Section~\ref{sec-trained-model-hosting}.
-
-The input of the constructor will be stored as attributes of the checker
-and can be accessed by the user through the \texttt{\$} operator.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(autovi)}
-\NormalTok{checker }\OtherTok{\textless{}{-}} \FunctionTok{auto\_vi}\NormalTok{(}\AttributeTok{fitted\_model =} \FunctionTok{lm}\NormalTok{(dist }\SpecialCharTok{\textasciitilde{}}\NormalTok{ speed, }\AttributeTok{data =}\NormalTok{ cars), }
-                   \AttributeTok{keras\_model =} \FunctionTok{get\_keras\_model}\NormalTok{(}\StringTok{"vss\_phn\_32"}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-Optionally, the user may specify the node index of the output layer of
-the trained computer vision model to be monitored by the checker via the
-\texttt{node\_index} argument if there are multiple output nodes. This
-is particularly useful for multiclass classifiers when the user wants to
-use one of the nodes as a VSS indicator.
-
-After initializing the object, you can print the checker to view its
-status.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{── }\SpecialCharTok{\textless{}}\NormalTok{AUTO\_VI object}\SpecialCharTok{\textgreater{}}
-\NormalTok{Status}\SpecialCharTok{:}
- \SpecialCharTok{{-}}\NormalTok{ Fitted model}\SpecialCharTok{:}\NormalTok{ lm}
- \SpecialCharTok{{-}}\NormalTok{ Keras model}\SpecialCharTok{:}\NormalTok{ (None, }\DecValTok{32}\NormalTok{, }\DecValTok{32}\NormalTok{, }\DecValTok{3}\NormalTok{) }\SpecialCharTok{+}\NormalTok{ (None, }\DecValTok{5}\NormalTok{) }\OtherTok{{-}\textgreater{}}\NormalTok{ (None, }\DecValTok{1}\NormalTok{)}
-    \SpecialCharTok{{-}}\NormalTok{ Output node index}\SpecialCharTok{:} \DecValTok{1}
- \SpecialCharTok{{-}}\NormalTok{ Result}\SpecialCharTok{:}\NormalTok{ UNKNOWN }
-\end{Highlighting}
-\end{Shaded}
-
-The status includes the list of regression model classes (as provided by
-the built-in \texttt{class()} function), the input and output shapes of
-the Keras model in the standard \texttt{Numpy} format
-\citep{harris2020array}, the output node index being monitored, and the
-assessment result. If no check has been run yet, the assessment result
-will display as ``UNKNOWN''.
-
-\subsubsection{Fitted Values and Residuals
-Extraction}\label{fitted-values-and-residuals-extraction}
-
-To be able to predict VSS for a residual plot, both fitted values and
-residuals are needed to be extracted from the regression model object
-supplied by the user. In R, statistical models like \texttt{lm} (linear
-model) and \texttt{glm} (generalized linear model) typically support the
-use of generic functions such as \texttt{fitted()} and \texttt{resid()}
-to retrieve these values. The \texttt{get\_fitted\_and\_resid()} method,
-called by the checker, relies on these generic functions by default.
-However, generic functions only work with classes that have appropriate
-method implementations. Some regression modeling packages may not fully
-adhere to the \texttt{stats} package guidelines for implementing these
-functions. In such cases, overriding the method becomes necessary.
-
-By design, the \texttt{get\_fitted\_and\_resid()} method accepts a
-regression model object as input and returns a \texttt{tibble} (a modern
-presentation of the \texttt{data.frame}) with two columns:
-\texttt{.fitted} and \texttt{.resid}, representing the fitted values and
-residuals, respectively. If no input is supplied, the method uses the
-regression model object stored in the checker. Although modules in the
-\texttt{autovi} infrastructure make minimal assumptions about other
-modules, they do require strictly defined input and output formats to
-ensure data validation and prevent fatal bugs. Therefore, any overridden
-method should follow to these conventions.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{get\_fitted\_and\_resid}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-# A tibble: 50 x 2
-   .fitted .resid
-     <dbl>  <dbl>
- 1   -1.85   3.85
- 2   -1.85  11.8 
- 3    9.95  -5.95
- 4    9.95  12.1 
- 5   13.9    2.12
- 6   17.8   -7.81
- 7   21.7   -3.74
- 8   21.7    4.26
- 9   21.7   12.3 
-10   25.7   -8.68
-# i 40 more rows
-\end{verbatim}
-
-\subsubsection{Data Extraction}\label{data-extraction}
-
-For linear regression model in R, the model frame contains all the data
-required by a formula for evaluation. This is essential for
-bootstrapping and refitting the model when constructing a bootstrapped
-distribution of VSS. Typically, the model frame can be extracted from
-the regression model object using the \texttt{model.frame()} generic
-function, which is the default method used by \texttt{get\_data()}.
-However, some regression models do not use a formula or are evaluated
-differently, potentially lacking a model frame. In such cases, users can
-either provide the data used to fit the regression model through the
-\texttt{data} argument when constructing the checker, or customize the
-method to better suit their needs. It's worth noting that this module is
-only necessary if bootstrapping is required, as the model frame is not
-used in other modules of the infrastructure.
-
-The \texttt{get\_data()} method accepts a regression model object as
-input and returns a \texttt{data.frame} representing the model frame of
-the fitted regression model. If no input is supplied, the regression
-model stored in the checker will be used.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{get\_data}\NormalTok{() }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{head}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-  dist speed
-1    2     4
-2   10     4
-3    4     7
-4   22     7
-5   16     8
-6   10     9
-\end{verbatim}
-
-\subsubsection{Bootstrapping and Model
-Refitting}\label{bootstrapping-and-model-refitting}
-
-Bootstrapping a regression model typically involves sampling the
-observations with replacement and refitting the model with the
-bootstrapped data. The \texttt{boot\_method()} method follows this
-bootstrapping scheme by default. It accepts a fitted regression model
-and a \texttt{data.frame} as inputs, and returns a \texttt{tibble} of
-bootstrapped residuals. If no inputs are provided, the method uses the
-regression model stored in the checker and the result of the
-\texttt{get\_data()} method.
-
-Note that instead of calling \texttt{get\_data()} implicitly within the
-method, it is used as part of the default argument definition. This
-approach allows users to bypass the \texttt{get\_data()} method entirely
-and directly supply a \texttt{data.frame} to initiate the bootstrap
-process. Many other methods in \texttt{autovi} adopt this principle when
-possible, where dependencies are explicitly listed in the formal
-arguments. This design choice enhances the reusability and isolation of
-modules, offers better control for testing, and simplifies the overall
-process.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{boot\_method}\NormalTok{(}\AttributeTok{data =}\NormalTok{ checker}\SpecialCharTok{$}\FunctionTok{get\_data}\NormalTok{())}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-# A tibble: 50 x 2
-   .fitted .resid
-     <dbl>  <dbl>
- 1   27.0   -2.96
- 2   38.8  -12.8 
- 3   34.8   -8.82
- 4   27.0  -13.0 
- 5   11.2    4.76
- 6   42.7   -2.68
- 7   42.7   -2.68
- 8   38.8  -18.8 
- 9   38.8   15.2 
-10   -4.47   6.47
-# i 40 more rows
-\end{verbatim}
-
-\subsubsection{Auxiliary Computation}\label{auxiliary-computation}
-
-As described in \citet{li2024automated}, in some cases, a residual plot
-alone may not provide enough information to accurately determine VSS.
-For instance, when the points in the residual plot have significant
-overlap, the trend and shape of the residual pattern can be difficult to
-discern. Including auxiliary variables, such as the number of
-observations, as additional inputs to the computer vision model can be
-beneficial. To address this, \texttt{autovi} includes internal functions
-within the checker that automatically detect the number of inputs
-required by the provided Keras model. If multiple inputs are necessary,
-the checker invokes the \texttt{auxiliary()} method to compute these
-additional inputs.
-
-The \texttt{auxiliary()} method takes a \texttt{data.frame} containing
-fitted values and residuals as input and returns a \texttt{data.frame}
-with five numeric columns. These columns represent four scagnostics ---
-``Monotonic'', ``Sparse'', ``Striped'', and ``Splines'' --- calculated
-using the \texttt{cassowaryr} package, as well as the number of
-observations. This approach is consistent with the training process of
-the computer vision models described in \citet{li2024automated}. If no
-\texttt{data.frame} is provided, the method will default to retrieving
-fitted values and residuals by calling
-\texttt{get\_fitted\_and\_resid()}.
-
-Technically, any Keras-implemented computer vision model can be adapted
-to accept an image as the primary input and additional variables as
-secondary inputs by adding a data pre-processing layer before the actual
-input layer. If users wish to override \texttt{auxiliary()}, the output
-should be a \texttt{data.frame} with a single row and the number of
-columns such that its concatenation matches the number of parameters for
-the corresponding layer in the supplied Keras model.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{auxiliary}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-# A tibble: 1 x 5
-  measure_monotonic measure_sparse measure_splines measure_striped     n
-              <dbl>          <dbl>           <dbl>           <dbl> <int>
-1            0.0621          0.470          0.0901            0.62    50
-\end{verbatim}
-
-\subsubsection{Null Residual Simulation}\label{sec-autovi-null-method}
-
-A fundamental element of the automated residual assessment described in
-\citet{li2024automated} is comparing the VSS of null plots with that of
-the true residual plot. However, due to the variety of regression
-models, there is no universal method for simulating null residuals that
-are consistent with model assumptions. Fortunately, for classical normal
-linear regression models, null residuals can be effectively simulated
-using the residual rotation method, as outlined in
-\citet{buja2009statistical}. This process involves generating random
-draws from a standard normal distribution, regressing these draws on the
-original predictors, and then rescaling the resulting residuals by the
-ratio of the residual sum of squares to the that of the original linear
-regression model. Other regression models, such as \texttt{glm}
-(generalized linear model) and \texttt{gam} (generalized additive
-model), generally cannot use this method to efficiently simulate null
-residuals. Therefore, it is recommended that users override the
-\texttt{null\_method()} to suit their specific model. The
-\texttt{null\_method()} takes a fitted regression model as input,
-defaulting to the regression model stored in the checker, and returns a
-\texttt{tibble}.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{null\_method}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-# A tibble: 50 x 2
-   .fitted  .resid
-     <dbl>   <dbl>
- 1   -1.85  18.2  
- 2   -1.85  -0.765
- 3    9.95 -12.8  
- 4    9.95  18.6  
- 5   13.9    2.57 
- 6   17.8    7.03 
- 7   21.7  -11.1  
- 8   21.7  -13.2  
- 9   21.7  -12.6  
-10   25.7    3.57 
-# i 40 more rows
-\end{verbatim}
-
-\subsubsection{Plotting}\label{plotting}
-
-Plotting is a crucial aspect of residual plot diagnostics because
-aesthetic elements like marker size, marker color, and auxiliary lines
-impact the presentation of information. There are computer vision models
-trained to handle images captured in various scenarios. For example, the
-VGG16 model \citep{simonyan2014very} can classify objects in images
-taken under different lighting conditions and is robust to image
-rotation. However, data plots are a special type of image as the
-plotting style can always be consistent if controlled properly.
-Therefore, we assume computer vision models built for reading residual
-plots will be trained with residual plots of a specific aesthetic style.
-In this case, it is best to predict plots using the same style for
-optimal performance. The plotting method \texttt{plot\_resid()} handles
-this aspect.
-
-\texttt{plot\_resid()} accepts a \texttt{data.frame} containing fitted
-values and residuals, along with several customization options: a
-\texttt{ggplot} theme, an \texttt{alpha} value to control the
-transparency of data points, a \texttt{size} value to set the size of
-data points, and a \texttt{stroke} value to define the thickness of data
-point edges. Additionally, it includes four Boolean arguments to toggle
-the display of axes, legends, grid lines, and a horizontal red line. By
-default, it replicates the style we used to generate the training
-samples for the computer vision models described in
-\citet{li2024automated}. In brief, the residual plot omits axis text and
-ticks, titles, and background grid lines, featuring only a red line at
-\(y = 0\). It retains only the necessary components of a residual plot.
-If the computer vision model is trained with a different but consistent
-aesthetic style, \texttt{plot\_resid()} should be overridden.
-
-The method returns a \texttt{ggplot} object
-(Figure~\ref{fig-autovi-plot-resid}), which can be saved as a PNG file
-in the following module. If no data is provided, the method will use
-\texttt{get\_fitted\_and\_resid()} to retrieve the fitted values and
-residuals from the regression model stored in the checker.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{plot\_resid}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{figure}[H]
-
-\centering{
-
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-plot-resid-1.pdf}
-
-}
-
-\caption{\label{fig-autovi-plot-resid}Residual plot of the regression
-model stored in the checker.}
-
-\end{figure}%
-
-To manually generate true residual plots, null plots, or bootstrapped
-residual plots, you can pass the corresponding \texttt{data.frame}
-produced by the \texttt{get\_fitted\_and\_resid()},
-\texttt{null\_method()}, and \texttt{boot\_method()} methods to the
-\texttt{plot\_resid()} method, respectively.
-
-\subsubsection{Plot Saving}\label{plot-saving}
-
-Another key aspect of a standardized residual plot is its resolution. In
-\citet{li2024automated}, we used an image format of 420 pixels in height
-and 525 pixels in width. This resolution was chosen because the original
-set, consisting of 20 residual plots arranged in a four by five grid,
-was represented by an image of 2100 by 2100 pixels. The
-\texttt{save\_plot()} method accepts a \texttt{ggplot} object as input
-and saves it as a PNG file to the location specified by the
-\texttt{path} argument. If no path is provided, the PNG file is saved to
-a temporary file.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{plot\_resid}\NormalTok{() }\SpecialCharTok{|\textgreater{}} 
-\NormalTok{  checker}\SpecialCharTok{$}\FunctionTok{save\_plot}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-[1] "/var/folders/61/bv7_1qzs20x6fjb2rsv7513r0000gn/T//Rtmp6Lce76/file135f86b4a7b69.png"
-\end{verbatim}
-
-\subsubsection{Image Reading and
-Resizing}\label{image-reading-and-resizing}
-
-When training computer vision models, it is common to test various input
-sizes for the same architecture to identify the optimal setup. This
-involves preparing the original training image at a higher resolution
-than required and then resizing it to match the input size during
-training. The \texttt{autovi} package includes a class,
-\texttt{KERAS\_WRAPPER}, to simplify this process. This Keras wrapper
-class features a method called \texttt{image\_to\_array()}, which reads
-an image as a \texttt{PIL} image using the \texttt{pillow} Python
-package, resizes it to the target input size required by the Keras
-model, and converts it to a \texttt{Numpy} array.
-
-To construct a \texttt{KERAS\_WRAPPER} object, you need to provide the
-Keras model as the main argument. However, users generally do not need
-to interact with this class directly, as the \texttt{autovi} checker
-automatically invokes its methods when performing VSS predictions. The
-\texttt{image\_to\_array()} method takes the path to the image file, the
-target height, and the target width as inputs and returns a
-\texttt{Numpy} array. If not specified, the target height and target
-width will be retrieved from the input layer of the Keras model by the
-\texttt{get\_input\_height()} and \texttt{get\_input\_width()} method of
-\texttt{KERAS\_WRAPPER}.
-
-The following code example demonstrate the way to manually generate the
-true residual plot, save it as PNG file, and load it back as
-\texttt{Numpy} array.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{wrapper }\OtherTok{\textless{}{-}} \FunctionTok{keras\_wrapper}\NormalTok{(}\AttributeTok{keras\_model =}\NormalTok{ checker}\SpecialCharTok{$}\NormalTok{keras\_model)  }
-\NormalTok{input\_array }\OtherTok{\textless{}{-}}\NormalTok{ checker}\SpecialCharTok{$}\FunctionTok{plot\_resid}\NormalTok{() }\SpecialCharTok{|\textgreater{}} 
-\NormalTok{  checker}\SpecialCharTok{$}\FunctionTok{save\_plot}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
-\NormalTok{  wrapper}\SpecialCharTok{$}\FunctionTok{image\_to\_array}\NormalTok{()}
-\NormalTok{input\_array}\SpecialCharTok{$}\NormalTok{shape}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-(1, 32, 32, 3)
-\end{verbatim}
-
-\subsubsection{Visual Signal Strength (VSS)
-Prediction}\label{visual-signal-strength-vss-prediction}
-
-VSS, as discussed in \citet{li2024automated}, estimates the distance
-between the input residual plot and a theoretically good residual plot.
-It can be defined in various ways, much like different methods for
-measuring the distance between two points. This will not impact the
-\texttt{autovi} infrastructure as long as the provided Keras model can
-predict the intended measure.
-
-There are several ways to obtain VSS from the checker, with the most
-direct being the \texttt{vss()} method. By default, this method predicts
-the VSS for the true residual plot. If a \texttt{ggplot} or a
-\texttt{data.frame}, such as null residuals generated by the
-\texttt{null\_method()}, is explicitly provided, the method will use
-that input to predict VSS accordingly. Note that if a \texttt{ggplot} is
-provided, auxiliary inputs must be supplied manually via the
-\texttt{auxiliary} argument, as we assume that auxiliary variables can
-not be computed directly from a \texttt{ggplot}.
-
-Another way to obtain VSS is by calling the \texttt{check()} method.
-This comprehensive method perform extensive diagnostics on the true
-residual plot and store the VSS in the \texttt{check\_result} field of
-the checker. Additionally, for obtaining VSS for null residual plots and
-bootstrapped residual plots, there are two specialized methods,
-\texttt{null\_vss()} and \texttt{boot\_vss()}, designed for this purpose
-respectively.
-
-Calling the \texttt{vss()} method without arguments will predict the VSS
-for the true residual plot and return the result as a single-element
-\texttt{tibble}.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{vss}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-# A tibble: 1 x 1
-    vss
-  <dbl>
-1  3.16
-\end{verbatim}
-
-Providing a \texttt{data.frame} of null residuals or a null residual
-plot yields the same VSS.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{null\_resid }\OtherTok{\textless{}{-}}\NormalTok{ checker}\SpecialCharTok{$}\FunctionTok{null\_method}\NormalTok{()}
-\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{vss}\NormalTok{(null\_resid)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-# A tibble: 1 x 1
-    vss
-  <dbl>
-1  1.23
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{null\_resid }\SpecialCharTok{|\textgreater{}}
-\NormalTok{  checker}\SpecialCharTok{$}\FunctionTok{plot\_resid}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
-\NormalTok{  checker}\SpecialCharTok{$}\FunctionTok{vss}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-# A tibble: 1 x 1
-    vss
-  <dbl>
-1  1.23
-\end{verbatim}
-
-The \texttt{null\_vss()} helper method primarily takes the number of
-null plots as input. If the user wants to use a ad hoc null simulation
-scheme, it can be provided via the \texttt{null\_method} argument.
-Intermediate results, including null residuals and null plots, can be
-returned by enabling \texttt{keep\_null\_data} and
-\texttt{keep\_null\_plot}. The VSS, along with null residuals and null
-plots, will be stored in a \texttt{tibble} with three columns. The
-following code example demonstrates how to predict the VSS for five null
-residual plots while keeping the intermediate results.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{null\_vss}\NormalTok{(}\DecValTok{5}\NormalTok{L, }
-                 \AttributeTok{keep\_null\_data =} \ConstantTok{TRUE}\NormalTok{, }
-                 \AttributeTok{keep\_null\_plot =} \ConstantTok{TRUE}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-# A tibble: 5 x 3
-    vss data              plot  
-  <dbl> <list>            <list>
-1 0.982 <tibble [50 x 2]> <gg>  
-2 1.58  <tibble [50 x 2]> <gg>  
-3 2.09  <tibble [50 x 2]> <gg>  
-4 0.742 <tibble [50 x 2]> <gg>  
-5 2.21  <tibble [50 x 2]> <gg>  
-\end{verbatim}
-
-The \texttt{boot\_vss()} helper method is similar to
-\texttt{null\_vss()}, with some differences in argument names. The
-following code example demonstrates how to predict the VSS for five
-bootstrapped residual plots while keeping the intermediate results.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{boot\_vss}\NormalTok{(}\DecValTok{5}\NormalTok{L,}
-                 \AttributeTok{keep\_boot\_data =} \ConstantTok{TRUE}\NormalTok{,}
-                 \AttributeTok{keep\_boot\_plot =} \ConstantTok{TRUE}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-# A tibble: 5 x 3
-    vss data              plot  
-  <dbl> <list>            <list>
-1  3.12 <tibble [50 x 2]> <gg>  
-2  2.37 <tibble [50 x 2]> <gg>  
-3  2.87 <tibble [50 x 2]> <gg>  
-4  1.85 <tibble [50 x 2]> <gg>  
-5  3.66 <tibble [50 x 2]> <gg>  
-\end{verbatim}
-
-\subsubsection{\texorpdfstring{\(p\)-value
-Computation}{p-value Computation}}\label{p-value-computation}
-
-Once we have obtained the VSS from both the true residual plot and the
-null plots, we can compute the \(p\)-value. This \(p\)-value represents
-the ratio of plots with VSS greater than or equal to that of the true
-residual plot. We can perform this calculation using the
-\texttt{check()} method. The main inputs for this method are the number
-of null plots and the number of bootstrapped plots to generate. If you
-need to access intermediate residuals and plots, you can enable the
-\texttt{keep\_data} and \texttt{keep\_plot} options. The method stores
-the final result in the \texttt{check\_result} field of the object. To
-obtain the p-value using the \texttt{check()} method, you can use the
-following code.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{check}\NormalTok{(}\AttributeTok{boot\_draws =} \DecValTok{100}\NormalTok{L, }\AttributeTok{null\_draws =} \DecValTok{100}\NormalTok{L)}
-\NormalTok{checker}\SpecialCharTok{$}\NormalTok{check\_result}\SpecialCharTok{$}\NormalTok{p\_value}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-[1] 0.02970297
-\end{verbatim}
-
-\subsection{Summary Plots}\label{summary-plots}
-
-After executing the \texttt{check()} method, \texttt{autovi} offers two
-visualization options for the assessment result through the
-\texttt{summary\_plot()} method, including the density plot and the rank
-plot. We have already discussed and interpreted the density plot in
-Section~\ref{sec-autovi-usage}. Here, we would like to highlight the
-flexibility in choosing which elements to display in the density plot as
-shown in Figure~\ref{fig-autovi-summary-plot-option}. For instance, you
-can omit the bootstrapped distribution by setting \texttt{boot\_dist} to
-\texttt{NULL}. Similarly, you can hide the null distribution
-(\texttt{null\_dist}), the \(p\)-value (\texttt{p\_value}), or the
-likelihood ratio (\texttt{likelihood\_ratio}) as needed. The following
-example demonstrates how to create a summary plot without the results
-from bootstrapped plots.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{summary\_plot}\NormalTok{(}\AttributeTok{boot\_dist =} \ConstantTok{NULL}\NormalTok{,}
-                     \AttributeTok{likelihood\_ratio =} \ConstantTok{NULL}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{figure}[H]
-
-\centering{
-
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-summary-plot-option-1.pdf}
-
-}
-
-\caption{\label{fig-autovi-summary-plot-option}Density plot of the VSS
-for null plots.}
-
-\end{figure}%
-
-This customization allows you to focus on specific aspects of the
-assessment, tailoring the visualization to your analytical needs.
-
-The rank plot (Figure~\ref{fig-autovi-rank-plot}), creating by setting
-\texttt{type} to ``rank'', is a bar plot where the \(x\)-axis represents
-the rank and the \(y\)-axis shows the VSS. The bar that is coloured in
-red corresponding to the VSS of the true residual plot. By examining the
-rank plot, you can intuitively understand how the observed VSS compares
-to the null VSSs and identify any outliers in the null distribution.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{summary\_plot}\NormalTok{(}\AttributeTok{type =} \StringTok{"rank"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{figure}[H]
-
-\centering{
-
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-rank-plot-1.pdf}
-
-}
-
-\caption{\label{fig-autovi-rank-plot}Rank plot of the VSS for null
-plots.}
-
-\end{figure}%
-
-\subsection{Feature Extraction}\label{feature-extraction}
-
-In addition to predicting VSS and computing \(p\)-values,
-\texttt{autovi} offers methods to extract features from any layer of the
-Keras model. To see which layers are available in the current Keras
-model, you can use the \texttt{list\_layer\_name()} method from the
-\texttt{KERAS\_WRAPPER} class.
-
-The following code example lists the layer names of the currently used
-Keras model:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{wrapper }\OtherTok{\textless{}{-}} \FunctionTok{keras\_wrapper}\NormalTok{(checker}\SpecialCharTok{$}\NormalTok{keras\_model)}
-\NormalTok{wrapper}\SpecialCharTok{$}\FunctionTok{list\_layer\_name}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
- [1] "input_1"                  "tf.__operators__.getitem"
- [3] "tf.nn.bias_add"           "grey_scale"              
- [5] "block1_conv1"             "batch_normalization"     
- [7] "activation"               "block1_conv2"            
- [9] "batch_normalization_1"    "activation_1"            
-[11] "block1_pool"              "dropout"                 
-[13] "block2_conv1"             "batch_normalization_2"   
-[15] "activation_2"             "block2_conv2"            
-[17] "batch_normalization_3"    "activation_3"            
-[19] "block2_pool"              "dropout_1"               
-[21] "block3_conv1"             "batch_normalization_4"   
-[23] "activation_4"             "block3_conv2"            
-[25] "batch_normalization_5"    "activation_5"            
-[27] "block3_conv3"             "batch_normalization_6"   
-[29] "activation_6"             "block3_pool"             
-[31] "dropout_2"                "block4_conv1"            
-[33] "batch_normalization_7"    "activation_7"            
-[35] "block4_conv2"             "batch_normalization_8"   
-[37] "activation_8"             "block4_conv3"            
-[39] "batch_normalization_9"    "activation_9"            
-[41] "block4_pool"              "dropout_3"               
-[43] "block5_conv1"             "batch_normalization_10"  
-[45] "activation_10"            "block5_conv2"            
-[47] "batch_normalization_11"   "activation_11"           
-[49] "block5_conv3"             "batch_normalization_12"  
-[51] "activation_12"            "block5_pool"             
-[53] "dropout_4"                "global_max_pooling2d"    
-[55] "additional_input"         "concatenate"             
-[57] "dense"                    "dropout_5"               
-[59] "activation_13"            "dense_1"                 
-\end{verbatim}
-
-Among these layers, the ``global\_max\_pooling2d'' layer is a 2D global
-max pooling layer that outputs the results from the last convolutional
-blocks. As \citet{simonyan2014very} noted, all preceding convolutional
-blocks can be viewed as a large feature extractor. Consequently, the
-output from this layer provides features that can be utilized for
-various purposes, such as performing transfer learning.
-
-To obtain the features, provide the layer name using the
-\texttt{extract\_feature\_from\_layer} argument in the
-\texttt{predict()} method. This will return a \texttt{tibble} with the
-VSS and all features extracted from that layer. Each row corresponds to
-one plot. The features will be flattened into 2D and named with the
-prefix ``f\_'' followed by a number from one to the total number of
-features.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{plot\_resid}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
-\NormalTok{  checker}\SpecialCharTok{$}\FunctionTok{save\_plot}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
-\NormalTok{  wrapper}\SpecialCharTok{$}\FunctionTok{image\_to\_array}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
-\NormalTok{  wrapper}\SpecialCharTok{$}\FunctionTok{predict}\NormalTok{(}\AttributeTok{auxiliary =}\NormalTok{ checker}\SpecialCharTok{$}\FunctionTok{auxiliary}\NormalTok{(),}
-                  \AttributeTok{extract\_feature\_from\_layer =} \StringTok{"global\_max\_pooling2d"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-# A tibble: 1 x 257
-    vss   f_1   f_2   f_3   f_4   f_5    f_6   f_7    f_8   f_9   f_10  f_11
-  <dbl> <dbl> <dbl> <dbl> <dbl> <dbl>  <dbl> <dbl>  <dbl> <dbl>  <dbl> <dbl>
-1  3.16 0.151     0     0     0     0 0.0203 0.109 0.0203     0 0.0834     0
-# i 245 more variables: f_12 <dbl>, f_13 <dbl>, f_14 <dbl>, f_15 <dbl>,
-#   f_16 <dbl>, f_17 <dbl>, f_18 <dbl>, f_19 <dbl>, f_20 <dbl>, f_21 <dbl>,
-#   f_22 <dbl>, f_23 <dbl>, f_24 <dbl>, f_25 <dbl>, f_26 <dbl>, f_27 <dbl>,
-#   f_28 <dbl>, f_29 <dbl>, f_30 <dbl>, f_31 <dbl>, f_32 <dbl>, f_33 <dbl>,
-#   f_34 <dbl>, f_35 <dbl>, f_36 <dbl>, f_37 <dbl>, f_38 <dbl>, f_39 <dbl>,
-#   f_40 <dbl>, f_41 <dbl>, f_42 <dbl>, f_43 <dbl>, f_44 <dbl>, f_45 <dbl>,
-#   f_46 <dbl>, f_47 <dbl>, f_48 <dbl>, f_49 <dbl>, f_50 <dbl>, f_51 <dbl>, ...
-\end{verbatim}
-
-Alternatively, the \texttt{AUTO\_VI} class provides a way to extract
-features using the \texttt{vss()} method. This method is essentially a
-high-level wrapper around the \texttt{predict()} method of
-\texttt{KERAS\_WRAPPER}, but it offers a more straightforward interface
-and better default arguments.
-
-The results from the previous code example can be replicated with a
-single line of code as shown below.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{checker}\SpecialCharTok{$}\FunctionTok{vss}\NormalTok{(}\AttributeTok{extract\_feature\_from\_layer =} \StringTok{"global\_max\_pooling2d"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-# A tibble: 1 x 257
-    vss   f_1   f_2   f_3   f_4   f_5    f_6   f_7    f_8   f_9   f_10  f_11
-  <dbl> <dbl> <dbl> <dbl> <dbl> <dbl>  <dbl> <dbl>  <dbl> <dbl>  <dbl> <dbl>
-1  3.16 0.151     0     0     0     0 0.0203 0.109 0.0203     0 0.0834     0
-# i 245 more variables: f_12 <dbl>, f_13 <dbl>, f_14 <dbl>, f_15 <dbl>,
-#   f_16 <dbl>, f_17 <dbl>, f_18 <dbl>, f_19 <dbl>, f_20 <dbl>, f_21 <dbl>,
-#   f_22 <dbl>, f_23 <dbl>, f_24 <dbl>, f_25 <dbl>, f_26 <dbl>, f_27 <dbl>,
-#   f_28 <dbl>, f_29 <dbl>, f_30 <dbl>, f_31 <dbl>, f_32 <dbl>, f_33 <dbl>,
-#   f_34 <dbl>, f_35 <dbl>, f_36 <dbl>, f_37 <dbl>, f_38 <dbl>, f_39 <dbl>,
-#   f_40 <dbl>, f_41 <dbl>, f_42 <dbl>, f_43 <dbl>, f_44 <dbl>, f_45 <dbl>,
-#   f_46 <dbl>, f_47 <dbl>, f_48 <dbl>, f_49 <dbl>, f_50 <dbl>, f_51 <dbl>, ...
-\end{verbatim}
-
-The argument \texttt{extract\_feature\_from\_layer} is also available in
-other functions that build on the \texttt{vss()} method, including
-\texttt{null\_vss()}, \texttt{boot\_vss()}, and \texttt{check()}.
-
-\subsection{Trained Model Hosting}\label{sec-trained-model-hosting}
-
-The trained computer vision models described in \citet{li2024automated}
-are hosted on a GitHub repository at
-\url{https://github.com/TengMCing/autovi_data}. Currently, there are six
-models available. You can view them by calling
-\texttt{list\_keras\_model()}, which will return a \texttt{tibble}
-showing the input shape and a description of each model.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{list\_keras\_model}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{str}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-tibble [6 x 11] (S3: tbl_df/tbl/data.frame)
- $ model_name          : chr [1:6] "vss_32" "vss_64" "vss_128" "vss_phn_32" ...
- $ path                : chr [1:6] "keras_model/vss_32.keras.zip" "keras_model/vss_64.keras.zip" "keras_model/vss_128.keras.zip" "keras_model/vss_phn_32.keras.zip" ...
- $ volume_path         : chr [1:6] "keras_model_volumes/vss_32.zip.001" "keras_model_volumes/vss_64.zip.001" "keras_model_volumes/vss_128.zip.001" "keras_model_volumes/vss_phn_32.zip.001" ...
- $ volume_size         : int [1:6] 4 1 8 2 8 8
- $ npz_path            : chr [1:6] "keras_model_npz/vss_32.npz" "keras_model_npz/vss_64.npz" "keras_model_npz/vss_128.npz" "keras_model_npz/vss_phn_32.npz" ...
- $ npz_py              : chr [1:6] "keras_model_npz/vss_32_rebuild.py" "keras_model_npz/vss_64_rebuild.py" "keras_model_npz/vss_128_rebuild.py" "keras_model_npz/vss_phn_32_rebuild.py" ...
- $ input_height        : int [1:6] 32 64 128 32 64 128
- $ input_width         : int [1:6] 32 64 128 32 64 128
- $ input_channels      : int [1:6] 3 3 3 3 3 3
- $ auxiliary_input_size: int [1:6] 0 0 0 5 5 5
- $ description         : chr [1:6] "A Keras model trained with residual plots containing non-linearity and heteroskedasticity patterns." "A Keras model trained with residual plots containing non-linearity and heteroskedasticity patterns." "A Keras model trained with residual plots containing non-linearity and heteroskedasticity patterns." "A Keras model trained with residual plots containing non-linearity, heteroskedasticity and non-normality patterns." ...
-\end{verbatim}
-
-The \texttt{get\_keras\_model()} function can be used to download a
-model to a temporary directory and load it into memory using
-\texttt{TensorFlow}. It requires only the model name, which is the value
-in the first column of the \texttt{tibble} returned by
-\texttt{list\_keras\_model()}.
+specific needs. These modules are discussed in detail on the software's
+website.
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{figures/autovi_web.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{figures/autovi_web.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{figures/autovi_web_type.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{figures/autovi_web_type.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{figures/autovi_web_result.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{figures/autovi_web_result.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{figures/autovi_web_result2.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{figures/autovi_web_result2.png}
 
@@
 
-\includegraphics[width=0.5\textwidth,height=\textheight]{figures/autovi_web_gradient_hide.png}
+\includegraphics[width=0.5\linewidth,height=\textheight,keepaspectratio]{figures/autovi_web_gradient_hide.png}
 
@@
 
-\includegraphics[width=0.8\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example1-1.png}
+\includegraphics[width=0.8\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example1-1.png}
 
@@
 
-\includegraphics[width=0.8\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example2-1.png}
+\includegraphics[width=0.8\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example2-1.png}
 
@@
 
-\includegraphics[width=0.55\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example3-1.png}
+\includegraphics[width=0.55\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example3-1.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example4-1.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example4-1.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example5-1.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example5-1.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example6-1.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example6-1.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example7-1.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example7-1.png}
 

### 2024-11-19 autovi_paper.qmd
done with cutting paper

@@
 
-## Numerical Summary {#sec-autovi-usage}
+## Usage {#sec-autovi-usage}
+
+### Numerical Summary {#sec-autovi-numerical}
 
@@
 
-## Visual Summary {#sec-autovi-visual}
+### Visual Summary {#sec-autovi-visual}
 
@@
 
-## Design {#sec-autovi-web-design}
+<!-- ## Design {#sec-autovi-web-design}-->
 
@@
 Region 5 is empty in the default view but will be populated with results once the analysis is started.
-"}
+", eval=FALSE}
 knitr::include_graphics("figures/autovi_web.png")
@@
 
-While the R package `autovi` aims to provide tools that can be extended to broader visual inference applications, `autovi.web` is only focus on providing  a straightforward and clean user interface.
+<!--The focus of `autovi.web` is on providing a straightforward and clean user interface.
 An overview of the graphical user interface of `autovi.web` is provided in @fig-autovi-web.
@@
 After uploading the CSV file, the user must select the correct format to ensure the web interface interprets the data correctly.
+-->
 
@@
 Compared to @fig-autovi-web, where the CSV type is a single residual plot, choosing a CSV type that includes a lineup of multiple residual plots adds a dropdown menu for specifying a column for the residual plot identifier.
-Additionally, an optional dropdown menu for specifying the true residual plot identifier will appear under the simulation settings."}
+Additionally, an optional dropdown menu for specifying the true residual plot identifier will appear under the simulation settings.", eval=FALSE}
 knitr::include_graphics("figures/autovi_web_type.png")
@@
 
-Region 3 of @fig-autovi-web is a panel for column selection and simulation settings.
+<!--Region 3 of @fig-autovi-web is a panel for column selection and simulation settings.
 As shown in @fig-autovi-web, if the CSV type is set to a single residual plot, there will be two dropdown menus for specifying the columns for fitted values and residuals, respectively.
@@
 Generally, there will be four result panels, as shown in @fig-autovi-web-result and @fig-autovi-web-result2.
+-->
 
@@
 In region 1, there is an interactive table detailing the VSS, with a summary of the analysis provided in the paragraph below.
-Region 2 displays a lineup of residual plots."}
+Region 2 displays a lineup of residual plots.", eval=FALSE}
 knitr::include_graphics("figures/autovi_web_result.png")
@@
 Region 1 presents a density plot comparing the bootstrapped VSS with the null VSS.
-Region 2 includes an attention map of the true residual plot."}
+Region 2 includes an attention map of the true residual plot.", eval=FALSE}
 knitr::include_graphics("figures/autovi_web_result2.png")
@@
 ```{r fig-autovi-web-gradient-hide, out.width = "50%", fig.cap = "The attention map is hidden if the assessment indicates a $p$-value greater than 0.05.
-A button is available to toggle the display of the attention map."}
+A button is available to toggle the display of the attention map.", eval=FALSE}
 knitr::include_graphics("figures/autovi_web_gradient_hide.png")
@@
 
-Region 6 of @fig-autovi-web-result contains an interactive table created with the R package `DT` [@dt], which provides the VSS.
+<!-- Region 6 of @fig-autovi-web-result contains an interactive table created with the R package `DT` [@dt], which provides the VSS.
 This table includes four columns: `.sample`, `vss`, `rank`, and `null`.
@@
 However, to provide users with the option to review it if they wish, a button will be available, as shown in @fig-autovi-web-gradient-hide.
-This button allows users to toggle the display of the attention map.
-
-## Workflow {#sec-autovi-web-workflow}
-
-The workflow of `autovi.web` is designed to be straightforward, with numbered steps displayed in each panel shown in @fig-autovi-web.
-There are two example datasets provided by the web application, as mentioned in @sec-autovi-web-design.
+This button allows users to toggle the display of the attention map.-->
+
+## Usage {#sec-autovi-web-workflow}
+
+The workflow of `autovi.web` is designed to be straightforward, with numbered steps displayed in each panel.
+There are two example datasets provided by the web application.
 The single residual plot example uses the `dino` dataset from the R package `datasauRus` [@datasaurus].
@@
 
-As shown in @fig-autovi-web-workflow-example1, to use the lineup example data, click the "Use Lineup Example" button.
+### Reading data and setting parameters
+
+The user can select to upload data as either a single set of residuals or a pre-computed lineup of residuals and nulls.
+Here we illustrate use with lineup example data sets (@fig-autovi-web-setup).
+To use the lineup example data, click the "Use Lineup Example" button.
 The data status will then update to show the number of rows and columns in the dataset, and the CSV type will automatically be selected to the correct option.
-Since the example dataset follows the variable naming conventions assumed by the web application, the columns for fitted values, residuals, and labels of residual plots are set automatically (@fig-autovi-web-workflow-example2).
+Since the example dataset follows the variable naming conventions assumed by the web application, the columns for fitted values, residuals, and labels of residual plots are set automatically (middle image).
 If the user is working with a custom dataset, these options must be set accordingly.
-Regardless of the dataset, the user must manually select the label for the true residual plot, as the web application allows assessments without this label.
-The next step is to click the play button to start the assessment.
-
-Results are provided in multiple panels as displayed in @fig-autovi-web-workflow-example3, @fig-autovi-web-workflow-example4, @fig-autovi-web-workflow-example5 and @fig-autovi-web-workflow-example6.
-In @fig-autovi-web-workflow-example3, the first row of the table is the most crucial to check, as it provides the VSS and the rank of the true residual plot among the other plots.
+Regardless of the dataset, the user must manually select the label for the true residual plot, whenever a lineup file is provided, as the web application allows assessments without this label.
+The last step is to click the play button (right image) to start the assessment.
+
+```{r fig-autovi-web-setup, out.width = "100%", fig.cap = 'To begin the workflow for `autovi` using the lineup example dataset, the user clicks the "Use Lineup Example" button (left) to load the example dataset, during which the data status and CSV type will be automatically updated.
+The target columns are selected automatically, though the user must manually select the label for the true residual plot (middle), as the web application permits assessment without this label.
+The user initiates the assessment of the lineup example data by clicking the run button (right).'}
+magick::image_read_pdf("figures/autovi_web_setup.pdf")
+```
+
+```{r fig-autovi-web-workflow-example1, out.width = "80%", fig.cap = 'To begin the workflow for `autovi` using the lineup example dataset, the user clicks the "Use Lineup Example" button to load the example dataset, during which the data status and CSV type will be automatically updated.', eval=FALSE}
+magick::image_read_pdf("figures/autovi_web_workflow_1.pdf")
+```
+
+```{r fig-autovi-web-workflow-example2, out.width = "80%", fig.cap = 'After clicking the button in @fig-autovi-web-workflow-example1, the target columns are selected automatically, though the user must manually select the label for the true residual plot, as the web application permits assessment without this label.', eval=FALSE}
+magick::image_read_pdf("figures/autovi_web_workflow_2.pdf")
+```
+
+```{r fig-autovi-web-workflow-example3, out.width = "55%", fig.cap = 'After finishing the required steps in @fig-autovi-web-workflow-example1 and @fig-autovi-web-workflow-example2, the user initiates the assessment of the lineup example data by clicking the run button.', eval=FALSE}
+magick::image_read_pdf("figures/autovi_web_workflow_3.pdf")
+```
+
+### Results provided
+
+Results are provided in multiple panels.<!-- as displayed in @fig-autovi-web-workflow-example3, @fig-autovi-web-workflow-example4, @fig-autovi-web-workflow-example5 and @fig-autovi-web-workflow-example6.
+In @fig-autovi-web-workflow-example3--> The first row of the table [@fig-autovi-web-lineup] is the most crucial to check, as it provides the VSS and the rank of the true residual plot among the other plots.
 The summary text beneath the table provides the $p$-value, which can be used for quick decision-making.
-In @fig-autovi-web-workflow-example4, the lineup is for manual inspection, and the user should see if the true residual plot is visually distinguishable from the other plots, to confirm if the model violation is serious.
-The density plot in @fig-autovi-web-workflow-example5 offers a more robust result, allowing the user to compare the distribution of bootstrapped VSS with the distribution of null VSS.
-Finally, the grayscale attention map shown in @fig-autovi-web-workflow-example6 can be used to check if the target visual features, like the non-linearity present in the lineup example, are captured by the computer vision model, ensuring the quality of the assessment.
-
-```{r fig-autovi-web-workflow-example1, out.width = "80%", fig.cap = 'To begin the workflow for `autovi` using the lineup example dataset, the user clicks the "Use Lineup Example" button to load the example dataset, during which the data status and CSV type will be automatically updated.'}
-magick::image_read_pdf("figures/autovi_web_workflow_1.pdf")
-```
-
-```{r fig-autovi-web-workflow-example2, out.width = "80%", fig.cap = 'After clicking the button in @fig-autovi-web-workflow-example1, the target columns are selected automatically, though the user must manually select the label for the true residual plot, as the web application permits assessment without this label.'}
-magick::image_read_pdf("figures/autovi_web_workflow_2.pdf")
-```
-
-```{r fig-autovi-web-workflow-example3, out.width = "55%", fig.cap = 'After finishing the required steps in @fig-autovi-web-workflow-example1 and @fig-autovi-web-workflow-example2, the user initiates the assessment of the lineup example data by clicking the run button.'}
-magick::image_read_pdf("figures/autovi_web_workflow_3.pdf")
-```
-
-```{r fig-autovi-web-workflow-example4, out.width = "100%", fig.cap = 'The VSS of the true residual plot is displayed in the first row of the table, with a summary text beneath the table providing the $p$-value to aid in decision-making.'}
+The lineup is for manual inspection, and the user should see if the true residual plot is visually distinguishable from the other plots, to confirm if the model violation is serious.
+
+The density plot in @fig-autovi-web-distributions offers a more robust result, allowing the user to compare the distribution of bootstrapped VSS with the distribution of null VSS.
+Finally, the grayscale attention map (right image) can be used to check if the target visual features, like the non-linearity present in the lineup example, are captured by the computer vision model, ensuring the quality of the assessment.
+
+```{r fig-autovi-web-lineup, out.width = "100%", fig.cap = 'Results for the lineup.
+The VSS of the true residual plot is displayed in the first row of the table of VSS values for all the null plots (left image), with a summary text beneath the table providing the $p$-value to aid in decision-making.
+A lineup of residual plots allows for manual inspection (right image).
+'}
+magick::image_read_pdf("figures/autovi_web_lineup.pdf")
+```
+
+```{r fig-autovi-web-distributions, out.width = "100%", fig.cap = 'Summaries assessing the strength of the pattern and which elements of the plot contribute.
+The density plot helps verify if the bootstrapped distribution differs from the null distribution (left image).
+The attention map (right image) offers insights into whether the computer vision model has captured the intended visual features of the true residual plot.'}
+magick::image_read_pdf("figures/autovi_web_distributions.pdf")
+```
+
+```{r fig-autovi-web-workflow-example4, out.width = "100%", fig.cap = 'The VSS of the true residual plot is displayed in the first row of the table, with a summary text beneath the table providing the $p$-value to aid in decision-making.', eval=FALSE}
 magick::image_read_pdf("figures/autovi_web_workflow_4.pdf")
@@
 
-```{r fig-autovi-web-workflow-example5, out.width = "100%", fig.cap = 'A lineup of residual plots allows for manual inspection.'}
+```{r fig-autovi-web-workflow-example5, out.width = "100%", fig.cap = 'A lineup of residual plots allows for manual inspection.', eval=FALSE}
 magick::image_read_pdf("figures/autovi_web_workflow_5.pdf")
@@
 
-```{r fig-autovi-web-workflow-example6, out.width = "100%", fig.cap = 'The density plot helps verify if the bootstrapped distribution differs from the null distribution.'}
+```{r fig-autovi-web-workflow-example6, out.width = "100%", fig.cap = 'The density plot helps verify if the bootstrapped distribution differs from the null distribution.', eval=FALSE}
 magick::image_read_pdf("figures/autovi_web_workflow_6.pdf")
@@
 
-```{r fig-autovi-web-workflow-example7, out.width = "100%", fig.cap = 'The attention map offers insights into whether the computer vision model has captured the intended visual features of the true residual plot.'}
+```{r fig-autovi-web-workflow-example7, out.width = "100%", fig.cap = 'The attention map offers insights into whether the computer vision model has captured the intended visual features of the true residual plot.', eval=FALSE}
 magick::image_read_pdf("figures/autovi_web_workflow_7.pdf")

### 2024-11-19 autovi_paper.tex
done with cutting paper

@@
 
-\subsection{Numerical Summary}\label{sec-autovi-usage}
+\subsection{Usage}\label{sec-autovi-usage}
+
+\subsubsection{Numerical Summary}\label{sec-autovi-numerical}
 
@@
 
-\subsection{Visual Summary}\label{sec-autovi-visual}
+\subsubsection{Visual Summary}\label{sec-autovi-visual}
 
@@
 programming experience. Additionally, updates are managed centrally,
-ensuring that users always have access to the latest features.
-
-The \texttt{autovi.web} interface is available at
-\url{autoviweb.netlify.app}. This section discusses the implementation
-based on \texttt{autovi.web} version 0.1.0.
+ensuring that users always have access to the latest features. This
+section discusses the implementation based on \texttt{autovi.web}
+version 0.1.0.
 
@@
 
-\subsection{Design}\label{sec-autovi-web-design}
-
-\begin{figure}
-
-\centering{
-
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{figures/autovi_web.png}
-
-}
-
-\caption{\label{fig-autovi-web}Overview of the \texttt{autovi.web}
-graphical user interface (GUI). This default view may change based on
-user interactions. Region 1 is the sidebar menu, containing the residual
-assessment tab and the information tab. Region 2 is the data upload
-panel, where users can provide a CSV file and specify the type of data
-it contains. Region 3 includes dropdown menus for selecting the columns
-to be analyzed, a slider to control the number of bootstrapping samples,
-and a numeric input box for setting the simulation seed. Region 4
-displays the initialization status and offers a button to start the
-analysis. Region 5 is empty in the default view but will be populated
-with results once the analysis is started.}
-
-\end{figure}%
-
-While the R package \texttt{autovi} aims to provide tools that can be
-extended to broader visual inference applications, \texttt{autovi.web}
-is only focus on providing a straightforward and clean user interface.
-An overview of the graphical user interface of \texttt{autovi.web} is
-provided in Figure~\ref{fig-autovi-web}. This is the default view of the
-web application, and there are five regions that user can mainly
-interact with. Region 1 of Figure~\ref{fig-autovi-web} is a sidebar menu
-which can switch between the analysis page and the information page. The
-analysis page is the focus of this section.
-
-Region 2 of Figure~\ref{fig-autovi-web} is a panel for data uploading
-and CSV type selection. Clicking the ``upload CSV'' button opens a
-window where the user can select a file from their local system. The
-data status displayed above the button provides information about the
-number of rows and columns in the current dataset. Additionally, there
-are two example datasets available beneath the ``upload CSV'' button:
-one is a lineup example using a CSV file with three columns, and the
-other is a single plot example using a CSV file with two columns. More
-details about these example datasets are be discussed in
-Section~\ref{sec-autovi-web-workflow}.
-
-While the \texttt{autovi} package typically expects a fitted regression
-model object provided by the user, this approach is impractical for a
-web interface. Saving the R model object to the filesystem involves
-extra steps and requires users to have specific knowledge, which does
-not align with the goal of the web application. Moreover, the regression
-model object may contain sensitive, non-shareable data, making it
-unsuitable for uploading. Additionally, model objects are often
-unnecessarily large, containing extra information not needed for
-residual diagnostics. In contrast, a CSV file is easier to generate
-using various software programs, not just R. CSV files are widely
-accepted and can be easily viewed and modified using common desktop
-applications like Excel. They are generally less sensitive than raw
-data, as they exclude most information about the predictors.
-
-The web application is designed to assess either a single residual plot
-or a lineup of residual plots. Therefore, it accepts only two types of
-CSV files: one with at least two columns representing the fitted values
-and residuals of a single residual plot, and another with at least three
-columns, where the additional column serves as the label or identifier
-for a lineup of multiple residual plots. For a single residual plot, 19
-null plots are generated by simulating normal random draws from a
-distribution with the same variance as the original residual plot, and
-comparisons are made with the original residual plot. For a lineup,
-comparisons are made among the plots within the lineup. After uploading
-the CSV file, the user must select the correct format to ensure the web
-interface interprets the data correctly.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{figures/autovi_web_type.png}
-
-}
-
-\caption{\label{fig-autovi-web-type}The panels for selecting target
-columns and simulation settings are updated when a different CSV type is
-selected in the left panel. Compared to Figure~\ref{fig-autovi-web},
-where the CSV type is a single residual plot, choosing a CSV type that
-includes a lineup of multiple residual plots adds a dropdown menu for
-specifying a column for the residual plot identifier. Additionally, an
-optional dropdown menu for specifying the true residual plot identifier
-will appear under the simulation settings.}
-
-\end{figure}%
-
-Region 3 of Figure~\ref{fig-autovi-web} is a panel for column selection
-and simulation settings. As shown in Figure~\ref{fig-autovi-web}, if the
-CSV type is set to a single residual plot, there will be two dropdown
-menus for specifying the columns for fitted values and residuals,
-respectively. The default variable names for these columns are
-\texttt{.fitted} and \texttt{.resid}. After uploading the CSV file, the
-content of these dropdown menus will be updated to reflect the existing
-columns in the dataset. As displayed in
-Figure~\ref{fig-autovi-web-type}, for the CSV type that is a lineup of
-multiple residual plots, an additional dropdown menu will appear for
-specifying the column of residual plot labels. The default variable name
-for this column is \texttt{.sample}. If this variable name does not
-exist in the dataset, the dropdown menu will remain empty, allowing the
-user to specify the correct column. The number of levels for each option
-in this dropdown menu will be displayed to help avoid the selection of a
-variable with too many levels, which could significantly slow down the
-application due to extensive computation.
-
-Under the simulation settings, there is a slider for specifying the
-number of bootstrapped samples needed for the assessment. A higher value
-on this slider will result in a more accurate bootstrap distribution
-estimation, though it will require more computation time. The simulation
-seed can be set in a numeric input box below the slider to control the
-reproducibility of the assessment. By default, a random seed is set each
-time the web page is refreshed. When the CSV type is a lineup of
-multiple residual plots, an optional dropdown menu will appear next to
-the simulation seed input box, allowing the user to specify an
-identifier for the true residual plot. If no label is provided for the
-true residual plot, the assessment will only estimate the VSS for each
-residual plot in the lineup, without providing a \(p\)-value, as it
-cannot be computed. Consequently, some result panels may be missing due
-to insufficient information. This option is useful when the lineup
-consists solely of null plots or if the user simply wants to obtain the
-VSS for multiple residual plots.
-
-Region 4 of Figure~\ref{fig-autovi-web} is the panel for triggering the
-assessment. It contains a large play button to start the assessment.
-Above the play button, a text message displays the status of
-\texttt{TensorFlow.js}, allowing users to monitor whether the JavaScript
-library and Keras model have been loaded correctly. The play button will
-remain disabled until both the data status in Region 1 and the
-\texttt{TensorFlow.js} status in Region 4 indicate that everything is
-ready, with both showing a green status.
-
-Once the play button is clicked, region 5 of Figure~\ref{fig-autovi-web}
-will be populated with panels displaying the assessment results.
-Generally, there will be four result panels, as shown in
-Figure~\ref{fig-autovi-web-result} and
-Figure~\ref{fig-autovi-web-result2}.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{figures/autovi_web_result.png}
-
-}
-
-\caption{\label{fig-autovi-web-result}The first two panels of results
-from the automated residual assessment are shown. The application
-provides four results panels in total, and these screenshots display the
-first two. In region 1, there is an interactive table detailing the VSS,
-with a summary of the analysis provided in the paragraph below. Region 2
-displays a lineup of residual plots.}
-
-\end{figure}%
-
-\begin{figure}
-
-\centering{
-
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{figures/autovi_web_result2.png}
-
-}
-
-\caption{\label{fig-autovi-web-result2}The last two panels of results
-from the automated residual assessment are shown. The application
-provides four results panels in total, and these screenshots display the
-final two. Region 1 presents a density plot comparing the bootstrapped
-VSS with the null VSS. Region 2 includes an attention map of the true
-residual plot.}
-
-\end{figure}%
-
-\begin{figure}
-
-\centering{
-
-\includegraphics[width=0.5\linewidth,height=\textheight,keepaspectratio]{figures/autovi_web_gradient_hide.png}
-
-}
-
-\caption{\label{fig-autovi-web-gradient-hide}The attention map is hidden
-if the assessment indicates a \(p\)-value greater than 0.05. A button is
-available to toggle the display of the attention map.}
-
-\end{figure}%
-
-Region 6 of Figure~\ref{fig-autovi-web-result} contains an interactive
-table created with the R package \texttt{DT} \citep{dt}, which provides
-the VSS. This table includes four columns: \texttt{.sample},
-\texttt{vss}, \texttt{rank}, and \texttt{null}. The \texttt{.sample}
-column shows the residual plot labels. For a CSV type that is a lineup,
-these labels are taken from an identifier column in the dataset
-specified by the user. In the case of the CSV type is a single residual
-plot, labels are automatically generated from 1 to 20, with the true
-residual plot receiving a randomly assigned label. The \texttt{vss}
-column displays the VSS for each residual plot, rounded to three decimal
-places. The \texttt{rank} column indicates the ranking of each residual
-plot based on VSS. The \texttt{null} column reveals whether the plot is
-a null plot. For the CSV type that is a single residual plot, only the
-true residual plot will have ``false'' in this column, while all other
-plots will be marked ``true.'' For the CSV type that is a lineup, if the
-true residual plot identifier has not been provided, this column will
-show ``NA'' to represent missing values. If the identifier is provided
-by user, the column behaves as if the CSV type is a single residual
-plot.
-
-The \texttt{DT} table provides several interactive features. Users can
-download the table in four formats, including text, CSV, Excel, and PDF,
-using the buttons located above the table. Additionally, the table is
-searchable via the text input field also positioned above it. Below the
-table, a text message displays the \(p\)-value of the assessment for the
-true residual plot and summarizes the number of null plots with VSS
-greater than that of the true residual plot. This helps the user
-determine whether the true residual plot shows visual patterns that
-suggest model violations.
-
-Region 7 of Figure~\ref{fig-autovi-web-result} provides a lineup of
-plots corresponding to each \texttt{.sample} value from the table in
-Region 6. Due to space limitations, a maximum of 20 residual plots will
-be displayed, ensuring that the true residual plot, if known, will be
-included in the lineup. The plots are generated using \texttt{ggplot2},
-the same as in \texttt{autovi}. Users can perform a visual test with
-this lineup to check if the true residual plot is distinguishable from
-the other plots, helping to determine the significance of model
-violations.
-
-Region 8 of Figure~\ref{fig-autovi-web-result2} displays the density
-plot for bootstrapped VSS and null VSS. The densities are shown in
-distinct colors that are friendly for colorblind users. A solid vertical
-line marks the VSS of the true residual plot, while rug lines at the
-bottom of the plot provide a clearer view of individual cases. Below the
-plot, a text message indicates the number and percentage of bootstrapped
-residual plots that would be rejected by the visual test when compared
-to the null plots. Note that the bootstrapped residual plots in this
-application are generated differently from \texttt{autovi}. Since we do
-not have the R model object, we can not refit the regression model with
-bootstrapped data. Instead, we bootstrap the residuals of the true
-residual plot directly to obtain bootstrapped residual plots. As as
-result, this panel will disappear when the true residual plot is
-unknown.
-
-Region 9 of Figure~\ref{fig-autovi-web-result2} displays an attention
-map for the true residual plot, generated by computing the gradient of
-the Keras model's output with respect to the greyscale input of the
-plot. The attention map helps to understand how the Keras model predicts
-VSS and which areas it is focusing on. We use a greyscale input because
-it is easier to generate a clear attention map in this format, and it
-usually conveys all the essential information, as most of the important
-details of the plot are drawn in black. If the \(p\)-value of the true
-residual plot is greater than 0.05, checking the attention map is not
-necessary. However, to provide users with the option to review it if
-they wish, a button will be available, as shown in
-Figure~\ref{fig-autovi-web-gradient-hide}. This button allows users to
-toggle the display of the attention map.
-
-\subsection{Workflow}\label{sec-autovi-web-workflow}
+\subsection{Usage}\label{sec-autovi-web-workflow}
 
 The workflow of \texttt{autovi.web} is designed to be straightforward,
-with numbered steps displayed in each panel shown in
-Figure~\ref{fig-autovi-web}. There are two example datasets provided by
-the web application, as mentioned in
-Section~\ref{sec-autovi-web-design}. The single residual plot example
-uses the \texttt{dino} dataset from the R package \texttt{datasauRus}
-\citep{datasaurus}. The lineup example uses residuals from a simulated
-regression model that has a non-linearity issue. We will walk through
-the lineup example to further demonstrate the workflow of the web
-application.
-
-As shown in Figure~\ref{fig-autovi-web-workflow-example1}, to use the
-lineup example data, click the ``Use Lineup Example'' button. The data
-status will then update to show the number of rows and columns in the
-dataset, and the CSV type will automatically be selected to the correct
-option. Since the example dataset follows the variable naming
+with numbered steps displayed in each panel. There are two example
+datasets provided by the web application. The single residual plot
+example uses the \texttt{dino} dataset from the R package
+\texttt{datasauRus} \citep{datasaurus}. The lineup example uses
+residuals from a simulated regression model that has a non-linearity
+issue. We will walk through the lineup example to further demonstrate
+the workflow of the web application.
+
+\subsubsection{Reading data and setting
+parameters}\label{reading-data-and-setting-parameters}
+
+The user can select to upload data as either a single set of residuals
+or a pre-computed lineup of residuals and nulls. Here we illustrate use
+with lineup example data sets (Figure~\ref{fig-autovi-web-setup}). To
+use the lineup example data, click the ``Use Lineup Example'' button.
+The data status will then update to show the number of rows and columns
+in the dataset, and the CSV type will automatically be selected to the
+correct option. Since the example dataset follows the variable naming
 conventions assumed by the web application, the columns for fitted
 values, residuals, and labels of residual plots are set automatically
-(Figure~\ref{fig-autovi-web-workflow-example2}). If the user is working
-with a custom dataset, these options must be set accordingly. Regardless
-of the dataset, the user must manually select the label for the true
-residual plot, as the web application allows assessments without this
-label. The next step is to click the play button to start the
+(middle image). If the user is working with a custom dataset, these
+options must be set accordingly. Regardless of the dataset, the user
+must manually select the label for the true residual plot, whenever a
+lineup file is provided, as the web application allows assessments
+without this label. The last step is to click the play button (right
+image) to start the assessment.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-setup-1.png}
+
+}
+
+\caption{\label{fig-autovi-web-setup}To begin the workflow for
+\texttt{autovi} using the lineup example dataset, the user clicks the
+``Use Lineup Example'' button (left) to load the example dataset, during
+which the data status and CSV type will be automatically updated. The
+target columns are selected automatically, though the user must manually
+select the label for the true residual plot (middle), as the web
+application permits assessment without this label. The user initiates
+the assessment of the lineup example data by clicking the run button
+(right).}
+
+\end{figure}%
+
+\subsubsection{Results provided}\label{results-provided}
+
+Results are provided in multiple panels. The first row of the table
+Figure~\ref{fig-autovi-web-lineup} is the most crucial to check, as it
+provides the VSS and the rank of the true residual plot among the other
+plots. The summary text beneath the table provides the \(p\)-value,
+which can be used for quick decision-making. The lineup is for manual
+inspection, and the user should see if the true residual plot is
+visually distinguishable from the other plots, to confirm if the model
+violation is serious.
+
+The density plot in Figure~\ref{fig-autovi-web-distributions} offers a
+more robust result, allowing the user to compare the distribution of
+bootstrapped VSS with the distribution of null VSS. Finally, the
+grayscale attention map (right image) can be used to check if the target
+visual features, like the non-linearity present in the lineup example,
+are captured by the computer vision model, ensuring the quality of the
 assessment.
 
-Results are provided in multiple panels as displayed in
-Figure~\ref{fig-autovi-web-workflow-example3},
-Figure~\ref{fig-autovi-web-workflow-example4},
-Figure~\ref{fig-autovi-web-workflow-example5} and
-Figure~\ref{fig-autovi-web-workflow-example6}. In
-Figure~\ref{fig-autovi-web-workflow-example3}, the first row of the
-table is the most crucial to check, as it provides the VSS and the rank
-of the true residual plot among the other plots. The summary text
-beneath the table provides the \(p\)-value, which can be used for quick
-decision-making. In Figure~\ref{fig-autovi-web-workflow-example4}, the
-lineup is for manual inspection, and the user should see if the true
-residual plot is visually distinguishable from the other plots, to
-confirm if the model violation is serious. The density plot in
-Figure~\ref{fig-autovi-web-workflow-example5} offers a more robust
-result, allowing the user to compare the distribution of bootstrapped
-VSS with the distribution of null VSS. Finally, the grayscale attention
-map shown in Figure~\ref{fig-autovi-web-workflow-example6} can be used
-to check if the target visual features, like the non-linearity present
-in the lineup example, are captured by the computer vision model,
-ensuring the quality of the assessment.
-
 \begin{figure}
@@
 
-\includegraphics[width=0.8\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example1-1.png}
-
-}
-
-\caption{\label{fig-autovi-web-workflow-example1}To begin the workflow
-for \texttt{autovi} using the lineup example dataset, the user clicks
-the ``Use Lineup Example'' button to load the example dataset, during
-which the data status and CSV type will be automatically updated.}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-lineup-1.png}
+
+}
+
+\caption{\label{fig-autovi-web-lineup}Results for the lineup. The VSS of
+the true residual plot is displayed in the first row of the table of VSS
+values for all the null plots (left image), with a summary text beneath
+the table providing the \(p\)-value to aid in decision-making. A lineup
+of residual plots allows for manual inspection (right image).}
 
@@
 
-\includegraphics[width=0.8\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example2-1.png}
-
-}
-
-\caption{\label{fig-autovi-web-workflow-example2}After clicking the
-button in Figure~\ref{fig-autovi-web-workflow-example1}, the target
-columns are selected automatically, though the user must manually select
-the label for the true residual plot, as the web application permits
-assessment without this label.}
-
-\end{figure}%
-
-\begin{figure}
-
-\centering{
-
-\includegraphics[width=0.55\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example3-1.png}
-
-}
-
-\caption{\label{fig-autovi-web-workflow-example3}After finishing the
-required steps in Figure~\ref{fig-autovi-web-workflow-example1} and
-Figure~\ref{fig-autovi-web-workflow-example2}, the user initiates the
-assessment of the lineup example data by clicking the run button.}
-
-\end{figure}%
-
-\begin{figure}
-
-\centering{
-
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example4-1.png}
-
-}
-
-\caption{\label{fig-autovi-web-workflow-example4}The VSS of the true
-residual plot is displayed in the first row of the table, with a summary
-text beneath the table providing the \(p\)-value to aid in
-decision-making.}
-
-\end{figure}%
-
-\begin{figure}
-
-\centering{
-
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example5-1.png}
-
-}
-
-\caption{\label{fig-autovi-web-workflow-example5}A lineup of residual
-plots allows for manual inspection.}
-
-\end{figure}%
-
-\begin{figure}
-
-\centering{
-
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example6-1.png}
-
-}
-
-\caption{\label{fig-autovi-web-workflow-example6}The density plot helps
-verify if the bootstrapped distribution differs from the null
-distribution.}
-
-\end{figure}%
-
-\begin{figure}
-
-\centering{
-
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-workflow-example7-1.png}
-
-}
-
-\caption{\label{fig-autovi-web-workflow-example7}The attention map
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-distributions-1.png}
+
+}
+
+\caption{\label{fig-autovi-web-distributions}Summaries assessing the
+strength of the pattern and which elements of the plot contribute. The
+density plot helps verify if the bootstrapped distribution differs from
+the null distribution (left image). The attention map (right image)
 offers insights into whether the computer vision model has captured the

### 2024-11-22 autovi_paper.qmd
fixed "however, the" and "it is would be"
fix "thus" -> "thus,"

@@
 Packages such as `nullabor` [@nullabor], `HLMdiag` [@loy2014hlmdiag], and `regressinator` [@regressinator], enable users to compare observed residual plots with samples from null distributions, helping to quantify the significance of any detected patterns.
-However, the
 
 However, as discussed in @li2024automated, the lineup protocol has significant limitations in large-scale applications due dependence on human labor.
-Thus a computer vision model was developed with an associated statistical testing procedure to automate the assessment of residual plots.
+Thus, a computer vision model was developed with an associated statistical testing procedure to automate the assessment of residual plots.
 This model takes a residual plot and a vector of auxiliary variables (such as the number of observations) as inputs and outputs the predicted visual signal strength (VSS).
@@
 The simulated example in (a) might be interpreted as a heteroscedastic pattern, however the automated reading would predict this to have a visual signal strength (VSS) of 1.53, with a corresponding $p$-value of 0.25.
-This means it is would be interpreted as a good residual plot, that there is nothing in the data to indicate a violation of model assumptions.
+This means it would be interpreted as a good residual plot, that there is nothing in the data to indicate a violation of model assumptions.
 Skewness in the predictor variables is generating the apparent heteroscedasticity, where the smaller variance in residuals at larger fitted values is due to smaller sample size only.

### 2024-11-23 autovi_paper.qmd
finish revising paper

@@
 The remaining seven modules are designed to be overridable, enabling users to tailor the infrastructure to their specific needs.
-These modules are discussed in detail on the software's website.
+These modules are discussed in detail on the software's website [https://tengmcing.github.io/autovi/](https://tengmcing.github.io/autovi/).
 <!-- in the following sections.-->
@@
 
-The `autovi.web` package extends the functionality of `autovi` by offering a user-friendly web interface for automated residual plot assessment.
+The `autovi.web` shiny application extends the functionality of `autovi` by offering a user-friendly web interface for automated residual plot assessment.
 This eliminates the common challenges associated with software installation, so users can avoid managing Python environments or handling version requirements for R libraries.
@@
 
-The package `autovi.web` is built using the `shiny` [@shiny] and `shinydashboard` [@shinydashboard] R packages.
+The interface `autovi.web` is built using the `shiny` [@shiny] and `shinydashboard` [@shinydashboard] R packages.
 Hosted on the [shinyapps.io](https://www.shinyapps.io) domain, the application is accessible through any modern web browser.
@@
 
-This paper presents new regression diagnostics software, the R package `autovi` and its accompanying web interface package, `autovi.web`.
+This paper presents new regression diagnostics software, the R package `autovi` and its accompanying web interface, `autovi.web`.
 It addresses a critical gap in the current landscape of statistical software.
@@
 
-The the current version of `autovi` can be installed from CRAN, and source code for both packages are available at [https://github.com/TengMCing/autovi](https://github.com/TengMCing/autovi).
+The current version of `autovi` can be installed from CRAN, and source code for both packages are available at [https://github.com/TengMCing/autovi](https://github.com/TengMCing/autovi) and [https://github.com/TengMCing/autovi_web](https://github.com/TengMCing/autovi_web) respectively.
 The web interface is available from [autoviweb.netlify.app](autoviweb.netlify.app).

### 2024-11-23 autovi_paper.tex
finish revising paper

@@
 \makeatletter
-\newsavebox\pandoc@box
-\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
-  \sbox\pandoc@box{#1}%
-  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
-  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
-  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
-  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
-  \else\usebox{\pandoc@box}%
-  \fi%
-}
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 % Set default figure placement to htbp
+\makeatletter
 \def\fps@figure{htbp}
@@
 
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 \usepackage[]{natbib}
@@
 with samples from null distributions, helping to quantify the
-significance of any detected patterns. However, the
+significance of any detected patterns.
 
@@
 has significant limitations in large-scale applications due dependence
-on human labor. Thus a computer vision model was developed with an
+on human labor. Thus, a computer vision model was developed with an
 associated statistical testing procedure to automate the assessment of
@@
 predict this to have a visual signal strength (VSS) of 1.53, with a
-corresponding \(p\)-value of 0.25. This means it is would be interpreted
-as a good residual plot, that there is nothing in the data to indicate a
+corresponding \(p\)-value of 0.25. This means it would be interpreted as
+a good residual plot, that there is nothing in the data to indicate a
 violation of model assumptions. Skewness in the predictor variables is
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-three-examples-1.pdf}
+\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-three-examples-1.pdf}
 
@@
 
-\includegraphics[width=0.6\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-plot-pair-1.pdf}
+\includegraphics[width=0.6\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-plot-pair-1.pdf}
 
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-summary-plot-1.pdf}
+\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-summary-plot-1.pdf}
 
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-diag-1.png}
+\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-diag-1.png}
 
@@
 specific needs. These modules are discussed in detail on the software's
-website.
+website \url{https://tengmcing.github.io/autovi/}.
 
@@
 
-The \texttt{autovi.web} package extends the functionality of
+The \texttt{autovi.web} shiny application extends the functionality of
 \texttt{autovi} by offering a user-friendly web interface for automated
@@
 
-The package \texttt{autovi.web} is built using the \texttt{shiny}
+The interface \texttt{autovi.web} is built using the \texttt{shiny}
 \citep{shiny} and \texttt{shinydashboard} \citep{shinydashboard} R
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-setup-1.png}
+\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-setup-1.png}
 
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-lineup-1.png}
+\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-lineup-1.png}
 
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-distributions-1.png}
+\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-distributions-1.png}
 
@@
 This paper presents new regression diagnostics software, the R package
-\texttt{autovi} and its accompanying web interface package,
-\texttt{autovi.web}. It addresses a critical gap in the current
-landscape of statistical software. While regression tools are widely
-available, effective and efficient diagnostic methods have lagged
-behind, particularly in the field of residual plot interpretation.
+\texttt{autovi} and its accompanying web interface, \texttt{autovi.web}.
+It addresses a critical gap in the current landscape of statistical
+software. While regression tools are widely available, effective and
+efficient diagnostic methods have lagged behind, particularly in the
+field of residual plot interpretation.
 
@@
 
-The the current version of \texttt{autovi} can be installed from CRAN,
-and source code for both packages are available at
-\url{https://github.com/TengMCing/autovi}. The web interface is
-available from \url{autoviweb.netlify.app}.
+The current version of \texttt{autovi} can be installed from CRAN, and
+source code for both packages are available at
+\url{https://github.com/TengMCing/autovi} and
+\url{https://github.com/TengMCing/autovi_web} respectively. The web
+interface is available from \url{autoviweb.netlify.app}.
 

### 2024-11-25 autovi_paper.qmd
fix metadata (including abstract)

--- 2024-11-22 autovi_paper.qmd
@@
 title: "Automated Residual Plot Assessment with the R Package autovi and Shiny App autovi.web"
-subtitle: ANZJS Quarto Template
 format:
@@
     include-in-header:
-      - template-header.tex
+      - header.tex
 date: today
@@
 abstract: |
-  Regression software is widely available, and there are many tools for generating diagnostics and computing conventional residual tests.
-However, the advice remains that the analyst should look at the residual plot to check the fit.
-Perhaps, one of the reasons is that conventional tests are too sensitive, strictly resulting in adequate models being abandoned.
-Visually assess the strength of patterns in residual plots requires human effort and suffers from the potential for inconsistent decisions from different analysts.
+  Visually assessing residual plots is the common advice for linear model diagnostics, however this approach requires manual human evaluation and thereby is not a scalable approach.
+Human evaluation also suffer from the potential for inconsistent decisions from different analysts.
 Using a lineup protocol, where the residual plot is embedded among null plots, can help to alleviate inconsistency, but requires even more human effort.

### 2024-11-25 autovi_paper.qmd
remove acknowledgement

@@
 abstract: |
-  Visually assessing residual plots is the common advice for linear model diagnostics, however this approach requires manual human evaluation and thereby is not a scalable approach.
+  Visually assessing residual plots is a common advice for linear model diagnostics, however this approach requires manual human evaluation and thereby is not scalable for assessing many models.
 Human evaluation also suffer from the potential for inconsistent decisions from different analysts.
@@
 For a user-provided sample of residuals, it predicts a measure of visual signal strength (VSS) and provides a suite of supporting information to assist the analyst decide on the appropriateness their model fit.
-# Below shows how acknowledgements should appear in the Journal.
-# Note that if you are acknowledging financial support, grant
-# numbers should *not* usually be specified.
-acknowledgement: >
-  The author acknowledges that this template is based on the latex template for Australian and New Zealand Journal of Statistics and intersperses some text from the original prototype document.
-\newline\vspace{1ex}\newline
-  Opinions and attitudes expressed in this document,
-  which are not explicitly designated as Journal policy, are those of
-  the author and are _not_ necessarily endorsed by the Journal,
-  its editorial board, its publisher Wiley or by the Australian
-  Statistical Publishing Association Inc.
 # Note that "keywords" should not include words and phrases
@@
 # capital letters) should *not* be capitalised.
-keywords: [initial data analysis, statistical graphics, data visualization, visual inference, computer vision, machine learning, hypothesis testing, regression analysis]
+keywords: [initial data analysis, statistical graphics, data visualization, visual inference, computer vision, machine learning, hypothesis testing, regression analysis, model diagnostics]
 bibliography: bibliography.bib  
@@
 
-Regression analysis is a widely used statistical modeling technique widely for data in many fields.
+Regression analysis is a widely used statistical modeling technique for data in many fields.
 There are a vast array of software for conducting regression modeling and generating diagnostics.
@@
 
-However, as discussed in @li2024automated, the lineup protocol has significant limitations in large-scale applications due dependence on human labor.
+However, as discussed in @li2024automated, the lineup protocol has significant limitations in large-scale applications due to dependence on human labor.
 Thus, a computer vision model was developed with an associated statistical testing procedure to automate the assessment of residual plots.
@@
 
-## Why use it {#sec-why}
+## Motivation for usage {#sec-why}
 
@@
 #| label: fig-three-examples
-#| fig-cap: "Reading residual plots can be a difficult task, particular for students new to statistical modeling.
-The autovi package makes it easier.
+#| fig-cap: "Reading residual plots can be a difficult task, particularly for students new to statistical modeling.
+The \\texttt{autovi} package makes it easier.
 Here are three examples of residual plots, which may appear to have structure.
@@
   geom_point() + 
-  ggtitle("a. simulated") +
+  ggtitle("(a) simulated") +
   theme_base(base_size = 12) + 
@@
   geom_point() + 
-  ggtitle("b. mtcars") +
+  ggtitle("(b) mtcars") +
   theme_base(base_size = 12) + 
@@
   geom_point() + 
-  ggtitle("c. surreal") +
+  ggtitle("(c) surreal") +
   theme_base(base_size = 12) + 
@@
 
-We recommend using the Shiny app `autovi.web` if encountering installation problems.
+We recommend using the Shiny app `autovi.web` if users encounter installation problems.
 
@@
 #| label: fig-autovi-diag
-#| fig-cap: "Diagram illustrating the infrastructure of the R package autovi.
+#| fig-cap: "Diagram illustrating the infrastructure of the R package \\texttt{autovi}.
 The modules in green are primary inputs provided by users.
@@
 The initial motivation for developing `autovi` was to create a convenient interface for sharing the models described and trained in @li2024automated.
-However, recognizing that the classical normal linear regression model represents a restricted class of models, we sought to avoid limiting the potential for future extensions, whether by the original developers or other users.
+However, recognizing that the classical normal linear regression model represents a restricted class of models, we sought to avoid limiting the potential for future extensions, whether by the original developers or other developers.
 As a result, the package was designed to function seamlessly with linear regression models with minimal modification and few required arguments, while also accommodating other classes of models through partial infrastructure substitution.
@@
 <!-- in the following sections.-->
-
+<!-- FIXME: ET: which website? >
 <!--

### 2024-11-25 autovi_paper.qmd
update wording

@@
 
-Determining the best way to implement the interface was difficult.
+Determining the best way to implement the backend was difficult.
 In our initial planning for `autovi.web`, we considered implementing the entire web application using the `webr` framework [@webr], which would have allowed the entire application to run directly in the user's browser.
@@
 The server-side configuration of `autovi.web` is carefully designed to support its functionality.
-Most required Python libraries, including `pillow` and `NumPy`, are pre-installed on the server.
+Most required Python libraries, including `pillow` and `numpy`, are pre-installed on the server.
 These libraries are integrated into the Shiny application using the `reticulate` package, which provides an interface between R and Python.
@@
 This choice enables native browser execution, enhancing compatibility across different user environments, and shifts the computational load from the server to the client-side.
-`TensorFlow.js` also offers better scalability and performance, especially when dealing with resource-intensive computer vision models on shinyapps.io.
+`TensorFlow.js` also offers better scalability and performance, especially when dealing with resource-intensive computer vision models on the web.
 
@@
 
-To allow communication between `TensorFlow.js` and other components of the Shiny application, the `shinyjs` R package is used.
+To allow communication between `TensorFlow.js` and other components of the Shiny application, the `shinyjs` R package [@shinyjs] is used.
 This package allows calling custom JavaScript code within the Shiny framework.
@@
 The lineup example uses residuals from a simulated regression model that has a non-linearity issue.
-We will walk through the lineup example to further demonstrate the workflow of the web application.
+We walk through the lineup example to further demonstrate the workflow of the web application.
 
@@
 
-The user can select to upload data as either a single set of residuals or a pre-computed lineup of residuals and nulls.
+The user can select to upload data as either a single set of residuals and fitted values in a two (or more) column CSV file or a pre-computed lineup of residuals and null datasets in a three (or more) column CSV file (i.e.
+multiple sets of residuals and fitted values with a column indicating the set label).
 Here we illustrate use with lineup example data sets (@fig-autovi-web-setup).
@@
 The data status will then update to show the number of rows and columns in the dataset, and the CSV type will automatically be selected to the correct option.
-Since the example dataset follows the variable naming conventions assumed by the web application, the columns for fitted values, residuals, and labels of residual plots are set automatically (middle image).
+Since the example dataset follows the variable naming conventions assumed by the web application, the columns for fitted values, residuals, and labels of residual plots are automatically mapped such that the column named as `.fitted` is mapped to fitted values, `.resid` is mapped to residuals and if applicable, `.sample` to labels of the residual set (middle image).
 If the user is working with a custom dataset, these options must be set accordingly.
-Regardless of the dataset, the user must manually select the label for the true residual plot, whenever a lineup file is provided, as the web application allows assessments without this label.
+Whenever a data containing a lineup, the user must manually select the label for the true residual plot, otherwise the web application does not provide all the results.
 The last step is to click the play button (right image) to start the assessment.
@@
 ```{r fig-autovi-web-setup, out.width = "100%", fig.cap = 'To begin the workflow for `autovi` using the lineup example dataset, the user clicks the "Use Lineup Example" button (left) to load the example dataset, during which the data status and CSV type will be automatically updated.
-The target columns are selected automatically, though the user must manually select the label for the true residual plot (middle), as the web application permits assessment without this label.
+The user must manually select the label for the true residual plot (middle) to compute further results.
 The user initiates the assessment of the lineup example data by clicking the run button (right).'}

### 2024-11-25 autovi_paper.tex
update wording

@@
 
-% The following \newcommands are intended for use in the *current*
-% document ("protoType"). It is unlikely that authors of papers submitted
-% to the Journal will need them.  (Of course if it turns out that you
-% do indeed need them, then by all means feel free to make use of them.)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{lipsum}
-
-\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
-T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\newcommand\MiKTeX{{\rmfamily M\kern-.05em \textsc{i\kern-.025em K}\kern-.08em
-T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\newcommand\PracTeX{{\rmfamily P\kern-.05em \textsc{r\kern-.025em a\kern-.025em
-c}\kern-.08em
-T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \usepackage{pmboxdraw}
@@
 \makeatother
-
 \ifLuaTeX
@@
 visualization, visual inference, computer vision, machine
-learning, hypothesis testing, regression analysis},
+learning, hypothesis testing, regression analysis, model diagnostics},
   colorlinks=true,
@@
 Shiny App autovi.web}
-\usepackage{etoolbox}
-\makeatletter
-\providecommand{\subtitle}[1]{% add subtitle to \maketitle
-  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
-}
-\makeatother
-\subtitle{ANZJS Quarto Template}
 
@@
 Susan VanderPlas\addressnum{3} and
-Klaus Ackermann
-\addressnum{1}
+Klaus Ackermann\addressnum{1}
 }
@@
 \begin{abstract}
-Regression software is widely available, and there are many tools for
-generating diagnostics and computing conventional residual tests.
-However, the advice remains that the analyst should look at the residual
-plot to check the fit. Perhaps, one of the reasons is that conventional
-tests are too sensitive, strictly resulting in adequate models being
-abandoned. Visually assess the strength of patterns in residual plots
-requires human effort and suffers from the potential for inconsistent
-decisions from different analysts. Using a lineup protocol, where the
-residual plot is embedded among null plots, can help to alleviate
-inconsistency, but requires even more human effort. This is the type of
-task that in today's world might employ a robot to do the tedious work
-for a human. Here we describe a new R package that includes a computer
-vision model for automated assessment of residual plots, and an
-accompanying Shiny app for ease of use. For a user-provided sample of
-residuals, it predicts a measure of visual signal strength (VSS) and
-provides a suite of supporting information to assist the analyst decide
-on the appropriateness their model fit.
+Visually assessing residual plots is a common advice for linear model
+diagnostics, however this approach requires manual human evaluation and
+thereby is not scalable for assessing many models. Human evaluation also
+suffer from the potential for inconsistent decisions from different
+analysts. Using a lineup protocol, where the residual plot is embedded
+among null plots, can help to alleviate inconsistency, but requires even
+more human effort. This is the type of task that in today's world might
+employ a robot to do the tedious work for a human. Here we describe a
+new R package that includes a computer vision model for automated
+assessment of residual plots, and an accompanying Shiny app for ease of
+use. For a user-provided sample of residuals, it predicts a measure of
+visual signal strength (VSS) and provides a suite of supporting
+information to assist the analyst decide on the appropriateness their
+model fit.
 \end{abstract}
@@
 visualization; visual inference; computer vision; machine
-learning; hypothesis testing; regression analysis}
-
-\ack{The author acknowledges that this template is based on the latex
-template for Australian and New Zealand Journal of Statistics and
-intersperses some text from the original prototype document.
-\newline\vspace{1ex}\newline Opinions and attitudes expressed in this
-document, which are not explicitly designated as Journal policy, are
-those of the author and are \emph{not} necessarily endorsed by the
-Journal, its editorial board, its publisher Wiley or by the Australian
-Statistical Publishing Association Inc.}
+learning; hypothesis testing; regression analysis; model diagnostics}
 
@@
 
-Regression analysis is a widely used statistical modeling technique
-widely for data in many fields. There are a vast array of software for
-conducting regression modeling and generating diagnostics. The package
+Regression analysis is a widely used statistical modeling technique for
+data in many fields. There are a vast array of software for conducting
+regression modeling and generating diagnostics. The package
 \texttt{lmtest} \citep{lmtest} provides a suite of conventional tests.
@@
 However, as discussed in \citet{li2024automated}, the lineup protocol
-has significant limitations in large-scale applications due dependence
-on human labor. Thus, a computer vision model was developed with an
-associated statistical testing procedure to automate the assessment of
-residual plots. This model takes a residual plot and a vector of
-auxiliary variables (such as the number of observations) as inputs and
-outputs the predicted visual signal strength (VSS). This strength
-estimates the distance between the residual distribution of the fitted
-regression model and the reference distribution assumed under correct
-model specification.
+has significant limitations in large-scale applications due to
+dependence on human labor. Thus, a computer vision model was developed
+with an associated statistical testing procedure to automate the
+assessment of residual plots. This model takes a residual plot and a
+vector of auxiliary variables (such as the number of observations) as
+inputs and outputs the predicted visual signal strength (VSS). This
+strength estimates the distance between the residual distribution of the
+fitted regression model and the reference distribution assumed under
+correct model specification.
 
@@
 
-\subsection{Why use it}\label{sec-why}
+\subsection{Motivation for usage}\label{sec-why}
 
@@
 \caption{\label{fig-three-examples}Reading residual plots can be a
-difficult task, particular for students new to statistical modeling. The
-autovi package makes it easier. Here are three examples of residual
-plots, which may appear to have structure. According to autovi, the
-visual signal strengths (VSS) of these three examples are approximately
-(a) 1.53, (b) 3.57, (c) 5.87, resulting in (b), (c) being significant
-violations of good residuals, but (a) is consistent with a good residual
-plot.}
+difficult task, particularly for students new to statistical modeling.
+The \texttt{autovi} package makes it easier. Here are three examples of
+residual plots, which may appear to have structure. According to autovi,
+the visual signal strengths (VSS) of these three examples are
+approximately (a) 1.53, (b) 3.57, (c) 5.87, resulting in (b), (c) being
+significant violations of good residuals, but (a) is consistent with a
+good residual plot.}
 
@@
 
-We recommend using the Shiny app \texttt{autovi.web} if encountering
+We recommend using the Shiny app \texttt{autovi.web} if users encounter
 installation problems.
@@
 \caption{\label{fig-autovi-diag}Diagram illustrating the infrastructure
-of the R package autovi. The modules in green are primary inputs
-provided by users. Modules in blue are overridable methods that can be
-modified to accommodate users' specific needs. The module in yellow is a
-pre-defined non-overridable method. The modules in red are primary
-outputs of the package.}
+of the R package \texttt{autovi}. The modules in green are primary
+inputs provided by users. Modules in blue are overridable methods that
+can be modified to accommodate users' specific needs. The module in
+yellow is a pre-defined non-overridable method. The modules in red are
+primary outputs of the package.}
 
@@
 sought to avoid limiting the potential for future extensions, whether by
-the original developers or other users. As a result, the package was
-designed to function seamlessly with linear regression models with
+the original developers or other developers. As a result, the package
+was designed to function seamlessly with linear regression models with
 minimal modification and few required arguments, while also
@@
 specific needs. These modules are discussed in detail on the software's
-website \url{https://tengmcing.github.io/autovi/}.
+website.
 
@@
 
-The \texttt{autovi.web} shiny application extends the functionality of
+The \texttt{autovi.web} package extends the functionality of
 \texttt{autovi} by offering a user-friendly web interface for automated
@@
 
-The interface \texttt{autovi.web} is built using the \texttt{shiny}
+The package \texttt{autovi.web} is built using the \texttt{shiny}
 \citep{shiny} and \texttt{shinydashboard} \citep{shinydashboard} R
@@
 
-Determining the best way to implement the interface was difficult. In
-our initial planning for \texttt{autovi.web}, we considered implementing
-the entire web application using the \texttt{webr} framework
-\citep{webr}, which would have allowed the entire application to run
-directly in the user's browser. However, this approach was not feasible
-at the time of writing this paper. The reason is that one of the R
-packages \texttt{autovi} depends on the R package \texttt{splancs}
+Determining the best way to implement the backend was difficult. In our
+initial planning for \texttt{autovi.web}, we considered implementing the
+entire web application using the \texttt{webr} framework \citep{webr},
+which would have allowed the entire application to run directly in the
+user's browser. However, this approach was not feasible at the time of
+writing this paper. The reason is that one of the R packages
+\texttt{autovi} depends on the R package \texttt{splancs}
 \citep{splancs}, which uses compiled Fortran code. A working Emscripten
@@
 designed to support its functionality. Most required Python libraries,
-including \texttt{pillow} and \texttt{NumPy}, are pre-installed on the
+including \texttt{pillow} and \texttt{numpy}, are pre-installed on the
 server. These libraries are integrated into the Shiny application using
@@
 performance, especially when dealing with resource-intensive computer
-vision models on shinyapps.io.
+vision models on the web.
 
@@
 To allow communication between \texttt{TensorFlow.js} and other
-components of the Shiny application, the \texttt{shinyjs} R package is
-used. This package allows calling custom JavaScript code within the
-Shiny framework. The specialized JavaScript code for initializing
-\texttt{TensorFlow.js} and calling \texttt{TensorFlow.js} for VSS
-prediction is deployed alongside the Shiny application as additional
-resources.
+components of the Shiny application, the \texttt{shinyjs} R package
+\citep{shinyjs} is used. This package allows calling custom JavaScript
+code within the Shiny framework. The specialized JavaScript code for
+initializing \texttt{TensorFlow.js} and calling \texttt{TensorFlow.js}
+for VSS prediction is deployed alongside the Shiny application as
+additional resources.
 
@@
 residuals from a simulated regression model that has a non-linearity
-issue. We will walk through the lineup example to further demonstrate
-the workflow of the web application.
+issue. We walk through the lineup example to further demonstrate the
+workflow of the web application.
 
@@
 The user can select to upload data as either a single set of residuals
-or a pre-computed lineup of residuals and nulls. Here we illustrate use
-with lineup example data sets (Figure~\ref{fig-autovi-web-setup}). To
-use the lineup example data, click the ``Use Lineup Example'' button.
-The data status will then update to show the number of rows and columns
-in the dataset, and the CSV type will automatically be selected to the
-correct option. Since the example dataset follows the variable naming
-conventions assumed by the web application, the columns for fitted
-values, residuals, and labels of residual plots are set automatically
-(middle image). If the user is working with a custom dataset, these
-options must be set accordingly. Regardless of the dataset, the user
-must manually select the label for the true residual plot, whenever a
-lineup file is provided, as the web application allows assessments
-without this label. The last step is to click the play button (right
-image) to start the assessment.
+and fitted values in a two (or more) column CSV file or a pre-computed
+lineup of residuals and null datasets in a three (or more) column CSV
+file (i.e.~multiple sets of residuals and fitted values with a column
+indicating the set label). Here we illustrate use with lineup example
+data sets (Figure~\ref{fig-autovi-web-setup}). To use the lineup example
+data, click the ``Use Lineup Example'' button. The data status will then
+update to show the number of rows and columns in the dataset, and the
+CSV type will automatically be selected to the correct option. Since the
+example dataset follows the variable naming conventions assumed by the
+web application, the columns for fitted values, residuals, and labels of
+residual plots are automatically mapped such that the column named as
+\texttt{.fitted} is mapped to fitted values, \texttt{.resid} is mapped
+to residuals and if applicable, \texttt{.sample} to labels of the
+residual set (middle image). If the user is working with a custom
+dataset, these options must be set accordingly. Whenever a data
+containing a lineup, the user must manually select the label for the
+true residual plot, otherwise the web application does not provide all
+the results. The last step is to click the play button (right image) to
+start the assessment.
 
@@
 which the data status and CSV type will be automatically updated. The
-target columns are selected automatically, though the user must manually
-select the label for the true residual plot (middle), as the web
-application permits assessment without this label. The user initiates
-the assessment of the lineup example data by clicking the run button
-(right).}
+user must manually select the label for the true residual plot (middle)
+to compute further results. The user initiates the assessment of the
+lineup example data by clicking the run button (right).}
 
@@
 This paper presents new regression diagnostics software, the R package
-\texttt{autovi} and its accompanying web interface, \texttt{autovi.web}.
-It addresses a critical gap in the current landscape of statistical
-software. While regression tools are widely available, effective and
-efficient diagnostic methods have lagged behind, particularly in the
-field of residual plot interpretation.
+\texttt{autovi} and its accompanying web interface package,
+\texttt{autovi.web}. It addresses a critical gap in the current
+landscape of statistical software. While regression tools are widely
+available, effective and efficient diagnostic methods have lagged
+behind, particularly in the field of residual plot interpretation.
 
@@
 
-The current version of \texttt{autovi} can be installed from CRAN, and
-source code for both packages are available at
-\url{https://github.com/TengMCing/autovi} and
-\url{https://github.com/TengMCing/autovi_web} respectively. The web
-interface is available from \url{autoviweb.netlify.app}.
+The the current version of \texttt{autovi} can be installed from CRAN,
+and source code for both packages are available at
+\url{https://github.com/TengMCing/autovi}. The web interface is
+available from \url{autoviweb.netlify.app}.
 

### 2024-11-25 autovi_paper.qmd
reproducibility with quarto and source code link

@@
 
-The the current version of `autovi` can be installed from CRAN, and source code for both packages are available at [https://github.com/TengMCing/autovi](https://github.com/TengMCing/autovi).
+The current version of `autovi` can be installed from CRAN, and source code for both packages are available at [https://github.com/TengMCing/autovi](https://github.com/TengMCing/autovi) and [https://github.com/TengMCing/autovi_web](https://github.com/TengMCing/autovi_web) respectively.
 The web interface is available from [autoviweb.netlify.app](autoviweb.netlify.app).
 
+This paper is reproducibly written using Quarto [@Allaire_Quarto_2024] powered by Pandoc version [@MacFarlane_Pandoc] and pdfTeX.
+The full source code to reproduce this paper is available at <https://github.com/TengMCing/autovi_paper>.
+
 These `R` packages were used for the work: `tidyverse` [@tidyverse], `lmtest` [@lmtest], `kableExtra` [@kableextra], `patchwork` [@patchwork], `rcartocolor` [@rcartocolor], `glue` [@glue],  `here` [@here], `magick` [@magick], `yardstick` [@yardstick] and `reticulate` [@reticulate].

### 2024-11-25 autovi_paper.tex
recompile the paper

@@
 \makeatother
+
 \ifLuaTeX
@@
 
+This paper is reproducibly written using Quarto
+\citep{Allaire_Quarto_2024} powered by Pandoc version
+\citep{MacFarlane_Pandoc} and pdfTeX. The full source code to reproduce
+this paper is available at
+\url{https://github.com/TengMCing/autovi_paper}.
+
 These \texttt{R} packages were used for the work: \texttt{tidyverse}

### 2024-11-25 autovi_paper.qmd
add a section about vss

@@
 
+# What is visual signal strength? {#sec-vss-desc}
+
+**Visual signal strength** (VSS) refers to how prominently a specific set of visual patterns appears in an image.
+In the context of regression model diagnostics, it describes the clarity of visual patterns on a diagnostic plot that may indicate model violations.
+This concept can be categorized as weak, moderate, or strong.
+However, in our study, we treat it as a continuous positive real variable.
+Importantly, its interpretation depends on how it is linked to a function of the data or the underlying data generating process.
+Consequently, the meaning of visual signal strength varies across different model classes and even within the same model, depending on the chosen function.
+
+In @li2024automated, visual signal strength was defined as an estimate of a distance measure that quantifies the disparity between the residual distribution of a fitted classical normal linear regression model and a reference distribution.
+This measure is based on the Kullback-Leibler (KL) divergence:
+
+\begin{equation*} \label{eq:kl-0}
+D = \log\left(1 + D_{KL}\right),
+\end{equation*}
+
+where $D_{KL}$ is given by:
+
+\begin{equation*} \label{eq:kl-1}
+D_{KL} = \int_{\mathbb{R}^{n}}\log\frac{p(\boldsymbol{e})}{q(\boldsymbol{e})}p(\boldsymbol{e})d\boldsymbol{e},
+\end{equation*}
+
+Here, $p(.)$ and $q(.)$ are the probability density functions of the reference residual distribution $P$ and the true residual distribution $Q$, respectively.
+
+This distance measure requires knowledge of the true residuals' data generating process, which is typically unknown.
+Therefore, it must be estimated.
+To address this, a computer vision model was trained to perform the estimation.
+
 # R package: autovi {#sec-autovi}
@@
 
-### Numerical Summary {#sec-autovi-numerical}
+### Numerical summary {#sec-autovi-numerical}
 
@@
 
-### Visual Summary {#sec-autovi-visual}
+### Visual summary {#sec-autovi-visual}
 
@@
 
-## Modularized Infrastructure {#sec-autovi-infrastructure}
+## Modularized infrastructure {#sec-autovi-infrastructure}
 
@@
 
-# Resources and Supplementary Material
+# Resources and supplementary material
 

### 2024-11-25 autovi_paper.tex
add a section about vss

@@
 
+\section{What is visual signal strength?}\label{sec-vss-desc}
+
+\textbf{Visual signal strength} (VSS) refers to how prominently a
+specific set of visual patterns appears in an image. In the context of
+regression model diagnostics, it describes the clarity of visual
+patterns on a diagnostic plot that may indicate model violations. This
+concept can be categorized as weak, moderate, or strong. However, in our
+study, we treat it as a continuous positive real variable. Importantly,
+its interpretation depends on how it is linked to a function of the data
+or the underlying data generating process. Consequently, the meaning of
+visual signal strength varies across different model classes and even
+within the same model, depending on the chosen function.
+
+In \citet{li2024automated}, visual signal strength was defined as an
+estimate of a distance measure that quantifies the disparity between the
+residual distribution of a fitted classical normal linear regression
+model and a reference distribution. This measure is based on the
+Kullback-Leibler (KL) divergence:
+
+\begin{equation*} \label{eq:kl-0}
+D = \log\left(1 + D_{KL}\right),
+\end{equation*}
+
+where \(D_{KL}\) is given by:
+
+\begin{equation*} \label{eq:kl-1}
+D_{KL} = \int_{\mathbb{R}^{n}}\log\frac{p(\boldsymbol{e})}{q(\boldsymbol{e})}p(\boldsymbol{e})d\boldsymbol{e},
+\end{equation*}
+
+Here, \(p(.)\) and \(q(.)\) are the probability density functions of the
+reference residual distribution \(P\) and the true residual distribution
+\(Q\), respectively.
+
+This distance measure requires knowledge of the true residuals' data
+generating process, which is typically unknown. Therefore, it must be
+estimated. To address this, a computer vision model was trained to
+perform the estimation.
+
 \section{R package: autovi}\label{sec-autovi}
@@
 
-\subsubsection{Numerical Summary}\label{sec-autovi-numerical}
+\subsubsection{Numerical summary}\label{sec-autovi-numerical}
 
@@
 
-\subsubsection{Visual Summary}\label{sec-autovi-visual}
+\subsubsection{Visual summary}\label{sec-autovi-visual}
 
@@
 
-\subsection{Modularized Infrastructure}\label{sec-autovi-infrastructure}
+\subsection{Modularized infrastructure}\label{sec-autovi-infrastructure}
 
@@
 
-\section{Resources and Supplementary
-Material}\label{resources-and-supplementary-material}
+\section{Resources and supplementary
+material}\label{resources-and-supplementary-material}
 

### 2024-11-25 autovi_paper.qmd
reword VSS description

@@
 Here we describe a new R package that includes a computer vision model for automated assessment of residual plots, and an accompanying Shiny app for ease of use.
-For a user-provided sample of residuals, it predicts a measure of visual signal strength (VSS) and provides a suite of supporting information to assist the analyst decide on the appropriateness their model fit.
+For a user-provided sample of residuals, it predicts a measure of visual signal strength and provides a suite of supporting information to assist the analyst decide on the appropriateness their model fit.
 # Note that "keywords" should not include words and phrases
@@
 
-**Visual signal strength** (VSS) refers to how prominently a specific set of visual patterns appears in an image.
+Visual signal strength (VSS) refers to how prominently a specific set of visual patterns appears in an image.
 In the context of regression model diagnostics, it describes the clarity of visual patterns on a diagnostic plot that may indicate model violations.
@@
 
-In @li2024automated, visual signal strength was defined as an estimate of a distance measure that quantifies the disparity between the residual distribution of a fitted classical normal linear regression model and a reference distribution.
+In @li2024automated, VSS was defined as an estimate of a distance measure that quantifies the disparity between the residual distribution of a fitted classical normal linear regression model and a reference distribution.
 This measure is based on the Kullback-Leibler (KL) divergence:
@@
 
-Here, $p(.)$ and $q(.)$ are the probability density functions of the reference residual distribution $P$ and the true residual distribution $Q$, respectively.
-
-This distance measure requires knowledge of the true residuals' data generating process, which is typically unknown.
-Therefore, it must be estimated.
-To address this, a computer vision model was trained to perform the estimation.
+here, $p(.)$ and $q(.)$ are the probability density functions of the reference residual distribution $P$ and the true residual distribution $Q$, respectively.
+
+This distance measure requires knowledge of the true residual distribution, which is typically unknown.
+Therefore, a computer vision model was used for estimating the residual distribution [see @li2024automated for more details].
 

### 2024-11-25 autovi_paper.tex
reword VSS description

@@
 use. For a user-provided sample of residuals, it predicts a measure of
-visual signal strength (VSS) and provides a suite of supporting
-information to assist the analyst decide on the appropriateness their
-model fit.
+visual signal strength and provides a suite of supporting information to
+assist the analyst decide on the appropriateness their model fit.
 \end{abstract}
@@
 
-\textbf{Visual signal strength} (VSS) refers to how prominently a
-specific set of visual patterns appears in an image. In the context of
-regression model diagnostics, it describes the clarity of visual
-patterns on a diagnostic plot that may indicate model violations. This
-concept can be categorized as weak, moderate, or strong. However, in our
-study, we treat it as a continuous positive real variable. Importantly,
-its interpretation depends on how it is linked to a function of the data
-or the underlying data generating process. Consequently, the meaning of
-visual signal strength varies across different model classes and even
-within the same model, depending on the chosen function.
+Visual signal strength (VSS) refers to how prominently a specific set of
+visual patterns appears in an image. In the context of regression model
+diagnostics, it describes the clarity of visual patterns on a diagnostic
+plot that may indicate model violations. This concept can be categorized
+as weak, moderate, or strong. However, in our study, we treat it as a
+continuous positive real variable. Importantly, its interpretation
+depends on how it is linked to a function of the data or the underlying
+data generating process. Consequently, the meaning of visual signal
+strength varies across different model classes and even within the same
+model, depending on the chosen function.
 
-In \citet{li2024automated}, visual signal strength was defined as an
-estimate of a distance measure that quantifies the disparity between the
-residual distribution of a fitted classical normal linear regression
-model and a reference distribution. This measure is based on the
-Kullback-Leibler (KL) divergence:
+In \citet{li2024automated}, VSS was defined as an estimate of a distance
+measure that quantifies the disparity between the residual distribution
+of a fitted classical normal linear regression model and a reference
+distribution. This measure is based on the Kullback-Leibler (KL)
+divergence:
 
@@
 
-Here, \(p(.)\) and \(q(.)\) are the probability density functions of the
+here, \(p(.)\) and \(q(.)\) are the probability density functions of the
 reference residual distribution \(P\) and the true residual distribution
@@
 
-This distance measure requires knowledge of the true residuals' data
-generating process, which is typically unknown. Therefore, it must be
-estimated. To address this, a computer vision model was trained to
-perform the estimation.
+This distance measure requires knowledge of the true residual
+distribution, which is typically unknown. Therefore, a computer vision
+model was used for estimating the residual distribution \citep[see][ for
+more details]{li2024automated}.
 

### 2024-11-25 autovi_paper.qmd
small typos in abstract and intro, and revised section 2

--- 2024-11-25 autovi_paper.qmd
@@
 ---
-title: "Automated Residual Plot Assessment with the R Package autovi and Shiny App autovi.web"
+title: "Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web"
 format:
@@
   Visually assessing residual plots is a common advice for linear model diagnostics, however this approach requires manual human evaluation and thereby is not scalable for assessing many models.
-Human evaluation also suffer from the potential for inconsistent decisions from different analysts.
+Human evaluation also has the potential to produce inconsistent decisions from different analysts.
 Using a lineup protocol, where the residual plot is embedded among null plots, can help to alleviate inconsistency, but requires even more human effort.
-This is the type of task that in today's world might employ a robot to do the tedious work for a human.
+This is the type of task that in today's world we might employ a robot to do the tedious work for a human.
 Here we describe a new R package that includes a computer vision model for automated assessment of residual plots, and an accompanying Shiny app for ease of use.
@@
 Regression analysis is a widely used statistical modeling technique for data in many fields.
-There are a vast array of software for conducting regression modeling and generating diagnostics.
+There is a vast array of software for conducting regression modeling and generating diagnostics.
 The package `lmtest` [@lmtest] provides a suite of conventional tests.
@@
 
-However relying solely on subjective assessments of these plots can lead to issues, such as over-interpreting random patterns as model violations.
+However, relying solely on subjective assessments of these plots can lead to issues such as over-interpreting random patterns as model violations.
 @li2024plot demonstrated that visual methods using the lineup protocol [@buja2009statistical] for assessing residuals are more useful, and also perform more practically than conventional tests due to their reduced sensitivity to minor departures.
-Packages such as `nullabor` [@nullabor], `HLMdiag` [@loy2014hlmdiag], and `regressinator` [@regressinator], enable users to compare observed residual plots with samples from null distributions, helping to quantify the significance of any detected patterns.
+Packages such as `nullabor` [@nullabor], `HLMdiag` [@loy2014hlmdiag], and `regressinator` [@regressinator], enable users to compare observed residual plots with plots of samples from null distributions, helping to quantify the significance of any detected patterns.
 
@@
 
-# What is visual signal strength? {#sec-vss-desc}
-
-**Visual signal strength** (VSS) refers to how prominently a specific set of visual patterns appears in an image.
+# Definition and computation of visual signal strength {#sec-vss-desc}
+
+To train a computer vision model a measure of the visible pattern in a plot is needed.
+We call this the **visual signal strength** (VSS) measuring how prominently a specific set of visual patterns appears in an image.
+This can be computed for a training set of data, and plots, where the generating distributions are specified.
+
 In the context of regression model diagnostics, it describes the clarity of visual patterns on a diagnostic plot that may indicate model violations.
@@
 Importantly, its interpretation depends on how it is linked to a function of the data or the underlying data generating process.
-Consequently, the meaning of visual signal strength varies across different model classes and even within the same model, depending on the chosen function.
-
-In @li2024automated, visual signal strength was defined as an estimate of a distance measure that quantifies the disparity between the residual distribution of a fitted classical normal linear regression model and a reference distribution.
+Consequently, the calculation of VSS can be vary across different model classes or within the same model, depending on the generating function.
+
+VSS is defined as an estimate of a distance measure that quantifies the disparity between the residual distribution of a fitted classical normal linear regression model and a reference distribution, and more details can be found in @li2024automated.
 This measure is based on the Kullback-Leibler (KL) divergence:

### 2024-11-25 autovi_paper.tex
small typos in abstract and intro, and revised section 2

--- 2024-11-25 autovi_paper.tex
@@
 \hypersetup{
-  pdftitle={Automated Residual Plot Assessment with the R Package autovi and Shiny App autovi.web},
+  pdftitle={Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web},
   pdfauthor={Weihao Li; Dianne Cook; Emi Tanaka; Susan VanderPlas; Klaus Ackermann},
@@
 \title{Automated Residual Plot Assessment with the R Package autovi and
-Shiny App autovi.web}
+the Shiny App autovi.web}
 
@@
 thereby is not scalable for assessing many models. Human evaluation also
-suffer from the potential for inconsistent decisions from different
+has the potential to produce inconsistent decisions from different
 analysts. Using a lineup protocol, where the residual plot is embedded
 among null plots, can help to alleviate inconsistency, but requires even
-more human effort. This is the type of task that in today's world might
-employ a robot to do the tedious work for a human. Here we describe a
-new R package that includes a computer vision model for automated
-assessment of residual plots, and an accompanying Shiny app for ease of
-use. For a user-provided sample of residuals, it predicts a measure of
-visual signal strength (VSS) and provides a suite of supporting
-information to assist the analyst decide on the appropriateness their
-model fit.
+more human effort. This is the type of task that in today's world we
+might employ a robot to do the tedious work for a human. Here we
+describe a new R package that includes a computer vision model for
+automated assessment of residual plots, and an accompanying Shiny app
+for ease of use. For a user-provided sample of residuals, it predicts a
+measure of visual signal strength (VSS) and provides a suite of
+supporting information to assist the analyst decide on the
+appropriateness their model fit.
 \end{abstract}
@@
 Regression analysis is a widely used statistical modeling technique for
-data in many fields. There are a vast array of software for conducting
+data in many fields. There is a vast array of software for conducting
 regression modeling and generating diagnostics. The package
@@
 
-However relying solely on subjective assessments of these plots can lead
-to issues, such as over-interpreting random patterns as model
+However, relying solely on subjective assessments of these plots can
+lead to issues such as over-interpreting random patterns as model
 violations. \citet{li2024plot} demonstrated that visual methods using
@@
 \citep{regressinator}, enable users to compare observed residual plots
-with samples from null distributions, helping to quantify the
+with plots of samples from null distributions, helping to quantify the
 significance of any detected patterns.
@@
 
-\section{What is visual signal strength?}\label{sec-vss-desc}
+\section{Definition and computation of visual signal
+strength}\label{sec-vss-desc}
 
-\textbf{Visual signal strength} (VSS) refers to how prominently a
-specific set of visual patterns appears in an image. In the context of
-regression model diagnostics, it describes the clarity of visual
-patterns on a diagnostic plot that may indicate model violations. This
-concept can be categorized as weak, moderate, or strong. However, in our
-study, we treat it as a continuous positive real variable. Importantly,
-its interpretation depends on how it is linked to a function of the data
-or the underlying data generating process. Consequently, the meaning of
-visual signal strength varies across different model classes and even
-within the same model, depending on the chosen function.
+To train a computer vision model a measure of the visible pattern in a
+plot is needed. We call this the \textbf{visual signal strength} (VSS)
+measuring how prominently a specific set of visual patterns appears in
+an image. This can be computed for a training set of data, and plots,
+where the generating distributions are specified.
 
-In \citet{li2024automated}, visual signal strength was defined as an
-estimate of a distance measure that quantifies the disparity between the
-residual distribution of a fitted classical normal linear regression
-model and a reference distribution. This measure is based on the
+In the context of regression model diagnostics, it describes the clarity
+of visual patterns on a diagnostic plot that may indicate model
+violations. This concept can be categorized as weak, moderate, or
+strong. However, in our study, we treat it as a continuous positive real
+variable. Importantly, its interpretation depends on how it is linked to
+a function of the data or the underlying data generating process.
+Consequently, the calculation of VSS can be vary across different model
+classes or within the same model, depending on the generating function.
+
+VSS is defined as an estimate of a distance measure that quantifies the
+disparity between the residual distribution of a fitted classical normal
+linear regression model and a reference distribution, and more details
+can be found in \citet{li2024automated}. This measure is based on the
 Kullback-Leibler (KL) divergence:
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-three-examples-1.pdf}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-three-examples-1.pdf}
 
@@
 
-\includegraphics[width=0.6\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-plot-pair-1.pdf}
+\includegraphics[width=0.6\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-plot-pair-1.pdf}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-setup-1.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-setup-1.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-lineup-1.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-lineup-1.png}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-distributions-1.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-distributions-1.png}
 

### 2024-11-25 autovi_paper.tex
reformat urls in resources

@@
 \makeatother
-
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 \usepackage[]{natbib}
@@
 source code for both packages are available at
-\url{https://github.com/TengMCing/autovi} and
-\url{https://github.com/TengMCing/autovi_web} respectively. The web
-interface is available from \url{autoviweb.netlify.app}.
+\href{https://github.com/TengMCing/autovi}{\texttt{github.com/TengMCing/autovi}}
+and
+\href{https://github.com/TengMCing/autovi_web}{\texttt{github.com/TengMCing/autovi\_web}}
+respectively. The web interface is available from
+\href{https://autoviweb.netlify.app/}{\texttt{autoviweb.netlify.app}}.
 
 This paper is reproducibly written using Quarto
-\citep{Allaire_Quarto_2024} powered by Pandoc version
-\citep{MacFarlane_Pandoc} and pdfTeX. The full source code to reproduce
-this paper is available at
-\url{https://github.com/TengMCing/autovi_paper}.
+\citep{Allaire_Quarto_2024} powered by Pandoc \citep{MacFarlane_Pandoc}
+and pdfTeX. The full source code to reproduce this paper is available at
+\href{https://github.com/TengMCing/autovi_paper}{\texttt{github.com/TengMCing/autovi\_paper}}.
 

### 2024-11-26 autovi_paper.qmd
modify the section desc and fix bibtex warning

@@
 
-The remainder of this paper is structured as follows: @sec-autovi provides a detailed documentation of the `autovi` package, including its usage and infrastructure.
+The remainder of this paper is structured as follows: @sec-vss-desc introduces the definition and computation of visual signal strength.
+@sec-autovi provides a detailed documentation of the `autovi` package, including its usage and infrastructure.
 @sec-autovi-web focuses on the `autovi.web` interface, describing its design and usage, along with illustrative examples.
@@
 
-The current version of `autovi` can be installed from CRAN, and source code for both packages are available at [https://github.com/TengMCing/autovi](https://github.com/TengMCing/autovi) and [https://github.com/TengMCing/autovi_web](https://github.com/TengMCing/autovi_web) respectively.
-The web interface is available from [autoviweb.netlify.app](autoviweb.netlify.app).
-
-This paper is reproducibly written using Quarto [@Allaire_Quarto_2024] powered by Pandoc version [@MacFarlane_Pandoc] and pdfTeX.
-The full source code to reproduce this paper is available at <https://github.com/TengMCing/autovi_paper>.
+The current version of `autovi` can be installed from CRAN, and source code for both packages are available at [`github.com/TengMCing/autovi`](https://github.com/TengMCing/autovi) and [`github.com/TengMCing/autovi_web`](https://github.com/TengMCing/autovi_web) respectively.
+The web interface is available from [`autoviweb.netlify.app`](https://autoviweb.netlify.app/).
+
+This paper is reproducibly written using Quarto [@Allaire_Quarto_2024] powered by Pandoc [@MacFarlane_Pandoc] and pdfTeX.
+The full source code to reproduce this paper is available at [`github.com/TengMCing/autovi_paper`](https://github.com/TengMCing/autovi_paper).
 

### 2024-11-26 autovi_paper.tex
modify the section desc and fix bibtex warning

@@
 The remainder of this paper is structured as follows:
-Section~\ref{sec-autovi} provides a detailed documentation of the
-\texttt{autovi} package, including its usage and infrastructure.
-Section~\ref{sec-autovi-web} focuses on the \texttt{autovi.web}
-interface, describing its design and usage, along with illustrative
-examples. Finally, Section~\ref{sec-autovi-conclusion} presents the main
-conclusions of this work.
+Section~\ref{sec-vss-desc} introduces the definition and computation of
+visual signal strength. Section~\ref{sec-autovi} provides a detailed
+documentation of the \texttt{autovi} package, including its usage and
+infrastructure. Section~\ref{sec-autovi-web} focuses on the
+\texttt{autovi.web} interface, describing its design and usage, along
+with illustrative examples. Finally, Section~\ref{sec-autovi-conclusion}
+presents the main conclusions of this work.
 

### 2024-11-26 autovi_paper.qmd
Join this sentence to the prev paragraph

@@
 This strength estimates the distance between the residual distribution of the fitted regression model and the reference distribution assumed under correct model specification.
-
+<!---->
 <!--Software for regression analysis tools is widely available.
@@
 These packages can be broadly categorized into three groups: general-purpose, enhanced visual diagnostics, and visual diagnostics with statistical testing.-->
-
+<!---->
 <!--General-purpose regression analysis tools are the most widely used group of packages.
@@
 However, as discussed in @li2024plot, relying solely on subjective assessments of these plots can lead to issues, such as over-interpreting random patterns as model violations.-->
-
+<!---->
 <!-- The second group consists of enhanced visual diagnostics tools, which provide advanced aids for interpreting diagnostic plots.
@@
 It also includes annotations from conventional tests, displayed as labels or text within the plot, to help avoid misinterpretation.-->
-
+<!---->
 <!-- The third group, visual diagnostics with statistical testing, offers tools for formally testing patterns observed in diagnostic plots [@buja2009statistical].
@@
 This strength estimates the distance between the residual distribution of the fitted regression model and the reference distribution assumed under correct model specification.-->
-
 To make the statistical testing procedure and trained computer vision model widely accessible, we developed the R package `autovi`, and a web interface, `autovi.web` to make it easy for users to automatically read their residual plots with the trained computer vision model.

### 2024-11-26 autovi_paper.qmd
Some rephrasing.

@@
 
-In the context of regression model diagnostics, it describes the clarity of visual patterns on a diagnostic plot that may indicate model violations.
-This concept can be categorized as weak, moderate, or strong.
-However, in our study, we treat it as a continuous positive real variable.
+In the context of regression model diagnostics, VSS describes the clarity of visual patterns on a diagnostic plot that may indicate model violations.
+Violations can be categorized as weak, moderate, or strong, but here we treat it as a continuous positive real variable.
 Importantly, its interpretation depends on how it is linked to a function of the data or the underlying data generating process.

### 2024-11-26 autovi_paper.qmd
Trying to streamline this to make it a bit less convoluted.

@@
 
-VSS is defined as an estimate of a distance measure that quantifies the disparity between the residual distribution of a fitted classical normal linear regression model and a reference distribution, and more details can be found in @li2024automated.
-This measure is based on the Kullback-Leibler (KL) divergence:
+VSS is an estimate of the distance between the residual distribution of a fitted classical normal linear regression model and a reference distribution; more details can be found in @li2024automated.
+The distance measure is based on the Kullback-Leibler (KL) divergence:
 

### 2024-11-26 autovi_paper.qmd
Comment -- Patrick needs to address
Some streamlining/rephrasing.

@@
 Therefore, a computer vision model was used for estimating the residual distribution [see @li2024automated for more details].
+XXX this isn't completely clear -- why is the computer vision model used to estimate the residual distribution?
+You need to provide at least a bit of the "why" so that this isn't a total non-sequitur.
+XXX
 
@@
 <!--While initially designed for linear regression residual diagnostics, it has the potential to be extended to broader visual inference applications, as we discuss in section @sec-autovi-infrastructure.-->
-
-There are two ways to access the package, directly using R or through a web interface, `autovi.web`.
-The web interface has the advantage that it can be used without installing Python, R and the relevant packages locally.
-
-## Motivation for usage {#sec-why}
+This functionality can be accessed through the R package `autovi`, or through a web interface, `autovi.web`, which allows use without the full installation of R, Python, and package dependencies on the user's system.
+locally.
+
+## Motivation {#sec-why}
 

### 2024-11-26 autovi_paper.qmd
A couple of comments

@@
 The `autovi` package is built on the `bandicoot` object-oriented programming (OOP) system [@bandicoot], marking a departure from R’s traditional S3 generic system.
-This OOP architecture enhances flexibility and modularity, allowing users to redefine key functions through method overriding.
+This OOP architecture enhances flexibility and modularity, allowing users to redefine key functions through method overriding XXX I think the technical term is overloading?
+XXX.
 While similar functionality could be achieved using R’s S3 system with generic functions, the OOP framework offers a more structured and extensible foundation for the package.
+XXX Not sure if this last sentence is necessary XXX
 

### 2024-11-26 autovi_paper.qmd
Making this more concise.

@@
 `ggplot2` [@ggplot2] generates the initial residual plots, saved as PNG files for visual input.
-The `cassowaryr` [@mason2022cassowaryr] library computes scagnostics (scatter plot diagnostics), providing numerical features that capture statistical properties of the plots.
+`cassowaryr` [@mason2022cassowaryr] computes scagnostics (scatter plot diagnostics), providing numerical features that capture statistical properties of the plots.
 These scagnostics complement the visual analysis by offering quantitative metrics as secondary input to the computer vision model.
-The `reticulate` [@reticulate] package bridges R and Python, enabling seamless communication between the two languages and supporting the integrated infrastructure.
+`reticulate` [@reticulate]  enables seamless communication between R and Python.
 

### 2024-11-26 autovi_paper.qmd
Streamlining

@@
 In Python, `pillow` [@clark2015pillow] handles image processing tasks such as reading and resizing PNG files of residual plots, then converting them into input tensors for further analysis.
-The `TensorFlow` [@abadi2016tensorflow] library, a key component of modern machine learning, is used to predict the VSS of these plots through a pre-trained convolutional neural network.
+`TensorFlow` [@abadi2016tensorflow], a key component of modern machine learning, is used to predict the VSS of these plots using a pre-trained convolutional neural network.
 

### 2024-11-26 autovi_paper.qmd
Condensing this -- could condense a bit further, but I'll let it go for now :)
streamlining/clarifying

@@
 
-The `autovi` package is available on CRAN. It is actively developed and maintained, with the latest updates accessible on GitHub. The code discussed in this paper is based on `autovi` version 0.4.1.
-
+The `autovi` package is available on CRAN. It is actively developed and maintained, with the latest updates accessible on GitHub. This paper uses `autovi` version 0.4.1.
 The package includes internal functions to check the current Python environment used by the `reticulate` package.
@@
 3.
-Call the `check()` method of the checker, which, by default, predicts the VSS for the true residual plot, 100 null plots, and 100 bootstrapped plots, storing the predictions internally.
-A concise report of the check results is then printed.
+Call the `check()` method of the checker, which, by default, predicts the VSS for the true residual plot, 100 null plots, and 100 bootstrapped plots.
+The method stores the predictions internally and prints a concise results report.
 

### 2024-11-26 autovi_paper.qmd
comment
I'd refer to documentation rather than the website here -- it should be in both places, so don't confine it to the web. If it's only on the website, we probably should add it to the full package documentation.

@@
 This visual summary provides an intuitive way to assess the model's fit and potential violations, allowing users to quickly grasp the results of the automated analysis.
+XXX It might be a good idea to include a basic message explaining the plot and how it's used when it is generated, because a lot of non-statisticians aren't going to be used to interpreting these plots XXX
 
@@
 The remaining seven modules are designed to be overridable, enabling users to tailor the infrastructure to their specific needs.
-These modules are discussed in detail on the software's website.
+These modules are discussed in detail in the package documentation.
 <!-- in the following sections.-->

### 2024-11-26 autovi_paper.qmd
Clarifying/streamlining this bit

@@
 In our initial planning for `autovi.web`, we considered implementing the entire web application using the `webr` framework [@webr], which would have allowed the entire application to run directly in the user's browser.
-However, this approach was not feasible at the time of writing this paper.
-The reason is that one of the R packages `autovi` depends on the R package `splancs` [@splancs], which uses compiled Fortran code.
-A working Emscripten [@zakai2011emscripten] version of this package, which would be required for `webr`, was not available.
+However, `webr` does not support packages which use compiled fortran code, which is required by `splancs` [@splancs], a dependency of `autovi`.
+In the future, it is possible that a working Emscripten [@zakai2011emscripten] version of this package may allow full `webr` support.
 
@@
 Another option we considered was renting a server where we could have full control, such as those provided by cloud platforms like Google Cloud Platform (GCP) or Amazon Web Services (AWS).
-However, correctly setting up the server and ensuring a secure deployment requires significant expertise.
+However, deploying and maintaining the server securely requires some expertise.
 Ultimately, the most practical solution was to use the `shiny` and `shinydashboard` frameworks, which are well-established in the R community and offer a solid foundation for web application development.

### 2024-11-26 autovi_paper.qmd
Slight streamlining here.

@@
 
-In contrast to `autovi`, `autovi.web` does not use the native Python version of `TensorFlow`.
-Instead, it leverages `TensorFlow.js`, a JavaScript library that allows the execution of machine learning models directly in the browser.
+In contrast to `autovi`, `autovi.web` leverages `TensorFlow.js`, a JavaScript library that allows the execution of machine learning models directly in the browser.
 This choice enables native browser execution, enhancing compatibility across different user environments, and shifts the computational load from the server to the client-side.

### 2024-11-27 autovi_paper.qmd
provide more details about the computer vision model

@@
 
-To train a computer vision model a measure of the visible pattern in a plot is needed.
-We call this the **visual signal strength** (VSS) measuring how prominently a specific set of visual patterns appears in an image.
+To train a computer vision model, a measure of the visible pattern in a plot is needed.
+We call this the **visual signal strength** (VSS), which measures how prominently a specific set of visual patterns appears in an image.
 This can be computed for a training set of data, and plots, where the generating distributions are specified.
@@
 
-This distance measure requires knowledge of the true residual distribution, which is typically unknown.
-Therefore, a computer vision model was used for estimating the residual distribution [see @li2024automated for more details].
-XXX this isn't completely clear -- why is the computer vision model used to estimate the residual distribution?
-You need to provide at least a bit of the "why" so that this isn't a total non-sequitur.
-XXX
+This distance measure depends on knowledge of the true residual distribution, which is often unknown.
+However, it can be estimated by identifying or approximating a mapping from a set of residuals to its corresponding distance measure.
+The computer vision model presented in @li2024automated approximates this mapping.
+It is trained on a large number of synthetic regression models, where the data-generating process is known, allowing the distance measure to be explicitly calculated.
+The model takes a residual plot as input and outputs the corresponding distance measure.
+Additional details are provided in @li2024automated.
 

### 2024-11-27 autovi_paper.tex
provide more details about the computer vision model

@@
 
-To train a computer vision model a measure of the visible pattern in a
-plot is needed. We call this the \textbf{visual signal strength} (VSS)
-measuring how prominently a specific set of visual patterns appears in
-an image. This can be computed for a training set of data, and plots,
+To train a computer vision model, a measure of the visible pattern in a
+plot is needed. We call this the \textbf{visual signal strength} (VSS),
+which measures how prominently a specific set of visual patterns appears
+in an image. This can be computed for a training set of data, and plots,
 where the generating distributions are specified.
 
-In the context of regression model diagnostics, it describes the clarity
-of visual patterns on a diagnostic plot that may indicate model
-violations. This concept can be categorized as weak, moderate, or
-strong. However, in our study, we treat it as a continuous positive real
-variable. Importantly, its interpretation depends on how it is linked to
-a function of the data or the underlying data generating process.
+In the context of regression model diagnostics, VSS describes the
+clarity of visual patterns on a diagnostic plot that may indicate model
+violations. Violations can be categorized as weak, moderate, or strong,
+but here we treat it as a continuous positive real variable.
+Importantly, its interpretation depends on how it is linked to a
+function of the data or the underlying data generating process.
 Consequently, the calculation of VSS can be vary across different model
@@
 
-VSS is defined as an estimate of a distance measure that quantifies the
-disparity between the residual distribution of a fitted classical normal
-linear regression model and a reference distribution, and more details
-can be found in \citet{li2024automated}. This measure is based on the
-Kullback-Leibler (KL) divergence:
+VSS is an estimate of the distance between the residual distribution of
+a fitted classical normal linear regression model and a reference
+distribution; more details can be found in \citet{li2024automated}. The
+distance measure is based on the Kullback-Leibler (KL) divergence:
 
@@
 
-This distance measure requires knowledge of the true residual
-distribution, which is typically unknown. Therefore, a computer vision
-model was used for estimating the residual distribution \citep[see][ for
-more details]{li2024automated}.
+This distance measure depends on knowledge of the true residual
+distribution, which is often unknown. However, it can be estimated by
+identifying or approximating a mapping from a set of residuals to its
+corresponding distance measure. The computer vision model presented in
+\citet{li2024automated} approximates this mapping. It is trained on a
+large number of synthetic regression models, where the data-generating
+process is known, allowing the distance measure to be explicitly
+calculated. The model takes a residual plot as input and outputs the
+corresponding distance measure. Additional details are provided in
+\citet{li2024automated}.
 
@@
 \texttt{autovi} stands for \textbf{auto}mated \textbf{v}isual
-\textbf{i}nference.
+\textbf{i}nference. This functionality can be accessed through the R
+package \texttt{autovi}, or through a web interface,
+\texttt{autovi.web}, which allows use without the full installation of
+R, Python, and package dependencies on the user's system. locally.
 
-There are two ways to access the package, directly using R or through a
-web interface, \texttt{autovi.web}. The web interface has the advantage
-that it can be used without installing Python, R and the relevant
-packages locally.
-
-\subsection{Motivation for usage}\label{sec-why}
+\subsection{Motivation}\label{sec-why}
 
@@
 enhances flexibility and modularity, allowing users to redefine key
-functions through method overriding. While similar functionality could
-be achieved using R's S3 system with generic functions, the OOP
-framework offers a more structured and extensible foundation for the
-package.
+functions through method overriding XXX I think the technical term is
+overloading? XXX. While similar functionality could be achieved using
+R's S3 system with generic functions, the OOP framework offers a more
+structured and extensible foundation for the package. XXX Not sure if
+this last sentence is necessary XXX
 
@@
 and resizing PNG files of residual plots, then converting them into
-input tensors for further analysis. The \texttt{TensorFlow}
-\citep{abadi2016tensorflow} library, a key component of modern machine
-learning, is used to predict the VSS of these plots through a
-pre-trained convolutional neural network.
+input tensors for further analysis. \texttt{TensorFlow}
+\citep{abadi2016tensorflow}, a key component of modern machine learning,
+is used to predict the VSS of these plots using a pre-trained
+convolutional neural network.
 
@@
 \texttt{ggplot2} \citep{ggplot2} generates the initial residual plots,
-saved as PNG files for visual input. The \texttt{cassowaryr}
-\citep{mason2022cassowaryr} library computes scagnostics (scatter plot
+saved as PNG files for visual input. \texttt{cassowaryr}
+\citep{mason2022cassowaryr} computes scagnostics (scatter plot
 diagnostics), providing numerical features that capture statistical
@@
 analysis by offering quantitative metrics as secondary input to the
-computer vision model. The \texttt{reticulate} \citep{reticulate}
-package bridges R and Python, enabling seamless communication between
-the two languages and supporting the integrated infrastructure.
+computer vision model. \texttt{reticulate} \citep{reticulate} enables
+seamless communication between R and Python.
 
@@
 developed and maintained, with the latest updates accessible on GitHub.
-The code discussed in this paper is based on \texttt{autovi} version
-0.4.1.
-
-The package includes internal functions to check the current Python
-environment used by the \texttt{reticulate} package. If the necessary
-Python packages are not installed in the Python interpreter, an error
-will be raised. If you want to select a specific Python environment, you
-can do so by calling the \texttt{reticulate::use\_python()} function
-before using the \texttt{autovi} package.
+This paper uses \texttt{autovi} version 0.4.1. The package includes
+internal functions to check the current Python environment used by the
+\texttt{reticulate} package. If the necessary Python packages are not
+installed in the Python interpreter, an error will be raised. If you
+want to select a specific Python environment, you can do so by calling
+the \texttt{reticulate::use\_python()} function before using the
+\texttt{autovi} package.
 
@@
   predicts the VSS for the true residual plot, 100 null plots, and 100
-  bootstrapped plots, storing the predictions internally. A concise
-  report of the check results is then printed.
+  bootstrapped plots. The method stores the predictions internally and
+  prints a concise results report.
 \end{enumerate}
@@
 and potential violations, allowing users to quickly grasp the results of
-the automated analysis.
+the automated analysis. XXX It might be a good idea to include a basic
+message explaining the plot and how it's used when it is generated,
+because a lot of non-statisticians aren't going to be used to
+interpreting these plots XXX
 
@@
 be overridable, enabling users to tailor the infrastructure to their
-specific needs. These modules are discussed in detail on the software's
-website.
+specific needs. These modules are discussed in detail in the package
+documentation.
 
@@
 which would have allowed the entire application to run directly in the
-user's browser. However, this approach was not feasible at the time of
-writing this paper. The reason is that one of the R packages
-\texttt{autovi} depends on the R package \texttt{splancs}
-\citep{splancs}, which uses compiled Fortran code. A working Emscripten
-\citep{zakai2011emscripten} version of this package, which would be
-required for \texttt{webr}, was not available.
+user's browser. However, \texttt{webr} does not support packages which
+use compiled fortran code, which is required by \texttt{splancs}
+\citep{splancs}, a dependency of \texttt{autovi}. In the future, it is
+possible that a working Emscripten \citep{zakai2011emscripten} version
+of this package may allow full \texttt{webr} support.
 
@@
 as those provided by cloud platforms like Google Cloud Platform (GCP) or
-Amazon Web Services (AWS). However, correctly setting up the server and
-ensuring a secure deployment requires significant expertise. Ultimately,
-the most practical solution was to use the \texttt{shiny} and
-\texttt{shinydashboard} frameworks, which are well-established in the R
-community and offer a solid foundation for web application development.
+Amazon Web Services (AWS). However, deploying and maintaining the server
+securely requires some expertise. Ultimately, the most practical
+solution was to use the \texttt{shiny} and \texttt{shinydashboard}
+frameworks, which are well-established in the R community and offer a
+solid foundation for web application development.
 
@@
 
-In contrast to \texttt{autovi}, \texttt{autovi.web} does not use the
-native Python version of \texttt{TensorFlow}. Instead, it leverages
+In contrast to \texttt{autovi}, \texttt{autovi.web} leverages
 \texttt{TensorFlow.js}, a JavaScript library that allows the execution

### 2024-11-27 autovi_paper.qmd
update implementation details

@@
 The `autovi` package is built on the `bandicoot` object-oriented programming (OOP) system [@bandicoot], marking a departure from R’s traditional S3 generic system.
-This OOP architecture enhances flexibility and modularity, allowing users to redefine key functions through method overriding XXX I think the technical term is overloading?
-XXX.
-While similar functionality could be achieved using R’s S3 system with generic functions, the OOP framework offers a more structured and extensible foundation for the package.
-XXX Not sure if this last sentence is necessary XXX
+This OOP architecture enhances flexibility and modularity, allowing users to redefine key functions through method overriding.
 

### 2024-11-27 autovi_paper.tex
update implementation details

@@
 enhances flexibility and modularity, allowing users to redefine key
-functions through method overriding XXX I think the technical term is
-overloading? XXX. While similar functionality could be achieved using
-R's S3 system with generic functions, the OOP framework offers a more
-structured and extensible foundation for the package. XXX Not sure if
-this last sentence is necessary XXX
+functions through method overriding.
 

### 2024-11-28 autovi_paper.qmd
made github issue
ready to submit

@@
 This visual summary provides an intuitive way to assess the model's fit and potential violations, allowing users to quickly grasp the results of the automated analysis.
-XXX It might be a good idea to include a basic message explaining the plot and how it's used when it is generated, because a lot of non-statisticians aren't going to be used to interpreting these plots XXX
 
@@
 
-The `autovi` R package, introduced in this paper, automates the assessment of residual plots by incorporating a computer vision model, eliminating the need for time-consuming and potentially inconsistent human interpretation.
+The `autovi` R package, introduced in this paper, automates the assessment of residual plots by incorporating a computer vision model, reducing reliance on time-consuming and potentially inconsistent human interpretation.
 This automation improves the efficiency of the diagnostic process and promotes consistency in model evaluation across different users and studies.

### 2024-11-28 autovi_paper.tex
made github issue
ready to submit

@@
 and potential violations, allowing users to quickly grasp the results of
-the automated analysis. XXX It might be a good idea to include a basic
-message explaining the plot and how it's used when it is generated,
-because a lot of non-statisticians aren't going to be used to
-interpreting these plots XXX
+the automated analysis.
 
@@
 assessment of residual plots by incorporating a computer vision model,
-eliminating the need for time-consuming and potentially inconsistent
-human interpretation. This automation improves the efficiency of the
+reducing reliance on time-consuming and potentially inconsistent human
+interpretation. This automation improves the efficiency of the
 diagnostic process and promotes consistency in model evaluation across

### 2024-11-28 autovi_paper.qmd
add one paragraph for d

@@
 
-\begin{equation*} \label{eq:kl-1}
+\begin{equation} \label{eq:kl-1}
 D_{KL} = \int_{\mathbb{R}^{n}}\log\frac{p(\boldsymbol{e})}{q(\boldsymbol{e})}p(\boldsymbol{e})d\boldsymbol{e},
+\end{equation}
+
+here, $p(.)$ and $q(.)$ are the probability density functions of the reference residual distribution $P$ and the true residual distribution $Q$, respectively.
+
+Equation \ref{eq:kl-1} can be adapted to different forms to account for various model violations.
+For instance, in the case of a linear regression model where necessary higher-order predictors, $\boldsymbol{Z}$, and their corresponding parameter, $\boldsymbol{\beta}_Z$, are omitted, the distance measure can be expanded as follows:
+
+\begin{equation*} \label{eq:kl-2}
+D_{KL} = \frac{1}{2}\left(\boldsymbol{\mu}_z^\top(\text{diag}(\boldsymbol{R}\sigma^2))^{-1}\boldsymbol{\mu}_z\right),
 \end{equation*}
 
-here, $p(.)$ and $q(.)$ are the probability density functions of the reference residual distribution $P$ and the true residual distribution $Q$, respectively.
+where $\boldsymbol{\mu}_z = \boldsymbol{R}\boldsymbol{Z}\boldsymbol{\beta}_z$, $\boldsymbol{R} = \boldsymbol{I}_n - \boldsymbol{X}(\boldsymbol{X}^\top\boldsymbol{X})^{-1}\boldsymbol{X}^\top$ and $\boldsymbol{X}$ is the design matrix of the regression model.
 

### 2024-11-28 autovi_paper.tex
add one paragraph for d

@@
 
-\begin{equation*} \label{eq:kl-1}
+\begin{equation} \label{eq:kl-1}
 D_{KL} = \int_{\mathbb{R}^{n}}\log\frac{p(\boldsymbol{e})}{q(\boldsymbol{e})}p(\boldsymbol{e})d\boldsymbol{e},
-\end{equation*}
+\end{equation}
 
@@
 \(Q\), respectively.
+
+Equation \ref{eq:kl-1} can be adapted to different forms to account for
+various model violations. For instance, in the case of a linear
+regression model where necessary higher-order predictors,
+\(\boldsymbol{Z}\), and their corresponding parameter,
+\(\boldsymbol{\beta}_Z\), are omitted, the distance measure can be
+expanded as follows:
+
+\begin{equation*} \label{eq:kl-2}
+D_{KL} = \frac{1}{2}\left(\boldsymbol{\mu}_z^\top(\text{diag}(\boldsymbol{R}\sigma^2))^{-1}\boldsymbol{\mu}_z\right),
+\end{equation*}
+
+where
+\(\boldsymbol{\mu}_z = \boldsymbol{R}\boldsymbol{Z}\boldsymbol{\beta}_z\),
+\(\boldsymbol{R} = \boldsymbol{I}_n - \boldsymbol{X}(\boldsymbol{X}^\top\boldsymbol{X})^{-1}\boldsymbol{X}^\top\)
+and \(\boldsymbol{X}\) is the design matrix of the regression model.
 

### 2024-11-28 autovi_paper.qmd
tweaked new paragraph

@@
 
-<!-- However, as discussed in @li2024plot, relying solely on subjective assessments of these plots can lead to issues, such as over-interpreting random patterns as model violations. -->
-
-<!-- To diagnose the fit of a model it is recommended that the residuals are plotted.
-If the fit is good, any variation remaining should be noise, consistent with sampling from a distribution specified by the error model.
-Deviations that might be observed from a residual plot are non-normality, heteroscedasticity, and other associations with the fitted values.-->
-
 However, relying solely on subjective assessments of these plots can lead to issues such as over-interpreting random patterns as model violations.
@@
 This strength estimates the distance between the residual distribution of the fitted regression model and the reference distribution assumed under correct model specification.
-<!---->
-<!--Software for regression analysis tools is widely available.
-The Comprehensive R Archive Network (CRAN) [@hornik2012comprehensive] hosts a vast array of packages, many of which provide tools to diagnose models using residual plots.
-These packages can be broadly categorized into three groups: general-purpose, enhanced visual diagnostics, and visual diagnostics with statistical testing.-->
-<!---->
-<!--General-purpose regression analysis tools are the most widely used group of packages.
-While not specifically designed for graphical diagnostics of residuals in linear regression, they include this functionality as part of a broader suite of statistical tools.
-For example, the `stats` package [@stats] offers standard diagnostic plots such as residuals vs.
-fitted values, quantile-quantile (Q-Q) plots, and residuals vs.
-leverage plots.
-Additional packages like `jtools` [@jtools], `olsrr` [@olsrr], `rockchalk` [@rockchalk], and `ggResidpanel` [@ggresidpanel] provide similar graphical diagnostics, often with alternative aesthetics or interactive features.
-All of these tools deliver the types of diagnostic plots outlined in the classical text by @cook1982residuals.
-However, as discussed in @li2024plot, relying solely on subjective assessments of these plots can lead to issues, such as over-interpreting random patterns as model violations.-->
-<!---->
-<!-- The second group consists of enhanced visual diagnostics tools, which provide advanced aids for interpreting diagnostic plots.
-For instance, `ecostats` [@warton_global_2023] incorporates simulation envelopes into residual plots, while `DHARMa` [@dharma] compares empirical quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical counterparts.
-`DHARMa` is particularly focused on detecting model violations such as heteroscedasticity, incorrect functional forms, and issues specific to generalized linear and mixed-effect models, like over/under-dispersion.
-It also includes annotations from conventional tests, displayed as labels or text within the plot, to help avoid misinterpretation.-->
-<!---->
-<!-- The third group, visual diagnostics with statistical testing, offers tools for formally testing patterns observed in diagnostic plots [@buja2009statistical].
-A common method for visual testing of residual plots is the lineup protocol, where the true residual plot is embedded within a set of null plots generated by simulating residuals under the null hypothesis $H_0$ that the regression model is correctly specified.
-Observers are asked to identify the plot that appears most different from the others.
-If a significant proportion of observers correctly identify the true residual plot, it provides evidence against $H_0$, as the true residual plot should be indistinguishable from the null plots if all residuals are generated by the same process, according to @buja2009statistical.
-Packages in this group, such as `nullabor` [@nullabor], `HLMdiag` [@loy2014hlmdiag], and `regressinator` [@regressinator], enable users to compare observed residual plots with samples from null distributions, helping to quantify the significance of any detected patterns.
--->
-
-<!-- However, as discussed in @li2024automated, the lineup protocol has significant limitations in large-scale applications due dependence on human labor.
-Thus a computer vision model was developed with an associated statistical testing procedure to automate the assessment of residual plots.
-This model takes a residual plot and a vector of auxiliary variables (such as the number of observations) as inputs and outputs the predicted visual signal strength (VSS).
-This strength estimates the distance between the residual distribution of the fitted regression model and the reference distribution assumed under correct model specification.-->
+
 To make the statistical testing procedure and trained computer vision model widely accessible, we developed the R package `autovi`, and a web interface, `autovi.web` to make it easy for users to automatically read their residual plots with the trained computer vision model.
@@
 
-Equation \ref{eq:kl-1} can be adapted to different forms to account for various model violations.
-For instance, in the case of a linear regression model where necessary higher-order predictors, $\boldsymbol{Z}$, and their corresponding parameter, $\boldsymbol{\beta}_Z$, are omitted, the distance measure can be expanded as follows:
+This distance measure depends on knowledge of the true residual distribution, which is unknown in practice.
+To compute $D_{KL}$ for the training samples, Equation \ref{eq:kl-1} takes different forms depending on the specific model violations.
+For instance, where necessary higher-order predictors, $\boldsymbol{Z}$, and their corresponding parameter, $\boldsymbol{\beta}_Z$, are omitted from the fitted linear model, the distance measure can be expanded as follows:
 
@@
 
-This distance measure depends on knowledge of the true residual distribution, which is often unknown.
-However, it can be estimated by identifying or approximating a mapping from a set of residuals to its corresponding distance measure.
-The computer vision model presented in @li2024automated approximates this mapping.
+The computer vision model approximates this mapping from a set of residuals to its corresponding distance measure.
 It is trained on a large number of synthetic regression models, where the data-generating process is known, allowing the distance measure to be explicitly calculated.
@@
 The name `autovi` stands for **auto**mated **v**isual **i**nference.
-<!--While initially designed for linear regression residual diagnostics, it has the potential to be extended to broader visual inference applications, as we discuss in section @sec-autovi-infrastructure.-->
 This functionality can be accessed through the R package `autovi`, or through a web interface, `autovi.web`, which allows use without the full installation of R, Python, and package dependencies on the user's system.
@@
 The $p$-value is the proportion of null plots (out of the total 100) that have VSS greater than or equal to that of the true residual plot.
-<!--We typically reject the null hypothesis when the $p$-value is smaller than or equal to a desired significance level, such as 5%.--> The report also provides sample quantiles of VSS for null samples and bootstrapped data plots, providing more information about the sampling variability and a likelihood of model violations.
+The report also provides sample quantiles of VSS for null samples and bootstrapped data plots, providing more information about the sampling variability and a likelihood of model violations.
 The likelihood is computed from the proportion of values greater than the observed VSS in both the bootstrapped data values and the simulated null values.

### 2024-11-28 autovi_paper.tex
tweaked new paragraph

@@
 
-Equation \ref{eq:kl-1} can be adapted to different forms to account for
-various model violations. For instance, in the case of a linear
-regression model where necessary higher-order predictors,
-\(\boldsymbol{Z}\), and their corresponding parameter,
-\(\boldsymbol{\beta}_Z\), are omitted, the distance measure can be
-expanded as follows:
+This distance measure depends on knowledge of the true residual
+distribution, which is unknown in practice. To compute \(D_{KL}\) for
+the training samples, Equation \ref{eq:kl-1} takes different forms
+depending on the specific model violations. For instance, where
+necessary higher-order predictors, \(\boldsymbol{Z}\), and their
+corresponding parameter, \(\boldsymbol{\beta}_Z\), are omitted from the
+fitted linear model, the distance measure can be expanded as follows:
 
@@
 
-This distance measure depends on knowledge of the true residual
-distribution, which is often unknown. However, it can be estimated by
-identifying or approximating a mapping from a set of residuals to its
-corresponding distance measure. The computer vision model presented in
-\citet{li2024automated} approximates this mapping. It is trained on a
+The computer vision model approximates this mapping from a set of
+residuals to its corresponding distance measure. It is trained on a
 large number of synthetic regression models, where the data-generating

### 2025-05-04 autovi_paper.qmd
Remove redundant word "be"
Update abstract

@@
 abstract: |
-  Visually assessing residual plots is a common advice for linear model diagnostics, however this approach requires manual human evaluation and thereby is not scalable for assessing many models.
-Human evaluation also has the potential to produce inconsistent decisions from different analysts.
-Using a lineup protocol, where the residual plot is embedded among null plots, can help to alleviate inconsistency, but requires even more human effort.
-This is the type of task that in today's world we might employ a robot to do the tedious work for a human.
-Here we describe a new R package that includes a computer vision model for automated assessment of residual plots, and an accompanying Shiny app for ease of use.
-For a user-provided sample of residuals, it predicts a measure of visual signal strength (VSS) and provides a suite of supporting information to assist the analyst decide on the appropriateness their model fit.
+  Visual assessment of residual plots is a common approach for diagnosing linear models, but it relies on manual evaluation, which does not scale well and can lead to inconsistent decisions across analysts.
+The lineup protocol, which embeds the observed plot among null plots, can reduce subjectivity but requires even more human effort.
+In today’s data-driven world, such tasks are well-suited for automation.
+We present a new R package that uses a computer vision model to automate the evaluation of residual plots.
+An accompanying Shiny app is provided for ease of use.
+Given a sample of residuals, the model predicts a visual signal strength (VSS) and offers supporting information to help analysts assess the adequacy of their model fit.
 # Note that "keywords" should not include words and phrases
@@
 Importantly, its interpretation depends on how it is linked to a function of the data or the underlying data generating process.
-Consequently, the calculation of VSS can be vary across different model classes or within the same model, depending on the generating function.
+Consequently, the calculation of VSS can vary across different model classes or within the same model, depending on the generating function.
 

### 2025-05-04 autovi_paper.tex
Update abstract

--- 2024-11-28 autovi_paper.tex
@@
 % The year in the following may need to be updated!
-\def\volumeyear{2024}
+\def\volumeyear{2025}
 
@@
 
-\date{2024}
+\date{2025}
 \begin{document}
@@
 \begin{abstract}
-Visually assessing residual plots is a common advice for linear model
-diagnostics, however this approach requires manual human evaluation and
-thereby is not scalable for assessing many models. Human evaluation also
-has the potential to produce inconsistent decisions from different
-analysts. Using a lineup protocol, where the residual plot is embedded
-among null plots, can help to alleviate inconsistency, but requires even
-more human effort. This is the type of task that in today's world we
-might employ a robot to do the tedious work for a human. Here we
-describe a new R package that includes a computer vision model for
-automated assessment of residual plots, and an accompanying Shiny app
-for ease of use. For a user-provided sample of residuals, it predicts a
-measure of visual signal strength (VSS) and provides a suite of
-supporting information to assist the analyst decide on the
-appropriateness their model fit.
+Visual assessment of residual plots is a common approach for diagnosing
+linear models, but it relies on manual evaluation, which does not scale
+well and can lead to inconsistent decisions across analysts. The lineup
+protocol, which embeds the observed plot among null plots, can reduce
+subjectivity but requires even more human effort. In today's data-driven
+world, such tasks are well-suited for automation. We present a new R
+package that uses a computer vision model to automate the evaluation of
+residual plots. An accompanying Shiny app is provided for ease of use.
+Given a sample of residuals, the model predicts a visual signal strength
+(VSS) and offers supporting information to help analysts assess the
+adequacy of their model fit.
 \end{abstract}

### 2025-05-07 autovi_paper.qmd
Improve sentence connection in first paragraph

@@
 There is a vast array of software for conducting regression modeling and generating diagnostics.
-The package `lmtest` [@lmtest] provides a suite of conventional tests.
-The `stats` package [@stats] offers standard diagnostic plots such as residuals vs.
+The package `lmtest` [@lmtest] provides a suite of conventional tests, while the `stats` package [@stats] offers standard diagnostic plots such as residuals vs.
 fitted values, quantile-quantile (Q-Q) plots, and residuals vs.
 leverage plots.
-Packages like `jtools` [@jtools], `olsrr` [@olsrr], `rockchalk` [@rockchalk], and `ggResidpanel` [@ggresidpanel] provide similar graphical diagnostics, often with alternative aesthetics or interactive features.
-All of these tools deliver the types of diagnostic plots outlined in the classical text by @cook1982residuals.
-The `ecostats` package [@warton_global_2023] incorporates simulation envelopes into residual plots, while `DHARMa` [@dharma] compares empirical quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical counterparts.
-`DHARMa` is particularly focused on detecting model violations such as heteroscedasticity, incorrect functional forms, and issues specific to generalized linear and mixed-effect models, like over/under-dispersion.
-It also includes conventional test annotations to help avoid misinterpretation.
+Additional packages like `jtools` [@jtools], `olsrr` [@olsrr], `rockchalk` [@rockchalk], and `ggResidpanel` [@ggresidpanel] deliver similar graphical diagnostics, often with enhanced aesthetics or interactive features.
+These tools collectively produce the core diagnostic plots outlined in the classical text by @cook1982residuals.
+The `ecostats` package [@warton_global_2023] extends these diagnostics by incorporating simulation envelopes into residual plots.
+Meanwhile, `DHARMa` [@dharma] compares empirical quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical counterparts, with a strong focus on identifying model violations such as heteroscedasticity, misspecified functional forms, and issues specific to generalized linear and mixed-effect models, like over/under-dispersion.
+It also provides conventional test annotations to reduce the risk of misinterpretation.
 

### 2025-05-07 autovi_paper.tex
Improve sentence connection in first paragraph

@@
 regression modeling and generating diagnostics. The package
-\texttt{lmtest} \citep{lmtest} provides a suite of conventional tests.
-The \texttt{stats} package \citep{stats} offers standard diagnostic
-plots such as residuals vs.~fitted values, quantile-quantile (Q-Q)
-plots, and residuals vs.~leverage plots. Packages like \texttt{jtools}
-\citep{jtools}, \texttt{olsrr} \citep{olsrr}, \texttt{rockchalk}
-\citep{rockchalk}, and \texttt{ggResidpanel} \citep{ggresidpanel}
-provide similar graphical diagnostics, often with alternative aesthetics
-or interactive features. All of these tools deliver the types of
-diagnostic plots outlined in the classical text by
+\texttt{lmtest} \citep{lmtest} provides a suite of conventional tests,
+while the \texttt{stats} package \citep{stats} offers standard
+diagnostic plots such as residuals vs.~fitted values, quantile-quantile
+(Q-Q) plots, and residuals vs.~leverage plots. Additional packages like
+\texttt{jtools} \citep{jtools}, \texttt{olsrr} \citep{olsrr},
+\texttt{rockchalk} \citep{rockchalk}, and \texttt{ggResidpanel}
+\citep{ggresidpanel} deliver similar graphical diagnostics, often with
+enhanced aesthetics or interactive features. These tools collectively
+produce the core diagnostic plots outlined in the classical text by
 \citet{cook1982residuals}. The \texttt{ecostats} package
-\citep{warton_global_2023} incorporates simulation envelopes into
-residual plots, while \texttt{DHARMa} \citep{dharma} compares empirical
-quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical
-counterparts. \texttt{DHARMa} is particularly focused on detecting model
-violations such as heteroscedasticity, incorrect functional forms, and
-issues specific to generalized linear and mixed-effect models, like
-over/under-dispersion. It also includes conventional test annotations to
-help avoid misinterpretation.
+\citep{warton_global_2023} extends these diagnostics by incorporating
+simulation envelopes into residual plots. Meanwhile, \texttt{DHARMa}
+\citep{dharma} compares empirical quantiles (0.25, 0.5, and 0.75) of
+scaled residuals to their theoretical counterparts, with a strong focus
+on identifying model violations such as heteroscedasticity, misspecified
+functional forms, and issues specific to generalized linear and
+mixed-effect models, like over/under-dispersion. It also provides
+conventional test annotations to reduce the risk of misinterpretation.
 
@@
 function of the data or the underlying data generating process.
-Consequently, the calculation of VSS can be vary across different model
+Consequently, the calculation of VSS can vary across different model
 classes or within the same model, depending on the generating function.

### 2025-05-07 autovi_paper.qmd
Improve the second paragraph

@@
 However, relying solely on subjective assessments of these plots can lead to issues such as over-interpreting random patterns as model violations.
-@li2024plot demonstrated that visual methods using the lineup protocol [@buja2009statistical] for assessing residuals are more useful, and also perform more practically than conventional tests due to their reduced sensitivity to minor departures.
-Packages such as `nullabor` [@nullabor], `HLMdiag` [@loy2014hlmdiag], and `regressinator` [@regressinator], enable users to compare observed residual plots with plots of samples from null distributions, helping to quantify the significance of any detected patterns.
+@li2024plot demonstrated that visual inference methods, particularly those using the lineup protocol [@buja2009statistical], offer more practical and reliable assessments of residual patterns than conventional tests, as they are less sensitive to minor departures.
+Packages such as `nullabor` [@nullabor], `HLMdiag` [@loy2014hlmdiag], and `regressinator` [@regressinator] support this approach by enabling users to compare observed residual plots with plots generated under null hypothesis, thereby helping to quantify the significance of any detected patterns.
 

### 2025-05-07 autovi_paper.tex
Improve the second paragraph

@@
 lead to issues such as over-interpreting random patterns as model
-violations. \citet{li2024plot} demonstrated that visual methods using
-the lineup protocol \citep{buja2009statistical} for assessing residuals
-are more useful, and also perform more practically than conventional
-tests due to their reduced sensitivity to minor departures. Packages
-such as \texttt{nullabor} \citep{nullabor}, \texttt{HLMdiag}
-\citep{loy2014hlmdiag}, and \texttt{regressinator}
-\citep{regressinator}, enable users to compare observed residual plots
-with plots of samples from null distributions, helping to quantify the
-significance of any detected patterns.
+violations. \citet{li2024plot} demonstrated that visual inference
+methods, particularly those using the lineup protocol
+\citep{buja2009statistical}, offer more practical and reliable
+assessments of residual patterns than conventional tests, as they are
+less sensitive to minor departures. Packages such as \texttt{nullabor}
+\citep{nullabor}, \texttt{HLMdiag} \citep{loy2014hlmdiag}, and
+\texttt{regressinator} \citep{regressinator} support this approach by
+enabling users to compare observed residual plots with plots generated
+under null hypothesis, thereby helping to quantify the significance of
+any detected patterns.
 

### 2025-05-07 autovi_paper.qmd
Improve the rest of the first section

@@
 
-However, as discussed in @li2024automated, the lineup protocol has significant limitations in large-scale applications due to dependence on human labor.
-Thus, a computer vision model was developed with an associated statistical testing procedure to automate the assessment of residual plots.
-This model takes a residual plot and a vector of auxiliary variables (such as the number of observations) as inputs and outputs the predicted visual signal strength (VSS).
-This strength estimates the distance between the residual distribution of the fitted regression model and the reference distribution assumed under correct model specification.
-
-To make the statistical testing procedure and trained computer vision model widely accessible, we developed the R package `autovi`, and a web interface, `autovi.web` to make it easy for users to automatically read their residual plots with the trained computer vision model.
+As noted in @li2024automated, the lineup protocol has significant limitations in large-scale applications due to its reliance on human labor.
+To overcome this constraint, a computer vision model was developed alongside a corresponding statistical testing procedure to autmoate the assessment of residual plots.
+The model takes as input a residual plot and a set of auxiliary variables (such as the number of observations) and outputs a predicted visual signal strength (VSS).
+This VSS estimates the degree of deviation between the residual distribution of the fitted model and the reference distribution expected under correct model specification.
+
+To make the statistical testing procedure and trained computer vision model widely accessible, we developed the R package `autovi` along with a companion web interface, `autovi.web`, which allows users to automatically assess their residual plots using the trained computer vision model.
 

### 2025-05-07 autovi_paper.tex
Improve the rest of the first section

@@
 
-However, as discussed in \citet{li2024automated}, the lineup protocol
-has significant limitations in large-scale applications due to
-dependence on human labor. Thus, a computer vision model was developed
-with an associated statistical testing procedure to automate the
-assessment of residual plots. This model takes a residual plot and a
-vector of auxiliary variables (such as the number of observations) as
-inputs and outputs the predicted visual signal strength (VSS). This
-strength estimates the distance between the residual distribution of the
-fitted regression model and the reference distribution assumed under
+As noted in \citet{li2024automated}, the lineup protocol has significant
+limitations in large-scale applications due to its reliance on human
+labor. To overcome this constraint, a computer vision model was
+developed alongside a corresponding statistical testing procedure to
+autmoate the assessment of residual plots. The model takes as input a
+residual plot and a set of auxiliary variables (such as the number of
+observations) and outputs a predicted visual signal strength (VSS). This
+VSS estimates the degree of deviation between the residual distribution
+of the fitted model and the reference distribution expected under
 correct model specification.
@@
 To make the statistical testing procedure and trained computer vision
-model widely accessible, we developed the R package \texttt{autovi}, and
-a web interface, \texttt{autovi.web} to make it easy for users to
-automatically read their residual plots with the trained computer vision
-model.
+model widely accessible, we developed the R package \texttt{autovi}
+along with a companion web interface, \texttt{autovi.web}, which allows
+users to automatically assess their residual plots using the trained
+computer vision model.
 

### 2025-05-07 autovi_paper.qmd
Improve the autovi summary

@@
 The name `autovi` stands for **auto**mated **v**isual **i**nference.
-This functionality can be accessed through the R package `autovi`, or through a web interface, `autovi.web`, which allows use without the full installation of R, Python, and package dependencies on the user's system.
-locally.
+This functionality can be accessed through the R package `autovi`, or through a web interface, `autovi.web`, which enables users to perform analyses without installing R, Python, or their associated dependencies locally.
 

### 2025-05-07 autovi_paper.qmd
make keras info visible

@@
 ```{r message=TRUE}
+if (!file.exists("cached_data/autovi_checker_demo_print.rds")) {
+  checker$keras_model <- get_keras_model("vss_phn_32") 
+  checker$check()
+  saveRDS(checker$..str..(), "cached_data/autovi_checker_demo_print.rds")
+} else {
+  cli::cli_h3(readRDS("cached_data/autovi_checker_demo_print.rds"))
+}
+```
+
+```{r}
 if (!file.exists("cached_data/autovi_check_demo.rds")) {
@@
 }
-
-checker
 ```

### 2025-05-07 autovi_paper.tex
Improve the autovi summary
make keras info visible

@@
 package \texttt{autovi}, or through a web interface,
-\texttt{autovi.web}, which allows use without the full installation of
-R, Python, and package dependencies on the user's system. locally.
+\texttt{autovi.web}, which enables users to perform analyses without
+installing R, Python, or their associated dependencies locally.
 
@@
  - Fitted model: lm
- - Keras model: UNKNOWN
+ - Keras model: (None, 32, 32, 3) + (None, 5) -> (None, 1)
     - Output node index: 1
  - Result:
-    - Observed visual signal strength: 3.162 (p-value = 0.0396)
+    - Observed visual signal strength: 3.16 (p-value = 0.0396)
     - Null visual signal strength: [100 draws]
@@
        - Quantiles: 
-          ╔═════════════════════════════════════════════════╗
+          ╔══════════════════════════════════════════╗
           ║  25%   50%   75%   80%   90%   95%   99% ║
-          ║0.8021 1.1109 1.5751 1.6656 1.9199 2.6564 3.3491 ║
-          ╚═════════════════════════════════════════════════╝
+          ║0.802 1.111 1.575 1.666 1.919 2.657 3.348 ║
+          ╚══════════════════════════════════════════╝
     - Bootstrapped visual signal strength: [100 draws]
-       - Mean: 2.786 (p-value = 0.05941)
+       - Mean: 2.795 (p-value = 0.05941)
        - Quantiles: 
@@
           ║  25%   50%   75%   80%   90%   95%   99% ║
-          ║2.452 2.925 3.173 3.285 3.463 3.505 3.652 ║
+          ║2.455 2.941 3.177 3.300 3.474 3.537 3.668 ║
           ╚══════════════════════════════════════════╝
-    - Likelihood ratio: 0.7275 (boot) / 0.06298 (null) = 11.55 
+    - Likelihood ratio: 0.7333 (boot) / 0.06284 (null) = 11.67 
 \end{verbatim}

### 2025-05-09 autovi_paper.qmd
Add an extension to GLM Poisson

@@
 
-The `autovi` package is available on CRAN. It is actively developed and maintained, with the latest updates accessible on GitHub. This paper uses `autovi` version 0.4.1.
+The `autovi` package is available on CRAN. It is actively developed and maintained, with the latest updates accessible on GitHub. This paper uses `autovi` version 0.4.2.
 The package includes internal functions to check the current Python environment used by the `reticulate` package.
@@
 These modules are discussed in detail in the package documentation.
+
+## Extension to Other Model Classes
+
+The `autovi` R package can be extended to accommodate other classes of models beyond linear regression, such as generalized linear models (`glm`).
+This is achieved by substituting the relevant overridable modules, as illustrated in @fig-autovi-diag.
+
+We provide an example of defining a new checker class tailored for Poisson regression using the `glm` framework:
+
+1. Define a new class using `new_class()` with `AUTO_VI` as the parent class.
+2.
+Override the necessary methods using `register_method()`.
+In this example, we use Pearson residuals.
+To simulate null residuals, we assume the fitted model is correct and the estimated coefficients are accurate.
+New response values are generated accordingly, and a new model is fitted to this simulated response.
+Null residuals are then extracted from this refitted model.
+3. Create an alias for the `instantiate()` method of the new class.
+
+```{r echo = TRUE}
+AUTO_GLM_VI <- new_class(AUTO_VI, class_name = "AUTO_GLM_VI")
+register_method(
+  AUTO_GLM_VI,
+  get_fitted_and_resid = function(fitted_model = self$fitted_model) {
+    tibble(.fitted = fitted(fitted_model),
+           .resid = resid(fitted_model, type = "pearson"))
+  },
+  null_method = function(fitted_model = self$fitted_model) {
+    dat <- model.frame(fitted_model)
+    dat[[1]] <- rpois(nrow(dat), lambda = fitted(fitted_model))
+    new_mod <- update(fitted_model, data = dat)
+    return(self$get_fitted_and_resid(new_mod))
+  }
+)
+auto_glm_vi <- AUTO_GLM_VI$instantiate
+```
+
+The resulting checker class can be employed analogously to the linear model case described in @sec-autovi-usage.
+For illustration, we fit a Poisson model in which the quadratic term of the predictor $x$ is intentionally omitted.
+This misspecification manifests as a pronounced U-shaped pattern in the lineup display, which is also successfully identified by the computer vision model, yielding a p-value substantially below the conventional threshold of 0.05.
+
+It is important to note, however, that the pre-trained computer vision model was developed specifically for diagnostic evaluation of linear regression.
+Its applicability to other model classes relies on the assumption that the null residual plots exhibit characteristics broadly consistent with those of well-behaved linear regression residuals, that is, residuals should be approximately randomly scattered around zero, display roughly constant variance across the range of fitted values, and exhibit no discernible structure or curvature.
+If these conditions are not met, or if model violations do not give rise to visually detectable patterns, the validity of the automated diagnostics may be compromised.
+For further discussion on extending the methodology to other model classes, refer to @li2024automated.
+
+```r
+set.seed(10086)
+x <- rnorm(300, sd = 0.5)
+y <- rpois(300, lambda = exp(1 + x + x^2))
+y_fit <- glm(y ~ x, family = "poisson")
+
+glm_checker <- auto_glm_vi(glm(y ~ x, family = "poisson"),
+                           keras_model = get_keras_model("vss_phn_32"))
+glm_checker$plot_lineup()
+```
+
+```{r include = FALSE}
+set.seed(10086)
+x <- rnorm(300, sd = 0.5)
+y <- rpois(300, lambda = exp(1 + x + x^2))
+y_fit <- glm(y ~ x, family = "poisson")
+
+glm_checker <- auto_glm_vi(glm(y ~ x, family = "poisson"))
+```
+
+```{r}
+glm_checker$plot_lineup()
+```
+
+```r
+glm_checker$check()
+```
+
+```{r message = TRUE}
+if (!file.exists("cached_data/autovi_glm_checker_demo_print.rds")) {
+  glm_checker <- auto_glm_vi(glm(y ~ x, family = "poisson"),
+                           keras_model = get_keras_model("vss_phn_32"))
+  glm_checker$check()
+  saveRDS(glm_checker$..str..(), "cached_data/autovi_glm_checker_demo_print.rds")
+} else {
+  cli::cli_h3(readRDS("cached_data/autovi_glm_checker_demo_print.rds"))
+}
+```
+
 <!-- in the following sections.-->

### 2025-05-09 autovi_paper.tex
Add an extension to GLM Poisson

@@
 developed and maintained, with the latest updates accessible on GitHub.
-This paper uses \texttt{autovi} version 0.4.1. The package includes
+This paper uses \texttt{autovi} version 0.4.2. The package includes
 internal functions to check the current Python environment used by the
@@
 
+\subsection{Extension to Other Model
+Classes}\label{extension-to-other-model-classes}
+
+The \texttt{autovi} R package can be extended to accommodate other
+classes of models beyond linear regression, such as generalized linear
+models (\texttt{glm}). This is achieved by substituting the relevant
+overridable modules, as illustrated in Figure~\ref{fig-autovi-diag}.
+
+We provide an example of defining a new checker class tailored for
+Poisson regression using the \texttt{glm} framework:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Define a new class using \texttt{new\_class()} with \texttt{AUTO\_VI}
+  as the parent class.
+\item
+  Override the necessary methods using \texttt{register\_method()}. In
+  this example, we use Pearson residuals. To simulate null residuals, we
+  assume the fitted model is correct and the estimated coefficients are
+  accurate. New response values are generated accordingly, and a new
+  model is fitted to this simulated response. Null residuals are then
+  extracted from this refitted model.
+\item
+  Create an alias for the \texttt{instantiate()} method of the new
+  class.
+\end{enumerate}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{AUTO\_GLM\_VI }\OtherTok{\textless{}{-}} \FunctionTok{new\_class}\NormalTok{(AUTO\_VI, }\AttributeTok{class\_name =} \StringTok{"AUTO\_GLM\_VI"}\NormalTok{)}
+\FunctionTok{register\_method}\NormalTok{(}
+\NormalTok{  AUTO\_GLM\_VI,}
+  \AttributeTok{get\_fitted\_and\_resid =} \ControlFlowTok{function}\NormalTok{(}\AttributeTok{fitted\_model =}\NormalTok{ self}\SpecialCharTok{$}\NormalTok{fitted\_model) \{}
+    \FunctionTok{tibble}\NormalTok{(}\AttributeTok{.fitted =} \FunctionTok{fitted}\NormalTok{(fitted\_model),}
+           \AttributeTok{.resid =} \FunctionTok{resid}\NormalTok{(fitted\_model, }\AttributeTok{type =} \StringTok{"pearson"}\NormalTok{))}
+\NormalTok{  \},}
+  \AttributeTok{null\_method =} \ControlFlowTok{function}\NormalTok{(}\AttributeTok{fitted\_model =}\NormalTok{ self}\SpecialCharTok{$}\NormalTok{fitted\_model) \{}
+\NormalTok{    dat }\OtherTok{\textless{}{-}} \FunctionTok{model.frame}\NormalTok{(fitted\_model)}
+\NormalTok{    dat[[}\DecValTok{1}\NormalTok{]] }\OtherTok{\textless{}{-}} \FunctionTok{rpois}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(dat), }\AttributeTok{lambda =} \FunctionTok{fitted}\NormalTok{(fitted\_model))}
+\NormalTok{    new\_mod }\OtherTok{\textless{}{-}} \FunctionTok{update}\NormalTok{(fitted\_model, }\AttributeTok{data =}\NormalTok{ dat)}
+    \FunctionTok{return}\NormalTok{(self}\SpecialCharTok{$}\FunctionTok{get\_fitted\_and\_resid}\NormalTok{(new\_mod))}
+\NormalTok{  \}}
+\NormalTok{)}
+\NormalTok{auto\_glm\_vi }\OtherTok{\textless{}{-}}\NormalTok{ AUTO\_GLM\_VI}\SpecialCharTok{$}\NormalTok{instantiate}
+\end{Highlighting}
+\end{Shaded}
+
+The resulting checker class can be employed analogously to the linear
+model case described in Section~\ref{sec-autovi-usage}. For
+illustration, we fit a Poisson model in which the quadratic term of the
+predictor \(x\) is intentionally omitted. This misspecification
+manifests as a pronounced U-shaped pattern in the lineup display, which
+is also successfully identified by the computer vision model, yielding a
+p-value substantially below the conventional threshold of 0.05.
+
+It is important to note, however, that the pre-trained computer vision
+model was developed specifically for diagnostic evaluation of linear
+regression. Its applicability to other model classes relies on the
+assumption that the null residual plots exhibit characteristics broadly
+consistent with those of well-behaved linear regression residuals, that
+is, residuals should be approximately randomly scattered around zero,
+display roughly constant variance across the range of fitted values, and
+exhibit no discernible structure or curvature. If these conditions are
+not met, or if model violations do not give rise to visually detectable
+patterns, the validity of the automated diagnostics may be compromised.
+For further discussion on extending the methodology to other model
+classes, refer to \citet{li2024automated}.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{set.seed}\NormalTok{(}\DecValTok{10086}\NormalTok{)}
+\NormalTok{x }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(}\DecValTok{300}\NormalTok{, }\AttributeTok{sd =} \FloatTok{0.5}\NormalTok{)}
+\NormalTok{y }\OtherTok{\textless{}{-}} \FunctionTok{rpois}\NormalTok{(}\DecValTok{300}\NormalTok{, }\AttributeTok{lambda =} \FunctionTok{exp}\NormalTok{(}\DecValTok{1} \SpecialCharTok{+}\NormalTok{ x }\SpecialCharTok{+}\NormalTok{ x}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{))}
+\NormalTok{y\_fit }\OtherTok{\textless{}{-}} \FunctionTok{glm}\NormalTok{(y }\SpecialCharTok{\textasciitilde{}}\NormalTok{ x, }\AttributeTok{family =} \StringTok{"poisson"}\NormalTok{)}
+
+\NormalTok{glm\_checker }\OtherTok{\textless{}{-}} \FunctionTok{auto\_glm\_vi}\NormalTok{(}\FunctionTok{glm}\NormalTok{(y }\SpecialCharTok{\textasciitilde{}}\NormalTok{ x, }\AttributeTok{family =} \StringTok{"poisson"}\NormalTok{),}
+                           \AttributeTok{keras\_model =} \FunctionTok{get\_keras\_model}\NormalTok{(}\StringTok{"vss\_phn\_32"}\NormalTok{))}
+\NormalTok{glm\_checker}\SpecialCharTok{$}\FunctionTok{plot\_lineup}\NormalTok{()}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}
+\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/unnamed-chunk-9-1.pdf}
+\end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{glm\_checker}\SpecialCharTok{$}\FunctionTok{check}\NormalTok{()}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+\end{verbatim}
+
+\begin{verbatim}
+-- <AUTO_GLM_VI object>
+Status:
+ - Fitted model: glm, lm
+ - Keras model: (None, 32, 32, 3) + (None, 5) -> (None, 1)
+    - Output node index: 1
+ - Result:
+    - Observed visual signal strength: 4.875 (p-value = 0.009901)
+    - Null visual signal strength: [100 draws]
+       - Mean: 1.331
+       - Quantiles: 
+          ╔══════════════════════════════════════════╗
+          ║  25%   50%   75%   80%   90%   95%   99% ║
+          ║1.035 1.233 1.488 1.644 1.941 2.276 2.639 ║
+          ╚══════════════════════════════════════════╝
+    - Bootstrapped visual signal strength: [100 draws]
+       - Mean: 5.51 (p-value = 0.009901)
+       - Quantiles: 
+          ╔══════════════════════════════════════════╗
+          ║  25%   50%   75%   80%   90%   95%   99% ║
+          ║5.330 5.505 5.698 5.735 5.830 5.903 6.013 ║
+          ╚══════════════════════════════════════════╝
+    - Likelihood ratio: 0.05096 (boot) / 0 (null) = Extremely large 
+\end{verbatim}
+
 \section{Web interface: autovi.web}\label{sec-autovi-web}

### 2025-05-09 autovi_paper.qmd
Give better name for the extended class

@@
 ```{r echo = TRUE}
-AUTO_GLM_VI <- new_class(AUTO_VI, class_name = "AUTO_GLM_VI")
+AUTO_POIS_VI <- new_class(AUTO_VI, class_name = "AUTO_POIS_VI")
 register_method(
-  AUTO_GLM_VI,
+  AUTO_POIS_VI,
   get_fitted_and_resid = function(fitted_model = self$fitted_model) {
@@
 )
-auto_glm_vi <- AUTO_GLM_VI$instantiate
+auto_pois_vi <- AUTO_POIS_VI$instantiate
 ```
@@
 ```r
-set.seed(10086)
 x <- rnorm(300, sd = 0.5)
 y <- rpois(300, lambda = exp(1 + x + x^2))
-y_fit <- glm(y ~ x, family = "poisson")
-
-glm_checker <- auto_glm_vi(glm(y ~ x, family = "poisson"),
-                           keras_model = get_keras_model("vss_phn_32"))
-glm_checker$plot_lineup()
+pois_checker <- auto_pois_vi(
+  glm(y ~ x, family = "poisson"),
+  keras_model = get_keras_model("vss_phn_32")
+)
+pois_checker$plot_lineup()
 ```
@@
 y <- rpois(300, lambda = exp(1 + x + x^2))
-y_fit <- glm(y ~ x, family = "poisson")
-
-glm_checker <- auto_glm_vi(glm(y ~ x, family = "poisson"))
-```
-
-```{r}
-glm_checker$plot_lineup()
-```
-
-```r
-glm_checker$check()
+pois_checker <- auto_pois_vi(glm(y ~ x, family = "poisson"))
+```
+
+```{r}
+pois_checker$plot_lineup()
+```
+
+```r
+pois_checker$check()
 ```
@@
 if (!file.exists("cached_data/autovi_glm_checker_demo_print.rds")) {
-  glm_checker <- auto_glm_vi(glm(y ~ x, family = "poisson"),
+  pois_checker <- auto_pois_vi(glm(y ~ x, family = "poisson"),
                                keras_model = get_keras_model("vss_phn_32"))
-  glm_checker$check()
-  saveRDS(glm_checker$..str..(), "cached_data/autovi_glm_checker_demo_print.rds")
+  pois_checker$check()
+  saveRDS(pois_checker$..str..(), "cached_data/autovi_glm_checker_demo_print.rds")
 } else {

### 2025-05-09 autovi_paper.tex
Give better name for the extended class

@@
 \begin{Highlighting}[]
-\NormalTok{AUTO\_GLM\_VI }\OtherTok{\textless{}{-}} \FunctionTok{new\_class}\NormalTok{(AUTO\_VI, }\AttributeTok{class\_name =} \StringTok{"AUTO\_GLM\_VI"}\NormalTok{)}
+\NormalTok{AUTO\_POIS\_VI }\OtherTok{\textless{}{-}} \FunctionTok{new\_class}\NormalTok{(AUTO\_VI, }\AttributeTok{class\_name =} \StringTok{"AUTO\_POIS\_VI"}\NormalTok{)}
 \FunctionTok{register\_method}\NormalTok{(}
-\NormalTok{  AUTO\_GLM\_VI,}
+\NormalTok{  AUTO\_POIS\_VI,}
   \AttributeTok{get\_fitted\_and\_resid =} \ControlFlowTok{function}\NormalTok{(}\AttributeTok{fitted\_model =}\NormalTok{ self}\SpecialCharTok{$}\NormalTok{fitted\_model) \{}
@@
 \NormalTok{)}
-\NormalTok{auto\_glm\_vi }\OtherTok{\textless{}{-}}\NormalTok{ AUTO\_GLM\_VI}\SpecialCharTok{$}\NormalTok{instantiate}
+\NormalTok{auto\_pois\_vi }\OtherTok{\textless{}{-}}\NormalTok{ AUTO\_POIS\_VI}\SpecialCharTok{$}\NormalTok{instantiate}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\FunctionTok{set.seed}\NormalTok{(}\DecValTok{10086}\NormalTok{)}
 \NormalTok{x }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(}\DecValTok{300}\NormalTok{, }\AttributeTok{sd =} \FloatTok{0.5}\NormalTok{)}
 \NormalTok{y }\OtherTok{\textless{}{-}} \FunctionTok{rpois}\NormalTok{(}\DecValTok{300}\NormalTok{, }\AttributeTok{lambda =} \FunctionTok{exp}\NormalTok{(}\DecValTok{1} \SpecialCharTok{+}\NormalTok{ x }\SpecialCharTok{+}\NormalTok{ x}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{))}
-\NormalTok{y\_fit }\OtherTok{\textless{}{-}} \FunctionTok{glm}\NormalTok{(y }\SpecialCharTok{\textasciitilde{}}\NormalTok{ x, }\AttributeTok{family =} \StringTok{"poisson"}\NormalTok{)}
-
-\NormalTok{glm\_checker }\OtherTok{\textless{}{-}} \FunctionTok{auto\_glm\_vi}\NormalTok{(}\FunctionTok{glm}\NormalTok{(y }\SpecialCharTok{\textasciitilde{}}\NormalTok{ x, }\AttributeTok{family =} \StringTok{"poisson"}\NormalTok{),}
-                           \AttributeTok{keras\_model =} \FunctionTok{get\_keras\_model}\NormalTok{(}\StringTok{"vss\_phn\_32"}\NormalTok{))}
-\NormalTok{glm\_checker}\SpecialCharTok{$}\FunctionTok{plot\_lineup}\NormalTok{()}
+\NormalTok{pois\_checker }\OtherTok{\textless{}{-}} \FunctionTok{auto\_pois\_vi}\NormalTok{(}
+  \FunctionTok{glm}\NormalTok{(y }\SpecialCharTok{\textasciitilde{}}\NormalTok{ x, }\AttributeTok{family =} \StringTok{"poisson"}\NormalTok{),}
+  \AttributeTok{keras\_model =} \FunctionTok{get\_keras\_model}\NormalTok{(}\StringTok{"vss\_phn\_32"}\NormalTok{)}
+\NormalTok{)}
+\NormalTok{pois\_checker}\SpecialCharTok{$}\FunctionTok{plot\_lineup}\NormalTok{()}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\NormalTok{glm\_checker}\SpecialCharTok{$}\FunctionTok{check}\NormalTok{()}
+\NormalTok{pois\_checker}\SpecialCharTok{$}\FunctionTok{check}\NormalTok{()}
 \end{Highlighting}
@@
 \begin{verbatim}
--- <AUTO_GLM_VI object>
+-- <AUTO_POIS_VI object>
 Status:

### 2025-05-09 autovi_paper.qmd
Add a section for null and boot residuals

@@
 
+# Definition and simulation of null and bootstrapped residuals {#sec-null-and-boot-desc}
+
+In the subsequent sections, we will frequently refer to null residuals and bootstrapped residuals, so it is helpful to first define and explain how they are generated.
+
+**Null residuals** are used to generate null plots within the lineup protocol framework, serving as the foundation for the statistical testing in our automated residual plot assessment.
+Specifically, they represent residuals generated under the null hypothesis that the model is correctly specified.
+A common method for simulating null residuals in linear regression involves sampling from a normal distribution with mean zero and variance equal to the estimated variance of the error term.
+These simulated residuals and their corresponding plots depict what one would expect from a correctly specified model.
+If the true residual plot exhibits noticeable deviations from these null plots, it may suggest model misspecification.
+
+Our computer vision model is trained to assign lower VSS to null plots and higher VSS to plots that display distinct patterns.
+Accordingly, statistical testing is performed by computing the proportion of null plots whose VSS equals or exceeds that of the observed residual plot.
+This proportion serves as a p-value for a one-sided hypothesis test.
+
+**Bootstrapped residuals** are obtained by refitting the model on bootstrap samples, which are generated by sampling individual observations with replacement from the original dataset.
+The residual plots obtained from these refitted models are evaluated using the same computer vision model.
+The predicted VSS from the bootstrapped plots provide an empirical estimate of the variation in the VSS of the observed residual plot.
+By examining the proportion of bootstrapped plots that also exhibit significant violations, we can assess whether the original conclusion is robust to sampling variability.
+
 # R package: autovi {#sec-autovi}

### 2025-05-09 autovi_paper.tex
Add a section for null and boot residuals

@@
 
+\section{Definition and simulation of null and bootstrapped
+residuals}\label{sec-null-and-boot-desc}
+
+In the subsequent sections, we will frequently refer to null residuals
+and bootstrapped residuals, so it is helpful to first define and explain
+how they are generated.
+
+\textbf{Null residuals} are used to generate null plots within the
+lineup protocol framework, serving as the foundation for the statistical
+testing in our automated residual plot assessment. Specifically, they
+represent residuals generated under the null hypothesis that the model
+is correctly specified. A common method for simulating null residuals in
+linear regression involves sampling from a normal distribution with mean
+zero and variance equal to the estimated variance of the error term.
+These simulated residuals and their corresponding plots depict what one
+would expect from a correctly specified model. If the true residual plot
+exhibits noticeable deviations from these null plots, it may suggest
+model misspecification.
+
+Our computer vision model is trained to assign lower VSS to null plots
+and higher VSS to plots that display distinct patterns. Accordingly,
+statistical testing is performed by computing the proportion of null
+plots whose VSS equals or exceeds that of the observed residual plot.
+This proportion serves as a p-value for a one-sided hypothesis test.
+
+\textbf{Bootstrapped residuals} are obtained by refitting the model on
+bootstrap samples, which are generated by sampling individual
+observations with replacement from the original dataset. The residual
+plots obtained from these refitted models are evaluated using the same
+computer vision model. The predicted VSS from the bootstrapped plots
+provide an empirical estimate of the variation in the VSS of the
+observed residual plot. By examining the proportion of bootstrapped
+plots that also exhibit significant violations, we can assess whether
+the original conclusion is robust to sampling variability.
+
 \section{R package: autovi}\label{sec-autovi}

### 2025-05-12 autovi_paper.qmd
Provide details about how CV is trained

@@
 The computer vision model approximates this mapping from a set of residuals to its corresponding distance measure.
-It is trained on a large number of synthetic regression models, where the data-generating process is known, allowing the distance measure to be explicitly calculated.
-The model takes a residual plot as input and outputs the corresponding distance measure.
+It is trained on a large number of synthetic regression models, each designed to simulate specific violations of classical linear regression assumptions.
+These models incorporate non-linearity through Hermite polynomial transformations of predictors, heteroskedasticity by making the error variance a predictor-dependent function, and non-normality by drawing residuals from distributions such as discrete, uniform, and lognormal.
+Both simple and multiple linear regression structures are used, with controlled parameters to generate diverse and complex residual patterns.
+Since the data-generating process is known, the distance measure $D$ can be explicitly calculated, enabling supervised training.
+The computer vision model takes a residual plot as input and outputs the corresponding distance measure, learning to quantify model violations directly from visual patterns.
 Additional details are provided in @li2024automated.

### 2025-05-12 autovi_paper.tex
Provide details about how CV is trained

@@
 residuals to its corresponding distance measure. It is trained on a
-large number of synthetic regression models, where the data-generating
-process is known, allowing the distance measure to be explicitly
-calculated. The model takes a residual plot as input and outputs the
-corresponding distance measure. Additional details are provided in
+large number of synthetic regression models, each designed to simulate
+specific violations of classical linear regression assumptions. These
+models incorporate non-linearity through Hermite polynomial
+transformations of predictors, heteroskedasticity by making the error
+variance a predictor-dependent function, and non-normality by drawing
+residuals from distributions such as discrete, uniform, and lognormal.
+Both simple and multiple linear regression structures are used, with
+controlled parameters to generate diverse and complex residual patterns.
+Since the data-generating process is known, the distance measure \(D\)
+can be explicitly calculated, enabling supervised training. The computer
+vision model takes a residual plot as input and outputs the
+corresponding distance measure, learning to quantify model violations
+directly from visual patterns. Additional details are provided in
 \citet{li2024automated}.
@@
 \begin{center}
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/unnamed-chunk-9-1.pdf}
+\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/unnamed-chunk-7-1.pdf}
 \end{center}

### 2025-05-12 autovi_paper.qmd
Provide brief desc for each module

@@
 
-The modules for VSS prediction and $p$-value computation are predefined and cannot be overridden, although users can interact with them directly through function arguments.
-Similarly, the image reading and resizing module is fixed but will adapt to different Keras models by checking their input shapes.
-The remaining seven modules are designed to be overridable, enabling users to tailor the infrastructure to their specific needs.
-These modules are discussed in detail in the package documentation.
+The package takes regression models and a `Keras` model as primary inputs.
+Modules for VSS prediction and $p$-value computation are fixed but accessible via function arguments, using `TensorFlow` for inference and statistical testing.
+The image loading module is also fixed, using `PIL` to read and resize images based on the `Keras` model’s input shape.
+The remaining seven modules are overridable, allowing users to adapt the workflow as needed.
+The data extraction module extracts a `data.frame` containing variables used in the regression model.
+The bootstrapping and refitting module resamples the data and refits the model.
+The fitted values and residuals extraction module returns these values as a `data.frame`.
+The auxiliary computation module calculates scagnostics such as monotonicity.
+The plotting module generates a `ggplot` in a standard format, and the plot saving module exports it at the same resolution as the training images.
+These modules are described in detail in the package documentation.
 

### 2025-05-12 autovi_paper.tex
Provide brief desc for each module

@@
 
-The modules for VSS prediction and \(p\)-value computation are
-predefined and cannot be overridden, although users can interact with
-them directly through function arguments. Similarly, the image reading
-and resizing module is fixed but will adapt to different Keras models by
-checking their input shapes. The remaining seven modules are designed to
-be overridable, enabling users to tailor the infrastructure to their
-specific needs. These modules are discussed in detail in the package
-documentation.
+The package takes regression models and a \texttt{Keras} model as
+primary inputs. Modules for VSS prediction and \(p\)-value computation
+are fixed but accessible via function arguments, using
+\texttt{TensorFlow} for inference and statistical testing. The image
+loading module is also fixed, using \texttt{PIL} to read and resize
+images based on the \texttt{Keras} model's input shape. The remaining
+seven modules are overridable, allowing users to adapt the workflow as
+needed. The data extraction module extracts a \texttt{data.frame}
+containing variables used in the regression model. The bootstrapping and
+refitting module resamples the data and refits the model. The fitted
+values and residuals extraction module returns these values as a
+\texttt{data.frame}. The auxiliary computation module calculates
+scagnostics such as monotonicity. The plotting module generates a
+\texttt{ggplot} in a standard format, and the plot saving module exports
+it at the same resolution as the training images. These modules are
+described in detail in the package documentation.
 

### 2025-05-12 autovi_paper.qmd
Add one sentence to explain attention map
Refine the pkg extension part

@@
 The `autovi` R package can be extended to accommodate other classes of models beyond linear regression, such as generalized linear models (`glm`).
-This is achieved by substituting the relevant overridable modules, as illustrated in @fig-autovi-diag.
+This is achieved by substituting the relevant overridable modules, and if needed, supplying a different `Keras` model.
 
@@
 
-It is important to note, however, that the pre-trained computer vision model was developed specifically for diagnostic evaluation of linear regression.
+It is important to note, however, that the pre-trained computer vision model included in `autovi`, such as `vss_phn_32` (see `list_keras_models()` for the full list of available models), was developed specifically for diagnostics of linear regression.
 Its applicability to other model classes relies on the assumption that the null residual plots exhibit characteristics broadly consistent with those of well-behaved linear regression residuals, that is, residuals should be approximately randomly scattered around zero, display roughly constant variance across the range of fitted values, and exhibit no discernible structure or curvature.
 If these conditions are not met, or if model violations do not give rise to visually detectable patterns, the validity of the automated diagnostics may be compromised.
-For further discussion on extending the methodology to other model classes, refer to @li2024automated.
+In such cases, users are encouraged to train and apply their own `Keras` models.
+Detailed guidance on model training and discussion on extending the methodology to other model classes can be found in @li2024automated.
 
@@
 Finally, the grayscale attention map (right image) can be used to check if the target visual features, like the non-linearity present in the lineup example, are captured by the computer vision model, ensuring the quality of the assessment.
+The attention map is the gradient of the model output with respect to the grayscale image input, indicating the sensitivity of the output to each pixel.
 

### 2025-05-12 autovi_paper.tex
Add one sentence to explain attention map
Refine the pkg extension part

@@
 models (\texttt{glm}). This is achieved by substituting the relevant
-overridable modules, as illustrated in Figure~\ref{fig-autovi-diag}.
+overridable modules, and if needed, supplying a different \texttt{Keras}
+model.
 
@@
 It is important to note, however, that the pre-trained computer vision
-model was developed specifically for diagnostic evaluation of linear
-regression. Its applicability to other model classes relies on the
-assumption that the null residual plots exhibit characteristics broadly
-consistent with those of well-behaved linear regression residuals, that
-is, residuals should be approximately randomly scattered around zero,
-display roughly constant variance across the range of fitted values, and
-exhibit no discernible structure or curvature. If these conditions are
-not met, or if model violations do not give rise to visually detectable
-patterns, the validity of the automated diagnostics may be compromised.
-For further discussion on extending the methodology to other model
-classes, refer to \citet{li2024automated}.
+model included in \texttt{autovi}, such as \texttt{vss\_phn\_32} (see
+\texttt{list\_keras\_models()} for the full list of available models),
+was developed specifically for diagnostics of linear regression. Its
+applicability to other model classes relies on the assumption that the
+null residual plots exhibit characteristics broadly consistent with
+those of well-behaved linear regression residuals, that is, residuals
+should be approximately randomly scattered around zero, display roughly
+constant variance across the range of fitted values, and exhibit no
+discernible structure or curvature. If these conditions are not met, or
+if model violations do not give rise to visually detectable patterns,
+the validity of the automated diagnostics may be compromised. In such
+cases, users are encouraged to train and apply their own \texttt{Keras}
+models. Detailed guidance on model training and discussion on extending
+the methodology to other model classes can be found in
+\citet{li2024automated}.
 
@@
 are captured by the computer vision model, ensuring the quality of the
-assessment.
+assessment. The attention map is the gradient of the model output with
+respect to the grayscale image input, indicating the sensitivity of the
+output to each pixel.
 

### 2025-05-12 autovi_paper.qmd
Refine lengthy sentences

@@
 An accompanying Shiny app is provided for ease of use.
-Given a sample of residuals, the model predicts a visual signal strength (VSS) and offers supporting information to help analysts assess the adequacy of their model fit.
+Given a sample of residuals, the model predicts a visual signal strength (VSS) and offers supporting information to help analysts assess model fit.
 # Note that "keywords" should not include words and phrases
@@
 
-VSS is an estimate of the distance between the residual distribution of a fitted classical normal linear regression model and a reference distribution; more details can be found in @li2024automated.
+VSS estimates the distance between the residual distribution of a fitted classical normal linear regression model and a reference distribution [see @li2024automated, for details].
 The distance measure is based on the Kullback-Leibler (KL) divergence:
@@
 
-The third example is generated using the `surreal` package [@surreal] where structured residuals are hidden in data, to be revealed if the correct model is specified.
-Here a quote based on Tukey is used as the residual structure "visual summaries focus on unexpected values".
+The third example is generated using the `surreal` package [@surreal], where structure residuals are embedded in the data.
+In this case, a quote inspired by Tukey, "visual summaries focus on unexpected values", is used to define the residual structure.
 The automated plot reading predicts the VSS to be 5.87, with a $p$-value less than 0.05.
-This structure is blindingly obvious visually, but a RESET test for nonlinear structure would not report a problem.
+Visually, the structure is strikingly clear, but a RESET test for nonlinear structure would not report a problem.
 (It would be detected by a Breusch-Pagan for heteroscedasticity and also Shapiro-Wilk test [@shapiro1965analysis] for non-normality.)
@@
 
-Due to the resource allocation policy of shinyapps.io, the server enters a sleep mode during periods of inactivity, resulting in the clearing of the local Python virtual environment.
-Consequently, when the application "wakes up" for a new user session, these libraries need to be reinstalled.
+Due to shinyapps.io's resource policy, inactive servers enter sleep mode, clearing the local Python environment.
+When reactivated for a new session, libraries must be reinstalled.
 While this ensures a clean environment for each session, it may lead to slightly longer loading times for the first user after a period of inactivity.

### 2025-05-12 autovi_paper.tex
Refine lengthy sentences

@@
 Given a sample of residuals, the model predicts a visual signal strength
-(VSS) and offers supporting information to help analysts assess the
-adequacy of their model fit.
+(VSS) and offers supporting information to help analysts assess model
+fit.
 \end{abstract}
@@
 
-VSS is an estimate of the distance between the residual distribution of
-a fitted classical normal linear regression model and a reference
-distribution; more details can be found in \citet{li2024automated}. The
-distance measure is based on the Kullback-Leibler (KL) divergence:
+VSS estimates the distance between the residual distribution of a fitted
+classical normal linear regression model and a reference distribution
+\citep[see][for details]{li2024automated}. The distance measure is based
+on the Kullback-Leibler (KL) divergence:
 
@@
 The third example is generated using the \texttt{surreal} package
-\citep{surreal} where structured residuals are hidden in data, to be
-revealed if the correct model is specified. Here a quote based on Tukey
-is used as the residual structure ``visual summaries focus on unexpected
-values''. The automated plot reading predicts the VSS to be 5.87, with a
-\(p\)-value less than 0.05. This structure is blindingly obvious
-visually, but a RESET test for nonlinear structure would not report a
-problem. (It would be detected by a Breusch-Pagan for heteroscedasticity
-and also Shapiro-Wilk test \citep{shapiro1965analysis} for
-non-normality.)
+\citep{surreal}, where structure residuals are embedded in the data. In
+this case, a quote inspired by Tukey, ``visual summaries focus on
+unexpected values'', is used to define the residual structure. The
+automated plot reading predicts the VSS to be 5.87, with a \(p\)-value
+less than 0.05. Visually, the structure is strikingly clear, but a RESET
+test for nonlinear structure would not report a problem. (It would be
+detected by a Breusch-Pagan for heteroscedasticity and also Shapiro-Wilk
+test \citep{shapiro1965analysis} for non-normality.)
 
@@
 
-Due to the resource allocation policy of shinyapps.io, the server enters
-a sleep mode during periods of inactivity, resulting in the clearing of
-the local Python virtual environment. Consequently, when the application
-``wakes up'' for a new user session, these libraries need to be
-reinstalled. While this ensures a clean environment for each session, it
-may lead to slightly longer loading times for the first user after a
-period of inactivity.
+Due to shinyapps.io's resource policy, inactive servers enter sleep
+mode, clearing the local Python environment. When reactivated for a new
+session, libraries must be reinstalled. While this ensures a clean
+environment for each session, it may lead to slightly longer loading
+times for the first user after a period of inactivity.
 

### 2025-05-12 autovi_paper.qmd
update address and email

@@
   - name: Weihao Li
-    email: weihao.li@monash.edu
+    email: patrick.li@anu.edu.au
     corresponding: true
@@
         address: Wellington Road, VIC 3800, Australia
+      - name: The Australian National University
+        department: Biological Data Science Institute
+        address: 46 Sullivan's Creek Road, ACT 2600, Australia
     orcid: 0000-0003-4959-106X

### 2025-05-12 autovi_paper.tex
update address and email

@@
 \author{
-Weihao Li\addressnum{1},
+Weihao Li\addressnum{1, 2},
 Dianne Cook\addressnum{1},
@@
 Hall, 3310 Holdrege St Suite 340, Lincoln, NE 68583, United States\\
-\hspace*{1ex} Email: \texttt{weihao.li@monash.edu}    
+\hspace*{1ex} Email: \texttt{patrick.li@anu.edu.au}    
 }

### 2025-05-12 autovi_paper.qmd
Add fig caption for the lineup, make paper more compact

@@
 } else {
-  cli::cli_h3(readRDS("cached_data/autovi_checker_demo_print.rds"))
+  cat(readRDS("cached_data/autovi_checker_demo_print.rds"))
 }
@@
 
-```{r fig-plot-pair, echo = TRUE, fig.height=2, fig.width=3, out.width="60%", fig.cap="True plot alongside one null plot, for quick comparison."}
+```{r fig-plot-pair, echo = TRUE, fig.height=2, fig.width=3, out.width="45%", fig.cap="True plot alongside one null plot, for quick comparison."}
 checker$plot_pair()
@@
 For illustration, we fit a Poisson model in which the quadratic term of the predictor $x$ is intentionally omitted.
-This misspecification manifests as a pronounced U-shaped pattern in the lineup display, which is also successfully identified by the computer vision model, yielding a p-value substantially below the conventional threshold of 0.05.
-
-It is important to note, however, that the pre-trained computer vision model included in `autovi`, such as `vss_phn_32` (see `list_keras_models()` for the full list of available models), was developed specifically for diagnostics of linear regression.
-Its applicability to other model classes relies on the assumption that the null residual plots exhibit characteristics broadly consistent with those of well-behaved linear regression residuals, that is, residuals should be approximately randomly scattered around zero, display roughly constant variance across the range of fitted values, and exhibit no discernible structure or curvature.
-If these conditions are not met, or if model violations do not give rise to visually detectable patterns, the validity of the automated diagnostics may be compromised.
-In such cases, users are encouraged to train and apply their own `Keras` models.
-Detailed guidance on model training and discussion on extending the methodology to other model classes can be found in @li2024automated.
+This misspecification manifests as a pronounced U-shaped pattern in the lineup display (see @fig-pois-lineup), which is also successfully identified by the computer vision model, yielding a p-value substantially below the conventional threshold of 0.05.
 
@@
 
-```{r}
+```{r fig-pois-lineup, fig.cap="A lineup of residual plots from Poisson generalized linear models, with the true residual plot at position 4, which displays a distinct U-shaped pattern.
+In contrast, the null plots show characteristics broadly consistent with well-behaved residuals from linear regression models.", fig.pos="H", out.width="80%"}
 pois_checker$plot_lineup()
@@
 } else {
-  cli::cli_h3(readRDS("cached_data/autovi_glm_checker_demo_print.rds"))
+  cat(readRDS("cached_data/autovi_glm_checker_demo_print.rds"))
 }
 ```
+
+It is important to note, however, that the pre-trained computer vision model included in `autovi`, such as `vss_phn_32` (see `list_keras_models()` for the full list of available models), was developed specifically for diagnostics of linear regression.
+Its applicability to other model classes relies on the assumption that the null residual plots exhibit characteristics broadly consistent with those of well-behaved linear regression residuals, that is, residuals should be approximately randomly scattered around zero, display roughly constant variance across the range of fitted values, and exhibit no discernible structure or curvature.
+If these conditions are not met, or if model violations do not give rise to visually detectable patterns, the validity of the automated diagnostics may be compromised.
+In such cases, users are encouraged to train and apply their own `Keras` models.
+Detailed guidance on model training and discussion on extending the methodology to other model classes can be found in @li2024automated.
 

### 2025-05-12 autovi_paper.tex
Add fig caption for the lineup, make paper more compact

@@
 \begin{verbatim}
-\end{verbatim}
-
-\begin{verbatim}
--- <AUTO_VI object>
+<AUTO_VI object>
  Status:
@@
 
-\includegraphics[width=0.6\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-plot-pair-1.pdf}
+\includegraphics[width=0.45\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-plot-pair-1.pdf}
 
@@
 predictor \(x\) is intentionally omitted. This misspecification
-manifests as a pronounced U-shaped pattern in the lineup display, which
-is also successfully identified by the computer vision model, yielding a
-p-value substantially below the conventional threshold of 0.05.
-
-It is important to note, however, that the pre-trained computer vision
-model included in \texttt{autovi}, such as \texttt{vss\_phn\_32} (see
-\texttt{list\_keras\_models()} for the full list of available models),
-was developed specifically for diagnostics of linear regression. Its
-applicability to other model classes relies on the assumption that the
-null residual plots exhibit characteristics broadly consistent with
-those of well-behaved linear regression residuals, that is, residuals
-should be approximately randomly scattered around zero, display roughly
-constant variance across the range of fitted values, and exhibit no
-discernible structure or curvature. If these conditions are not met, or
-if model violations do not give rise to visually detectable patterns,
-the validity of the automated diagnostics may be compromised. In such
-cases, users are encouraged to train and apply their own \texttt{Keras}
-models. Detailed guidance on model training and discussion on extending
-the methodology to other model classes can be found in
-\citet{li2024automated}.
+manifests as a pronounced U-shaped pattern in the lineup display (see
+Figure~\ref{fig-pois-lineup}), which is also successfully identified by
+the computer vision model, yielding a p-value substantially below the
+conventional threshold of 0.05.
 
@@
 
-\begin{center}
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/unnamed-chunk-7-1.pdf}
-\end{center}
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics[width=0.8\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-pois-lineup-1.pdf}
+
+}
+
+\caption{\label{fig-pois-lineup}A lineup of residual plots from Poisson
+generalized linear models, with the true residual plot at position 4,
+which displays a distinct U-shaped pattern. In contrast, the null plots
+show characteristics broadly consistent with well-behaved residuals from
+linear regression models.}
+
+\end{figure}%
 
@@
 \begin{verbatim}
-\end{verbatim}
-
-\begin{verbatim}
--- <AUTO_POIS_VI object>
+<AUTO_POIS_VI object>
  Status:
@@
 
+It is important to note, however, that the pre-trained computer vision
+model included in \texttt{autovi}, such as \texttt{vss\_phn\_32} (see
+\texttt{list\_keras\_models()} for the full list of available models),
+was developed specifically for diagnostics of linear regression. Its
+applicability to other model classes relies on the assumption that the
+null residual plots exhibit characteristics broadly consistent with
+those of well-behaved linear regression residuals, that is, residuals
+should be approximately randomly scattered around zero, display roughly
+constant variance across the range of fitted values, and exhibit no
+discernible structure or curvature. If these conditions are not met, or
+if model violations do not give rise to visually detectable patterns,
+the validity of the automated diagnostics may be compromised. In such
+cases, users are encouraged to train and apply their own \texttt{Keras}
+models. Detailed guidance on model training and discussion on extending
+the methodology to other model classes can be found in
+\citet{li2024automated}.
+
 \section{Web interface: autovi.web}\label{sec-autovi-web}

### 2025-05-13 response_to_reviews.md
Upload cover letter and response to reviews

## Response to reviewers

We thank the reviewers for their reviews. We have adressed it as follows.

### Referee 1

> 1. The Abstract could be improved further. Certain sentences in the Abstract contain grammatical errors and are hard to read.

We have revised the abstract to improve its clarity and readability. The new version is as follows.

> Visual assessment of residual plots is a common approach for diagnosing linear models, but it relies on manual evaluation, which does not scale well and can lead to inconsistent decisions across analysts. The lineup protocol, which embeds the observed plot among null plots, can reduce subjectivity but requires even more human effort. In today’s data-driven world, such tasks are well-suited for automation. We present a new R package that uses a computer vision model to automate the evaluation of residual plots. An accompanying Shiny app is provided for ease of use. Given a sample of residuals, the model predicts a visual signal strength (VSS) and offers supporting information to help analysts assess the adequacy of their model fit.

> 2. The "autovi.web" RShiny app (e.g., https://akdd4t-patrick-li.shinyapps.io/autovi_web/) lacks clear instructions regarding the format of CSV files it accepts. As a result, some users may upload the original dataset instead of a two-column CSV file with fitted values and residuals.

We have updated the app to include clearer instructions on the required input format.

> 3. One suggestion is to consider integrating the widely-used regression model fitting functions (e.g., lm(), aov() or glm ()) into "autovi" to automate the model fitting and assessment of residuals.

Thank you for the suggestion. We agree that this is a valuable direction for future development. However, it lies beyond the scope of the current manuscript. We have added a new Section 4.6 that discusses how the workflow could be extended to accommodate broader model classes.

> 4. Finally, please check the English in the manuscript. Certain lengthy sentences can be hard to understand.

We have revised the manuscript to improve clarity and gammar. Notable changes include:

- Section 2 
    - Original: "VSS is an estimate of the distance between the residual distribution of a fitted classical normal linear regression model and a reference distribution; more details can be found in Li et al. 2024b."
    - Revised: "VSS estiates the distance between the residual distribution of a fitted classical normal linear regression model and a reference distribution (see Li et al. 2024b, for65details)."

- Section 5.1 
    - Original: "Due to the resource allocation policy of shinyapps.io, the server enters a sleep mode during periods of inactivity, resulting in the clearing of the local Python virtual environment. Consequently, when the application "wakes up" for a new user session, these libraries need to be reinstalled."
    - Revised: "Due to shinyapps.io's resource policy, inactive servers enter sleep mode, clearing the local Python environment. When reactivated for a new session, libraries must be reinstalled."

- Section 4.1 
    - Original: "The third example is generated using the `surreal` package (Balamuta 2024) where structured residuals are hidden in data, to be revealed if the correct model is specified. Here a quote based on Tukey is used as the residual structure 'visual summaries focus on unexpected values'."
    - Revised: "The third example is generated using the `surreal` package (Balamuta 2024), where structure residuals are embedded in the data. In this case, a quote inspired by Tukey 'visual summaries focus on unexpected values', is used to define the residual structure."

- Section 4.1 
    - Original: "This structure is blindingly obvious visually,"
    - Revised: "Visually, the structure is strikingly clear,"

### Referee 2

> - some introduction on generating the null plot and bootstrap residual, which provides some background to understand the code summary in page 7 and Figure 3 on the comparison between VSS from the two scenarios.

We have added a new Section 3 to introduce the definitions and generation procedures for null plots and bootstrapped residuals, providing necessary context for Figure 3.

> - information on the type/ scope of regression models used to train the cv model in Section 2 to understand the applicability of the cv model.

We have expanded the final paragraph of Section 2 to describe the types of regression models used for training. This provides better insight into the model’s scope and applicability.

> - a brief description of each module in Figure 4, for example, what does auxiliary computation (in Figure 4) include?

We have extended the last paragraph of Section 4.5 to include brief descriptions of each module in Figure 4, including the tasks performed under "auxiliary computation".

> - the necessary changes need to make to extend the workflow to diagnose other models e.g. GLM, in Section 3.5.

This will require training and testing the computer vision model across a broader range of models, including those with different types of assumption departures. Future research could build on our prototype to support this broader class. In the meantime, we have added Section 4.6 to illustrate how the workflow could potentially be extended to other model types.

> - the term "attention map" used in line 331 and Figure 7 caption is not introduced in the paper.

We have added a definition for "attention map" as follows:

> The attention map is the gradient of the model output with respect to the grayscale image input, indicating the sensitivity of the output to each pixel.

> - The authors may consider moving Section 3.5 earlier in Section 3 to provide an overview of the package.

Thank you for the suggestion. We considered this structure but chose to prioritize a streamlined usage summary early in the manuscript, based on the assumption that many readers will be primarily interested in applying the tool.

> - The infrastructure is built on the bandicoot OOP system, could the authors comment on this choice compared to the latest S7?

The `bandicoot` system is a custom object-oriented system tailored for our development needs, in a similar spirit to how `ggproto` is used within `ggplot2`. A detailed comparison with newer systems like `S7` is beyond the scope of this paper.

> - The word "be" in line 60 is redundunt in the sentence.

Thank you. This has been corrected.

### 2025-05-13 response_to_reviews.md
added bandicoot library call and fixed spelling in response

@@
 
-We thank the reviewers for their reviews. We have adressed it as follows.
+We thank the reviewers for their reviews. We have addressed it as follows.
 
@@
 
-We have revised the manuscript to improve clarity and gammar. Notable changes include:
+We have revised the manuscript to improve clarity and grammar. Notable changes include:
 
@@
 2024b."
-    - Revised: "VSS estiates the distance between the residual distribution of a fitted classical normal linear regression model and a reference distribution (see Li et al. 2024b, for65details)."
+    - Revised: "VSS estimates the distance between the residual distribution of a fitted classical normal linear regression model and a reference distribution (see Li et al. 2024b, for65details)."
 
@@
 
-> - The word "be" in line 60 is redundunt in the sentence.
+> - The word "be" in line 60 is redundant in the sentence.
 

### 2025-05-13 autovi_paper.qmd
added bandicoot library call and fixed spelling in response

@@
 library(ggthemes)
+library(bandicoot)
 

### 2025-05-13 autovi_paper.tex
added bandicoot library call and fixed spelling in response

@@
+% Options for packages loaded elsewhere
 % Options for packages loaded elsewhere
@@
   times]{anzsauth}
-
+\usepackage{xcolor}
 \usepackage{amsmath,amssymb}
+\setcounter{secnumdepth}{5}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
@@
 \makeatother
-\usepackage{xcolor}
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{5}
 % Make \paragraph and \subparagraph free-standing
@@
 
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+\usepackage{longtable,booktabs,array}
 \usepackage{calc} % for calculating minipage widths
@@
 \makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\newsavebox\pandoc@box
+\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
+  \sbox\pandoc@box{#1}%
+  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
+  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
+  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
+  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
+  \else\usebox{\pandoc@box}%
+  \fi%
+}
 % Set default figure placement to htbp
-\makeatletter
 \def\fps@figure{htbp}
 \makeatother
+
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+\usepackage[]{natbib}
+\bibliographystyle{anzsj}
 
@@
 \makeatother
-
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\usepackage[]{natbib}
-\bibliographystyle{anzsj}
 \usepackage{bookmark}
-
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 
-\includegraphics[width=0.45\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-plot-pair-1.pdf}
+\includegraphics[width=0.45\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-plot-pair-1.pdf}
 
@@
 
-\includegraphics[width=0.8\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-pois-lineup-1.pdf}
+\includegraphics[width=0.8\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-pois-lineup-1.pdf}
 

### 2025-05-14 autovi_paper_submission1.qmd
original submission and the diff

--- 2025-05-12 autovi_paper.qmd
@@
   - name: Weihao Li
-    email: patrick.li@anu.edu.au
+    email: weihao.li@monash.edu
     corresponding: true
@@
         address: Wellington Road, VIC 3800, Australia
-      - name: The Australian National University
-        department: Biological Data Science Institute
-        address: 46 Sullivan's Creek Road, ACT 2600, Australia
     orcid: 0000-0003-4959-106X
@@
 abstract: |
-  Visual assessment of residual plots is a common approach for diagnosing linear models, but it relies on manual evaluation, which does not scale well and can lead to inconsistent decisions across analysts.
-The lineup protocol, which embeds the observed plot among null plots, can reduce subjectivity but requires even more human effort.
-In today’s data-driven world, such tasks are well-suited for automation.
-We present a new R package that uses a computer vision model to automate the evaluation of residual plots.
-An accompanying Shiny app is provided for ease of use.
-Given a sample of residuals, the model predicts a visual signal strength (VSS) and offers supporting information to help analysts assess model fit.
+  Visually assessing residual plots is a common advice for linear model diagnostics, however this approach requires manual human evaluation and thereby is not scalable for assessing many models.
+Human evaluation also has the potential to produce inconsistent decisions from different analysts.
+Using a lineup protocol, where the residual plot is embedded among null plots, can help to alleviate inconsistency, but requires even more human effort.
+This is the type of task that in today's world we might employ a robot to do the tedious work for a human.
+Here we describe a new R package that includes a computer vision model for automated assessment of residual plots, and an accompanying Shiny app for ease of use.
+For a user-provided sample of residuals, it predicts a measure of visual signal strength (VSS) and provides a suite of supporting information to assist the analyst decide on the appropriateness their model fit.
 # Note that "keywords" should not include words and phrases
@@
 There is a vast array of software for conducting regression modeling and generating diagnostics.
-The package `lmtest` [@lmtest] provides a suite of conventional tests, while the `stats` package [@stats] offers standard diagnostic plots such as residuals vs.
+The package `lmtest` [@lmtest] provides a suite of conventional tests.
+The `stats` package [@stats] offers standard diagnostic plots such as residuals vs.
 fitted values, quantile-quantile (Q-Q) plots, and residuals vs.
 leverage plots.
-Additional packages like `jtools` [@jtools], `olsrr` [@olsrr], `rockchalk` [@rockchalk], and `ggResidpanel` [@ggresidpanel] deliver similar graphical diagnostics, often with enhanced aesthetics or interactive features.
-These tools collectively produce the core diagnostic plots outlined in the classical text by @cook1982residuals.
-The `ecostats` package [@warton_global_2023] extends these diagnostics by incorporating simulation envelopes into residual plots.
-Meanwhile, `DHARMa` [@dharma] compares empirical quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical counterparts, with a strong focus on identifying model violations such as heteroscedasticity, misspecified functional forms, and issues specific to generalized linear and mixed-effect models, like over/under-dispersion.
-It also provides conventional test annotations to reduce the risk of misinterpretation.
+Packages like `jtools` [@jtools], `olsrr` [@olsrr], `rockchalk` [@rockchalk], and `ggResidpanel` [@ggresidpanel] provide similar graphical diagnostics, often with alternative aesthetics or interactive features.
+All of these tools deliver the types of diagnostic plots outlined in the classical text by @cook1982residuals.
+The `ecostats` package [@warton_global_2023] incorporates simulation envelopes into residual plots, while `DHARMa` [@dharma] compares empirical quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical counterparts.
+`DHARMa` is particularly focused on detecting model violations such as heteroscedasticity, incorrect functional forms, and issues specific to generalized linear and mixed-effect models, like over/under-dispersion.
+It also includes conventional test annotations to help avoid misinterpretation.
+
+<!-- However, as discussed in @li2024plot, relying solely on subjective assessments of these plots can lead to issues, such as over-interpreting random patterns as model violations. -->
+
+<!-- To diagnose the fit of a model it is recommended that the residuals are plotted.
+If the fit is good, any variation remaining should be noise, consistent with sampling from a distribution specified by the error model.
+Deviations that might be observed from a residual plot are non-normality, heteroscedasticity, and other associations with the fitted values.-->
 
 However, relying solely on subjective assessments of these plots can lead to issues such as over-interpreting random patterns as model violations.
-@li2024plot demonstrated that visual inference methods, particularly those using the lineup protocol [@buja2009statistical], offer more practical and reliable assessments of residual patterns than conventional tests, as they are less sensitive to minor departures.
-Packages such as `nullabor` [@nullabor], `HLMdiag` [@loy2014hlmdiag], and `regressinator` [@regressinator] support this approach by enabling users to compare observed residual plots with plots generated under null hypothesis, thereby helping to quantify the significance of any detected patterns.
-
-As noted in @li2024automated, the lineup protocol has significant limitations in large-scale applications due to its reliance on human labor.
-To overcome this constraint, a computer vision model was developed alongside a corresponding statistical testing procedure to autmoate the assessment of residual plots.
-The model takes as input a residual plot and a set of auxiliary variables (such as the number of observations) and outputs a predicted visual signal strength (VSS).
-This VSS estimates the degree of deviation between the residual distribution of the fitted model and the reference distribution expected under correct model specification.
-
-To make the statistical testing procedure and trained computer vision model widely accessible, we developed the R package `autovi` along with a companion web interface, `autovi.web`, which allows users to automatically assess their residual plots using the trained computer vision model.
-
-The remainder of this paper is structured as follows: @sec-vss-desc introduces the definition and computation of visual signal strength.
-@sec-autovi provides a detailed documentation of the `autovi` package, including its usage and infrastructure.
+@li2024plot demonstrated that visual methods using the lineup protocol [@buja2009statistical] for assessing residuals are more useful, and also perform more practically than conventional tests due to their reduced sensitivity to minor departures.
+Packages such as `nullabor` [@nullabor], `HLMdiag` [@loy2014hlmdiag], and `regressinator` [@regressinator], enable users to compare observed residual plots with plots of samples from null distributions, helping to quantify the significance of any detected patterns.
+
+However, as discussed in @li2024automated, the lineup protocol has significant limitations in large-scale applications due to dependence on human labor.
+Thus, a computer vision model was developed with an associated statistical testing procedure to automate the assessment of residual plots.
+This model takes a residual plot and a vector of auxiliary variables (such as the number of observations) as inputs and outputs the predicted visual signal strength (VSS).
+This strength estimates the distance between the residual distribution of the fitted regression model and the reference distribution assumed under correct model specification.
+
+<!--Software for regression analysis tools is widely available.
+The Comprehensive R Archive Network (CRAN) [@hornik2012comprehensive] hosts a vast array of packages, many of which provide tools to diagnose models using residual plots.
+These packages can be broadly categorized into three groups: general-purpose, enhanced visual diagnostics, and visual diagnostics with statistical testing.-->
+
+<!--General-purpose regression analysis tools are the most widely used group of packages.
+While not specifically designed for graphical diagnostics of residuals in linear regression, they include this functionality as part of a broader suite of statistical tools.
+For example, the `stats` package [@stats] offers standard diagnostic plots such as residuals vs.
+fitted values, quantile-quantile (Q-Q) plots, and residuals vs.
+leverage plots.
+Additional packages like `jtools` [@jtools], `olsrr` [@olsrr], `rockchalk` [@rockchalk], and `ggResidpanel` [@ggresidpanel] provide similar graphical diagnostics, often with alternative aesthetics or interactive features.
+All of these tools deliver the types of diagnostic plots outlined in the classical text by @cook1982residuals.
+However, as discussed in @li2024plot, relying solely on subjective assessments of these plots can lead to issues, such as over-interpreting random patterns as model violations.-->
+
+<!-- The second group consists of enhanced visual diagnostics tools, which provide advanced aids for interpreting diagnostic plots.
+For instance, `ecostats` [@warton_global_2023] incorporates simulation envelopes into residual plots, while `DHARMa` [@dharma] compares empirical quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical counterparts.
+`DHARMa` is particularly focused on detecting model violations such as heteroscedasticity, incorrect functional forms, and issues specific to generalized linear and mixed-effect models, like over/under-dispersion.
+It also includes annotations from conventional tests, displayed as labels or text within the plot, to help avoid misinterpretation.-->
+
+<!-- The third group, visual diagnostics with statistical testing, offers tools for formally testing patterns observed in diagnostic plots [@buja2009statistical].
+A common method for visual testing of residual plots is the lineup protocol, where the true residual plot is embedded within a set of null plots generated by simulating residuals under the null hypothesis $H_0$ that the regression model is correctly specified.
+Observers are asked to identify the plot that appears most different from the others.
+If a significant proportion of observers correctly identify the true residual plot, it provides evidence against $H_0$, as the true residual plot should be indistinguishable from the null plots if all residuals are generated by the same process, according to @buja2009statistical.
+Packages in this group, such as `nullabor` [@nullabor], `HLMdiag` [@loy2014hlmdiag], and `regressinator` [@regressinator], enable users to compare observed residual plots with samples from null distributions, helping to quantify the significance of any detected patterns.
+-->
+
+<!-- However, as discussed in @li2024automated, the lineup protocol has significant limitations in large-scale applications due dependence on human labor.
+Thus a computer vision model was developed with an associated statistical testing procedure to automate the assessment of residual plots.
+This model takes a residual plot and a vector of auxiliary variables (such as the number of observations) as inputs and outputs the predicted visual signal strength (VSS).
+This strength estimates the distance between the residual distribution of the fitted regression model and the reference distribution assumed under correct model specification.-->
+
+To make the statistical testing procedure and trained computer vision model widely accessible, we developed the R package `autovi`, and a web interface, `autovi.web` to make it easy for users to automatically read their residual plots with the trained computer vision model.
+
+The remainder of this paper is structured as follows: @sec-autovi provides a detailed documentation of the `autovi` package, including its usage and infrastructure.
 @sec-autovi-web focuses on the `autovi.web` interface, describing its design and usage, along with illustrative examples.
@@
 
-To train a computer vision model, a measure of the visible pattern in a plot is needed.
-We call this the **visual signal strength** (VSS), which measures how prominently a specific set of visual patterns appears in an image.
+To train a computer vision model a measure of the visible pattern in a plot is needed.
+We call this the **visual signal strength** (VSS) measuring how prominently a specific set of visual patterns appears in an image.
 This can be computed for a training set of data, and plots, where the generating distributions are specified.
 
-In the context of regression model diagnostics, VSS describes the clarity of visual patterns on a diagnostic plot that may indicate model violations.
-Violations can be categorized as weak, moderate, or strong, but here we treat it as a continuous positive real variable.
+In the context of regression model diagnostics, it describes the clarity of visual patterns on a diagnostic plot that may indicate model violations.
+This concept can be categorized as weak, moderate, or strong.
+However, in our study, we treat it as a continuous positive real variable.
 Importantly, its interpretation depends on how it is linked to a function of the data or the underlying data generating process.
-Consequently, the calculation of VSS can vary across different model classes or within the same model, depending on the generating function.
-
-VSS estimates the distance between the residual distribution of a fitted classical normal linear regression model and a reference distribution [see @li2024automated, for details].
-The distance measure is based on the Kullback-Leibler (KL) divergence:
+Consequently, the calculation of VSS can be vary across different model classes or within the same model, depending on the generating function.
+
+VSS is defined as an estimate of a distance measure that quantifies the disparity between the residual distribution of a fitted classical normal linear regression model and a reference distribution, and more details can be found in @li2024automated.
+This measure is based on the Kullback-Leibler (KL) divergence:
 
@@
 
-\begin{equation} \label{eq:kl-1}
+\begin{equation*} \label{eq:kl-1}
 D_{KL} = \int_{\mathbb{R}^{n}}\log\frac{p(\boldsymbol{e})}{q(\boldsymbol{e})}p(\boldsymbol{e})d\boldsymbol{e},
-\end{equation}
+\end{equation*}
 
@@
 
-This distance measure depends on knowledge of the true residual distribution, which is unknown in practice.
-To compute $D_{KL}$ for the training samples, Equation \ref{eq:kl-1} takes different forms depending on the specific model violations.
-For instance, where necessary higher-order predictors, $\boldsymbol{Z}$, and their corresponding parameter, $\boldsymbol{\beta}_Z$, are omitted from the fitted linear model, the distance measure can be expanded as follows:
-
-\begin{equation*} \label{eq:kl-2}
-D_{KL} = \frac{1}{2}\left(\boldsymbol{\mu}_z^\top(\text{diag}(\boldsymbol{R}\sigma^2))^{-1}\boldsymbol{\mu}_z\right),
-\end{equation*}
-
-where $\boldsymbol{\mu}_z = \boldsymbol{R}\boldsymbol{Z}\boldsymbol{\beta}_z$, $\boldsymbol{R} = \boldsymbol{I}_n - \boldsymbol{X}(\boldsymbol{X}^\top\boldsymbol{X})^{-1}\boldsymbol{X}^\top$ and $\boldsymbol{X}$ is the design matrix of the regression model.
-
-The computer vision model approximates this mapping from a set of residuals to its corresponding distance measure.
-It is trained on a large number of synthetic regression models, each designed to simulate specific violations of classical linear regression assumptions.
-These models incorporate non-linearity through Hermite polynomial transformations of predictors, heteroskedasticity by making the error variance a predictor-dependent function, and non-normality by drawing residuals from distributions such as discrete, uniform, and lognormal.
-Both simple and multiple linear regression structures are used, with controlled parameters to generate diverse and complex residual patterns.
-Since the data-generating process is known, the distance measure $D$ can be explicitly calculated, enabling supervised training.
-The computer vision model takes a residual plot as input and outputs the corresponding distance measure, learning to quantify model violations directly from visual patterns.
-Additional details are provided in @li2024automated.
-
-# Definition and simulation of null and bootstrapped residuals {#sec-null-and-boot-desc}
-
-In the subsequent sections, we will frequently refer to null residuals and bootstrapped residuals, so it is helpful to first define and explain how they are generated.
-
-**Null residuals** are used to generate null plots within the lineup protocol framework, serving as the foundation for the statistical testing in our automated residual plot assessment.
-Specifically, they represent residuals generated under the null hypothesis that the model is correctly specified.
-A common method for simulating null residuals in linear regression involves sampling from a normal distribution with mean zero and variance equal to the estimated variance of the error term.
-These simulated residuals and their corresponding plots depict what one would expect from a correctly specified model.
-If the true residual plot exhibits noticeable deviations from these null plots, it may suggest model misspecification.
-
-Our computer vision model is trained to assign lower VSS to null plots and higher VSS to plots that display distinct patterns.
-Accordingly, statistical testing is performed by computing the proportion of null plots whose VSS equals or exceeds that of the observed residual plot.
-This proportion serves as a p-value for a one-sided hypothesis test.
-
-**Bootstrapped residuals** are obtained by refitting the model on bootstrap samples, which are generated by sampling individual observations with replacement from the original dataset.
-The residual plots obtained from these refitted models are evaluated using the same computer vision model.
-The predicted VSS from the bootstrapped plots provide an empirical estimate of the variation in the VSS of the observed residual plot.
-By examining the proportion of bootstrapped plots that also exhibit significant violations, we can assess whether the original conclusion is robust to sampling variability.
+This distance measure requires knowledge of the true residual distribution, which is typically unknown.
+Therefore, a computer vision model was used for estimating the residual distribution [see @li2024automated for more details].
 
@@
 The name `autovi` stands for **auto**mated **v**isual **i**nference.
-This functionality can be accessed through the R package `autovi`, or through a web interface, `autovi.web`, which enables users to perform analyses without installing R, Python, or their associated dependencies locally.
-
-## Motivation {#sec-why}
+<!--While initially designed for linear regression residual diagnostics, it has the potential to be extended to broader visual inference applications, as we discuss in section @sec-autovi-infrastructure.-->
+
+There are two ways to access the package, directly using R or through a web interface, `autovi.web`.
+The web interface has the advantage that it can be used without installing Python, R and the relevant packages locally.
+
+## Motivation for usage {#sec-why}
 
@@
 
-The third example is generated using the `surreal` package [@surreal], where structure residuals are embedded in the data.
-In this case, a quote inspired by Tukey, "visual summaries focus on unexpected values", is used to define the residual structure.
+The third example is generated using the `surreal` package [@surreal] where structured residuals are hidden in data, to be revealed if the correct model is specified.
+Here a quote based on Tukey is used as the residual structure "visual summaries focus on unexpected values".
 The automated plot reading predicts the VSS to be 5.87, with a $p$-value less than 0.05.
-Visually, the structure is strikingly clear, but a RESET test for nonlinear structure would not report a problem.
+This structure is blindingly obvious visually, but a RESET test for nonlinear structure would not report a problem.
 (It would be detected by a Breusch-Pagan for heteroscedasticity and also Shapiro-Wilk test [@shapiro1965analysis] for non-normality.)
@@
 This OOP architecture enhances flexibility and modularity, allowing users to redefine key functions through method overriding.
+While similar functionality could be achieved using R’s S3 system with generic functions, the OOP framework offers a more structured and extensible foundation for the package.
 
@@
 In Python, `pillow` [@clark2015pillow] handles image processing tasks such as reading and resizing PNG files of residual plots, then converting them into input tensors for further analysis.
-`TensorFlow` [@abadi2016tensorflow], a key component of modern machine learning, is used to predict the VSS of these plots using a pre-trained convolutional neural network.
+The `TensorFlow` [@abadi2016tensorflow] library, a key component of modern machine learning, is used to predict the VSS of these plots through a pre-trained convolutional neural network.
 
@@
 `ggplot2` [@ggplot2] generates the initial residual plots, saved as PNG files for visual input.
-`cassowaryr` [@mason2022cassowaryr] computes scagnostics (scatter plot diagnostics), providing numerical features that capture statistical properties of the plots.
+The `cassowaryr` [@mason2022cassowaryr] library computes scagnostics (scatter plot diagnostics), providing numerical features that capture statistical properties of the plots.
 These scagnostics complement the visual analysis by offering quantitative metrics as secondary input to the computer vision model.
-`reticulate` [@reticulate]  enables seamless communication between R and Python.
+The `reticulate` [@reticulate] package bridges R and Python, enabling seamless communication between the two languages and supporting the integrated infrastructure.
 
@@
 
-The `autovi` package is available on CRAN. It is actively developed and maintained, with the latest updates accessible on GitHub. This paper uses `autovi` version 0.4.2.
+The `autovi` package is available on CRAN. It is actively developed and maintained, with the latest updates accessible on GitHub. The code discussed in this paper is based on `autovi` version 0.4.1.
+
 The package includes internal functions to check the current Python environment used by the `reticulate` package.
@@
 3.
-Call the `check()` method of the checker, which, by default, predicts the VSS for the true residual plot, 100 null plots, and 100 bootstrapped plots.
-The method stores the predictions internally and prints a concise results report.
+Call the `check()` method of the checker, which, by default, predicts the VSS for the true residual plot, 100 null plots, and 100 bootstrapped plots, storing the predictions internally.
+A concise report of the check results is then printed.
 
@@
 ```{r message=TRUE}
-if (!file.exists("cached_data/autovi_checker_demo_print.rds")) {
-  checker$keras_model <- get_keras_model("vss_phn_32") 
-  checker$check()
-  saveRDS(checker$..str..(), "cached_data/autovi_checker_demo_print.rds")
-} else {
-  cli::cli_h3(readRDS("cached_data/autovi_checker_demo_print.rds"))
-}
-```
-
-```{r}
 if (!file.exists("cached_data/autovi_check_demo.rds")) {
@@
 }
+
+checker
 ```
@@
 The $p$-value is the proportion of null plots (out of the total 100) that have VSS greater than or equal to that of the true residual plot.
-The report also provides sample quantiles of VSS for null samples and bootstrapped data plots, providing more information about the sampling variability and a likelihood of model violations.
+<!--We typically reject the null hypothesis when the $p$-value is smaller than or equal to a desired significance level, such as 5%.--> The report also provides sample quantiles of VSS for null samples and bootstrapped data plots, providing more information about the sampling variability and a likelihood of model violations.
 The likelihood is computed from the proportion of values greater than the observed VSS in both the bootstrapped data values and the simulated null values.
@@
 
-The package takes regression models and a `Keras` model as primary inputs.
-Modules for VSS prediction and $p$-value computation are fixed but accessible via function arguments, using `TensorFlow` for inference and statistical testing.
-The image loading module is also fixed, using `PIL` to read and resize images based on the `Keras` model’s input shape.
-The remaining seven modules are overridable, allowing users to adapt the workflow as needed.
-The data extraction module extracts a `data.frame` containing variables used in the regression model.
-The bootstrapping and refitting module resamples the data and refits the model.
-The fitted values and residuals extraction module returns these values as a `data.frame`.
-The auxiliary computation module calculates scagnostics such as monotonicity.
-The plotting module generates a `ggplot` in a standard format, and the plot saving module exports it at the same resolution as the training images.
-These modules are described in detail in the package documentation.
-
-## Extension to Other Model Classes
-
-The `autovi` R package can be extended to accommodate other classes of models beyond linear regression, such as generalized linear models (`glm`).
-This is achieved by substituting the relevant overridable modules, and if needed, supplying a different `Keras` model.
-
-We provide an example of defining a new checker class tailored for Poisson regression using the `glm` framework:
-
-1. Define a new class using `new_class()` with `AUTO_VI` as the parent class.
-2.
-Override the necessary methods using `register_method()`.
-In this example, we use Pearson residuals.
-To simulate null residuals, we assume the fitted model is correct and the estimated coefficients are accurate.
-New response values are generated accordingly, and a new model is fitted to this simulated response.
-Null residuals are then extracted from this refitted model.
-3. Create an alias for the `instantiate()` method of the new class.
-
-```{r echo = TRUE}
-AUTO_POIS_VI <- new_class(AUTO_VI, class_name = "AUTO_POIS_VI")
-register_method(
-  AUTO_POIS_VI,
-  get_fitted_and_resid = function(fitted_model = self$fitted_model) {
-    tibble(.fitted = fitted(fitted_model),
-           .resid = resid(fitted_model, type = "pearson"))
-  },
-  null_method = function(fitted_model = self$fitted_model) {
-    dat <- model.frame(fitted_model)
-    dat[[1]] <- rpois(nrow(dat), lambda = fitted(fitted_model))
-    new_mod <- update(fitted_model, data = dat)
-    return(self$get_fitted_and_resid(new_mod))
-  }
-)
-auto_pois_vi <- AUTO_POIS_VI$instantiate
-```
-
-The resulting checker class can be employed analogously to the linear model case described in @sec-autovi-usage.
-For illustration, we fit a Poisson model in which the quadratic term of the predictor $x$ is intentionally omitted.
-This misspecification manifests as a pronounced U-shaped pattern in the lineup display, which is also successfully identified by the computer vision model, yielding a p-value substantially below the conventional threshold of 0.05.
-
-It is important to note, however, that the pre-trained computer vision model included in `autovi`, such as `vss_phn_32` (see `list_keras_models()` for the full list of available models), was developed specifically for diagnostics of linear regression.
-Its applicability to other model classes relies on the assumption that the null residual plots exhibit characteristics broadly consistent with those of well-behaved linear regression residuals, that is, residuals should be approximately randomly scattered around zero, display roughly constant variance across the range of fitted values, and exhibit no discernible structure or curvature.
-If these conditions are not met, or if model violations do not give rise to visually detectable patterns, the validity of the automated diagnostics may be compromised.
-In such cases, users are encouraged to train and apply their own `Keras` models.
-Detailed guidance on model training and discussion on extending the methodology to other model classes can be found in @li2024automated.
-
-```r
-x <- rnorm(300, sd = 0.5)
-y <- rpois(300, lambda = exp(1 + x + x^2))
-pois_checker <- auto_pois_vi(
-  glm(y ~ x, family = "poisson"),
-  keras_model = get_keras_model("vss_phn_32")
-)
-pois_checker$plot_lineup()
-```
-
-```{r include = FALSE}
-set.seed(10086)
-x <- rnorm(300, sd = 0.5)
-y <- rpois(300, lambda = exp(1 + x + x^2))
-pois_checker <- auto_pois_vi(glm(y ~ x, family = "poisson"))
-```
-
-```{r}
-pois_checker$plot_lineup()
-```
-
-```r
-pois_checker$check()
-```
-
-```{r message = TRUE}
-if (!file.exists("cached_data/autovi_glm_checker_demo_print.rds")) {
-  pois_checker <- auto_pois_vi(glm(y ~ x, family = "poisson"),
-                               keras_model = get_keras_model("vss_phn_32"))
-  pois_checker$check()
-  saveRDS(pois_checker$..str..(), "cached_data/autovi_glm_checker_demo_print.rds")
-} else {
-  cli::cli_h3(readRDS("cached_data/autovi_glm_checker_demo_print.rds"))
-}
-```
-
+The modules for VSS prediction and $p$-value computation are predefined and cannot be overridden, although users can interact with them directly through function arguments.
+Similarly, the image reading and resizing module is fixed but will adapt to different Keras models by checking their input shapes.
+The remaining seven modules are designed to be overridable, enabling users to tailor the infrastructure to their specific needs.
+These modules are discussed in detail on the software's website.
 <!-- in the following sections.-->
@@
 In our initial planning for `autovi.web`, we considered implementing the entire web application using the `webr` framework [@webr], which would have allowed the entire application to run directly in the user's browser.
-However, `webr` does not support packages which use compiled fortran code, which is required by `splancs` [@splancs], a dependency of `autovi`.
-In the future, it is possible that a working Emscripten [@zakai2011emscripten] version of this package may allow full `webr` support.
+However, this approach was not feasible at the time of writing this paper.
+The reason is that one of the R packages `autovi` depends on the R package `splancs` [@splancs], which uses compiled Fortran code.
+A working Emscripten [@zakai2011emscripten] version of this package, which would be required for `webr`, was not available.
 
@@
 Another option we considered was renting a server where we could have full control, such as those provided by cloud platforms like Google Cloud Platform (GCP) or Amazon Web Services (AWS).
-However, deploying and maintaining the server securely requires some expertise.
+However, correctly setting up the server and ensuring a secure deployment requires significant expertise.
 Ultimately, the most practical solution was to use the `shiny` and `shinydashboard` frameworks, which are well-established in the R community and offer a solid foundation for web application development.
@@
 
-Due to shinyapps.io's resource policy, inactive servers enter sleep mode, clearing the local Python environment.
-When reactivated for a new session, libraries must be reinstalled.
+Due to the resource allocation policy of shinyapps.io, the server enters a sleep mode during periods of inactivity, resulting in the clearing of the local Python virtual environment.
+Consequently, when the application "wakes up" for a new user session, these libraries need to be reinstalled.
 While this ensures a clean environment for each session, it may lead to slightly longer loading times for the first user after a period of inactivity.
 
-In contrast to `autovi`, `autovi.web` leverages `TensorFlow.js`, a JavaScript library that allows the execution of machine learning models directly in the browser.
+In contrast to `autovi`, `autovi.web` does not use the native Python version of `TensorFlow`.
+Instead, it leverages `TensorFlow.js`, a JavaScript library that allows the execution of machine learning models directly in the browser.
 This choice enables native browser execution, enhancing compatibility across different user environments, and shifts the computational load from the server to the client-side.
@@
 Finally, the grayscale attention map (right image) can be used to check if the target visual features, like the non-linearity present in the lineup example, are captured by the computer vision model, ensuring the quality of the assessment.
-The attention map is the gradient of the model output with respect to the grayscale image input, indicating the sensitivity of the output to each pixel.
 
@@
 
-The `autovi` R package, introduced in this paper, automates the assessment of residual plots by incorporating a computer vision model, reducing reliance on time-consuming and potentially inconsistent human interpretation.
+The `autovi` R package, introduced in this paper, automates the assessment of residual plots by incorporating a computer vision model, eliminating the need for time-consuming and potentially inconsistent human interpretation.
 This automation improves the efficiency of the diagnostic process and promotes consistency in model evaluation across different users and studies.

### 2025-05-14 autovi_paper_submission1.tex
original submission and the diff

--- 2025-05-13 autovi_paper.tex
@@
-% Options for packages loaded elsewhere
 % Options for packages loaded elsewhere
@@
   times]{anzsauth}
-\usepackage{xcolor}
+
 \usepackage{amsmath,amssymb}
-\setcounter{secnumdepth}{5}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math} % this also loads fontspec
+  \usepackage{unicode-math}
   \defaultfontfeatures{Scale=MatchLowercase}
@@
 \makeatother
+\usepackage{xcolor}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{5}
 % Make \paragraph and \subparagraph free-standing
@@
 
-\usepackage{longtable,booktabs,array}
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
 \usepackage{calc} % for calculating minipage widths
@@
 \makeatother
-
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-\usepackage[]{natbib}
-\bibliographystyle{anzsj}
 
@@
 \makeatother
+
+\usepackage[]{natbib}
+\bibliographystyle{anzsj}
 \usepackage{bookmark}
+
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
+\urlstyle{same} % disable monospaced font for URLs
 \hypersetup{
@@
 \author{
-Weihao Li\addressnum{1, 2},
+Weihao Li\addressnum{1},
 Dianne Cook\addressnum{1},
@@
 Hall, 3310 Holdrege St Suite 340, Lincoln, NE 68583, United States\\
-\hspace*{1ex} Email: \texttt{patrick.li@anu.edu.au}    
+\hspace*{1ex} Email: \texttt{weihao.li@monash.edu}    
 }
@@
 \begin{abstract}
-Visual assessment of residual plots is a common approach for diagnosing
-linear models, but it relies on manual evaluation, which does not scale
-well and can lead to inconsistent decisions across analysts. The lineup
-protocol, which embeds the observed plot among null plots, can reduce
-subjectivity but requires even more human effort. In today's data-driven
-world, such tasks are well-suited for automation. We present a new R
-package that uses a computer vision model to automate the evaluation of
-residual plots. An accompanying Shiny app is provided for ease of use.
-Given a sample of residuals, the model predicts a visual signal strength
-(VSS) and offers supporting information to help analysts assess model
-fit.
+Visually assessing residual plots is a common advice for linear model
+diagnostics, however this approach requires manual human evaluation and
+thereby is not scalable for assessing many models. Human evaluation also
+has the potential to produce inconsistent decisions from different
+analysts. Using a lineup protocol, where the residual plot is embedded
+among null plots, can help to alleviate inconsistency, but requires even
+more human effort. This is the type of task that in today's world we
+might employ a robot to do the tedious work for a human. Here we
+describe a new R package that includes a computer vision model for
+automated assessment of residual plots, and an accompanying Shiny app
+for ease of use. For a user-provided sample of residuals, it predicts a
+measure of visual signal strength (VSS) and provides a suite of
+supporting information to assist the analyst decide on the
+appropriateness their model fit.
 \end{abstract}
@@
 regression modeling and generating diagnostics. The package
-\texttt{lmtest} \citep{lmtest} provides a suite of conventional tests,
-while the \texttt{stats} package \citep{stats} offers standard
-diagnostic plots such as residuals vs.~fitted values, quantile-quantile
-(Q-Q) plots, and residuals vs.~leverage plots. Additional packages like
-\texttt{jtools} \citep{jtools}, \texttt{olsrr} \citep{olsrr},
-\texttt{rockchalk} \citep{rockchalk}, and \texttt{ggResidpanel}
-\citep{ggresidpanel} deliver similar graphical diagnostics, often with
-enhanced aesthetics or interactive features. These tools collectively
-produce the core diagnostic plots outlined in the classical text by
+\texttt{lmtest} \citep{lmtest} provides a suite of conventional tests.
+The \texttt{stats} package \citep{stats} offers standard diagnostic
+plots such as residuals vs.~fitted values, quantile-quantile (Q-Q)
+plots, and residuals vs.~leverage plots. Packages like \texttt{jtools}
+\citep{jtools}, \texttt{olsrr} \citep{olsrr}, \texttt{rockchalk}
+\citep{rockchalk}, and \texttt{ggResidpanel} \citep{ggresidpanel}
+provide similar graphical diagnostics, often with alternative aesthetics
+or interactive features. All of these tools deliver the types of
+diagnostic plots outlined in the classical text by
 \citet{cook1982residuals}. The \texttt{ecostats} package
-\citep{warton_global_2023} extends these diagnostics by incorporating
-simulation envelopes into residual plots. Meanwhile, \texttt{DHARMa}
-\citep{dharma} compares empirical quantiles (0.25, 0.5, and 0.75) of
-scaled residuals to their theoretical counterparts, with a strong focus
-on identifying model violations such as heteroscedasticity, misspecified
-functional forms, and issues specific to generalized linear and
-mixed-effect models, like over/under-dispersion. It also provides
-conventional test annotations to reduce the risk of misinterpretation.
+\citep{warton_global_2023} incorporates simulation envelopes into
+residual plots, while \texttt{DHARMa} \citep{dharma} compares empirical
+quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical
+counterparts. \texttt{DHARMa} is particularly focused on detecting model
+violations such as heteroscedasticity, incorrect functional forms, and
+issues specific to generalized linear and mixed-effect models, like
+over/under-dispersion. It also includes conventional test annotations to
+help avoid misinterpretation.
 
@@
 lead to issues such as over-interpreting random patterns as model
-violations. \citet{li2024plot} demonstrated that visual inference
-methods, particularly those using the lineup protocol
-\citep{buja2009statistical}, offer more practical and reliable
-assessments of residual patterns than conventional tests, as they are
-less sensitive to minor departures. Packages such as \texttt{nullabor}
-\citep{nullabor}, \texttt{HLMdiag} \citep{loy2014hlmdiag}, and
-\texttt{regressinator} \citep{regressinator} support this approach by
-enabling users to compare observed residual plots with plots generated
-under null hypothesis, thereby helping to quantify the significance of
-any detected patterns.
-
-As noted in \citet{li2024automated}, the lineup protocol has significant
-limitations in large-scale applications due to its reliance on human
-labor. To overcome this constraint, a computer vision model was
-developed alongside a corresponding statistical testing procedure to
-autmoate the assessment of residual plots. The model takes as input a
-residual plot and a set of auxiliary variables (such as the number of
-observations) and outputs a predicted visual signal strength (VSS). This
-VSS estimates the degree of deviation between the residual distribution
-of the fitted model and the reference distribution expected under
+violations. \citet{li2024plot} demonstrated that visual methods using
+the lineup protocol \citep{buja2009statistical} for assessing residuals
+are more useful, and also perform more practically than conventional
+tests due to their reduced sensitivity to minor departures. Packages
+such as \texttt{nullabor} \citep{nullabor}, \texttt{HLMdiag}
+\citep{loy2014hlmdiag}, and \texttt{regressinator}
+\citep{regressinator}, enable users to compare observed residual plots
+with plots of samples from null distributions, helping to quantify the
+significance of any detected patterns.
+
+However, as discussed in \citet{li2024automated}, the lineup protocol
+has significant limitations in large-scale applications due to
+dependence on human labor. Thus, a computer vision model was developed
+with an associated statistical testing procedure to automate the
+assessment of residual plots. This model takes a residual plot and a
+vector of auxiliary variables (such as the number of observations) as
+inputs and outputs the predicted visual signal strength (VSS). This
+strength estimates the distance between the residual distribution of the
+fitted regression model and the reference distribution assumed under
 correct model specification.
@@
 To make the statistical testing procedure and trained computer vision
-model widely accessible, we developed the R package \texttt{autovi}
-along with a companion web interface, \texttt{autovi.web}, which allows
-users to automatically assess their residual plots using the trained
-computer vision model.
+model widely accessible, we developed the R package \texttt{autovi}, and
+a web interface, \texttt{autovi.web} to make it easy for users to
+automatically read their residual plots with the trained computer vision
+model.
 
 The remainder of this paper is structured as follows:
-Section~\ref{sec-vss-desc} introduces the definition and computation of
-visual signal strength. Section~\ref{sec-autovi} provides a detailed
-documentation of the \texttt{autovi} package, including its usage and
-infrastructure. Section~\ref{sec-autovi-web} focuses on the
-\texttt{autovi.web} interface, describing its design and usage, along
-with illustrative examples. Finally, Section~\ref{sec-autovi-conclusion}
-presents the main conclusions of this work.
+Section~\ref{sec-autovi} provides a detailed documentation of the
+\texttt{autovi} package, including its usage and infrastructure.
+Section~\ref{sec-autovi-web} focuses on the \texttt{autovi.web}
+interface, describing its design and usage, along with illustrative
+examples. Finally, Section~\ref{sec-autovi-conclusion} presents the main
+conclusions of this work.
 
@@
 
-To train a computer vision model, a measure of the visible pattern in a
-plot is needed. We call this the \textbf{visual signal strength} (VSS),
-which measures how prominently a specific set of visual patterns appears
-in an image. This can be computed for a training set of data, and plots,
+To train a computer vision model a measure of the visible pattern in a
+plot is needed. We call this the \textbf{visual signal strength} (VSS)
+measuring how prominently a specific set of visual patterns appears in
+an image. This can be computed for a training set of data, and plots,
 where the generating distributions are specified.
 
-In the context of regression model diagnostics, VSS describes the
-clarity of visual patterns on a diagnostic plot that may indicate model
-violations. Violations can be categorized as weak, moderate, or strong,
-but here we treat it as a continuous positive real variable.
-Importantly, its interpretation depends on how it is linked to a
-function of the data or the underlying data generating process.
-Consequently, the calculation of VSS can vary across different model
+In the context of regression model diagnostics, it describes the clarity
+of visual patterns on a diagnostic plot that may indicate model
+violations. This concept can be categorized as weak, moderate, or
+strong. However, in our study, we treat it as a continuous positive real
+variable. Importantly, its interpretation depends on how it is linked to
+a function of the data or the underlying data generating process.
+Consequently, the calculation of VSS can be vary across different model
 classes or within the same model, depending on the generating function.
 
-VSS estimates the distance between the residual distribution of a fitted
-classical normal linear regression model and a reference distribution
-\citep[see][for details]{li2024automated}. The distance measure is based
-on the Kullback-Leibler (KL) divergence:
+VSS is defined as an estimate of a distance measure that quantifies the
+disparity between the residual distribution of a fitted classical normal
+linear regression model and a reference distribution, and more details
+can be found in \citet{li2024automated}. This measure is based on the
+Kullback-Leibler (KL) divergence:
 
@@
 
-This distance measure depends on knowledge of the true residual
-distribution, which is unknown in practice. To compute \(D_{KL}\) for
-the training samples, Equation \ref{eq:kl-1} takes different forms
-depending on the specific model violations. For instance, where
-necessary higher-order predictors, \(\boldsymbol{Z}\), and their
-corresponding parameter, \(\boldsymbol{\beta}_Z\), are omitted from the
-fitted linear model, the distance measure can be expanded as follows:
-
-\begin{equation*} \label{eq:kl-2}
-D_{KL} = \frac{1}{2}\left(\boldsymbol{\mu}_z^\top(\text{diag}(\boldsymbol{R}\sigma^2))^{-1}\boldsymbol{\mu}_z\right),
-\end{equation*}
-
-where
-\(\boldsymbol{\mu}_z = \boldsymbol{R}\boldsymbol{Z}\boldsymbol{\beta}_z\),
-\(\boldsymbol{R} = \boldsymbol{I}_n - \boldsymbol{X}(\boldsymbol{X}^\top\boldsymbol{X})^{-1}\boldsymbol{X}^\top\)
-and \(\boldsymbol{X}\) is the design matrix of the regression model.
-
-The computer vision model approximates this mapping from a set of
-residuals to its corresponding distance measure. It is trained on a
-large number of synthetic regression models, each designed to simulate
-specific violations of classical linear regression assumptions. These
-models incorporate non-linearity through Hermite polynomial
-transformations of predictors, heteroskedasticity by making the error
-variance a predictor-dependent function, and non-normality by drawing
-residuals from distributions such as discrete, uniform, and lognormal.
-Both simple and multiple linear regression structures are used, with
-controlled parameters to generate diverse and complex residual patterns.
-Since the data-generating process is known, the distance measure \(D\)
-can be explicitly calculated, enabling supervised training. The computer
-vision model takes a residual plot as input and outputs the
-corresponding distance measure, learning to quantify model violations
-directly from visual patterns. Additional details are provided in
-\citet{li2024automated}.
-
-\section{Definition and simulation of null and bootstrapped
-residuals}\label{sec-null-and-boot-desc}
-
-In the subsequent sections, we will frequently refer to null residuals
-and bootstrapped residuals, so it is helpful to first define and explain
-how they are generated.
-
-\textbf{Null residuals} are used to generate null plots within the
-lineup protocol framework, serving as the foundation for the statistical
-testing in our automated residual plot assessment. Specifically, they
-represent residuals generated under the null hypothesis that the model
-is correctly specified. A common method for simulating null residuals in
-linear regression involves sampling from a normal distribution with mean
-zero and variance equal to the estimated variance of the error term.
-These simulated residuals and their corresponding plots depict what one
-would expect from a correctly specified model. If the true residual plot
-exhibits noticeable deviations from these null plots, it may suggest
-model misspecification.
-
-Our computer vision model is trained to assign lower VSS to null plots
-and higher VSS to plots that display distinct patterns. Accordingly,
-statistical testing is performed by computing the proportion of null
-plots whose VSS equals or exceeds that of the observed residual plot.
-This proportion serves as a p-value for a one-sided hypothesis test.
-
-\textbf{Bootstrapped residuals} are obtained by refitting the model on
-bootstrap samples, which are generated by sampling individual
-observations with replacement from the original dataset. The residual
-plots obtained from these refitted models are evaluated using the same
-computer vision model. The predicted VSS from the bootstrapped plots
-provide an empirical estimate of the variation in the VSS of the
-observed residual plot. By examining the proportion of bootstrapped
-plots that also exhibit significant violations, we can assess whether
-the original conclusion is robust to sampling variability.
+This distance measure requires knowledge of the true residual
+distribution, which is typically unknown. Therefore, a computer vision
+model was used for estimating the residual distribution \citep[see][ for
+more details]{li2024automated}.
 
@@
 \texttt{autovi} stands for \textbf{auto}mated \textbf{v}isual
-\textbf{i}nference. This functionality can be accessed through the R
-package \texttt{autovi}, or through a web interface,
-\texttt{autovi.web}, which enables users to perform analyses without
-installing R, Python, or their associated dependencies locally.
-
-\subsection{Motivation}\label{sec-why}
+\textbf{i}nference.
+
+There are two ways to access the package, directly using R or through a
+web interface, \texttt{autovi.web}. The web interface has the advantage
+that it can be used without installing Python, R and the relevant
+packages locally.
+
+\subsection{Motivation for usage}\label{sec-why}
 
@@
 The third example is generated using the \texttt{surreal} package
-\citep{surreal}, where structure residuals are embedded in the data. In
-this case, a quote inspired by Tukey, ``visual summaries focus on
-unexpected values'', is used to define the residual structure. The
-automated plot reading predicts the VSS to be 5.87, with a \(p\)-value
-less than 0.05. Visually, the structure is strikingly clear, but a RESET
-test for nonlinear structure would not report a problem. (It would be
-detected by a Breusch-Pagan for heteroscedasticity and also Shapiro-Wilk
-test \citep{shapiro1965analysis} for non-normality.)
+\citep{surreal} where structured residuals are hidden in data, to be
+revealed if the correct model is specified. Here a quote based on Tukey
+is used as the residual structure ``visual summaries focus on unexpected
+values''. The automated plot reading predicts the VSS to be 5.87, with a
+\(p\)-value less than 0.05. This structure is blindingly obvious
+visually, but a RESET test for nonlinear structure would not report a
+problem. (It would be detected by a Breusch-Pagan for heteroscedasticity
+and also Shapiro-Wilk test \citep{shapiro1965analysis} for
+non-normality.)
 
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-three-examples-1.pdf}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_submission1_files/figure-pdf/fig-three-examples-1.pdf}
 
@@
 enhances flexibility and modularity, allowing users to redefine key
-functions through method overriding.
+functions through method overriding. While similar functionality could
+be achieved using R's S3 system with generic functions, the OOP
+framework offers a more structured and extensible foundation for the
+package.
 
@@
 and resizing PNG files of residual plots, then converting them into
-input tensors for further analysis. \texttt{TensorFlow}
-\citep{abadi2016tensorflow}, a key component of modern machine learning,
-is used to predict the VSS of these plots using a pre-trained
-convolutional neural network.
+input tensors for further analysis. The \texttt{TensorFlow}
+\citep{abadi2016tensorflow} library, a key component of modern machine
+learning, is used to predict the VSS of these plots through a
+pre-trained convolutional neural network.
 
@@
 \texttt{ggplot2} \citep{ggplot2} generates the initial residual plots,
-saved as PNG files for visual input. \texttt{cassowaryr}
-\citep{mason2022cassowaryr} computes scagnostics (scatter plot
+saved as PNG files for visual input. The \texttt{cassowaryr}
+\citep{mason2022cassowaryr} library computes scagnostics (scatter plot
 diagnostics), providing numerical features that capture statistical
@@
 analysis by offering quantitative metrics as secondary input to the
-computer vision model. \texttt{reticulate} \citep{reticulate} enables
-seamless communication between R and Python.
+computer vision model. The \texttt{reticulate} \citep{reticulate}
+package bridges R and Python, enabling seamless communication between
+the two languages and supporting the integrated infrastructure.
 
@@
 developed and maintained, with the latest updates accessible on GitHub.
-This paper uses \texttt{autovi} version 0.4.2. The package includes
-internal functions to check the current Python environment used by the
-\texttt{reticulate} package. If the necessary Python packages are not
-installed in the Python interpreter, an error will be raised. If you
-want to select a specific Python environment, you can do so by calling
-the \texttt{reticulate::use\_python()} function before using the
-\texttt{autovi} package.
+The code discussed in this paper is based on \texttt{autovi} version
+0.4.1.
+
+The package includes internal functions to check the current Python
+environment used by the \texttt{reticulate} package. If the necessary
+Python packages are not installed in the Python interpreter, an error
+will be raised. If you want to select a specific Python environment, you
+can do so by calling the \texttt{reticulate::use\_python()} function
+before using the \texttt{autovi} package.
 
@@
   predicts the VSS for the true residual plot, 100 null plots, and 100
-  bootstrapped plots. The method stores the predictions internally and
-  prints a concise results report.
+  bootstrapped plots, storing the predictions internally. A concise
+  report of the check results is then printed.
 \end{enumerate}
@@
 \begin{verbatim}
-<AUTO_VI object>
+\end{verbatim}
+
+\begin{verbatim}
+-- <AUTO_VI object>
 Status:
  - Fitted model: lm
-  - Keras model: (None, 32, 32, 3) + (None, 5) -> (None, 1)
+ - Keras model: UNKNOWN
     - Output node index: 1
  - Result:
-     - Observed visual signal strength: 3.16 (p-value = 0.0396)
+    - Observed visual signal strength: 3.162 (p-value = 0.0396)
     - Null visual signal strength: [100 draws]
@@
        - Quantiles: 
-           ╔══════════════════════════════════════════╗
+          ╔═════════════════════════════════════════════════╗
           ║   25%    50%    75%    80%    90%    95%    99% ║
-           ║0.802 1.111 1.575 1.666 1.919 2.657 3.348 ║
-           ╚══════════════════════════════════════════╝
+          ║0.8021 1.1109 1.5751 1.6656 1.9199 2.6564 3.3491 ║
+          ╚═════════════════════════════════════════════════╝
     - Bootstrapped visual signal strength: [100 draws]
-        - Mean: 2.795 (p-value = 0.05941)
+       - Mean: 2.786 (p-value = 0.05941)
        - Quantiles: 
@@
           ║  25%   50%   75%   80%   90%   95%   99% ║
-           ║2.455 2.941 3.177 3.300 3.474 3.537 3.668 ║
+          ║2.452 2.925 3.173 3.285 3.463 3.505 3.652 ║
           ╚══════════════════════════════════════════╝
-     - Likelihood ratio: 0.7333 (boot) / 0.06284 (null) = 11.67
+    - Likelihood ratio: 0.7275 (boot) / 0.06298 (null) = 11.55 
 \end{verbatim}
@@
 
-\includegraphics[width=0.45\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-plot-pair-1.pdf}
+\includegraphics[width=0.6\linewidth,height=\textheight,keepaspectratio]{autovi_paper_submission1_files/figure-pdf/fig-plot-pair-1.pdf}
 
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-summary-plot-1.pdf}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_submission1_files/figure-pdf/fig-summary-plot-1.pdf}
 
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-diag-1.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_submission1_files/figure-pdf/fig-autovi-diag-1.png}
 
@@
 
-The package takes regression models and a \texttt{Keras} model as
-primary inputs. Modules for VSS prediction and \(p\)-value computation
-are fixed but accessible via function arguments, using
-\texttt{TensorFlow} for inference and statistical testing. The image
-loading module is also fixed, using \texttt{PIL} to read and resize
-images based on the \texttt{Keras} model's input shape. The remaining
-seven modules are overridable, allowing users to adapt the workflow as
-needed. The data extraction module extracts a \texttt{data.frame}
-containing variables used in the regression model. The bootstrapping and
-refitting module resamples the data and refits the model. The fitted
-values and residuals extraction module returns these values as a
-\texttt{data.frame}. The auxiliary computation module calculates
-scagnostics such as monotonicity. The plotting module generates a
-\texttt{ggplot} in a standard format, and the plot saving module exports
-it at the same resolution as the training images. These modules are
-described in detail in the package documentation.
-
-\subsection{Extension to Other Model
-Classes}\label{extension-to-other-model-classes}
-
-The \texttt{autovi} R package can be extended to accommodate other
-classes of models beyond linear regression, such as generalized linear
-models (\texttt{glm}). This is achieved by substituting the relevant
-overridable modules, and if needed, supplying a different \texttt{Keras}
-model.
-
-We provide an example of defining a new checker class tailored for
-Poisson regression using the \texttt{glm} framework:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Define a new class using \texttt{new\_class()} with \texttt{AUTO\_VI}
-  as the parent class.
-\item
-  Override the necessary methods using \texttt{register\_method()}. In
-  this example, we use Pearson residuals. To simulate null residuals, we
-  assume the fitted model is correct and the estimated coefficients are
-  accurate. New response values are generated accordingly, and a new
-  model is fitted to this simulated response. Null residuals are then
-  extracted from this refitted model.
-\item
-  Create an alias for the \texttt{instantiate()} method of the new
-  class.
-\end{enumerate}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{AUTO\_POIS\_VI }\OtherTok{\textless{}{-}} \FunctionTok{new\_class}\NormalTok{(AUTO\_VI, }\AttributeTok{class\_name =} \StringTok{"AUTO\_POIS\_VI"}\NormalTok{)}
-\FunctionTok{register\_method}\NormalTok{(}
-\NormalTok{  AUTO\_POIS\_VI,}
-  \AttributeTok{get\_fitted\_and\_resid =} \ControlFlowTok{function}\NormalTok{(}\AttributeTok{fitted\_model =}\NormalTok{ self}\SpecialCharTok{$}\NormalTok{fitted\_model) \{}
-    \FunctionTok{tibble}\NormalTok{(}\AttributeTok{.fitted =} \FunctionTok{fitted}\NormalTok{(fitted\_model),}
-           \AttributeTok{.resid =} \FunctionTok{resid}\NormalTok{(fitted\_model, }\AttributeTok{type =} \StringTok{"pearson"}\NormalTok{))}
-\NormalTok{  \},}
-  \AttributeTok{null\_method =} \ControlFlowTok{function}\NormalTok{(}\AttributeTok{fitted\_model =}\NormalTok{ self}\SpecialCharTok{$}\NormalTok{fitted\_model) \{}
-\NormalTok{    dat }\OtherTok{\textless{}{-}} \FunctionTok{model.frame}\NormalTok{(fitted\_model)}
-\NormalTok{    dat[[}\DecValTok{1}\NormalTok{]] }\OtherTok{\textless{}{-}} \FunctionTok{rpois}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(dat), }\AttributeTok{lambda =} \FunctionTok{fitted}\NormalTok{(fitted\_model))}
-\NormalTok{    new\_mod }\OtherTok{\textless{}{-}} \FunctionTok{update}\NormalTok{(fitted\_model, }\AttributeTok{data =}\NormalTok{ dat)}
-    \FunctionTok{return}\NormalTok{(self}\SpecialCharTok{$}\FunctionTok{get\_fitted\_and\_resid}\NormalTok{(new\_mod))}
-\NormalTok{  \}}
-\NormalTok{)}
-\NormalTok{auto\_pois\_vi }\OtherTok{\textless{}{-}}\NormalTok{ AUTO\_POIS\_VI}\SpecialCharTok{$}\NormalTok{instantiate}
-\end{Highlighting}
-\end{Shaded}
-
-The resulting checker class can be employed analogously to the linear
-model case described in Section~\ref{sec-autovi-usage}. For
-illustration, we fit a Poisson model in which the quadratic term of the
-predictor \(x\) is intentionally omitted. This misspecification
-manifests as a pronounced U-shaped pattern in the lineup display (see
-Figure~\ref{fig-pois-lineup}), which is also successfully identified by
-the computer vision model, yielding a p-value substantially below the
-conventional threshold of 0.05.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{x }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(}\DecValTok{300}\NormalTok{, }\AttributeTok{sd =} \FloatTok{0.5}\NormalTok{)}
-\NormalTok{y }\OtherTok{\textless{}{-}} \FunctionTok{rpois}\NormalTok{(}\DecValTok{300}\NormalTok{, }\AttributeTok{lambda =} \FunctionTok{exp}\NormalTok{(}\DecValTok{1} \SpecialCharTok{+}\NormalTok{ x }\SpecialCharTok{+}\NormalTok{ x}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{))}
-\NormalTok{pois\_checker }\OtherTok{\textless{}{-}} \FunctionTok{auto\_pois\_vi}\NormalTok{(}
-  \FunctionTok{glm}\NormalTok{(y }\SpecialCharTok{\textasciitilde{}}\NormalTok{ x, }\AttributeTok{family =} \StringTok{"poisson"}\NormalTok{),}
-  \AttributeTok{keras\_model =} \FunctionTok{get\_keras\_model}\NormalTok{(}\StringTok{"vss\_phn\_32"}\NormalTok{)}
-\NormalTok{)}
-\NormalTok{pois\_checker}\SpecialCharTok{$}\FunctionTok{plot\_lineup}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{figure}[H]
-
-\centering{
-
-\includegraphics[width=0.8\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-pois-lineup-1.pdf}
-
-}
-
-\caption{\label{fig-pois-lineup}A lineup of residual plots from Poisson
-generalized linear models, with the true residual plot at position 4,
-which displays a distinct U-shaped pattern. In contrast, the null plots
-show characteristics broadly consistent with well-behaved residuals from
-linear regression models.}
-
-\end{figure}%
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{pois\_checker}\SpecialCharTok{$}\FunctionTok{check}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-<AUTO_POIS_VI object>
- Status:
-  - Fitted model: glm, lm
-  - Keras model: (None, 32, 32, 3) + (None, 5) -> (None, 1)
-     - Output node index: 1
-  - Result:
-     - Observed visual signal strength: 4.875 (p-value = 0.009901)
-     - Null visual signal strength: [100 draws]
-        - Mean: 1.331
-        - Quantiles: 
-           ╔══════════════════════════════════════════╗
-           ║  25%   50%   75%   80%   90%   95%   99% ║
-           ║1.035 1.233 1.488 1.644 1.941 2.276 2.639 ║
-           ╚══════════════════════════════════════════╝
-     - Bootstrapped visual signal strength: [100 draws]
-        - Mean: 5.51 (p-value = 0.009901)
-        - Quantiles: 
-           ╔══════════════════════════════════════════╗
-           ║  25%   50%   75%   80%   90%   95%   99% ║
-           ║5.330 5.505 5.698 5.735 5.830 5.903 6.013 ║
-           ╚══════════════════════════════════════════╝
-     - Likelihood ratio: 0.05096 (boot) / 0 (null) = Extremely large
-\end{verbatim}
-
-It is important to note, however, that the pre-trained computer vision
-model included in \texttt{autovi}, such as \texttt{vss\_phn\_32} (see
-\texttt{list\_keras\_models()} for the full list of available models),
-was developed specifically for diagnostics of linear regression. Its
-applicability to other model classes relies on the assumption that the
-null residual plots exhibit characteristics broadly consistent with
-those of well-behaved linear regression residuals, that is, residuals
-should be approximately randomly scattered around zero, display roughly
-constant variance across the range of fitted values, and exhibit no
-discernible structure or curvature. If these conditions are not met, or
-if model violations do not give rise to visually detectable patterns,
-the validity of the automated diagnostics may be compromised. In such
-cases, users are encouraged to train and apply their own \texttt{Keras}
-models. Detailed guidance on model training and discussion on extending
-the methodology to other model classes can be found in
-\citet{li2024automated}.
+The modules for VSS prediction and \(p\)-value computation are
+predefined and cannot be overridden, although users can interact with
+them directly through function arguments. Similarly, the image reading
+and resizing module is fixed but will adapt to different Keras models by
+checking their input shapes. The remaining seven modules are designed to
+be overridable, enabling users to tailor the infrastructure to their
+specific needs. These modules are discussed in detail on the software's
+website.
 
@@
 which would have allowed the entire application to run directly in the
-user's browser. However, \texttt{webr} does not support packages which
-use compiled fortran code, which is required by \texttt{splancs}
-\citep{splancs}, a dependency of \texttt{autovi}. In the future, it is
-possible that a working Emscripten \citep{zakai2011emscripten} version
-of this package may allow full \texttt{webr} support.
+user's browser. However, this approach was not feasible at the time of
+writing this paper. The reason is that one of the R packages
+\texttt{autovi} depends on the R package \texttt{splancs}
+\citep{splancs}, which uses compiled Fortran code. A working Emscripten
+\citep{zakai2011emscripten} version of this package, which would be
+required for \texttt{webr}, was not available.
 
@@
 as those provided by cloud platforms like Google Cloud Platform (GCP) or
-Amazon Web Services (AWS). However, deploying and maintaining the server
-securely requires some expertise. Ultimately, the most practical
-solution was to use the \texttt{shiny} and \texttt{shinydashboard}
-frameworks, which are well-established in the R community and offer a
-solid foundation for web application development.
+Amazon Web Services (AWS). However, correctly setting up the server and
+ensuring a secure deployment requires significant expertise. Ultimately,
+the most practical solution was to use the \texttt{shiny} and
+\texttt{shinydashboard} frameworks, which are well-established in the R
+community and offer a solid foundation for web application development.
 
@@
 
-Due to shinyapps.io's resource policy, inactive servers enter sleep
-mode, clearing the local Python environment. When reactivated for a new
-session, libraries must be reinstalled. While this ensures a clean
-environment for each session, it may lead to slightly longer loading
-times for the first user after a period of inactivity.
-
-In contrast to \texttt{autovi}, \texttt{autovi.web} leverages
+Due to the resource allocation policy of shinyapps.io, the server enters
+a sleep mode during periods of inactivity, resulting in the clearing of
+the local Python virtual environment. Consequently, when the application
+``wakes up'' for a new user session, these libraries need to be
+reinstalled. While this ensures a clean environment for each session, it
+may lead to slightly longer loading times for the first user after a
+period of inactivity.
+
+In contrast to \texttt{autovi}, \texttt{autovi.web} does not use the
+native Python version of \texttt{TensorFlow}. Instead, it leverages
 \texttt{TensorFlow.js}, a JavaScript library that allows the execution
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-setup-1.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_submission1_files/figure-pdf/fig-autovi-web-setup-1.png}
 
@@
 are captured by the computer vision model, ensuring the quality of the
-assessment. The attention map is the gradient of the model output with
-respect to the grayscale image input, indicating the sensitivity of the
-output to each pixel.
+assessment.
 
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-lineup-1.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_submission1_files/figure-pdf/fig-autovi-web-lineup-1.png}
 
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_files/figure-pdf/fig-autovi-web-distributions-1.png}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{autovi_paper_submission1_files/figure-pdf/fig-autovi-web-distributions-1.png}
 
@@
 assessment of residual plots by incorporating a computer vision model,
-reducing reliance on time-consuming and potentially inconsistent human
-interpretation. This automation improves the efficiency of the
+eliminating the need for time-consuming and potentially inconsistent
+human interpretation. This automation improves the efficiency of the
 diagnostic process and promotes consistency in model evaluation across

### 2025-05-14 response_to_reviews.qmd
response to review as pdf

--- 2025-05-13 response_to_reviews.md
@@
-## Response to reviewers
+---
+title: Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web
+subtitle: Response to reviewers
+date: today
+filters:
+   - latex-environment
+environments: [reviewer]
+format: 
+  pdf:
+    keep-tex: true
+    include-in-header:
+      text: | 
+       \usepackage[dvipsnames]{xcolor}
+       \newenvironment{reviewer}{
+       \color{violet}}
+       {}
+       \renewenvironment{quote}{%
+        \list{}{%
+          \leftmargin0.5cm   % this is the adjusting screw
+          \itshape
+          \rightmargin\leftmargin
+        }
+        \item\relax
+       }
+       {\endlist}
+---
 
-We thank the reviewers for their reviews. We have addressed it as follows.
+We thank the reviewers for their comments (colored in ${\color{violet}\text{purple}}$ below).
+We have addressed it as below (in black).
+We also submit the difference between the previously submitted document and the revised version produced via `latexdiff`.
 
@@
 
-> 1. The Abstract could be improved further. Certain sentences in the Abstract contain grammatical errors and are hard to read.
+::: reviewer
+
+1. The Abstract could be improved further. Certain sentences in the Abstract contain grammatical errors and are hard to read.
+
+:::
 
@@
 
-> 2.
+::: reviewer
+
+2.
 The "autovi.web" RShiny app (e.g., https://akdd4t-patrick-li.shinyapps.io/autovi_web/) lacks clear instructions regarding the format of CSV files it accepts.
@@
 
+:::
+
 We have updated the app to include clearer instructions on the required input format.
 
-> 3. One suggestion is to consider integrating the widely-used regression model fitting functions (e.g., lm(), aov() or glm ()) into "autovi" to automate the model fitting and assessment of residuals.
+::: reviewer
+
+3. One suggestion is to consider integrating the widely-used regression model fitting functions (e.g., lm(), aov() or glm ()) into "autovi" to automate the model fitting and assessment of residuals.
+
+:::
 
@@
 
-> 4. Finally, please check the English in the manuscript. Certain lengthy sentences can be hard to understand.
+::: reviewer
+
+4. Finally, please check the English in the manuscript. Certain lengthy sentences can be hard to understand.
+
+:::
 
@@
 
-> - some introduction on generating the null plot and bootstrap residual, which provides some background to understand the code summary in page 7 and Figure 3 on the comparison between VSS from the two scenarios.
+::: reviewer
+
+- some introduction on generating the null plot and bootstrap residual, which provides some background to understand the code summary in page 7 and Figure 3 on the comparison between VSS from the two scenarios.
+
+:::
 
@@
 
-> - information on the type/ scope of regression models used to train the cv model in Section 2 to understand the applicability of the cv model.
+::: reviewer
+
+- information on the type/ scope of regression models used to train the cv model in Section 2 to understand the applicability of the cv model.
+
+:::
 
@@
 
-> - a brief description of each module in Figure 4, for example, what does auxiliary computation (in Figure 4) include?
+::: reviewer
+
+- a brief description of each module in Figure 4, for example, what does auxiliary computation (in Figure 4) include?
+
+:::
 
@@
 
-> - the necessary changes need to make to extend the workflow to diagnose other models e.g. GLM, in Section 3.5.
+::: reviewer
+
+- the necessary changes need to make to extend the workflow to diagnose other models e.g. GLM, in Section 3.5.
+
+:::
 
@@
 
-> - the term "attention map" used in line 331 and Figure 7 caption is not introduced in the paper.
+::: ::: reviewer
+
+- the term "attention map" used in line 331 and Figure 7 caption is not introduced in the paper.
+
+:::
 
@@
 
-> - The authors may consider moving Section 3.5 earlier in Section 3 to provide an overview of the package.
+::: reviewer
+
+- The authors may consider moving Section 3.5 earlier in Section 3 to provide an overview of the package.
+
+:::
 
@@
 
-> - The infrastructure is built on the bandicoot OOP system, could the authors comment on this choice compared to the latest S7?
+::: reviewer
+
+- The infrastructure is built on the bandicoot OOP system, could the authors comment on this choice compared to the latest S7?
+
+:::
 
@@
 
-> - The word "be" in line 60 is redundant in the sentence.
+::: reviewer
+
+- The word "be" in line 60 is redundant in the sentence.
+
+:::
 

### 2025-05-14 response_to_reviews.qmd
update response to reviewers

@@
   pdf:
-    keep-tex: true
     include-in-header:
@@
        {\endlist}
+bibliography: bibliography.bib  
+suppress-bibliography: true
 ---
@@
 We have addressed it as below (in black).
-We also submit the difference between the previously submitted document and the revised version produced via `latexdiff`.
+We also submit the difference between the previously submitted document and the revised version produced via `latexdiff` (named `diff.pdf`).
 
@@
 We have updated the app to include clearer instructions on the required input format.
+More specifically, the app now includes information for specific requirement of the input CSV and an information icon which shows another optional input column for multiple lineups on hover.
 
@@
 We agree that this is a valuable direction for future development.
-However, it lies beyond the scope of the current manuscript.
 We have added a new Section 4.6 that discusses how the workflow could be extended to accommodate broader model classes.
+We note, however, that this extension is only applicable for certain class of models as the computer vision model is trained on a fitted-vs-residual plot, which is not the optimal plot for diagnostic of, say, logistic model.
+Future research would benefit from building computer vision models tailored for visual dianostics suitable for other class of models.
 
@@
 
-We have revised the manuscript to improve clarity and grammar. Notable changes include:
+We have revised the manuscript to improve clarity and grammar.
+These are most easily seen via the document (`diff.pdf`) which shows the difference between the original and revised version.
+Notable changes include:
 
@@
 
-We have added a new Section 3 to introduce the definitions and generation procedures for null plots and bootstrapped residuals, providing necessary context for Figure 3.
+We have added a new Section 3 (shown below) to introduce the definitions and generation procedures for null plots and bootstrapped residuals, providing necessary context for Figure 3.
+
+> In the subsequent sections, we will frequently refer to null residuals and bootstrapped residuals, so it is helpful to first define and explain how they are generated.
+>
+> **Null residuals** are used to generate null plots within the lineup protocol framework, serving as the foundation for the statistical testing in our automated residual plot assessment.
+Specifically, they represent residuals generated under the null hypothesis that the model is correctly specified.
+A common method for simulating null residuals in linear regression involves sampling from a normal distribution with mean zero and variance equal to the estimated variance of the error term.
+These simulated residuals and their corresponding plots depict what one would expect from a correctly specified model.
+If the true residual plot exhibits noticeable deviations from these null plots, it may suggest model misspecification.
+>
+> Our computer vision model is trained to assign lower VSS to null plots and higher VSS to plots that display distinct patterns.
+Accordingly, statistical testing is performed by computing the proportion of null plots whose VSS equals or exceeds that of the observed residual plot.
+This proportion serves as a p-value for a one-sided hypothesis test.
+>
+> **Bootstrapped residuals** are obtained by refitting the model on bootstrap samples, which are generated by sampling individual observations with replacement from the original dataset.
+The residual plots obtained from these refitted models are evaluated using the same computer vision model.
+The predicted VSS from the bootstrapped plots provide an empirical estimate of the variation in the VSS of the observed residual plot.
+By examining the proportion of bootstrapped plots that also exhibit significant violations, we can assess whether the original conclusion is robust to sampling variability.
 
@@
 
+> The computer vision model approximates this mapping from a set of residuals to its corresponding distance measure.
+It is trained on a large number of synthetic regression models, each designed to simulate specific violations of classical linear regression assumptions.
+These models incorporate non-linearity through Hermite polynomial transformations of predictors, heteroskedasticity by making the error variance a predictor-dependent function, and non-normality by drawing residuals from distributions such as discrete, uniform, and lognormal.
+Both simple and multiple linear regression structures are used, with controlled parameters to generate diverse and complex residual patterns.
+Since the data-generating process is known, the distance measure $D$ can be explicitly calculated, enabling supervised training.
+The computer vision model takes a residual plot as input and outputs the corresponding distance measure, learning to quantify model violations directly from visual patterns.
+Additional details are provided in @li2024automated.
+
 ::: reviewer
@@
 We have extended the last paragraph of Section 4.5 to include brief descriptions of each module in Figure 4, including the tasks performed under "auxiliary computation".
+
+> The package takes regression models and a `Keras` model as primary inputs.
+Modules for VSS prediction and $p$-value computation are fixed but accessible via function arguments, using `TensorFlow` for inference and statistical testing.
+The image loading module is also fixed, using `PIL` to read and resize images based on the `Keras` model’s input shape.
+The remaining seven modules are overridable, allowing users to adapt the workflow as needed.
+The data extraction module extracts a `data.frame` containing variables used in the regression model.
+The bootstrapping and refitting module resamples the data and refits the model.
+The fitted values and residuals extraction module returns these values as a `data.frame`.
+The auxiliary computation module calculates scagnostics such as monotonicity.
+The plotting module generates a `ggplot` in a standard format, and the plot saving module exports it at the same resolution as the training images.
+These modules are described in detail in the package documentation.
 
@@
 
-::: ::: reviewer
+::: reviewer
 
@@
 The `bandicoot` system is a custom object-oriented system tailored for our development needs, in a similar spirit to how `ggproto` is used within `ggplot2`.
-A detailed comparison with newer systems like `S7` is beyond the scope of this paper.
+The `S7` system is quite new (first published on CRAN on 2024-11-07) and yet to be mature or have widespread usage.
 

### 2025-05-14 autovi_paper.tex
add about the section 3 in the intro

@@
 Section~\ref{sec-vss-desc} introduces the definition and computation of
-visual signal strength. Section~\ref{sec-autovi} provides a detailed
-documentation of the \texttt{autovi} package, including its usage and
-infrastructure. Section~\ref{sec-autovi-web} focuses on the
-\texttt{autovi.web} interface, describing its design and usage, along
-with illustrative examples. Finally, Section~\ref{sec-autovi-conclusion}
-presents the main conclusions of this work.
+visual signal strength. Section~\ref{sec-null-and-boot-desc} expands on
+the computation of the null and bootstrapped residuals.
+Section~\ref{sec-autovi} provides a detailed documentation of the
+\texttt{autovi} package, including its usage and infrastructure.
+Section~\ref{sec-autovi-web} focuses on the \texttt{autovi.web}
+interface, describing its design and usage, along with illustrative
+examples. Finally, Section~\ref{sec-autovi-conclusion} presents the main
+conclusions of this work.
 

### 2025-09-04 autovi_paper.qmd
add about the section 3 in the intro
Fix the format for packages/software

@@
 In today’s data-driven world, such tasks are well-suited for automation.
-We present a new R package that uses a computer vision model to automate the evaluation of residual plots.
-An accompanying Shiny app is provided for ease of use.
+We present a new \textsf{R} package that uses a computer vision model to automate the evaluation of residual plots.
+An accompanying \textsf{Shiny} app is provided for ease of use.
 Given a sample of residuals, the model predicts a visual signal strength (VSS) and offers supporting information to help analysts assess model fit.
@@
 There is a vast array of software for conducting regression modeling and generating diagnostics.
-The package `lmtest` [@lmtest] provides a suite of conventional tests, while the `stats` package [@stats] offers standard diagnostic plots such as residuals vs.
+The package \textsf{lmtest} [@lmtest] provides a suite of conventional tests, while the \textsf{stats} package [@stats] offers standard diagnostic plots such as residuals vs.
 fitted values, quantile-quantile (Q-Q) plots, and residuals vs.
 leverage plots.
-Additional packages like `jtools` [@jtools], `olsrr` [@olsrr], `rockchalk` [@rockchalk], and `ggResidpanel` [@ggresidpanel] deliver similar graphical diagnostics, often with enhanced aesthetics or interactive features.
+Additional packages like \textsf{jtools} [@jtools], \textsf{olsrr} [@olsrr], \textsf{rockchalk} [@rockchalk], and \textsf{ggResidpanel} [@ggresidpanel] deliver similar graphical diagnostics, often with enhanced aesthetics or interactive features.
 These tools collectively produce the core diagnostic plots outlined in the classical text by @cook1982residuals.
-The `ecostats` package [@warton_global_2023] extends these diagnostics by incorporating simulation envelopes into residual plots.
-Meanwhile, `DHARMa` [@dharma] compares empirical quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical counterparts, with a strong focus on identifying model violations such as heteroscedasticity, misspecified functional forms, and issues specific to generalized linear and mixed-effect models, like over/under-dispersion.
+The \textsf{ecostats} package [@warton_global_2023] extends these diagnostics by incorporating simulation envelopes into residual plots.
+Meanwhile, \textsf{DHARMa} [@dharma] compares empirical quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical counterparts, with a strong focus on identifying model violations such as heteroscedasticity, misspecified functional forms, and issues specific to generalized linear and mixed-effect models, like over/under-dispersion.
 It also provides conventional test annotations to reduce the risk of misinterpretation.
@@
 @li2024plot demonstrated that visual inference methods, particularly those using the lineup protocol [@buja2009statistical], offer more practical and reliable assessments of residual patterns than conventional tests, as they are less sensitive to minor departures.
-Packages such as `nullabor` [@nullabor], `HLMdiag` [@loy2014hlmdiag], and `regressinator` [@regressinator] support this approach by enabling users to compare observed residual plots with plots generated under null hypothesis, thereby helping to quantify the significance of any detected patterns.
+Packages such as \textsf{nullabor} [@nullabor], \textsf{HLMdiag} [@loy2014hlmdiag], and \textsf{regressinator} [@regressinator] support this approach by enabling users to compare observed residual plots with plots generated under null hypothesis, thereby helping to quantify the significance of any detected patterns.
 
@@
 
-To make the statistical testing procedure and trained computer vision model widely accessible, we developed the R package `autovi` along with a companion web interface, `autovi.web`, which allows users to automatically assess their residual plots using the trained computer vision model.
+To make the statistical testing procedure and trained computer vision model widely accessible, we developed the R package \textsf{autovi} along with a companion web interface, \textsf{autovi.web}, which allows users to automatically assess their residual plots using the trained computer vision model.
 
 The remainder of this paper is structured as follows: @sec-vss-desc introduces the definition and computation of visual signal strength.
-@sec-autovi provides a detailed documentation of the `autovi` package, including its usage and infrastructure.
-@sec-autovi-web focuses on the `autovi.web` interface, describing its design and usage, along with illustrative examples.
+@sec-null-and-boot-desc expands on the computation of the null and bootstrapped residuals.
+@sec-autovi provides a detailed documentation of the \textsf{autovi} package, including its usage and infrastructure.
+@sec-autovi-web focuses on the \textsf{autovi.web} interface, describing its design and usage, along with illustrative examples.
 Finally, @sec-autovi-conclusion presents the main conclusions of this work.
@@
 
-<!-- in the following sections.-->
-<!-- FIXME: ET: which website? >
-<!--
-### Initialization
-
-An `autovi` checker can be initialized by supplying two primary inputs, including a regression model object, such as an `lm` object representing the result of a linear regression model, and a trained computer vision model compatible with the `Keras` [@chollet2015keras] Application Programming Interface (API), to the `AUTO_VI` class constructor `auto_vi()`.
-The `residual_checker()` introduced in @sec-autovi-usage is a thin wrapper around `auto_vi()`, which will call `get_keras_model()` during initialization.
-`get_keras_model()` is a function to download a trained computer vision model (described in @li2024automated) from GitHub.
-“vss_phn_32” specifies a model that predicts VSS and is trained on residuals with polynomial, heteroscedasticity, and non-normality patterns (phn).
-More details about the hosted models will be provided in @sec-trained-model-hosting.
-
-The input of the constructor will be stored as attributes of the checker and can be accessed by the user through the `$` operator.
-
-```r
-library(autovi)
-checker <- auto_vi(fitted_model = lm(dist ~ speed, data = cars), 
-                   keras_model = get_keras_model("vss_phn_32"))
-```
-
-Optionally, the user may specify the node index of the output layer of the trained computer vision model to be monitored by the checker via the `node_index` argument if there are multiple output nodes.
-This is particularly useful for multiclass classifiers when the user wants to use one of the nodes as a VSS indicator.
-
-After initializing the object, you can print the checker to view its status.
-
-```r
-── <AUTO_VI object>
-Status:
- - Fitted model: lm
- - Keras model: (None, 32, 32, 3) + (None, 5) -> (None, 1)
-    - Output node index: 1
- - Result: UNKNOWN 
-```
-
-The status includes the list of regression model classes (as provided by the built-in `class()` function), the input and output shapes of the Keras model in the standard `Numpy` format [@harris2020array], the output node index being monitored, and the assessment result.
-If no check has been run yet, the assessment result will display as "UNKNOWN".
-
-### Fitted Values and Residuals Extraction
-
-To be able to predict VSS for a residual plot, both fitted values and residuals are needed to be extracted from the regression model object supplied by the user.
-In R, statistical models like `lm` (linear model) and `glm` (generalized linear model) typically support the use of generic functions such as `fitted()` and `resid()` to retrieve these values.
-The `get_fitted_and_resid()` method, called by the checker, relies on these generic functions by default.
-However, generic functions only work with classes that have appropriate method implementations.
-Some regression modeling packages may not fully adhere to the `stats` package guidelines for implementing these functions.
-In such cases, overriding the method becomes necessary.
-
-By design, the `get_fitted_and_resid()` method accepts a regression model object as input and returns a `tibble` (a modern presentation of the `data.frame`) with two columns: `.fitted` and `.resid`, representing the fitted values and residuals, respectively.
-If no input is supplied, the method uses the regression model object stored in the checker.
-Although modules in the `autovi` infrastructure make minimal assumptions about other modules, they do require strictly defined input and output formats to ensure data validation and prevent fatal bugs.
-Therefore, any overridden method should follow to these conventions.
-
-```{r echo=TRUE}
-checker$get_fitted_and_resid()
-```
-
-### Data Extraction
-
-For linear regression model in R, the model frame contains all the data required by a formula for evaluation.
-This is essential for bootstrapping and refitting the model when constructing a bootstrapped distribution of VSS.
-Typically, the model frame can be extracted from the regression model object using the `model.frame()` generic function, which is the default method used by `get_data()`.
-However, some regression models do not use a formula or are evaluated differently, potentially lacking a model frame.
-In such cases, users can either provide the data used to fit the regression model through the `data` argument when constructing the checker, or customize the method to better suit their needs.
-It's worth noting that this module is only necessary if bootstrapping is required, as the model frame is not used in other modules of the infrastructure.
-
-The `get_data()` method accepts a regression model object as input and returns a `data.frame` representing the model frame of the fitted regression model.
-If no input is supplied, the regression model stored in the checker will be used.
-
-```{r echo=TRUE}
-checker$get_data() |> 
-  head()
-```
-
-### Bootstrapping and Model Refitting
-
-Bootstrapping a regression model typically involves sampling the observations with replacement and refitting the model with the bootstrapped data.
-The `boot_method()` method follows this bootstrapping scheme by default.
-It accepts a fitted regression model and a `data.frame` as inputs, and returns a `tibble` of bootstrapped residuals.
-If no inputs are provided, the method uses the regression model stored in the checker and the result of the `get_data()` method.
-
-Note that instead of calling `get_data()` implicitly within the method, it is used as part of the default argument definition.
-This approach allows users to bypass the `get_data()` method entirely and directly supply a `data.frame` to initiate the bootstrap process.
-Many other methods in `autovi` adopt this principle when possible, where dependencies are explicitly listed in the formal arguments.
-This design choice enhances the reusability and isolation of modules, offers better control for testing, and simplifies the overall process.
-
-```{r echo=TRUE}
-checker$boot_method(data = checker$get_data())
-```
-
-### Auxiliary Computation
-
-As described in @li2024automated, in some cases, a residual plot alone may not provide enough information to accurately determine VSS.
-For instance, when the points in the residual plot have significant overlap, the trend and shape of the residual pattern can be difficult to discern.
-Including auxiliary variables, such as the number of observations, as additional inputs to the computer vision model can be beneficial.
-To address this, `autovi` includes internal functions within the checker that automatically detect the number of inputs required by the provided Keras model.
-If multiple inputs are necessary, the checker invokes the `auxiliary()` method to compute these additional inputs.
-
-The `auxiliary()` method takes a `data.frame` containing fitted values and residuals as input and returns a `data.frame` with five numeric columns.
-These columns represent four scagnostics — "Monotonic", "Sparse", "Striped", and "Splines" — calculated using the `cassowaryr` package, as well as the number of observations.
-This approach is consistent with the training process of the computer vision models described in @li2024automated.
-If no `data.frame` is provided, the method will default to retrieving fitted values and residuals by calling `get_fitted_and_resid()`.
-
-Technically, any Keras-implemented computer vision model can be adapted to accept an image as the primary input and additional variables as secondary inputs by adding a data pre-processing layer before the actual input layer.
-If users wish to override `auxiliary()`, the output should be a `data.frame` with a single row and the number of columns such that its concatenation matches the number of parameters for the corresponding layer in the supplied Keras model.
-
-```{r echo=TRUE}
-checker$auxiliary()
-```
-
-### Null Residual Simulation {#sec-autovi-null-method}
-
-A fundamental element of the automated residual assessment described in @li2024automated is comparing the VSS of null plots with that of the true residual plot.
-However, due to the variety of regression models, there is no universal method for simulating null residuals that are consistent with model assumptions.
-Fortunately, for classical normal linear regression models, null residuals can be effectively simulated using the residual rotation method, as outlined in @buja2009statistical.
-This process involves generating random draws from a standard normal distribution, regressing these draws on the original predictors, and then rescaling the resulting residuals by the ratio of the residual sum of squares to the that of the original linear regression model.
-Other regression models, such as `glm` (generalized linear model) and `gam` (generalized additive model), generally cannot use this method to efficiently simulate null residuals.
-Therefore, it is recommended that users override the `null_method()` to suit their specific model.
-The `null_method()` takes a fitted regression model as input, defaulting to the regression model stored in the checker, and returns a `tibble`.
-
-```{r echo=TRUE}
-checker$null_method()
-```
-
-### Plotting
-
-Plotting is a crucial aspect of residual plot diagnostics because aesthetic elements like marker size, marker color, and auxiliary lines impact the presentation of information.
-There are computer vision models trained to handle images captured in various scenarios.
-For example, the VGG16 model [@simonyan2014very] can classify objects in images taken under different lighting conditions and is robust to image rotation.
-However, data plots are a special type of image as the plotting style can always be consistent if controlled properly.
-Therefore, we assume computer vision models built for reading residual plots will be trained with residual plots of a specific aesthetic style.
-In this case, it is best to predict plots using the same style for optimal performance.
-The plotting method `plot_resid()` handles this aspect.
-
-`plot_resid()` accepts a `data.frame` containing fitted values and residuals, along with several customization options: a `ggplot` theme, an `alpha` value to control the transparency of data points, a `size` value to set the size of data points, and a `stroke` value to define the thickness of data point edges.
-Additionally, it includes four Boolean arguments to toggle the display of axes, legends, grid lines, and a horizontal red line.
-By default, it replicates the style we used to generate the training samples for the computer vision models described in @li2024automated.
-In brief, the residual plot omits axis text and ticks, titles, and background grid lines, featuring only a red line at $y = 0$.
-It retains only the necessary components of a residual plot.
-If the computer vision model is trained with a different but consistent aesthetic style, `plot_resid()` should be overridden.
-
-The method returns a `ggplot` object (@fig-autovi-plot-resid), which can be saved as a PNG file in the following module.
-If no data is provided, the method will use `get_fitted_and_resid()` to retrieve the fitted values and residuals from the regression model stored in the checker.
-
-```{r fig-autovi-plot-resid, echo=TRUE, fig.height=3, fig.width=4, fig.cap = "Residual plot of the regression model stored in the checker."}
-checker$plot_resid()
-```
-
-To manually generate true residual plots, null plots, or bootstrapped residual plots, you can pass the corresponding `data.frame` produced by the `get_fitted_and_resid()`, `null_method()`, and `boot_method()` methods to the `plot_resid()` method, respectively.
-
-### Plot Saving
-
-Another key aspect of a standardized residual plot is its resolution.
-In @li2024automated, we used an image format of 420 pixels in height and 525 pixels in width.
-This resolution was chosen because the original set, consisting of 20 residual plots arranged in a four by five grid, was represented by an image of 2100 by 2100 pixels.
-The `save_plot()` method accepts a `ggplot` object as input and saves it as a PNG file to the location specified by the `path` argument.
-If no path is provided, the PNG file is saved to a temporary file.
-
-```{r echo=TRUE}
-checker$plot_resid() |> 
-  checker$save_plot()
-```
-
-### Image Reading and Resizing
-
-When training computer vision models, it is common to test various input sizes for the same architecture to identify the optimal setup.
-This involves preparing the original training image at a higher resolution than required and then resizing it to match the input size during training.
-The `autovi` package includes a class, `KERAS_WRAPPER`, to simplify this process.
-This Keras wrapper class features a method called `image_to_array()`, which reads an image as a `PIL` image using the `pillow` Python package, resizes it to the target input size required by the Keras model, and converts it to a `Numpy` array.
-
-To construct a `KERAS_WRAPPER` object, you need to provide the Keras model as the main argument.
-However, users generally do not need to interact with this class directly, as the `autovi` checker automatically invokes its methods when performing VSS predictions.
-The `image_to_array()` method takes the path to the image file, the target height, and the target width as inputs and returns a `Numpy` array.
-If not specified, the target height and target width will be retrieved from the input layer of the Keras model by the `get_input_height()` and `get_input_width()` method of `KERAS_WRAPPER`.
-
-The following code example demonstrate the way to manually generate the true residual plot, save it as PNG file, and load it back as `Numpy` array.
-
-```r
-wrapper <- keras_wrapper(keras_model = checker$keras_model)  
-input_array <- checker$plot_resid() |> 
-  checker$save_plot() |>
-  wrapper$image_to_array()
-input_array$shape
-```
-
-```{r}
-# If the Keras model can not be loaded
-if (!file.exists("cached_data/autovi_check_demo.rds")) {
-  wrapper <- keras_wrapper(keras_model = checker$keras_model)  
-  input_array <- checker$plot_resid() |> 
-    checker$save_plot() |>
-    wrapper$image_to_array()
-  input_array$shape
-} else {
-  cat("(1, 32, 32, 3)")
-}
-```
-
-### Visual Signal Strength (VSS) Prediction
-
-VSS, as discussed in @li2024automated, estimates the distance between the input residual plot and a theoretically good  residual plot.
-It can be defined in various ways, much like different methods for measuring the distance between two points.
-This will not impact the `autovi` infrastructure as long as the provided Keras model can predict the intended measure.
-
-There are several ways to obtain VSS from the checker, with the most direct being the `vss()` method.
-By default, this method predicts the VSS for the true residual plot.
-If a `ggplot` or a `data.frame`, such as null residuals generated by the `null_method()`, is explicitly provided, the method will use that input to predict VSS accordingly.
-Note that if a `ggplot` is provided, auxiliary inputs must be supplied manually via the `auxiliary` argument, as we assume that auxiliary variables can not be computed directly from a `ggplot`.
-
-Another way to obtain VSS is by calling the `check()` method.
-This comprehensive method perform extensive diagnostics on the true residual plot and store the VSS in the `check_result` field of the checker.
-Additionally, for obtaining VSS for null residual plots and bootstrapped residual plots, there are two specialized methods, `null_vss()` and `boot_vss()`, designed for this purpose respectively.
-
-Calling the `vss()` method without arguments will predict the VSS for the true residual plot and return the result as a single-element `tibble`.
-
-```r
-checker$vss()
-```
-
-```{r}
-if (!file.exists("cached_data/autovi_check_demo_2.rds")) {
-  checker$keras_model <- get_keras_model("vss_phn_32") 
-  saveRDS(checker$vss(), "cached_data/autovi_check_demo_2.rds")
-  checker$vss()
-} else {
-  readRDS("cached_data/autovi_check_demo_2.rds")
-}
-```
-
-Providing a `data.frame` of null residuals or a null residual plot yields the same VSS.
-
-```r
-null_resid <- checker$null_method()
-checker$vss(null_resid)
-```
-
-```{r}
-null_resid <- checker$null_method()
-
-if (!file.exists("cached_data/autovi_check_demo_3.rds")) {
-  checker$keras_model <- get_keras_model("vss_phn_32") 
-  saveRDS(checker$vss(null_resid), "cached_data/autovi_check_demo_3.rds")
-  checker$vss(null_resid)
-} else {
-  readRDS("cached_data/autovi_check_demo_3.rds")
-}
-```
-
-```r
-null_resid |>
-  checker$plot_resid() |>
-  checker$vss()
-```
-
-```{r}
-readRDS("cached_data/autovi_check_demo_3.rds")
-```
-
-The `null_vss()` helper method primarily takes the number of null plots as input.
-If the user wants to use a ad hoc null simulation scheme, it can be provided via the `null_method` argument.
-Intermediate results, including null residuals and null plots, can be returned by enabling `keep_null_data` and `keep_null_plot`.
-The VSS, along with null residuals and null plots, will be stored in a `tibble` with three columns.
-The following code example demonstrates how to predict the VSS for five null residual plots while keeping the intermediate results.
-
-```r
-checker$null_vss(5L, 
-                 keep_null_data = TRUE, 
-                 keep_null_plot = TRUE)
-```
-
-```{r}
-if (!file.exists("cached_data/autovi_check_demo_4.rds")) {
-  checker$keras_model <- get_keras_model("vss_phn_32") 
-  result <- checker$null_vss(5L, 
-                             keep_null_data = TRUE, 
-                             keep_null_plot = TRUE)
-  saveRDS(result, "cached_data/autovi_check_demo_4.rds")
-  result
-} else {
-  readRDS("cached_data/autovi_check_demo_4.rds")
-}
-```
-
-The `boot_vss()` helper method is similar to `null_vss()`, with some differences in argument names.
-The following code example demonstrates how to predict the VSS for five bootstrapped residual plots while keeping the intermediate results.
-
-```r
-checker$boot_vss(5L,
-                 keep_boot_data = TRUE,
-                 keep_boot_plot = TRUE)
-```
-
-```{r}
-if (!file.exists("cached_data/autovi_check_demo_5.rds")) {
-  checker$keras_model <- get_keras_model("vss_phn_32") 
-  result <- checker$boot_vss(5L, 
-                             keep_boot_data = TRUE, 
-                             keep_boot_plot = TRUE)
-  saveRDS(result, "cached_data/autovi_check_demo_5.rds")
-  result
-} else {
-  readRDS("cached_data/autovi_check_demo_5.rds")
-}
-```
-
-### $p$-value Computation
-
-Once we have obtained the VSS from both the true residual plot and the null plots, we can compute the $p$-value.
-This $p$-value represents the ratio of plots with VSS greater than or equal to that of the true residual plot.
-We can perform this calculation using the `check()` method.
-The main inputs for this method are the number of null plots and the number of bootstrapped plots to generate.
-If you need to access intermediate residuals and plots, you can enable the `keep_data` and `keep_plot` options.
-The method stores the final result in the `check_result` field of the object.
-To obtain the p-value using the `check()` method, you can use the following code.
-
-```r
-checker$check(boot_draws = 100L, null_draws = 100L)
-checker$check_result$p_value
-```
-
-```{r}
-if (!file.exists("cached_data/autovi_check_demo_6.rds")) {
-  checker$keras_model <- get_keras_model("vss_phn_32") 
-  checker$check(boot_draws = 100L, null_draws = 100L)
-  saveRDS(checker$check_result, "cached_data/autovi_check_demo_6.rds")
-} else {
-  checker$check_result <- readRDS("cached_data/autovi_check_demo_6.rds")
-}
-
-checker$check_result$p_value
-```
-
-## Summary Plots
-
-After executing the `check()` method, `autovi` offers two visualization options for the assessment result through the `summary_plot()` method, including the density plot and the rank plot.
-We have already discussed and interpreted the density plot in @sec-autovi-usage.
-Here, we would like to highlight the flexibility in choosing which elements to display in the density plot as shown in @fig-autovi-summary-plot-option.
-For instance, you can omit the bootstrapped distribution by setting `boot_dist` to `NULL`.
-Similarly, you can hide the null distribution (`null_dist`), the $p$-value (`p_value`), or the likelihood ratio (`likelihood_ratio`) as needed.
-The following example demonstrates how to create a summary plot without the results from bootstrapped plots.
-
-```{r fig-autovi-summary-plot-option, echo=TRUE, fig.cap = "Density plot of the VSS for null plots."}
-checker$summary_plot(boot_dist = NULL,
-                     likelihood_ratio = NULL)
-```
-
-This customization allows you to focus on specific aspects of the assessment, tailoring the visualization to your analytical needs.
-
-The rank plot (@fig-autovi-rank-plot), creating by setting `type` to "rank", is a bar plot where the $x$-axis represents the rank and the $y$-axis shows the VSS.
-The bar that is coloured in red corresponding to the VSS of the true residual plot.
-By examining the rank plot, you can intuitively understand how the observed VSS compares to the null VSSs and identify any outliers in the null distribution.
-
-```{r fig-autovi-rank-plot, echo=TRUE, fig.cap = "Rank plot of the VSS for null plots."}
-checker$summary_plot(type = "rank")
-```
-
-## Feature Extraction
-
-In addition to predicting VSS and computing $p$-values, `autovi` offers methods to extract features from any layer of the Keras model.
-To see which layers are available in the current Keras model, you can use the `list_layer_name()` method from the `KERAS_WRAPPER` class.
-
-The following code example lists the layer names of the currently used Keras model:
-
-```r
-wrapper <- keras_wrapper(checker$keras_model)
-wrapper$list_layer_name()
-```
-
-```{r}
-if (!file.exists("cached_data/autovi_check_demo_8.rds")) {
-  wrapper <- keras_wrapper(get_keras_model("vss_phn_32"))
-  result <- wrapper$list_layer_name()
-  saveRDS(result, "cached_data/autovi_check_demo_8.rds")
-} else {
-  readRDS("cached_data/autovi_check_demo_8.rds")
-}
-```
-
-Among these layers, the "global_max_pooling2d" layer is a 2D global max pooling layer that outputs the results from the last convolutional blocks.
-As @simonyan2014very noted, all preceding convolutional blocks can be viewed as a large feature extractor.
-Consequently, the output from this layer provides features that can be utilized for various purposes, such as performing transfer learning.
-
-To obtain the features, provide the layer name using the `extract_feature_from_layer` argument in the `predict()` method.
-This will return a `tibble` with the VSS and all features extracted from that layer.
-Each row corresponds to one plot.
-The features will be flattened into 2D and named with the prefix "f_" followed by a number from one to the total number of features.
-
-```r
-checker$plot_resid() |>
-  checker$save_plot() |>
-  wrapper$image_to_array() |>
-  wrapper$predict(auxiliary = checker$auxiliary(),
-                  extract_feature_from_layer = "global_max_pooling2d")
-```
-
-```{r}
-if (!file.exists("cached_data/autovi_check_demo_7.rds")) {
-  checker$keras_model <- get_keras_model("vss_phn_32") 
-  result <- checker$plot_resid() |>
-    checker$save_plot() |>
-    wrapper$image_to_array() |>
-    wrapper$predict(auxiliary = checker$auxiliary(),
-                    extract_feature_from_layer = "global_max_pooling2d")
-  saveRDS(result, "cached_data/autovi_check_demo_7.rds")
-} else {
-  readRDS("cached_data/autovi_check_demo_7.rds")
-}
-```
-
-Alternatively, the `AUTO_VI` class provides a way to extract features using the `vss()` method.
-This method is essentially a high-level wrapper around the `predict()` method of `KERAS_WRAPPER`, but it offers a more straightforward interface and better default arguments.
-
-The results from the previous code example can be replicated with a single line of code as shown below.
-
-```r
-checker$vss(extract_feature_from_layer = "global_max_pooling2d")
-```
-
-```{r}
-readRDS("cached_data/autovi_check_demo_7.rds")
-```
-
-The argument `extract_feature_from_layer` is also available in other functions that build on the `vss()` method, including `null_vss()`, `boot_vss()`, and `check()`.
-
-## Trained Model Hosting {#sec-trained-model-hosting}
-
-The trained computer vision models described in @li2024automated are hosted on a GitHub repository at [https://github.com/TengMCing/autovi_data](https://github.com/TengMCing/autovi_data).
-Currently, there are six models available.
-You can view them by calling `list_keras_model()`, which will return a `tibble` showing the input shape and a description of each model.
-
-```{r echo = TRUE}
-list_keras_model() |>
-  str()
-```
-
-The `get_keras_model()` function can be used to download a model to a temporary directory and load it into memory using `TensorFlow`.
-It requires only the model name, which is the value in the first column of the `tibble` returned by `list_keras_model()`.
--->
-
 # Web interface: autovi.web {#sec-autovi-web}
@@
 Additionally, updates are managed centrally, ensuring that users always have access to the latest features.
-<!--The `autovi.web` interface is available at [autoviweb.netlify.app](autoviweb.netlify.app).--> This section discusses the implementation based on `autovi.web` version 0.1.0.
+This section discusses the implementation based on `autovi.web` version 0.1.0.
 
@@
 
-<!-- ## Design {#sec-autovi-web-design}-->
-
 ```{r fig-autovi-web, out.width = "100%", fig.cap = "Overview of the `autovi.web` graphical user interface (GUI).
@@
 
-<!--The focus of `autovi.web` is on providing a straightforward and clean user interface.
-An overview of the graphical user interface of `autovi.web` is provided in @fig-autovi-web.
-This is the default view of the web application, and there are five regions that user can mainly interact with.
-Region 1 of @fig-autovi-web is a sidebar menu which can switch between the analysis page and the information page.
-The analysis page is the focus of this section.
-
-Region 2 of @fig-autovi-web is a panel for data uploading and CSV type selection.
-Clicking the "upload CSV" button opens a window where the user can select a file from their local system.
-The data status displayed above the button provides information about the number of rows and columns in the current dataset.
-Additionally, there are two example datasets available beneath the "upload CSV" button: one is a lineup example using a CSV file with three columns, and the other is a single plot example using a CSV file with two columns.
-More details about these example datasets are be discussed in @sec-autovi-web-workflow.
-
-While the `autovi` package typically expects a fitted regression model object provided by the user, this approach is impractical for a web interface.
-Saving the R model object to the filesystem involves extra steps and requires users to have specific knowledge, which does not align with the goal of the web application.
-Moreover, the regression model object may contain sensitive, non-shareable data, making it unsuitable for uploading.
-Additionally, model objects are often unnecessarily large, containing extra information not needed for residual diagnostics.
-In contrast, a CSV file is easier to generate using various software programs, not just R.
-CSV files are widely accepted and can be easily viewed and modified using common desktop applications like Excel.
-They are generally less sensitive than raw data, as they exclude most information about the predictors.
-
-The web application is designed to assess either a single residual plot or a lineup of residual plots.
-Therefore, it accepts only two types of CSV files: one with at least two columns representing the fitted values and residuals of a single residual plot, and another with at least three columns, where the additional column serves as the label or identifier for a lineup of multiple residual plots.
-For a single residual plot, 19 null plots are generated by simulating normal random draws from a distribution with the same variance as the original residual plot, and comparisons are made with the original residual plot.
-For a lineup, comparisons are made among the plots within the lineup.
-After uploading the CSV file, the user must select the correct format to ensure the web interface interprets the data correctly.
--->
-
 ```{r fig-autovi-web-type, out.width = "100%", fig.cap = "The panels for selecting target columns and simulation settings are updated when a different CSV type is selected in the left panel.
@@
 ```
-
-<!--Region 3 of @fig-autovi-web is a panel for column selection and simulation settings.
-As shown in @fig-autovi-web, if the CSV type is set to a single residual plot, there will be two dropdown menus for specifying the columns for fitted values and residuals, respectively.
-The default variable names for these columns are `.fitted` and `.resid`.
-After uploading the CSV file, the content of these dropdown menus will be updated to reflect the existing columns in the dataset.
-As displayed in @fig-autovi-web-type, for the CSV type that is a lineup of multiple residual plots, an additional dropdown menu will appear for specifying the column of residual plot labels.
-The default variable name for this column is `.sample`.
-If this variable name does not exist in the dataset, the dropdown menu will remain empty, allowing the user to specify the correct column.
-The number of levels for each option in this dropdown menu will be displayed to help avoid the selection of a variable with too many levels, which could significantly slow down the application due to extensive computation.
-
-Under the simulation settings, there is a slider for specifying the number of bootstrapped samples needed for the assessment.
-A higher value on this slider will result in a more accurate bootstrap distribution estimation, though it will require more computation time.
-The simulation seed can be set in a numeric input box below the slider to control the reproducibility of the assessment.
-By default, a random seed is set each time the web page is refreshed.
-When the CSV type is a lineup of multiple residual plots, an optional dropdown menu will appear next to the simulation seed input box, allowing the user to specify an identifier for the true residual plot.
-If no label is provided for the true residual plot, the assessment will only estimate the VSS for each residual plot in the lineup, without providing a $p$-value, as it cannot be computed.
-Consequently, some result panels may be missing due to insufficient information.
-This option is useful when the lineup consists solely of null plots or if the user simply wants to obtain the VSS for multiple residual plots.
-
-Region 4 of @fig-autovi-web is the panel for triggering the assessment.
-It contains a large play button to start the assessment.
-Above the play button, a text message displays the status of `TensorFlow.js`, allowing users to monitor whether the JavaScript library and Keras model have been loaded correctly.
-The play button will remain disabled until both the data status in Region 1 and the `TensorFlow.js` status in Region 4 indicate that everything is ready, with both showing a green status.
-
-Once the play button is clicked, region 5 of @fig-autovi-web will be populated with panels displaying the assessment results.
-Generally, there will be four result panels, as shown in @fig-autovi-web-result and @fig-autovi-web-result2.
--->
 
@@
 ```
-
-<!-- Region 6 of @fig-autovi-web-result contains an interactive table created with the R package `DT` [@dt], which provides the VSS.
-This table includes four columns: `.sample`, `vss`, `rank`, and `null`.
-The `.sample` column shows the residual plot labels.
-For a CSV type that is a lineup, these labels are taken from an identifier column in the dataset specified by the user.
-In the case of the CSV type is a single residual plot, labels are automatically generated from 1 to 20, with the true residual plot receiving a randomly assigned label.
-The `vss` column displays the VSS for each residual plot, rounded to three decimal places.
-The `rank` column indicates the ranking of each residual plot based on VSS.
-The `null` column reveals whether the plot is a null plot.
-For the CSV type that is a single residual plot, only the true residual plot will have "false" in this column, while all other plots will be marked "true." For the CSV type that is a lineup, if the true residual plot identifier has not been provided, this column will show "NA" to represent missing values.
-If the identifier is provided by user, the column behaves as if the CSV type is a single residual plot.
-
-The `DT` table provides several interactive features.
-Users can download the table in four formats, including text, CSV, Excel, and PDF, using the buttons located above the table.
-Additionally, the table is searchable via the text input field also positioned above it.
-Below the table, a text message displays the $p$-value of the assessment for the true residual plot and summarizes the number of null plots with VSS greater than that of the true residual plot.
-This helps the user determine whether the true residual plot shows visual patterns that suggest model violations.
-
-Region 7 of @fig-autovi-web-result provides a lineup of plots corresponding to each `.sample` value from the table in Region 6.
-Due to space limitations, a maximum of 20 residual plots will be displayed, ensuring that the true residual plot, if known, will be included in the lineup.
-The plots are generated using `ggplot2`, the same as in `autovi`.
-Users can perform a visual test with this lineup to check if the true residual plot is distinguishable from the other plots, helping to determine the significance of model violations.
-
-Region 8 of @fig-autovi-web-result2 displays the density plot for bootstrapped VSS and null VSS.
-The densities are shown in distinct colors that are friendly for colorblind users.
-A solid vertical line marks the VSS of the true residual plot, while rug lines at the bottom of the plot provide a clearer view of individual cases.
-Below the plot, a text message indicates the number and percentage of bootstrapped residual plots that would be rejected by the visual test when compared to the null plots.
-Note that the bootstrapped residual plots in this application are generated differently from `autovi`.
-Since we do not have the R model object, we can not refit the regression model with bootstrapped data.
-Instead, we bootstrap the residuals of the true residual plot directly to obtain bootstrapped residual plots.
-As as result, this panel will disappear when the true residual plot is unknown.
-
-Region 9 of @fig-autovi-web-result2 displays an attention map for the true residual plot, generated by computing the gradient of the Keras model's output with respect to the greyscale input of the plot.
-The attention map helps to understand how the Keras model predicts VSS and which areas it is focusing on.
-We use a greyscale input because it is easier to generate a clear attention map in this format, and it usually conveys all the essential information, as most of the important details of the plot are drawn in black.
-If the $p$-value of the true residual plot is greater than 0.05, checking the attention map is not necessary.
-However, to provide users with the option to review it if they wish, a button will be available, as shown in @fig-autovi-web-gradient-hide.
-This button allows users to toggle the display of the attention map.-->
 
@@
 
-Results are provided in multiple panels.<!-- as displayed in @fig-autovi-web-workflow-example3, @fig-autovi-web-workflow-example4, @fig-autovi-web-workflow-example5 and @fig-autovi-web-workflow-example6.
-In @fig-autovi-web-workflow-example3--> The first row of the table [@fig-autovi-web-lineup] is the most crucial to check, as it provides the VSS and the rank of the true residual plot among the other plots.
+Results are provided in multiple panels.
+The first row of the table [@fig-autovi-web-lineup] is the most crucial to check, as it provides the VSS and the rank of the true residual plot among the other plots.
 The summary text beneath the table provides the $p$-value, which can be used for quick decision-making.

### 2025-09-04 autovi_paper.tex
Fix the format for packages/software

--- 2025-05-12 autovi_paper.tex
@@
 subjectivity but requires even more human effort. In today's data-driven
-world, such tasks are well-suited for automation. We present a new R
-package that uses a computer vision model to automate the evaluation of
-residual plots. An accompanying Shiny app is provided for ease of use.
-Given a sample of residuals, the model predicts a visual signal strength
-(VSS) and offers supporting information to help analysts assess model
-fit.
+world, such tasks are well-suited for automation. We present a new
+\textsf{R} package that uses a computer vision model to automate the
+evaluation of residual plots. An accompanying \textsf{Shiny} app is
+provided for ease of use. Given a sample of residuals, the model
+predicts a visual signal strength (VSS) and offers supporting
+information to help analysts assess model fit.
 \end{abstract}
@@
 regression modeling and generating diagnostics. The package
-\texttt{lmtest} \citep{lmtest} provides a suite of conventional tests,
-while the \texttt{stats} package \citep{stats} offers standard
+\textsf{lmtest} \citep{lmtest} provides a suite of conventional tests,
+while the \textsf{stats} package \citep{stats} offers standard
 diagnostic plots such as residuals vs.~fitted values, quantile-quantile
 (Q-Q) plots, and residuals vs.~leverage plots. Additional packages like
-\texttt{jtools} \citep{jtools}, \texttt{olsrr} \citep{olsrr},
-\texttt{rockchalk} \citep{rockchalk}, and \texttt{ggResidpanel}
+\textsf{jtools} \citep{jtools}, \textsf{olsrr} \citep{olsrr},
+\textsf{rockchalk} \citep{rockchalk}, and \textsf{ggResidpanel}
 \citep{ggresidpanel} deliver similar graphical diagnostics, often with
@@
 produce the core diagnostic plots outlined in the classical text by
-\citet{cook1982residuals}. The \texttt{ecostats} package
+\citet{cook1982residuals}. The \textsf{ecostats} package
 \citep{warton_global_2023} extends these diagnostics by incorporating
-simulation envelopes into residual plots. Meanwhile, \texttt{DHARMa}
+simulation envelopes into residual plots. Meanwhile, \textsf{DHARMa}
 \citep{dharma} compares empirical quantiles (0.25, 0.5, and 0.75) of
@@
 assessments of residual patterns than conventional tests, as they are
-less sensitive to minor departures. Packages such as \texttt{nullabor}
-\citep{nullabor}, \texttt{HLMdiag} \citep{loy2014hlmdiag}, and
-\texttt{regressinator} \citep{regressinator} support this approach by
+less sensitive to minor departures. Packages such as \textsf{nullabor}
+\citep{nullabor}, \textsf{HLMdiag} \citep{loy2014hlmdiag}, and
+\textsf{regressinator} \citep{regressinator} support this approach by
 enabling users to compare observed residual plots with plots generated
@@
 To make the statistical testing procedure and trained computer vision
-model widely accessible, we developed the R package \texttt{autovi}
-along with a companion web interface, \texttt{autovi.web}, which allows
+model widely accessible, we developed the R package \textsf{autovi}
+along with a companion web interface, \textsf{autovi.web}, which allows
 users to automatically assess their residual plots using the trained
@@
 Section~\ref{sec-vss-desc} introduces the definition and computation of
-visual signal strength. Section~\ref{sec-autovi} provides a detailed
-documentation of the \texttt{autovi} package, including its usage and
-infrastructure. Section~\ref{sec-autovi-web} focuses on the
-\texttt{autovi.web} interface, describing its design and usage, along
-with illustrative examples. Finally, Section~\ref{sec-autovi-conclusion}
-presents the main conclusions of this work.
+visual signal strength. Section~\ref{sec-null-and-boot-desc} expands on
+the computation of the null and bootstrapped residuals.
+Section~\ref{sec-autovi} provides a detailed documentation of the
+\textsf{autovi} package, including its usage and infrastructure.
+Section~\ref{sec-autovi-web} focuses on the \textsf{autovi.web}
+interface, describing its design and usage, along with illustrative
+examples. Finally, Section~\ref{sec-autovi-conclusion} presents the main
+conclusions of this work.
 

### 2025-09-04 autovi_paper.qmd
Fix the title

@@
 ---
-title: "Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web"
+title: Automated residual plot assessment with the R package \textsf{autovi} and the Shiny app \textsf{autovi.web}
 format:

### 2025-09-04 autovi_paper.tex
Fix the title

@@
 \hypersetup{
-  pdftitle={Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web},
+  pdftitle={Automated residual plot assessment with the R package  and the Shiny app },
   pdfauthor={Weihao Li; Dianne Cook; Emi Tanaka; Susan VanderPlas; Klaus Ackermann},
@@
 
-\title{Automated Residual Plot Assessment with the R Package autovi and
-the Shiny App autovi.web}
+\title{Automated residual plot assessment with the R package
+\textsf{autovi} and the Shiny app \textsf{autovi.web}}
 

### 2025-09-04 autovi_paper.qmd
Fix math notaion and some packages

--- 2025-09-04 autovi_paper.qmd
@@
 ---
-title: "Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web"
+title: Automated residual plot assessment with the \textsf{R} package \textsf{autovi} and the \textsf{Shiny} app \textsf{autovi.web}
 format:
@@
 
-To make the statistical testing procedure and trained computer vision model widely accessible, we developed the R package \textsf{autovi} along with a companion web interface, \textsf{autovi.web}, which allows users to automatically assess their residual plots using the trained computer vision model.
+To make the statistical testing procedure and trained computer vision model widely accessible, we developed the \textsf{R} package \textsf{autovi} along with a companion web interface, \textsf{autovi.web}, which allows users to automatically assess their residual plots using the trained computer vision model.
 
@@
 
-In the context of regression model diagnostics, VSS describes the clarity of visual patterns on a diagnostic plot that may indicate model violations.
+In the context of classical normal linear regression model diagnostics, VSS describes the clarity of visual patterns on a diagnostic plot that may indicate model violations.
 Violations can be categorized as weak, moderate, or strong, but here we treat it as a continuous positive real variable.
@@
 \begin{equation} \label{eq:kl-1}
-D_{KL} = \int_{\mathbb{R}^{n}}\log\frac{p(\boldsymbol{e})}{q(\boldsymbol{e})}p(\boldsymbol{e})d\boldsymbol{e},
+D_{KL} = \int_{\mathbb{R}^{n}}\log\frac{p(\hat{\boldsymbol{e}})}{q(\hat{\boldsymbol{e}})}p(\hat{\boldsymbol{e}})d\hat{\boldsymbol{e}},
 \end{equation}
 
-here, $p(.)$ and $q(.)$ are the probability density functions of the reference residual distribution $P$ and the true residual distribution $Q$, respectively.
+here, $\hat{\boldsymbol{e}}$ denotes the residual vector from the regression model, and $p(\cdot)$ and $q(\cdot)$ are the probability density functions of the reference residual distribution $\mathrm{P}$ and the true residual distribution $\mathrm{Q}$, respectively.
 
 This distance measure depends on knowledge of the true residual distribution, which is unknown in practice.
-To compute $D_{KL}$ for the training samples, Equation \ref{eq:kl-1} takes different forms depending on the specific model violations.
+To compute $D_{KL}$ for the training samples, Equation (\ref{eq:kl-1}) takes different forms depending on the specific model violations.
 For instance, where necessary higher-order predictors, $\boldsymbol{Z}$, and their corresponding parameter, $\boldsymbol{\beta}_Z$, are omitted from the fitted linear model, the distance measure can be expanded as follows:
@@
 
-# R package: autovi {#sec-autovi}
+# \textsf{R} package: autovi {#sec-autovi}
 
@@
 The name `autovi` stands for **auto**mated **v**isual **i**nference.
-This functionality can be accessed through the R package `autovi`, or through a web interface, `autovi.web`, which enables users to perform analyses without installing R, Python, or their associated dependencies locally.
+This functionality can be accessed through the \textsf{R} package `autovi`, or through a web interface, `autovi.web`, which enables users to perform analyses without installing \textsf{R}, \textsf{Python}, or their associated dependencies locally.
 
@@
 The `autovi` infrastructure effectively integrates multiple programming languages and libraries into a comprehensive analytical tool.
-It relies on five core libraries from Python and R, each playing a critical role in the analysis pipeline.
-In Python, `pillow` [@clark2015pillow] handles image processing tasks such as reading and resizing PNG files of residual plots, then converting them into input tensors for further analysis.
+It relies on five core libraries from \textsf{Python} and \textsf{R}, each playing a critical role in the analysis pipeline.
+In \textsf{Python}, `pillow` [@clark2015pillow] handles image processing tasks such as reading and resizing PNG files of residual plots, then converting them into input tensors for further analysis.
 `TensorFlow` [@abadi2016tensorflow], a key component of modern machine learning, is used to predict the VSS of these plots using a pre-trained convolutional neural network.
 
-In the R environment, `autovi` utilizes several libraries.
+In the \textsf{R} environment, `autovi` utilizes several libraries.
 `ggplot2` [@ggplot2] generates the initial residual plots, saved as PNG files for visual input.
@@
 These scagnostics complement the visual analysis by offering quantitative metrics as secondary input to the computer vision model.
-`reticulate` [@reticulate]  enables seamless communication between R and Python.
+`reticulate` [@reticulate]  enables seamless communication between \textsf{R} and \textsf{Python}.
 
@@
 The `autovi` package is available on CRAN. It is actively developed and maintained, with the latest updates accessible on GitHub. This paper uses `autovi` version 0.4.2.
-The package includes internal functions to check the current Python environment used by the `reticulate` package.
-If the necessary Python packages are not installed in the Python interpreter, an error will be raised.
-If you want to select a specific Python environment, you can do so by calling the `reticulate::use_python()` function before using the `autovi` package.
+The package includes internal functions to check the current \textsf{Python} environment used by the `reticulate` package.
+If the necessary \textsf{Python} packages are not installed in the \textsf{Python} interpreter, an error will be raised.
+If you want to select a specific \textsf{Python} environment, you can do so by calling the `reticulate::use_python()` function before using the `autovi` package.
 
-We recommend using the Shiny app `autovi.web` if users encounter installation problems.
+We recommend using the \textsf{Shiny} app `autovi.web` if users encounter installation problems.
 
@@
 #| label: fig-autovi-diag
-#| fig-cap: "Diagram illustrating the infrastructure of the R package \\texttt{autovi}.
+#| fig-cap: "Diagram illustrating the infrastructure of the \textsf{R} package \\texttt{autovi}.
 The modules in green are primary inputs provided by users.
@@
 
-The `autovi` R package can be extended to accommodate other classes of models beyond linear regression, such as generalized linear models (`glm`).
+The `autovi` \textsf{R} package can be extended to accommodate other classes of models beyond linear regression, such as generalized linear models (`glm`).
 This is achieved by substituting the relevant overridable modules, and if needed, supplying a different `Keras` model.
@@
 
-The `autovi.web` shiny application extends the functionality of `autovi` by offering a user-friendly web interface for automated residual plot assessment.
-This eliminates the common challenges associated with software installation, so users can avoid managing Python environments or handling version requirements for R libraries.
-The platform is cross-platform and accessible on various devices and operating systems, making it suitable even for users without R programming experience.
+The `autovi.web` \textsf{Shiny} application extends the functionality of `autovi` by offering a user-friendly web interface for automated residual plot assessment.
+This eliminates the common challenges associated with software installation, so users can avoid managing \textsf{Python} environments or handling version requirements for \textsf{R} libraries.
+The platform is cross-platform and accessible on various devices and operating systems, making it suitable even for users without \textsf{R} programming experience.
 Additionally, updates are managed centrally, ensuring that users always have access to the latest features.
@@
 
-The interface `autovi.web` is built using the `shiny` [@shiny] and `shinydashboard` [@shinydashboard] R packages.
+The interface `autovi.web` is built using the `shiny` [@shiny] and `shinydashboard` [@shinydashboard] \textsf{R} packages.
 Hosted on the [shinyapps.io](https://www.shinyapps.io) domain, the application is accessible through any modern web browser.
-The R packages `htmltools` [@htmltools] and `shinycssloaders` [@shinycssloaders] are used to render markdown documentation in shiny application, and for loading animations for shiny widgets, respectively.
+The \textsf{R} packages `htmltools` [@htmltools] and `shinycssloaders` [@shinycssloaders] are used to render markdown documentation in \textsf{Shiny} application, and for loading animations for \textsf{Shiny} widgets, respectively.
 
@@
 
-We also explored the possibility of implementing the web interface using frameworks built on other languages, such as Python.
-However, server hosting domains that natively support Python servers typically do not have the latest version of R installed.
-Additionally, calling R from Python is typically done using the `rpy2` Python library [@rpy2], but this approach can be awkward when dealing with language syntax related to non-standard evaluation.
+We also explored the possibility of implementing the web interface using frameworks built on other languages, such as \textsf{Python}.
+However, server hosting domains that natively support \textsf{Python} servers typically do not have the latest version of \textsf{R} installed.
+Additionally, calling \textsf{R} from \textsf{Python} is typically done using the `rpy2` \textsf{Python} library [@rpy2], but this approach can be awkward when dealing with language syntax related to non-standard evaluation.
 Another option we considered was renting a server where we could have full control, such as those provided by cloud platforms like Google Cloud Platform (GCP) or Amazon Web Services (AWS).
 However, deploying and maintaining the server securely requires some expertise.
-Ultimately, the most practical solution was to use the `shiny` and `shinydashboard` frameworks, which are well-established in the R community and offer a solid foundation for web application development.
+Ultimately, the most practical solution was to use the `shiny` and `shinydashboard` frameworks, which are well-established in the \textsf{R} community and offer a solid foundation for web application development.
 
 The server-side configuration of `autovi.web` is carefully designed to support its functionality.
-Most required Python libraries, including `pillow` and `numpy`, are pre-installed on the server.
-These libraries are integrated into the Shiny application using the `reticulate` package, which provides an interface between R and Python.
+Most required \textsf{Python} libraries, including `pillow` and `numpy`, are pre-installed on the server.
+These libraries are integrated into the \textsf{Shiny} application using the `reticulate` package, which provides an interface between \textsf{R} and \textsf{Python}.
 
-Due to shinyapps.io's resource policy, inactive servers enter sleep mode, clearing the local Python environment.
+Due to shinyapps.io's resource policy, inactive servers enter sleep mode, clearing the local \textsf{Python} environment.
 When reactivated for a new session, libraries must be reinstalled.
@@
 While `autovi` requires downloading the pre-trained computer vision models from GitHub, these models in ".keras" file format are incompatible with `TensorFlow.js`.
-Therefore, we extract and store the model weights in JSON files and include them as extra resources in the Shiny application.
+Therefore, we extract and store the model weights in JSON files and include them as extra resources in the \textsf{Shiny} application.
 When the application initializes, `TensorFlow.js` rebuilds the computer vision model using these pre-stored weights.
 
-To allow communication between `TensorFlow.js` and other components of the Shiny application, the `shinyjs` R package [@shinyjs] is used.
-This package allows calling custom JavaScript code within the Shiny framework.
-The specialized JavaScript code for initializing `TensorFlow.js` and calling `TensorFlow.js` for VSS prediction is deployed alongside the Shiny application as additional resources.
+To allow communication between `TensorFlow.js` and other components of the \textsf{Shiny} application, the `shinyjs` \textsf{R} package [@shinyjs] is used.
+This package allows calling custom JavaScript code within the \textsf{Shiny} framework.
+The specialized JavaScript code for initializing `TensorFlow.js` and calling `TensorFlow.js` for VSS prediction is deployed alongside the \textsf{Shiny} application as additional resources.
 
@@
 There are two example datasets provided by the web application.
-The single residual plot example uses the `dino` dataset from the R package `datasauRus` [@datasaurus].
+The single residual plot example uses the `dino` dataset from the \textsf{R} package `datasauRus` [@datasaurus].
 The lineup example uses residuals from a simulated regression model that has a non-linearity issue.
@@
 
-This paper presents new regression diagnostics software, the R package `autovi` and its accompanying web interface, `autovi.web`.
+This paper presents new regression diagnostics software, the \textsf{R} package `autovi` and its accompanying web interface, `autovi.web`.
 It addresses a critical gap in the current landscape of statistical software.
@@
 
-The `autovi` R package, introduced in this paper, automates the assessment of residual plots by incorporating a computer vision model, reducing reliance on time-consuming and potentially inconsistent human interpretation.
+The `autovi` \textsf{R} package, introduced in this paper, automates the assessment of residual plots by incorporating a computer vision model, reducing reliance on time-consuming and potentially inconsistent human interpretation.
 This automation improves the efficiency of the diagnostic process and promotes consistency in model evaluation across different users and studies.
 
-The development of the accompanying Shiny app, `autovi.web`, expands access to these advanced diagnostic tools, by providing a user-friendly interface.
+The development of the accompanying \textsf{Shiny} app, `autovi.web`, expands access to these advanced diagnostic tools, by providing a user-friendly interface.
 It makes automated residual plot assessment accessible to a broader audience, including those who may not have extensive programming experience.
@@
 
-The current version of `autovi` can be installed from CRAN, and source code for both packages are available at [`github.com/TengMCing/autovi`](https://github.com/TengMCing/autovi) and [`github.com/TengMCing/autovi_web`](https://github.com/TengMCing/autovi_web) respectively.
+The current version of \textsf{autovi} can be installed from CRAN, and source code for both packages are available at [`github.com/TengMCing/autovi`](https://github.com/TengMCing/autovi) and [`github.com/TengMCing/autovi_web`](https://github.com/TengMCing/autovi_web) respectively.
 The web interface is available from [`autoviweb.netlify.app`](https://autoviweb.netlify.app/).
@@
 
-These `R` packages were used for the work: `tidyverse` [@tidyverse], `lmtest` [@lmtest], `kableExtra` [@kableextra], `patchwork` [@patchwork], `rcartocolor` [@rcartocolor], `glue` [@glue],  `here` [@here], `magick` [@magick], `yardstick` [@yardstick] and `reticulate` [@reticulate].
+These \textsf{R} packages were used for the work: \textsf{tidyverse} [@tidyverse], \textsf{lmtest} [@lmtest], \textsf{kableExtra} [@kableextra], \textsf{patchwork} [@patchwork], \textsf{rcartocolor} [@rcartocolor], \textsf{glue} [@glue],  \textsf{here} [@here], \textsf{magick} [@magick], \textsf{yardstick} [@yardstick] and \textsf{reticulate} [@reticulate].

### 2025-09-04 autovi_paper.tex
Fix math notaion and some packages

@@
 \hypersetup{
-  pdftitle={Automated residual plot assessment with the R package  and the Shiny app },
+  pdftitle={Automated residual plot assessment with the  package  and the  app },
   pdfauthor={Weihao Li; Dianne Cook; Emi Tanaka; Susan VanderPlas; Klaus Ackermann},
@@
 
-\title{Automated residual plot assessment with the R package
-\textsf{autovi} and the Shiny app \textsf{autovi.web}}
+\title{Automated residual plot assessment with the \textsf{R} package
+\textsf{autovi} and the \textsf{Shiny} app \textsf{autovi.web}}
 
@@
 To make the statistical testing procedure and trained computer vision
-model widely accessible, we developed the R package \textsf{autovi}
-along with a companion web interface, \textsf{autovi.web}, which allows
-users to automatically assess their residual plots using the trained
-computer vision model.
+model widely accessible, we developed the \textsf{R} package
+\textsf{autovi} along with a companion web interface,
+\textsf{autovi.web}, which allows users to automatically assess their
+residual plots using the trained computer vision model.
 
@@
 
-In the context of regression model diagnostics, VSS describes the
-clarity of visual patterns on a diagnostic plot that may indicate model
-violations. Violations can be categorized as weak, moderate, or strong,
-but here we treat it as a continuous positive real variable.
-Importantly, its interpretation depends on how it is linked to a
-function of the data or the underlying data generating process.
+In the context of classical normal linear regression model diagnostics,
+VSS describes the clarity of visual patterns on a diagnostic plot that
+may indicate model violations. Violations can be categorized as weak,
+moderate, or strong, but here we treat it as a continuous positive real
+variable. Importantly, its interpretation depends on how it is linked to
+a function of the data or the underlying data generating process.
 Consequently, the calculation of VSS can vary across different model
@@
 \begin{equation} \label{eq:kl-1}
-D_{KL} = \int_{\mathbb{R}^{n}}\log\frac{p(\boldsymbol{e})}{q(\boldsymbol{e})}p(\boldsymbol{e})d\boldsymbol{e},
+D_{KL} = \int_{\mathbb{R}^{n}}\log\frac{p(\hat{\boldsymbol{e}})}{q(\hat{\boldsymbol{e}})}p(\hat{\boldsymbol{e}})d\hat{\boldsymbol{e}},
 \end{equation}
 
-here, \(p(.)\) and \(q(.)\) are the probability density functions of the
-reference residual distribution \(P\) and the true residual distribution
-\(Q\), respectively.
+here, \(\hat{\boldsymbol{e}}\) denotes the residual vector from the
+regression model, and \(p(\cdot)\) and \(q(\cdot)\) are the probability
+density functions of the reference residual distribution \(\mathrm{P}\)
+and the true residual distribution \(\mathrm{Q}\), respectively.
 
@@
 distribution, which is unknown in practice. To compute \(D_{KL}\) for
-the training samples, Equation \ref{eq:kl-1} takes different forms
+the training samples, Equation (\ref{eq:kl-1}) takes different forms
 depending on the specific model violations. For instance, where
@@
 
-\section{R package: autovi}\label{sec-autovi}
+\section{\texorpdfstring{\textsf{R} package:
+autovi}{ package: autovi}}\label{sec-autovi}
 
@@
 \texttt{autovi} stands for \textbf{auto}mated \textbf{v}isual
-\textbf{i}nference. This functionality can be accessed through the R
-package \texttt{autovi}, or through a web interface,
+\textbf{i}nference. This functionality can be accessed through the
+\textsf{R} package \texttt{autovi}, or through a web interface,
 \texttt{autovi.web}, which enables users to perform analyses without
-installing R, Python, or their associated dependencies locally.
+installing \textsf{R}, \textsf{Python}, or their associated dependencies
+locally.
 
@@
 programming languages and libraries into a comprehensive analytical
-tool. It relies on five core libraries from Python and R, each playing a
-critical role in the analysis pipeline. In Python, \texttt{pillow}
-\citep{clark2015pillow} handles image processing tasks such as reading
-and resizing PNG files of residual plots, then converting them into
-input tensors for further analysis. \texttt{TensorFlow}
-\citep{abadi2016tensorflow}, a key component of modern machine learning,
-is used to predict the VSS of these plots using a pre-trained
-convolutional neural network.
-
-In the R environment, \texttt{autovi} utilizes several libraries.
-\texttt{ggplot2} \citep{ggplot2} generates the initial residual plots,
-saved as PNG files for visual input. \texttt{cassowaryr}
+tool. It relies on five core libraries from \textsf{Python} and
+\textsf{R}, each playing a critical role in the analysis pipeline. In
+\textsf{Python}, \texttt{pillow} \citep{clark2015pillow} handles image
+processing tasks such as reading and resizing PNG files of residual
+plots, then converting them into input tensors for further analysis.
+\texttt{TensorFlow} \citep{abadi2016tensorflow}, a key component of
+modern machine learning, is used to predict the VSS of these plots using
+a pre-trained convolutional neural network.
+
+In the \textsf{R} environment, \texttt{autovi} utilizes several
+libraries. \texttt{ggplot2} \citep{ggplot2} generates the initial
+residual plots, saved as PNG files for visual input. \texttt{cassowaryr}
 \citep{mason2022cassowaryr} computes scagnostics (scatter plot
@@
 computer vision model. \texttt{reticulate} \citep{reticulate} enables
-seamless communication between R and Python.
+seamless communication between \textsf{R} and \textsf{Python}.
 
@@
 This paper uses \texttt{autovi} version 0.4.2. The package includes
-internal functions to check the current Python environment used by the
-\texttt{reticulate} package. If the necessary Python packages are not
-installed in the Python interpreter, an error will be raised. If you
-want to select a specific Python environment, you can do so by calling
-the \texttt{reticulate::use\_python()} function before using the
+internal functions to check the current \textsf{Python} environment used
+by the \texttt{reticulate} package. If the necessary \textsf{Python}
+packages are not installed in the \textsf{Python} interpreter, an error
+will be raised. If you want to select a specific \textsf{Python}
+environment, you can do so by calling the
+\texttt{reticulate::use\_python()} function before using the
 \texttt{autovi} package.
 
-We recommend using the Shiny app \texttt{autovi.web} if users encounter
-installation problems.
+We recommend using the \textsf{Shiny} app \texttt{autovi.web} if users
+encounter installation problems.
 
@@
 \caption{\label{fig-autovi-diag}Diagram illustrating the infrastructure
-of the R package \texttt{autovi}. The modules in green are primary
-inputs provided by users. Modules in blue are overridable methods that
-can be modified to accommodate users' specific needs. The module in
-yellow is a pre-defined non-overridable method. The modules in red are
-primary outputs of the package.}
+of the extsf\{R\} package \texttt{autovi}. The modules in green are
+primary inputs provided by users. Modules in blue are overridable
+methods that can be modified to accommodate users' specific needs. The
+module in yellow is a pre-defined non-overridable method. The modules in
+red are primary outputs of the package.}
 
@@
 
-The \texttt{autovi} R package can be extended to accommodate other
-classes of models beyond linear regression, such as generalized linear
-models (\texttt{glm}). This is achieved by substituting the relevant
-overridable modules, and if needed, supplying a different \texttt{Keras}
-model.
+The \texttt{autovi} \textsf{R} package can be extended to accommodate
+other classes of models beyond linear regression, such as generalized
+linear models (\texttt{glm}). This is achieved by substituting the
+relevant overridable modules, and if needed, supplying a different
+\texttt{Keras} model.
 
@@
 
-The \texttt{autovi.web} shiny application extends the functionality of
-\texttt{autovi} by offering a user-friendly web interface for automated
-residual plot assessment. This eliminates the common challenges
-associated with software installation, so users can avoid managing
-Python environments or handling version requirements for R libraries.
-The platform is cross-platform and accessible on various devices and
-operating systems, making it suitable even for users without R
-programming experience. Additionally, updates are managed centrally,
-ensuring that users always have access to the latest features. This
-section discusses the implementation based on \texttt{autovi.web}
-version 0.1.0.
+The \texttt{autovi.web} \textsf{Shiny} application extends the
+functionality of \texttt{autovi} by offering a user-friendly web
+interface for automated residual plot assessment. This eliminates the
+common challenges associated with software installation, so users can
+avoid managing \textsf{Python} environments or handling version
+requirements for \textsf{R} libraries. The platform is cross-platform
+and accessible on various devices and operating systems, making it
+suitable even for users without \textsf{R} programming experience.
+Additionally, updates are managed centrally, ensuring that users always
+have access to the latest features. This section discusses the
+implementation based on \texttt{autovi.web} version 0.1.0.
 
@@
 The interface \texttt{autovi.web} is built using the \texttt{shiny}
-\citep{shiny} and \texttt{shinydashboard} \citep{shinydashboard} R
-packages. Hosted on the \href{https://www.shinyapps.io}{shinyapps.io}
-domain, the application is accessible through any modern web browser.
-The R packages \texttt{htmltools} \citep{htmltools} and
-\texttt{shinycssloaders} \citep{shinycssloaders} are used to render
-markdown documentation in shiny application, and for loading animations
-for shiny widgets, respectively.
+\citep{shiny} and \texttt{shinydashboard} \citep{shinydashboard}
+\textsf{R} packages. Hosted on the
+\href{https://www.shinyapps.io}{shinyapps.io} domain, the application is
+accessible through any modern web browser. The \textsf{R} packages
+\texttt{htmltools} \citep{htmltools} and \texttt{shinycssloaders}
+\citep{shinycssloaders} are used to render markdown documentation in
+\textsf{Shiny} application, and for loading animations for
+\textsf{Shiny} widgets, respectively.
 
@@
 We also explored the possibility of implementing the web interface using
-frameworks built on other languages, such as Python. However, server
-hosting domains that natively support Python servers typically do not
-have the latest version of R installed. Additionally, calling R from
-Python is typically done using the \texttt{rpy2} Python library
-\citep{rpy2}, but this approach can be awkward when dealing with
-language syntax related to non-standard evaluation. Another option we
-considered was renting a server where we could have full control, such
-as those provided by cloud platforms like Google Cloud Platform (GCP) or
-Amazon Web Services (AWS). However, deploying and maintaining the server
-securely requires some expertise. Ultimately, the most practical
-solution was to use the \texttt{shiny} and \texttt{shinydashboard}
-frameworks, which are well-established in the R community and offer a
-solid foundation for web application development.
+frameworks built on other languages, such as \textsf{Python}. However,
+server hosting domains that natively support \textsf{Python} servers
+typically do not have the latest version of \textsf{R} installed.
+Additionally, calling \textsf{R} from \textsf{Python} is typically done
+using the \texttt{rpy2} \textsf{Python} library \citep{rpy2}, but this
+approach can be awkward when dealing with language syntax related to
+non-standard evaluation. Another option we considered was renting a
+server where we could have full control, such as those provided by cloud
+platforms like Google Cloud Platform (GCP) or Amazon Web Services (AWS).
+However, deploying and maintaining the server securely requires some
+expertise. Ultimately, the most practical solution was to use the
+\texttt{shiny} and \texttt{shinydashboard} frameworks, which are
+well-established in the \textsf{R} community and offer a solid
+foundation for web application development.
 
 The server-side configuration of \texttt{autovi.web} is carefully
-designed to support its functionality. Most required Python libraries,
-including \texttt{pillow} and \texttt{numpy}, are pre-installed on the
-server. These libraries are integrated into the Shiny application using
-the \texttt{reticulate} package, which provides an interface between R
-and Python.
+designed to support its functionality. Most required \textsf{Python}
+libraries, including \texttt{pillow} and \texttt{numpy}, are
+pre-installed on the server. These libraries are integrated into the
+\textsf{Shiny} application using the \texttt{reticulate} package, which
+provides an interface between \textsf{R} and \textsf{Python}.
 
 Due to shinyapps.io's resource policy, inactive servers enter sleep
-mode, clearing the local Python environment. When reactivated for a new
-session, libraries must be reinstalled. While this ensures a clean
-environment for each session, it may lead to slightly longer loading
-times for the first user after a period of inactivity.
+mode, clearing the local \textsf{Python} environment. When reactivated
+for a new session, libraries must be reinstalled. While this ensures a
+clean environment for each session, it may lead to slightly longer
+loading times for the first user after a period of inactivity.
 
@@
 store the model weights in JSON files and include them as extra
-resources in the Shiny application. When the application initializes,
-\texttt{TensorFlow.js} rebuilds the computer vision model using these
-pre-stored weights.
+resources in the \textsf{Shiny} application. When the application
+initializes, \texttt{TensorFlow.js} rebuilds the computer vision model
+using these pre-stored weights.
 
 To allow communication between \texttt{TensorFlow.js} and other
-components of the Shiny application, the \texttt{shinyjs} R package
-\citep{shinyjs} is used. This package allows calling custom JavaScript
-code within the Shiny framework. The specialized JavaScript code for
-initializing \texttt{TensorFlow.js} and calling \texttt{TensorFlow.js}
-for VSS prediction is deployed alongside the Shiny application as
-additional resources.
+components of the \textsf{Shiny} application, the \texttt{shinyjs}
+\textsf{R} package \citep{shinyjs} is used. This package allows calling
+custom JavaScript code within the \textsf{Shiny} framework. The
+specialized JavaScript code for initializing \texttt{TensorFlow.js} and
+calling \texttt{TensorFlow.js} for VSS prediction is deployed alongside
+the \textsf{Shiny} application as additional resources.
 
@@
 datasets provided by the web application. The single residual plot
-example uses the \texttt{dino} dataset from the R package
+example uses the \texttt{dino} dataset from the \textsf{R} package
 \texttt{datasauRus} \citep{datasaurus}. The lineup example uses
@@
 
-This paper presents new regression diagnostics software, the R package
-\texttt{autovi} and its accompanying web interface, \texttt{autovi.web}.
-It addresses a critical gap in the current landscape of statistical
-software. While regression tools are widely available, effective and
-efficient diagnostic methods have lagged behind, particularly in the
-field of residual plot interpretation.
-
-The \texttt{autovi} R package, introduced in this paper, automates the
-assessment of residual plots by incorporating a computer vision model,
-reducing reliance on time-consuming and potentially inconsistent human
-interpretation. This automation improves the efficiency of the
-diagnostic process and promotes consistency in model evaluation across
-different users and studies.
-
-The development of the accompanying Shiny app, \texttt{autovi.web},
-expands access to these advanced diagnostic tools, by providing a
-user-friendly interface. It makes automated residual plot assessment
-accessible to a broader audience, including those who may not have
-extensive programming experience. This web-based solution effectively
-addresses the potential barriers to adoption, such as complex
-dependencies and installation requirements, that are often associated
-with advanced statistical software.
+This paper presents new regression diagnostics software, the \textsf{R}
+package \texttt{autovi} and its accompanying web interface,
+\texttt{autovi.web}. It addresses a critical gap in the current
+landscape of statistical software. While regression tools are widely
+available, effective and efficient diagnostic methods have lagged
+behind, particularly in the field of residual plot interpretation.
+
+The \texttt{autovi} \textsf{R} package, introduced in this paper,
+automates the assessment of residual plots by incorporating a computer
+vision model, reducing reliance on time-consuming and potentially
+inconsistent human interpretation. This automation improves the
+efficiency of the diagnostic process and promotes consistency in model
+evaluation across different users and studies.
+
+The development of the accompanying \textsf{Shiny} app,
+\texttt{autovi.web}, expands access to these advanced diagnostic tools,
+by providing a user-friendly interface. It makes automated residual plot
+assessment accessible to a broader audience, including those who may not
+have extensive programming experience. This web-based solution
+effectively addresses the potential barriers to adoption, such as
+complex dependencies and installation requirements, that are often
+associated with advanced statistical software.
 
@@
 
-The current version of \texttt{autovi} can be installed from CRAN, and
+The current version of \textsf{autovi} can be installed from CRAN, and
 source code for both packages are available at
@@
 
-These \texttt{R} packages were used for the work: \texttt{tidyverse}
-\citep{tidyverse}, \texttt{lmtest} \citep{lmtest}, \texttt{kableExtra}
-\citep{kableextra}, \texttt{patchwork} \citep{patchwork},
-\texttt{rcartocolor} \citep{rcartocolor}, \texttt{glue} \citep{glue},
-\texttt{here} \citep{here}, \texttt{magick} \citep{magick},
-\texttt{yardstick} \citep{yardstick} and \texttt{reticulate}
+These \textsf{R} packages were used for the work: \textsf{tidyverse}
+\citep{tidyverse}, \textsf{lmtest} \citep{lmtest}, \textsf{kableExtra}
+\citep{kableextra}, \textsf{patchwork} \citep{patchwork},
+\textsf{rcartocolor} \citep{rcartocolor}, \textsf{glue} \citep{glue},
+\textsf{here} \citep{here}, \textsf{magick} \citep{magick},
+\textsf{yardstick} \citep{yardstick} and \textsf{reticulate}
 \citep{reticulate}.

### 2025-09-06 autovi_paper.qmd
Fix most paper issues

@@
 ---
-title: Automated residual plot assessment with the \textsf{R} package \textsf{autovi} and the \textsf{Shiny} app \textsf{autovi.web}
+title: Automated residual plot assessment with the \textsf{R} package \textsf{autovi} and the \textsf{Shiny} application \textsf{autovi.web}
 format:
@@
 We present a new \textsf{R} package that uses a computer vision model to automate the evaluation of residual plots.
-An accompanying \textsf{Shiny} app is provided for ease of use.
+An accompanying \textsf{Shiny} application is provided for ease of use.
 Given a sample of residuals, the model predicts a visual signal strength (VSS) and offers supporting information to help analysts assess model fit.
@@
   out.width = "100%", 
-  fig.align = "center")
+  fig.align = "center",
+  dev = "pdf")
 ```
@@
 As noted in @li2024automated, the lineup protocol has significant limitations in large-scale applications due to its reliance on human labor.
-To overcome this constraint, a computer vision model was developed alongside a corresponding statistical testing procedure to autmoate the assessment of residual plots.
+To overcome this constraint, a computer vision model was developed alongside a corresponding statistical testing procedure to automate the assessment of residual plots.
 The model takes as input a residual plot and a set of auxiliary variables (such as the number of observations) and outputs a predicted visual signal strength (VSS).
@@
 
-# \textsf{R} package: autovi {#sec-autovi}
+# \textsf{R} package: \textsf{autovi} {#sec-autovi}
 
-The main purpose of `autovi` is to provide rejection decisions and $p$-values for testing the null hypothesis ($H_0$) that the regression model is correctly specified.
+The main purpose of \textsf{autovi} is to provide rejection decisions and $p$-values for testing the null hypothesis ($H_0$) that the regression model is correctly specified.
 The package provides automated interpretation of residual plots using computer vision.
-The name `autovi` stands for **auto**mated **v**isual **i**nference.
-This functionality can be accessed through the \textsf{R} package `autovi`, or through a web interface, `autovi.web`, which enables users to perform analyses without installing \textsf{R}, \textsf{Python}, or their associated dependencies locally.
+The name \textsf{autovi} stands for **auto**mated **v**isual **i**nference.
+This functionality can be accessed through the \textsf{R} package \textsf{autovi}, or through a web interface, \textsf{autovi.web}, which enables users to perform analyses without installing \textsf{R}, \textsf{Python}, or their associated dependencies locally.
 
@@
 Skewness in the predictor variables is generating the apparent heteroscedasticity, where the smaller variance in residuals at larger fitted values is due to smaller sample size only.
-The Breusch-Pagan test  [@breusch1979simple] for heteroscedasticity would also not reject this as good residual plot.
+The Breusch--Pagan test  [@breusch1979simple] for heteroscedasticity would also not reject this as good residual plot.
 
-The data in (b) is generated by fitting a linear model predicting `mpg` based on `hp` using the `datasets::mtcars`.
+The data in (b) is generated by fitting a linear model predicting `mpg` based on `hp` using the \textsf{datasets}`::mtcars`.
 It is a small data set, and there is a hint of nonlinear structure not captured by the model.
@@
 
-The third example is generated using the `surreal` package [@surreal], where structure residuals are embedded in the data.
-In this case, a quote inspired by Tukey, "visual summaries focus on unexpected values", is used to define the residual structure.
+The third example is generated using the \textsf{surreal} package [@surreal], where structure residuals are embedded in the data.
+In this case, a quote inspired by Tukey, 'visual summaries focus on unexpected values', is used to define the residual structure.
 The automated plot reading predicts the VSS to be 5.87, with a $p$-value less than 0.05.
 Visually, the structure is strikingly clear, but a RESET test for nonlinear structure would not report a problem.
-(It would be detected by a Breusch-Pagan for heteroscedasticity and also Shapiro-Wilk test [@shapiro1965analysis] for non-normality.)
+(It would be detected by a Breusch--Pagan for heteroscedasticity and also Shapiro--Wilk test [@shapiro1965analysis] for non-normality.)
 
@@
 #| fig-cap: "Reading residual plots can be a difficult task, particularly for students new to statistical modeling.
-The \\texttt{autovi} package makes it easier.
+The \\textsf{autovi} package makes it easier.
 Here are three examples of residual plots, which may appear to have structure.
@@
 
-The `autovi` package is built on the `bandicoot` object-oriented programming (OOP) system [@bandicoot], marking a departure from R’s traditional S3 generic system.
+The \textsf{autovi} package is built on the \textsf{bandicoot} object-oriented programming (OOP) system [@bandicoot], marking a departure from \textsf{R}’s traditional S3 generic system.
 This OOP architecture enhances flexibility and modularity, allowing users to redefine key functions through method overriding.
 
-The `autovi` infrastructure effectively integrates multiple programming languages and libraries into a comprehensive analytical tool.
+The \textsf{autovi} infrastructure effectively integrates multiple programming languages and libraries into a comprehensive analytical tool.
 It relies on five core libraries from \textsf{Python} and \textsf{R}, each playing a critical role in the analysis pipeline.
-In \textsf{Python}, `pillow` [@clark2015pillow] handles image processing tasks such as reading and resizing PNG files of residual plots, then converting them into input tensors for further analysis.
-`TensorFlow` [@abadi2016tensorflow], a key component of modern machine learning, is used to predict the VSS of these plots using a pre-trained convolutional neural network.
+In \textsf{Python}, \textsf{pillow} [@clark2015pillow] handles image processing tasks such as reading and resizing PNG files of residual plots, then converting them into input tensors for further analysis.
+\textsf{TensorFlow} [@abadi2016tensorflow], a key component of modern machine learning, is used to predict the VSS of these plots using a pre-trained convolutional neural network.
 
-In the \textsf{R} environment, `autovi` utilizes several libraries.
-`ggplot2` [@ggplot2] generates the initial residual plots, saved as PNG files for visual input.
-`cassowaryr` [@mason2022cassowaryr] computes scagnostics (scatter plot diagnostics), providing numerical features that capture statistical properties of the plots.
+In the \textsf{R} environment, \textsf{autovi} utilizes several libraries.
+\textsf{ggplot2} [@ggplot2] generates the initial residual plots, saved as PNG files for visual input.
+\textsf{cassowaryr} [@mason2022cassowaryr] computes scagnostics (scatter plot diagnostics), providing numerical features that capture statistical properties of the plots.
 These scagnostics complement the visual analysis by offering quantitative metrics as secondary input to the computer vision model.
-`reticulate` [@reticulate]  enables seamless communication between \textsf{R} and \textsf{Python}.
+\textsf{reticulate} [@reticulate]  enables seamless communication between \textsf{R} and \textsf{Python}.
 
@@
 
-The `autovi` package is available on CRAN. It is actively developed and maintained, with the latest updates accessible on GitHub. This paper uses `autovi` version 0.4.2.
-The package includes internal functions to check the current \textsf{Python} environment used by the `reticulate` package.
+The \textsf{autovi} package is available on CRAN. It is actively developed and maintained, with the latest updates accessible on GitHub. This paper uses \textsf{autovi} version 0.4.2.
+The package includes internal functions to check the current \textsf{Python} environment used by the \textsf{reticulate} package.
 If the necessary \textsf{Python} packages are not installed in the \textsf{Python} interpreter, an error will be raised.
-If you want to select a specific \textsf{Python} environment, you can do so by calling the `reticulate::use_python()` function before using the `autovi` package.
+If you want to select a specific \textsf{Python} environment, you can do so by calling the \textsf{reticulate}`::use_python()` function before using the \textsf{autovi} package.
 
-We recommend using the \textsf{Shiny} app `autovi.web` if users encounter installation problems.
+We recommend using the \textsf{Shiny} application \textsf{autovi.web} if users encounter installation problems.
 
@@
 
-1. Load the `autovi` package using the `library()` function.
+1. Load the \textsf{autovi} package using the `library()` function.
 2. Create a checker object with a linear regression model.
@@
 #| label: fig-autovi-diag
-#| fig-cap: "Diagram illustrating the infrastructure of the \textsf{R} package \\texttt{autovi}.
+#| fig-cap: "Diagram illustrating the infrastructure of the \\textsf{R} package \\textsf{autovi}.
 The modules in green are primary inputs provided by users.
@@
 The modules in red are primary outputs of the package."
-magick::image_read_pdf("figures/autovi.pdf")
+knitr::include_graphics("figures/autovi.pdf")
 ```
 
-The initial motivation for developing `autovi` was to create a convenient interface for sharing the models described and trained in @li2024automated.
+The initial motivation for developing \textsf{autovi} was to create a convenient interface for sharing the models described and trained in @li2024automated.
 However, recognizing that the classical normal linear regression model represents a restricted class of models, we sought to avoid limiting the potential for future extensions, whether by the original developers or other developers.
 As a result, the package was designed to function seamlessly with linear regression models with minimal modification and few required arguments, while also accommodating other classes of models through partial infrastructure substitution.
-This modular and customizable design allows `autovi` to handle a wide range of residual diagnostics tasks.
+This modular and customisable design allows \textsf{autovi} to handle a wide range of residual diagnostics tasks.
 
-The infrastructure of `autovi` consists of ten core modules: data extraction, bootstrapping and model refitting, fitted values and residuals extraction, auxiliary computation, null residual simulation, plotting, plot saving, image reading and resizing, VSS prediction, and $p$-value computation.
+The infrastructure of \textsf{autovi} consists of ten core modules: data extraction, bootstrapping and model refitting, fitted values and residuals extraction, auxiliary computation, null residual simulation, plotting, plot saving, image reading and resizing, VSS prediction, and $p$-value computation.
 Each module is designed with minimal dependency on the preceding modules, allowing users to customize parts of the infrastructure without affecting its overall integrity.
@@
 
-The package takes regression models and a `Keras` model as primary inputs.
-Modules for VSS prediction and $p$-value computation are fixed but accessible via function arguments, using `TensorFlow` for inference and statistical testing.
-The image loading module is also fixed, using `PIL` to read and resize images based on the `Keras` model’s input shape.
+The package takes regression models and a \textsf{Keras} model as primary inputs.
+Modules for VSS prediction and $p$-value computation are fixed but accessible via function arguments, using \textsf{TensorFlow} for inference and statistical testing.
+The image loading module is also fixed, using \textsf{PIL} to read and resize images based on the \textsf{Keras} model’s input shape.
 The remaining seven modules are overridable, allowing users to adapt the workflow as needed.
@@
 
-## Extension to Other Model Classes
+## Extension to other model classes
 
-The `autovi` \textsf{R} package can be extended to accommodate other classes of models beyond linear regression, such as generalized linear models (`glm`).
-This is achieved by substituting the relevant overridable modules, and if needed, supplying a different `Keras` model.
+The \textsf{autovi} \textsf{R} package can be extended to accommodate other classes of models beyond linear regression, such as generalized linear models (`glm`).
+This is achieved by substituting the relevant overridable modules, and if needed, supplying a different \textsf{Keras} model.
 
@@
 
-It is important to note, however, that the pre-trained computer vision model included in `autovi`, such as `vss_phn_32` (see `list_keras_models()` for the full list of available models), was developed specifically for diagnostics of linear regression.
+It is important to note, however, that the pre-trained computer vision model included in \textsf{autovi}, such as `vss_phn_32` (see `list_keras_models()` for the full list of available models), was developed specifically for diagnostics of linear regression.
 Its applicability to other model classes relies on the assumption that the null residual plots exhibit characteristics broadly consistent with those of well-behaved linear regression residuals, that is, residuals should be approximately randomly scattered around zero, display roughly constant variance across the range of fitted values, and exhibit no discernible structure or curvature.
 If these conditions are not met, or if model violations do not give rise to visually detectable patterns, the validity of the automated diagnostics may be compromised.
-In such cases, users are encouraged to train and apply their own `Keras` models.
+In such cases, users are encouraged to train and apply their own \textsf{Keras} models.
 Detailed guidance on model training and discussion on extending the methodology to other model classes can be found in @li2024automated.
 
-# Web interface: autovi.web {#sec-autovi-web}
+# Web interface: \textsf{autovi.web} {#sec-autovi-web}
 
-The `autovi.web` \textsf{Shiny} application extends the functionality of `autovi` by offering a user-friendly web interface for automated residual plot assessment.
+The \textsf{autovi.web} \textsf{Shiny} application extends the functionality of \textsf{autovi} by offering a user-friendly web interface for automated residual plot assessment.
 This eliminates the common challenges associated with software installation, so users can avoid managing \textsf{Python} environments or handling version requirements for \textsf{R} libraries.
@@
 Additionally, updates are managed centrally, ensuring that users always have access to the latest features.
-This section discusses the implementation based on `autovi.web` version 0.1.0.
+This section discusses the implementation based on \textsf{autovi.web} version 0.1.0.
 
@@
 
-The interface `autovi.web` is built using the `shiny` [@shiny] and `shinydashboard` [@shinydashboard] \textsf{R} packages.
+The interface \textsf{autovi.web} is built using the \textsf{shiny} [@shiny] and \textsf{shinydashboard} [@shinydashboard] \textsf{R} packages.
 Hosted on the [shinyapps.io](https://www.shinyapps.io) domain, the application is accessible through any modern web browser.
-The \textsf{R} packages `htmltools` [@htmltools] and `shinycssloaders` [@shinycssloaders] are used to render markdown documentation in \textsf{Shiny} application, and for loading animations for \textsf{Shiny} widgets, respectively.
+The \textsf{R} packages \textsf{htmltools} [@htmltools] and \textsf{shinycssloaders} [@shinycssloaders] are used to render markdown documentation in \textsf{Shiny} application, and for loading animations for \textsf{Shiny} widgets, respectively.
 
 Determining the best way to implement the backend was difficult.
-In our initial planning for `autovi.web`, we considered implementing the entire web application using the `webr` framework [@webr], which would have allowed the entire application to run directly in the user's browser.
-However, `webr` does not support packages which use compiled fortran code, which is required by `splancs` [@splancs], a dependency of `autovi`.
-In the future, it is possible that a working Emscripten [@zakai2011emscripten] version of this package may allow full `webr` support.
+In our initial planning for \textsf{autovi.web}, we considered implementing the entire web application using the \textsf{webr} framework [@webr], which would have allowed the entire application to run directly in the user's browser.
+However, \textsf{webr} does not support packages which use compiled \textsf{Fortran} code, which is required by \textsf{splancs} [@splancs], a dependency of \textsf{autovi}.
+In the future, it is possible that a working \textsf{Emscripten} [@zakai2011emscripten] version of this package may allow full \textsf{webr} support.
 
@@
 However, server hosting domains that natively support \textsf{Python} servers typically do not have the latest version of \textsf{R} installed.
-Additionally, calling \textsf{R} from \textsf{Python} is typically done using the `rpy2` \textsf{Python} library [@rpy2], but this approach can be awkward when dealing with language syntax related to non-standard evaluation.
+Additionally, calling \textsf{R} from \textsf{Python} is typically done using the \textsf{rpy2} \textsf{Python} library [@rpy2], but this approach can be awkward when dealing with language syntax related to non-standard evaluation.
 Another option we considered was renting a server where we could have full control, such as those provided by cloud platforms like Google Cloud Platform (GCP) or Amazon Web Services (AWS).
 However, deploying and maintaining the server securely requires some expertise.
-Ultimately, the most practical solution was to use the `shiny` and `shinydashboard` frameworks, which are well-established in the \textsf{R} community and offer a solid foundation for web application development.
+Ultimately, the most practical solution was to use the \textsf{shiny} and \textsf{shinydashboard} frameworks, which are well-established in the \textsf{R} community and offer a solid foundation for web application development.
 
-The server-side configuration of `autovi.web` is carefully designed to support its functionality.
-Most required \textsf{Python} libraries, including `pillow` and `numpy`, are pre-installed on the server.
-These libraries are integrated into the \textsf{Shiny} application using the `reticulate` package, which provides an interface between \textsf{R} and \textsf{Python}.
+The server-side configuration of \textsf{autovi.web} is carefully designed to support its functionality.
+Most required \textsf{Python} libraries, including \textsf{pillow} and \textsf{numpy}, are pre-installed on the server.
+These libraries are integrated into the \textsf{Shiny} application using the \textsf{reticulate} package, which provides an interface between \textsf{R} and \textsf{Python}.
 
-Due to shinyapps.io's resource policy, inactive servers enter sleep mode, clearing the local \textsf{Python} environment.
+Due to [shinyapps.io](https://www.shinyapps.io)'s resource policy, inactive servers enter sleep mode, clearing the local \textsf{Python} environment.
 When reactivated for a new session, libraries must be reinstalled.
@@
 
-In contrast to `autovi`, `autovi.web` leverages `TensorFlow.js`, a JavaScript library that allows the execution of machine learning models directly in the browser.
+In contrast to \textsf{autovi}, \textsf{autovi.web} leverages \textsf{TensorFlow.js}, a \textsf{JavaScript} library that allows the execution of machine learning models directly in the browser.
 This choice enables native browser execution, enhancing compatibility across different user environments, and shifts the computational load from the server to the client-side.
-`TensorFlow.js` also offers better scalability and performance, especially when dealing with resource-intensive computer vision models on the web.
+\textsf{TensorFlow.js} also offers better scalability and performance, especially when dealing with resource-intensive computer vision models on the web.
 
-While `autovi` requires downloading the pre-trained computer vision models from GitHub, these models in ".keras" file format are incompatible with `TensorFlow.js`.
+While \textsf{autovi} requires downloading the pre-trained computer vision models from GitHub, these models in '.keras' file format are incompatible with \textsf{TensorFlow.js}.
 Therefore, we extract and store the model weights in JSON files and include them as extra resources in the \textsf{Shiny} application.
-When the application initializes, `TensorFlow.js` rebuilds the computer vision model using these pre-stored weights.
+When the application initializes, \textsf{TensorFlow.js} rebuilds the computer vision model using these pre-stored weights.
 
-To allow communication between `TensorFlow.js` and other components of the \textsf{Shiny} application, the `shinyjs` \textsf{R} package [@shinyjs] is used.
-This package allows calling custom JavaScript code within the \textsf{Shiny} framework.
-The specialized JavaScript code for initializing `TensorFlow.js` and calling `TensorFlow.js` for VSS prediction is deployed alongside the \textsf{Shiny} application as additional resources.
+To allow communication between \textsf{TensorFlow.js} and other components of the \textsf{Shiny} application, the \textsf{shinyjs} \textsf{R} package [@shinyjs] is used.
+This package allows calling custom \textsf{JavaScript} code within the \textsf{Shiny} framework.
+The specialized \textsf{JavaScript} code for initializing \textsf{TensorFlow.js} and calling \textsf{TensorFlow.js} for VSS prediction is deployed alongside the \textsf{Shiny} application as additional resources.
 
-```{r fig-autovi-web, out.width = "100%", fig.cap = "Overview of the `autovi.web` graphical user interface (GUI).
+```{r fig-autovi-web, out.width = "100%", fig.cap = "Overview of the \\textsf{autovi.web} graphical user interface (GUI).
 This default view may change based on user interactions.
@@
 
-The workflow of `autovi.web` is designed to be straightforward, with numbered steps displayed in each panel.
+The workflow of \textsf{autovi.web} is designed to be straightforward, with numbered steps displayed in each panel.
 There are two example datasets provided by the web application.
-The single residual plot example uses the `dino` dataset from the \textsf{R} package `datasauRus` [@datasaurus].
+The single residual plot example uses the `dino` dataset from the \textsf{R} package \textsf{datasauRus} [@datasaurus].
 The lineup example uses residuals from a simulated regression model that has a non-linearity issue.
@@
 Here we illustrate use with lineup example data sets (@fig-autovi-web-setup).
-To use the lineup example data, click the "Use Lineup Example" button.
+To use the lineup example data, click the 'Use Lineup Example' button.
 The data status will then update to show the number of rows and columns in the dataset, and the CSV type will automatically be selected to the correct option.
@@
 
-```{r fig-autovi-web-setup, out.width = "100%", fig.cap = 'To begin the workflow for `autovi` using the lineup example dataset, the user clicks the "Use Lineup Example" button (left) to load the example dataset, during which the data status and CSV type will be automatically updated.
+```{r fig-autovi-web-setup, out.width = "100%", fig.cap = "To begin the workflow for \\textsf{autovi} using the lineup example dataset, the user clicks the 'Use Lineup Example' button (left) to load the example dataset, during which the data status and CSV type will be automatically updated.
 The user must manually select the label for the true residual plot (middle) to compute further results.
-The user initiates the assessment of the lineup example data by clicking the run button (right).'}
-magick::image_read_pdf("figures/autovi_web_setup.pdf")
+The user initiates the assessment of the lineup example data by clicking the run button (right)."}
+knitr::include_graphics("figures/autovi_web_setup.pdf")
 ```
 
-```{r fig-autovi-web-workflow-example1, out.width = "80%", fig.cap = 'To begin the workflow for `autovi` using the lineup example dataset, the user clicks the "Use Lineup Example" button to load the example dataset, during which the data status and CSV type will be automatically updated.', eval=FALSE}
+```{r fig-autovi-web-workflow-example1, out.width = "80%", fig.cap = 'To begin the workflow for \\textsf{autovi} using the lineup example dataset, the user clicks the "Use Lineup Example" button to load the example dataset, during which the data status and CSV type will be automatically updated.', eval=FALSE}
 magick::image_read_pdf("figures/autovi_web_workflow_1.pdf")
@@
 '}
-magick::image_read_pdf("figures/autovi_web_lineup.pdf")
+knitr::include_graphics("figures/autovi_web_lineup.pdf")
 ```
@@
 The attention map (right image) offers insights into whether the computer vision model has captured the intended visual features of the true residual plot.'}
-magick::image_read_pdf("figures/autovi_web_distributions.pdf")
+knitr::include_graphics("figures/autovi_web_distributions.pdf")
 ```
@@
 
-This paper presents new regression diagnostics software, the \textsf{R} package `autovi` and its accompanying web interface, `autovi.web`.
+This paper presents new regression diagnostics software, the \textsf{R} package \textsf{autovi} and its accompanying web interface, \textsf{autovi.web}.
 It addresses a critical gap in the current landscape of statistical software.
@@
 
-The `autovi` \textsf{R} package, introduced in this paper, automates the assessment of residual plots by incorporating a computer vision model, reducing reliance on time-consuming and potentially inconsistent human interpretation.
+The \textsf{autovi} \textsf{R} package, introduced in this paper, automates the assessment of residual plots by incorporating a computer vision model, reducing reliance on time-consuming and potentially inconsistent human interpretation.
 This automation improves the efficiency of the diagnostic process and promotes consistency in model evaluation across different users and studies.
 
-The development of the accompanying \textsf{Shiny} app, `autovi.web`, expands access to these advanced diagnostic tools, by providing a user-friendly interface.
+The development of the accompanying \textsf{Shiny} app, \textsf{autovi.web}, expands access to these advanced diagnostic tools, by providing a user-friendly interface.
 It makes automated residual plot assessment accessible to a broader audience, including those who may not have extensive programming experience.
@@
 
-The combination of `autovi` and `autovi.web` offers a comprehensive solution to the challenges of residual plot interpretation in regression analysis.
+The combination of \textsf{autovi} and \textsf{autovi.web} offers a comprehensive solution to the challenges of residual plot interpretation in regression analysis.
 These tools have the potential to significantly improve the quality and consistency of model diagnostics across various fields, from academic research to industry applications.
@@
 
-The framework established by `autovi` and `autovi.web` opens up exciting possibilities for further research and development.
+The framework established by \textsf{autovi} and \textsf{autovi.web} opens up exciting possibilities for further research and development.
 Future work could explore the extension of these automated assessment techniques to other types of diagnostic plots and statistical models, potentially revolutionizing how we approach statistical inference using visual displays more broadly.
@@
 
-This paper is reproducibly written using Quarto [@Allaire_Quarto_2024] powered by Pandoc [@MacFarlane_Pandoc] and pdfTeX.
+This paper is reproducibly written using \textsf{Quarto} [@Allaire_Quarto_2024] powered by \textsf{Pandoc} [@MacFarlane_Pandoc] and \textsf{pdfTeX}.
 The full source code to reproduce this paper is available at [`github.com/TengMCing/autovi_paper`](https://github.com/TengMCing/autovi_paper).

### 2025-09-06 autovi_paper.tex
Fix most paper issues

@@
 \hypersetup{
-  pdftitle={Automated residual plot assessment with the  package  and the  app },
+  pdftitle={Automated residual plot assessment with the  package  and the  application },
   pdfauthor={Weihao Li; Dianne Cook; Emi Tanaka; Susan VanderPlas; Klaus Ackermann},
@@
 \title{Automated residual plot assessment with the \textsf{R} package
-\textsf{autovi} and the \textsf{Shiny} app \textsf{autovi.web}}
+\textsf{autovi} and the \textsf{Shiny} application \textsf{autovi.web}}
 
@@
 \textsf{R} package that uses a computer vision model to automate the
-evaluation of residual plots. An accompanying \textsf{Shiny} app is
-provided for ease of use. Given a sample of residuals, the model
+evaluation of residual plots. An accompanying \textsf{Shiny} application
+is provided for ease of use. Given a sample of residuals, the model
 predicts a visual signal strength (VSS) and offers supporting
@@
 developed alongside a corresponding statistical testing procedure to
-autmoate the assessment of residual plots. The model takes as input a
+automate the assessment of residual plots. The model takes as input a
 residual plot and a set of auxiliary variables (such as the number of
@@
 \section{\texorpdfstring{\textsf{R} package:
-autovi}{ package: autovi}}\label{sec-autovi}
-
-The main purpose of \texttt{autovi} is to provide rejection decisions
+\textsf{autovi}}{ package: }}\label{sec-autovi}
+
+The main purpose of \textsf{autovi} is to provide rejection decisions
 and \(p\)-values for testing the null hypothesis (\(H_0\)) that the
@@
 interpretation of residual plots using computer vision. The name
-\texttt{autovi} stands for \textbf{auto}mated \textbf{v}isual
+\textsf{autovi} stands for \textbf{auto}mated \textbf{v}isual
 \textbf{i}nference. This functionality can be accessed through the
-\textsf{R} package \texttt{autovi}, or through a web interface,
-\texttt{autovi.web}, which enables users to perform analyses without
+\textsf{R} package \textsf{autovi}, or through a web interface,
+\textsf{autovi.web}, which enables users to perform analyses without
 installing \textsf{R}, \textsf{Python}, or their associated dependencies
@@
 in residuals at larger fitted values is due to smaller sample size only.
-The Breusch-Pagan test \citep{breusch1979simple} for heteroscedasticity
+The Breusch--Pagan test \citep{breusch1979simple} for heteroscedasticity
 would also not reject this as good residual plot.
@@
 The data in (b) is generated by fitting a linear model predicting
-\texttt{mpg} based on \texttt{hp} using the \texttt{datasets::mtcars}.
-It is a small data set, and there is a hint of nonlinear structure not
-captured by the model. The automated plot reading would predict a VSS of
-3.57, which has a \(p\)-value less than 0.05. That is, the nonlinear
-structure is most likely real, and indicates a problem with the model.
-The conventional test, a Ramsey Regression Equation Specification Error
-Test (RESET) \citep{ramsey1969tests} would also strongly detect the
-nonlinearity.
-
-The third example is generated using the \texttt{surreal} package
+\texttt{mpg} based on \texttt{hp} using the
+\textsf{datasets}\texttt{::mtcars}. It is a small data set, and there is
+a hint of nonlinear structure not captured by the model. The automated
+plot reading would predict a VSS of 3.57, which has a \(p\)-value less
+than 0.05. That is, the nonlinear structure is most likely real, and
+indicates a problem with the model. The conventional test, a Ramsey
+Regression Equation Specification Error Test (RESET)
+\citep{ramsey1969tests} would also strongly detect the nonlinearity.
+
+The third example is generated using the \textsf{surreal} package
 \citep{surreal}, where structure residuals are embedded in the data. In
-this case, a quote inspired by Tukey, ``visual summaries focus on
-unexpected values'', is used to define the residual structure. The
+this case, a quote inspired by Tukey, `visual summaries focus on
+unexpected values', is used to define the residual structure. The
 automated plot reading predicts the VSS to be 5.87, with a \(p\)-value
@@
 test for nonlinear structure would not report a problem. (It would be
-detected by a Breusch-Pagan for heteroscedasticity and also Shapiro-Wilk
-test \citep{shapiro1965analysis} for non-normality.)
+detected by a Breusch--Pagan for heteroscedasticity and also
+Shapiro--Wilk test \citep{shapiro1965analysis} for non-normality.)
 
@@
 difficult task, particularly for students new to statistical modeling.
-The \texttt{autovi} package makes it easier. Here are three examples of
+The \textsf{autovi} package makes it easier. Here are three examples of
 residual plots, which may appear to have structure. According to autovi,
@@
 
-The \texttt{autovi} package is built on the \texttt{bandicoot}
+The \textsf{autovi} package is built on the \textsf{bandicoot}
 object-oriented programming (OOP) system \citep{bandicoot}, marking a
-departure from R's traditional S3 generic system. This OOP architecture
-enhances flexibility and modularity, allowing users to redefine key
-functions through method overriding.
-
-The \texttt{autovi} infrastructure effectively integrates multiple
+departure from \textsf{R}'s traditional S3 generic system. This OOP
+architecture enhances flexibility and modularity, allowing users to
+redefine key functions through method overriding.
+
+The \textsf{autovi} infrastructure effectively integrates multiple
 programming languages and libraries into a comprehensive analytical
@@
 \textsf{R}, each playing a critical role in the analysis pipeline. In
-\textsf{Python}, \texttt{pillow} \citep{clark2015pillow} handles image
+\textsf{Python}, \textsf{pillow} \citep{clark2015pillow} handles image
 processing tasks such as reading and resizing PNG files of residual
 plots, then converting them into input tensors for further analysis.
-\texttt{TensorFlow} \citep{abadi2016tensorflow}, a key component of
+\textsf{TensorFlow} \citep{abadi2016tensorflow}, a key component of
 modern machine learning, is used to predict the VSS of these plots using
@@
 
-In the \textsf{R} environment, \texttt{autovi} utilizes several
-libraries. \texttt{ggplot2} \citep{ggplot2} generates the initial
-residual plots, saved as PNG files for visual input. \texttt{cassowaryr}
+In the \textsf{R} environment, \textsf{autovi} utilizes several
+libraries. \textsf{ggplot2} \citep{ggplot2} generates the initial
+residual plots, saved as PNG files for visual input. \textsf{cassowaryr}
 \citep{mason2022cassowaryr} computes scagnostics (scatter plot
@@
 analysis by offering quantitative metrics as secondary input to the
-computer vision model. \texttt{reticulate} \citep{reticulate} enables
+computer vision model. \textsf{reticulate} \citep{reticulate} enables
 seamless communication between \textsf{R} and \textsf{Python}.
@@
 
-The \texttt{autovi} package is available on CRAN. It is actively
+The \textsf{autovi} package is available on CRAN. It is actively
 developed and maintained, with the latest updates accessible on GitHub.
-This paper uses \texttt{autovi} version 0.4.2. The package includes
+This paper uses \textsf{autovi} version 0.4.2. The package includes
 internal functions to check the current \textsf{Python} environment used
-by the \texttt{reticulate} package. If the necessary \textsf{Python}
+by the \textsf{reticulate} package. If the necessary \textsf{Python}
 packages are not installed in the \textsf{Python} interpreter, an error
@@
 environment, you can do so by calling the
-\texttt{reticulate::use\_python()} function before using the
-\texttt{autovi} package.
-
-We recommend using the \textsf{Shiny} app \texttt{autovi.web} if users
-encounter installation problems.
+\textsf{reticulate}\texttt{::use\_python()} function before using the
+\textsf{autovi} package.
+
+We recommend using the \textsf{Shiny} application \textsf{autovi.web} if
+users encounter installation problems.
 
@@
 \item
-  Load the \texttt{autovi} package using the \texttt{library()}
+  Load the \textsf{autovi} package using the \texttt{library()}
   function.
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-diag-1.png}
+\includegraphics[width=1\textwidth,height=\textheight]{figures/autovi.pdf}
 
@@
 \caption{\label{fig-autovi-diag}Diagram illustrating the infrastructure
-of the extsf\{R\} package \texttt{autovi}. The modules in green are
+of the \textsf{R} package \textsf{autovi}. The modules in green are
 primary inputs provided by users. Modules in blue are overridable
@@
 
-The initial motivation for developing \texttt{autovi} was to create a
+The initial motivation for developing \textsf{autovi} was to create a
 convenient interface for sharing the models described and trained in
@@
 accommodating other classes of models through partial infrastructure
-substitution. This modular and customizable design allows
-\texttt{autovi} to handle a wide range of residual diagnostics tasks.
-
-The infrastructure of \texttt{autovi} consists of ten core modules: data
+substitution. This modular and customisable design allows
+\textsf{autovi} to handle a wide range of residual diagnostics tasks.
+
+The infrastructure of \textsf{autovi} consists of ten core modules: data
 extraction, bootstrapping and model refitting, fitted values and
@@
 
-The package takes regression models and a \texttt{Keras} model as
+The package takes regression models and a \textsf{Keras} model as
 primary inputs. Modules for VSS prediction and \(p\)-value computation
 are fixed but accessible via function arguments, using
-\texttt{TensorFlow} for inference and statistical testing. The image
-loading module is also fixed, using \texttt{PIL} to read and resize
-images based on the \texttt{Keras} model's input shape. The remaining
+\textsf{TensorFlow} for inference and statistical testing. The image
+loading module is also fixed, using \textsf{PIL} to read and resize
+images based on the \textsf{Keras} model's input shape. The remaining
 seven modules are overridable, allowing users to adapt the workflow as
@@
 
-\subsection{Extension to Other Model
-Classes}\label{extension-to-other-model-classes}
-
-The \texttt{autovi} \textsf{R} package can be extended to accommodate
+\subsection{Extension to other model
+classes}\label{extension-to-other-model-classes}
+
+The \textsf{autovi} \textsf{R} package can be extended to accommodate
 other classes of models beyond linear regression, such as generalized
@@
 relevant overridable modules, and if needed, supplying a different
-\texttt{Keras} model.
+\textsf{Keras} model.
 
@@
 It is important to note, however, that the pre-trained computer vision
-model included in \texttt{autovi}, such as \texttt{vss\_phn\_32} (see
+model included in \textsf{autovi}, such as \texttt{vss\_phn\_32} (see
 \texttt{list\_keras\_models()} for the full list of available models),
@@
 the validity of the automated diagnostics may be compromised. In such
-cases, users are encouraged to train and apply their own \texttt{Keras}
+cases, users are encouraged to train and apply their own \textsf{Keras}
 models. Detailed guidance on model training and discussion on extending
@@
 
-\section{Web interface: autovi.web}\label{sec-autovi-web}
-
-The \texttt{autovi.web} \textsf{Shiny} application extends the
-functionality of \texttt{autovi} by offering a user-friendly web
+\section{\texorpdfstring{Web interface:
+\textsf{autovi.web}}{Web interface: }}\label{sec-autovi-web}
+
+The \textsf{autovi.web} \textsf{Shiny} application extends the
+functionality of \textsf{autovi} by offering a user-friendly web
 interface for automated residual plot assessment. This eliminates the
@@
 have access to the latest features. This section discusses the
-implementation based on \texttt{autovi.web} version 0.1.0.
+implementation based on \textsf{autovi.web} version 0.1.0.
 
@@
 
-The interface \texttt{autovi.web} is built using the \texttt{shiny}
-\citep{shiny} and \texttt{shinydashboard} \citep{shinydashboard}
+The interface \textsf{autovi.web} is built using the \textsf{shiny}
+\citep{shiny} and \textsf{shinydashboard} \citep{shinydashboard}
 \textsf{R} packages. Hosted on the
@@
 accessible through any modern web browser. The \textsf{R} packages
-\texttt{htmltools} \citep{htmltools} and \texttt{shinycssloaders}
+\textsf{htmltools} \citep{htmltools} and \textsf{shinycssloaders}
 \citep{shinycssloaders} are used to render markdown documentation in
@@
 Determining the best way to implement the backend was difficult. In our
-initial planning for \texttt{autovi.web}, we considered implementing the
-entire web application using the \texttt{webr} framework \citep{webr},
+initial planning for \textsf{autovi.web}, we considered implementing the
+entire web application using the \textsf{webr} framework \citep{webr},
 which would have allowed the entire application to run directly in the
-user's browser. However, \texttt{webr} does not support packages which
-use compiled fortran code, which is required by \texttt{splancs}
-\citep{splancs}, a dependency of \texttt{autovi}. In the future, it is
-possible that a working Emscripten \citep{zakai2011emscripten} version
-of this package may allow full \texttt{webr} support.
+user's browser. However, \textsf{webr} does not support packages which
+use compiled \textsf{Fortran} code, which is required by
+\textsf{splancs} \citep{splancs}, a dependency of \textsf{autovi}. In
+the future, it is possible that a working \textsf{Emscripten}
+\citep{zakai2011emscripten} version of this package may allow full
+\textsf{webr} support.
 
@@
 Additionally, calling \textsf{R} from \textsf{Python} is typically done
-using the \texttt{rpy2} \textsf{Python} library \citep{rpy2}, but this
+using the \textsf{rpy2} \textsf{Python} library \citep{rpy2}, but this
 approach can be awkward when dealing with language syntax related to
@@
 expertise. Ultimately, the most practical solution was to use the
-\texttt{shiny} and \texttt{shinydashboard} frameworks, which are
+\textsf{shiny} and \textsf{shinydashboard} frameworks, which are
 well-established in the \textsf{R} community and offer a solid
@@
 
-The server-side configuration of \texttt{autovi.web} is carefully
+The server-side configuration of \textsf{autovi.web} is carefully
 designed to support its functionality. Most required \textsf{Python}
-libraries, including \texttt{pillow} and \texttt{numpy}, are
+libraries, including \textsf{pillow} and \textsf{numpy}, are
 pre-installed on the server. These libraries are integrated into the
-\textsf{Shiny} application using the \texttt{reticulate} package, which
+\textsf{Shiny} application using the \textsf{reticulate} package, which
 provides an interface between \textsf{R} and \textsf{Python}.
 
-Due to shinyapps.io's resource policy, inactive servers enter sleep
-mode, clearing the local \textsf{Python} environment. When reactivated
-for a new session, libraries must be reinstalled. While this ensures a
-clean environment for each session, it may lead to slightly longer
-loading times for the first user after a period of inactivity.
-
-In contrast to \texttt{autovi}, \texttt{autovi.web} leverages
-\texttt{TensorFlow.js}, a JavaScript library that allows the execution
-of machine learning models directly in the browser. This choice enables
-native browser execution, enhancing compatibility across different user
-environments, and shifts the computational load from the server to the
-client-side. \texttt{TensorFlow.js} also offers better scalability and
-performance, especially when dealing with resource-intensive computer
-vision models on the web.
-
-While \texttt{autovi} requires downloading the pre-trained computer
-vision models from GitHub, these models in ``.keras'' file format are
-incompatible with \texttt{TensorFlow.js}. Therefore, we extract and
+Due to \href{https://www.shinyapps.io}{shinyapps.io}'s resource policy,
+inactive servers enter sleep mode, clearing the local \textsf{Python}
+environment. When reactivated for a new session, libraries must be
+reinstalled. While this ensures a clean environment for each session, it
+may lead to slightly longer loading times for the first user after a
+period of inactivity.
+
+In contrast to \textsf{autovi}, \textsf{autovi.web} leverages
+\textsf{TensorFlow.js}, a \textsf{JavaScript} library that allows the
+execution of machine learning models directly in the browser. This
+choice enables native browser execution, enhancing compatibility across
+different user environments, and shifts the computational load from the
+server to the client-side. \textsf{TensorFlow.js} also offers better
+scalability and performance, especially when dealing with
+resource-intensive computer vision models on the web.
+
+While \textsf{autovi} requires downloading the pre-trained computer
+vision models from GitHub, these models in `.keras' file format are
+incompatible with \textsf{TensorFlow.js}. Therefore, we extract and
 store the model weights in JSON files and include them as extra
 resources in the \textsf{Shiny} application. When the application
-initializes, \texttt{TensorFlow.js} rebuilds the computer vision model
+initializes, \textsf{TensorFlow.js} rebuilds the computer vision model
 using these pre-stored weights.
 
-To allow communication between \texttt{TensorFlow.js} and other
-components of the \textsf{Shiny} application, the \texttt{shinyjs}
+To allow communication between \textsf{TensorFlow.js} and other
+components of the \textsf{Shiny} application, the \textsf{shinyjs}
 \textsf{R} package \citep{shinyjs} is used. This package allows calling
-custom JavaScript code within the \textsf{Shiny} framework. The
-specialized JavaScript code for initializing \texttt{TensorFlow.js} and
-calling \texttt{TensorFlow.js} for VSS prediction is deployed alongside
-the \textsf{Shiny} application as additional resources.
+custom \textsf{JavaScript} code within the \textsf{Shiny} framework. The
+specialized \textsf{JavaScript} code for initializing
+\textsf{TensorFlow.js} and calling \textsf{TensorFlow.js} for VSS
+prediction is deployed alongside the \textsf{Shiny} application as
+additional resources.
 
@@
 
-The workflow of \texttt{autovi.web} is designed to be straightforward,
+The workflow of \textsf{autovi.web} is designed to be straightforward,
 with numbered steps displayed in each panel. There are two example
@@
 example uses the \texttt{dino} dataset from the \textsf{R} package
-\texttt{datasauRus} \citep{datasaurus}. The lineup example uses
+\textsf{datasauRus} \citep{datasaurus}. The lineup example uses
 residuals from a simulated regression model that has a non-linearity
@@
 data sets (Figure~\ref{fig-autovi-web-setup}). To use the lineup example
-data, click the ``Use Lineup Example'' button. The data status will then
+data, click the `Use Lineup Example' button. The data status will then
 update to show the number of rows and columns in the dataset, and the
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-setup-1.png}
+\includegraphics[width=1\textwidth,height=\textheight]{figures/autovi_web_setup.pdf}
 
@@
 \caption{\label{fig-autovi-web-setup}To begin the workflow for
-\texttt{autovi} using the lineup example dataset, the user clicks the
-``Use Lineup Example'' button (left) to load the example dataset, during
+\textsf{autovi} using the lineup example dataset, the user clicks the
+`Use Lineup Example' button (left) to load the example dataset, during
 which the data status and CSV type will be automatically updated. The
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-lineup-1.png}
+\includegraphics[width=1\textwidth,height=\textheight]{figures/autovi_web_lineup.pdf}
 
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-autovi-web-distributions-1.png}
+\includegraphics[width=1\textwidth,height=\textheight]{figures/autovi_web_distributions.pdf}
 
@@
 This paper presents new regression diagnostics software, the \textsf{R}
-package \texttt{autovi} and its accompanying web interface,
-\texttt{autovi.web}. It addresses a critical gap in the current
+package \textsf{autovi} and its accompanying web interface,
+\textsf{autovi.web}. It addresses a critical gap in the current
 landscape of statistical software. While regression tools are widely
@@
 
-The \texttt{autovi} \textsf{R} package, introduced in this paper,
+The \textsf{autovi} \textsf{R} package, introduced in this paper,
 automates the assessment of residual plots by incorporating a computer
@@
 The development of the accompanying \textsf{Shiny} app,
-\texttt{autovi.web}, expands access to these advanced diagnostic tools,
+\textsf{autovi.web}, expands access to these advanced diagnostic tools,
 by providing a user-friendly interface. It makes automated residual plot
@@
 
-The combination of \texttt{autovi} and \texttt{autovi.web} offers a
+The combination of \textsf{autovi} and \textsf{autovi.web} offers a
 comprehensive solution to the challenges of residual plot interpretation
@@
 
-The framework established by \texttt{autovi} and \texttt{autovi.web}
+The framework established by \textsf{autovi} and \textsf{autovi.web}
 opens up exciting possibilities for further research and development.
@@
 
-This paper is reproducibly written using Quarto
-\citep{Allaire_Quarto_2024} powered by Pandoc \citep{MacFarlane_Pandoc}
-and pdfTeX. The full source code to reproduce this paper is available at
+This paper is reproducibly written using \textsf{Quarto}
+\citep{Allaire_Quarto_2024} powered by \textsf{Pandoc}
+\citep{MacFarlane_Pandoc} and \textsf{pdfTeX}. The full source code to
+reproduce this paper is available at
 \href{https://github.com/TengMCing/autovi_paper}{\texttt{github.com/TengMCing/autovi\_paper}}.

### 2025-09-07 autovi_paper.qmd
Use AU spellling

@@
   quarto-anzjs-pdf:
+    keep-md: true
     keep-tex: true  
@@
 # capital letters) should *not* be capitalised.
-keywords: [initial data analysis, statistical graphics, data visualization, visual inference, computer vision, machine learning, hypothesis testing, regression analysis, model diagnostics]
+keywords: [initial data analysis, statistical graphics, data visualisation, visual inference, computer vision, machine learning, hypothesis testing, regression analysis, model diagnostics]
 bibliography: bibliography.bib  
@@
 
-Regression analysis is a widely used statistical modeling technique for data in many fields.
-There is a vast array of software for conducting regression modeling and generating diagnostics.
+Regression analysis is a widely used statistical modelling technique for data in many fields.
+There is a vast array of software for conducting regression modelling and generating diagnostics.
 The package \textsf{lmtest} [@lmtest] provides a suite of conventional tests, while the \textsf{stats} package [@stats] offers standard diagnostic plots such as residuals vs.
@@
 The \textsf{ecostats} package [@warton_global_2023] extends these diagnostics by incorporating simulation envelopes into residual plots.
-Meanwhile, \textsf{DHARMa} [@dharma] compares empirical quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical counterparts, with a strong focus on identifying model violations such as heteroscedasticity, misspecified functional forms, and issues specific to generalized linear and mixed-effect models, like over/under-dispersion.
+Meanwhile, \textsf{DHARMa} [@dharma] compares empirical quantiles (0.25, 0.5, and 0.75) of scaled residuals to their theoretical counterparts, with a strong focus on identifying model violations such as heteroscedasticity, misspecified functional forms, and issues specific to generalised linear and mixed-effect models, like over/under-dispersion.
 It also provides conventional test annotations to reduce the risk of misinterpretation.
@@
 In the context of classical normal linear regression model diagnostics, VSS describes the clarity of visual patterns on a diagnostic plot that may indicate model violations.
-Violations can be categorized as weak, moderate, or strong, but here we treat it as a continuous positive real variable.
+Violations can be categorised as weak, moderate, or strong, but here we treat it as a continuous positive real variable.
 Importantly, its interpretation depends on how it is linked to a function of the data or the underlying data generating process.
@@
 It is trained on a large number of synthetic regression models, each designed to simulate specific violations of classical linear regression assumptions.
-These models incorporate non-linearity through Hermite polynomial transformations of predictors, heteroskedasticity by making the error variance a predictor-dependent function, and non-normality by drawing residuals from distributions such as discrete, uniform, and lognormal.
+These models incorporate non-linearity through Hermite polynomial transformations of predictors, heteroscedasticity by making the error variance a predictor-dependent function, and non-normality by drawing residuals from distributions such as discrete, uniform, and lognormal.
 Both simple and multiple linear regression structures are used, with controlled parameters to generate diverse and complex residual patterns.
@@
 #| label: fig-three-examples
-#| fig-cap: "Reading residual plots can be a difficult task, particularly for students new to statistical modeling.
+#| fig-cap: "Reading residual plots can be a difficult task, particularly for students new to statistical modelling.
 The \\textsf{autovi} package makes it easier.
@@
 
-The package offers a straightforward visualization of the assessment result through the `summary_plot()` function.
+The package offers a straightforward visualisation of the assessment result through the `summary_plot()` function.
 
@@
 The initial motivation for developing \textsf{autovi} was to create a convenient interface for sharing the models described and trained in @li2024automated.
-However, recognizing that the classical normal linear regression model represents a restricted class of models, we sought to avoid limiting the potential for future extensions, whether by the original developers or other developers.
+However, recognising that the classical normal linear regression model represents a restricted class of models, we sought to avoid limiting the potential for future extensions, whether by the original developers or other developers.
 As a result, the package was designed to function seamlessly with linear regression models with minimal modification and few required arguments, while also accommodating other classes of models through partial infrastructure substitution.
@@
 The infrastructure of \textsf{autovi} consists of ten core modules: data extraction, bootstrapping and model refitting, fitted values and residuals extraction, auxiliary computation, null residual simulation, plotting, plot saving, image reading and resizing, VSS prediction, and $p$-value computation.
-Each module is designed with minimal dependency on the preceding modules, allowing users to customize parts of the infrastructure without affecting its overall integrity.
+Each module is designed with minimal dependency on the preceding modules, allowing users to customise parts of the infrastructure without affecting its overall integrity.
 An overview of this infrastructure is illustrated in @fig-autovi-diag.
@@
 
-The \textsf{autovi} \textsf{R} package can be extended to accommodate other classes of models beyond linear regression, such as generalized linear models (`glm`).
+The \textsf{autovi} \textsf{R} package can be extended to accommodate other classes of models beyond linear regression, such as generalised linear models (`glm`).
 This is achieved by substituting the relevant overridable modules, and if needed, supplying a different \textsf{Keras} model.
@@
 
-```{r fig-pois-lineup, fig.cap="A lineup of residual plots from Poisson generalized linear models, with the true residual plot at position 4, which displays a distinct U-shaped pattern.
+```{r fig-pois-lineup, fig.cap="A lineup of residual plots from Poisson generalised linear models, with the true residual plot at position 4, which displays a distinct U-shaped pattern.
 In contrast, the null plots show characteristics broadly consistent with well-behaved residuals from linear regression models.", fig.pos="H", out.width="80%"}
@@
 Therefore, we extract and store the model weights in JSON files and include them as extra resources in the \textsf{Shiny} application.
-When the application initializes, \textsf{TensorFlow.js} rebuilds the computer vision model using these pre-stored weights.
+When the application initialises, \textsf{TensorFlow.js} rebuilds the computer vision model using these pre-stored weights.
 
@@
 This package allows calling custom \textsf{JavaScript} code within the \textsf{Shiny} framework.
-The specialized \textsf{JavaScript} code for initializing \textsf{TensorFlow.js} and calling \textsf{TensorFlow.js} for VSS prediction is deployed alongside the \textsf{Shiny} application as additional resources.
+The specialised \textsf{JavaScript} code for initialising \textsf{TensorFlow.js} and calling \textsf{TensorFlow.js} for VSS prediction is deployed alongside the \textsf{Shiny} application as additional resources.
 
@@
 The framework established by \textsf{autovi} and \textsf{autovi.web} opens up exciting possibilities for further research and development.
-Future work could explore the extension of these automated assessment techniques to other types of diagnostic plots and statistical models, potentially revolutionizing how we approach statistical inference using visual displays more broadly.
+Future work could explore the extension of these automated assessment techniques to other types of diagnostic plots and statistical models, potentially revolutionising how we approach statistical inference using visual displays more broadly.
 

### 2025-09-07 autovi_paper.tex
Use AU spellling

@@
   pdfkeywords={initial data analysis, statistical graphics, data
-visualization, visual inference, computer vision, machine
+visualisation, visual inference, computer vision, machine
 learning, hypothesis testing, regression analysis, model diagnostics},
@@
 \keywords{initial data analysis; statistical graphics; data
-visualization; visual inference; computer vision; machine
+visualisation; visual inference; computer vision; machine
 learning; hypothesis testing; regression analysis; model diagnostics}
@@
 
-Regression analysis is a widely used statistical modeling technique for
+Regression analysis is a widely used statistical modelling technique for
 data in many fields. There is a vast array of software for conducting
-regression modeling and generating diagnostics. The package
+regression modelling and generating diagnostics. The package
 \textsf{lmtest} \citep{lmtest} provides a suite of conventional tests,
@@
 on identifying model violations such as heteroscedasticity, misspecified
-functional forms, and issues specific to generalized linear and
+functional forms, and issues specific to generalised linear and
 mixed-effect models, like over/under-dispersion. It also provides
@@
 VSS describes the clarity of visual patterns on a diagnostic plot that
-may indicate model violations. Violations can be categorized as weak,
+may indicate model violations. Violations can be categorised as weak,
 moderate, or strong, but here we treat it as a continuous positive real
@@
 models incorporate non-linearity through Hermite polynomial
-transformations of predictors, heteroskedasticity by making the error
+transformations of predictors, heteroscedasticity by making the error
 variance a predictor-dependent function, and non-normality by drawing
@@
 \caption{\label{fig-three-examples}Reading residual plots can be a
-difficult task, particularly for students new to statistical modeling.
+difficult task, particularly for students new to statistical modelling.
 The \textsf{autovi} package makes it easier. Here are three examples of
@@
 
-The package offers a straightforward visualization of the assessment
+The package offers a straightforward visualisation of the assessment
 result through the \texttt{summary\_plot()} function.
@@
 convenient interface for sharing the models described and trained in
-\citet{li2024automated}. However, recognizing that the classical normal
+\citet{li2024automated}. However, recognising that the classical normal
 linear regression model represents a restricted class of models, we
@@
 \(p\)-value computation. Each module is designed with minimal dependency
-on the preceding modules, allowing users to customize parts of the
+on the preceding modules, allowing users to customise parts of the
 infrastructure without affecting its overall integrity. An overview of
@@
 The \textsf{autovi} \textsf{R} package can be extended to accommodate
-other classes of models beyond linear regression, such as generalized
+other classes of models beyond linear regression, such as generalised
 linear models (\texttt{glm}). This is achieved by substituting the
@@
 \caption{\label{fig-pois-lineup}A lineup of residual plots from Poisson
-generalized linear models, with the true residual plot at position 4,
+generalised linear models, with the true residual plot at position 4,
 which displays a distinct U-shaped pattern. In contrast, the null plots
@@
 resources in the \textsf{Shiny} application. When the application
-initializes, \textsf{TensorFlow.js} rebuilds the computer vision model
+initialises, \textsf{TensorFlow.js} rebuilds the computer vision model
 using these pre-stored weights.
@@
 custom \textsf{JavaScript} code within the \textsf{Shiny} framework. The
-specialized \textsf{JavaScript} code for initializing
+specialised \textsf{JavaScript} code for initialising
 \textsf{TensorFlow.js} and calling \textsf{TensorFlow.js} for VSS
@@
 techniques to other types of diagnostic plots and statistical models,
-potentially revolutionizing how we approach statistical inference using
+potentially revolutionising how we approach statistical inference using
 visual displays more broadly.

### 2025-09-08 autovi_paper.qmd
Submitted version

@@
     keep-tex: true  
-    shorttitle: "Automated Residual Plot Assessment"
+    shorttitle: "Automated residual plot assessment"
     double-space: true
@@
       - name: The Australian National University
-        department: Biological Data Science Institute
-        address: 46 Sullivan's Creek Road, ACT 2600, Australia
+        department: Research School of Finance, Actuarial Studies and Statistics
+        address: CBE Building 26C, Kingsley Street, ACT 2600, Australia
     orcid: 0000-0003-4959-106X
@@
       - name: The Australian National University
-        department: Biological Data Science Institute
-        address: 46 Sullivan's Creek Road, ACT 2600, Australia
+        department: Research School of Finance, Actuarial Studies and Statistics
+        address: CBE Building 26C, Kingsley Street, ACT 2600, Australia
     orcid: 0000-0002-1455-259X
@@
 
-As noted in @li2024automated, the lineup protocol has significant limitations in large-scale applications due to its reliance on human labor.
+As noted in @li2024automated, the lineup protocol has significant limitations in large-scale applications due to its reliance on human labour.
 To overcome this constraint, a computer vision model was developed alongside a corresponding statistical testing procedure to automate the assessment of residual plots.

### 2025-09-08 autovi_paper.tex
Fix one more AU spelling
Submitted version

@@
 \runningheads{
-Automated Residual Plot Assessment
+Automated residual plot assessment
 }{
@@
 Statistics, Monash University, Wellington Road, VIC 3800, Australia\\
-\addressnum{2} Biological Data Science Institute, The Australian
-National University, 46 Sullivan's Creek Road, ACT 2600, Australia\\
+\addressnum{2} Research School of Finance, Actuarial Studies and
+Statistics, The Australian National University, CBE Building 26C,
+Kingsley Street, ACT 2600, Australia\\
 \addressnum{3} Department of Statistics, University of Nebraska, Hardin
@@
 limitations in large-scale applications due to its reliance on human
-labor. To overcome this constraint, a computer vision model was
+labour. To overcome this constraint, a computer vision model was
 developed alongside a corresponding statistical testing procedure to
